### 2017-05-23 Setup/report.tex
added setup

\documentclass[a4paper,10pt]{report}
% \usepackage[utf8]{inputenc}
% \usepackage{jheppub} 
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage[dvips,table]{xcolor} 
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{caption}
\usepackage
[subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
{subcaption}

\renewcommand{\topfraction}{1}
\renewcommand{\bottomfraction}{1}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}    
\renewcommand{\textfraction}{0.07}
\renewcommand{\floatpagefraction}{0.9}

\newcommand{\eq}[1]{\begin{equation} #1 \end{equation}}
\newcommand{\eqa}[1]{\begin{eqnarray} #1 \end{eqnarray}}

\setlength{\clubpenalty}{10000}
\setlength{\widowpenalty}{10000}
\setlength{\displaywidowpenalty}{10000}
% \allowdisplaybreaks[1]

\input{macros.tex}

% Title Page
\title{Monte Carlo comparisons \\
VBSCAN Cost Action}
\author{Mathieu Pellen, Marco Zaro, \\
Alexander Karlberg, Michael Rauch, J\"urgen Reuter}

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\part{Introduction}

\part{$\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$}

\section{Input parameters}

- Centre-of-mass energy of $13\TeV$ at the LHC. \\
%
- Parton distribution function (PDF): NNPDF-3.0 at NLO with $\alpha_{\rm s} \left( \MZ \right) = 0.118$ (we use it at both LO and NLO). The
LHAPDF ID for this set is 260000.\\
%
- Flavour scheme: fixed $N_\text{F}=5$ flavour scheme ( no bottom quark appear in the final or initial state). 
This means that the bottom quark is considered massless. \\
%
- Renormalisation scheme: complex-mass scheme if possible. If other schemes are used, we have to estimate the possible differences.
%
- Factorisation scheme: ${\overline{\rm MS}}$ as for NNPDF. \\
%
- Scales: factorisation and renormalisation scale, $\mu_R = \mu_F = \MW$. \\
%
- $\alpha$: $G_\mu$ scheme with:
%
\begin{equation}
  \alpha = \frac{\sqrt{2}}{\pi} G_\mu \MW^2 \left( 1 - \frac{\MW^2}{\MZ^2} \right)  \qquad \text{with}  \qquad   \GF    = 1.16637\times 10^{-5}\GeV.            
\end{equation}
%
The numerical value is: $\alpha = 7.555310522369 \times 10^{-3}$. \\
%
- Mass and width of the massive particles:
% 
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
\end{alignat}
%
The pole masses and widths entering the calculation are expressed in terms of the measured on-shell (OS) values for the W and Z bosons according to
%
\begin{equation}
        M_V = \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,,\qquad  \Gamma_V = \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
\end{equation}
%
Hence the numerical values are
\begin{alignat}{2}
                \MZ &=  91.1534806191827\GeV,      & \quad \quad \quad \GZ &= 2.494266378772824\GeV,  \nonumber \\
                \MW &=  80.3579736098775\GeV,       & \GW &= 2.084298998278219\GeV.
\end{alignat}
%
- Experimental signature:
two equally charged leptons, missing transverse energy and at least two jets. \\
- Clustering: QCD partons are clustered into jets using the anti-$k_\text{T}$ algorithm  with jet-resolution parameter $R=0.4$.
Photons from real radiation are recombined with the final-state quarks into jets or with the charged leptons into dressed leptons, in both cases via the anti-$k_\text{T}$ algorithm and a resolution parameter $R=0.1$ 
(this applies only when computing the EW corrections). \\
%
- Rapidity definition: $y=\frac{1}{2}\ln \frac{E+p_z}{E-p_z}$ where $E$ is the energy of the parton and $p_z$ the component of its momentum along the beam axis. \\
%
- Distance definition:
\begin{equation}
        \Delta R_{ij} = \sqrt{(\Delta \phi_{ij})^2+(\Delta y_{ij})^2},
\end{equation}
with $\Delta \phi_{ij}=\phi_i-\phi_j$ being the azimuthal-angle difference and $\Delta y_{ij} = y_i-y_j$ being the rapidity difference. \\
%
- Definition of the missing transverse energy: transverse momentum of the sum of the two neutrinos momenta. \\
%
- Cuts on the leptons:
\begin{align}
 \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3.
\end{align}
%
- Missing energy cut:
\begin{align}
  \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV
\end{align}
%
- Jet definition:
%
\begin{align}
 \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5,\qquad\Delta R_{\Pj\Pl} > 0.3 .
\end{align}
%
- Out of these 2/3 jets, the two hardest in pT (tagged jets)are required to have:
\begin{align}
 m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
\end{align}

\section{Codes}

\subsection{ {\sc POWHEG}: Alexander Karlberg}
VBF approximation? \\
\subsection{ {\sc VBFNLO}: Michael Rauch}
VBF approximation \\
\subsection{ {\sc WHIZARD}: J\"urgen Reuter}
Full matrix element \\
\subsection{ \recola: Mathieu Pellen}
Full matrix element \\
\subsection{ \madgraph: Marco Zaro}
To be checked what is possible \\

\section{Observables}
- Cross section within cuts. \\
- Distribution in the number of jets. \\
- Invariant mass of the two hardest jets (two tagged jets). \\
$[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
- $\ptsub{\Pj_1,\Pj_2}$ and $y_{\Pj_1,\Pj_2}$ of the two tagged jets (not their sum) \\
$\ptsub{\Pj_1,\Pj_2}$: $[0; 1\TeV]$ with bins of size $25\GeV$ (40 bins). \\
$y_{\Pj_1,\Pj_2}$: $[-5;5]$ with bins of size $0.5$ (20 bins). \\
- Invariant mass of the two charged leptons. \\
$[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
- Zeppenfeld variable for $\mu^+$ and $\Pe^+$: \\
$z^*_\ell = |y_\ell - \left(y_{\Pj_1}+y_{\Pj_2} \right)/2|/|\Delta y_{\Pj\Pj}|$ \\
$[0;1.5]$ with bins of size $0.05$ (30 bins).

\section{Numerical results}

\subsection{LO $\mathcal{O}\left(\alpha^6\right)$}

\subsection{NLO $\mathcal{O}\left(\alpha^6\alpha_{\rm s}\right)$}

\part{Conclusion}

\part{Acknowledgments}

Karlsruhe for hosting the documents used for the comparison.

\end{document}

### 2017-06-07 Setup/report.tex
small changes
just one small correction to neglect the photon contributions
added comparison table for the various codes

@@
 \usepackage{hyperref}
+\usepackage{tabularx}
 \usepackage{caption}
@@
 This means that the bottom quark is considered massless. \\
+%
+- Photon induced are neglected (for now). \\
 %
@@
 \begin{align}
- \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5,\qquad\Delta R_{\Pj\Pl} > 0.3 .
+ \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5 .
 \end{align}
@@
 \end{align}
+%
+- All jets in the event are required to satisfy 
+\begin{align}
+ \qquad\Delta R_{\Pj\Pl} > 0.3 .
+\end{align}
 
 \section{Codes}
+\begin{table}
+    \footnotesize
+    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
+        Contact person  &  Code  &  $\mathcal O(g_W^6)$ $s/t/u$  &  $\mathcal O(g_W^6)$ interf.  &  Off-shell  &  NF QCD  &  EW corr. to $\mathcal O(g_W^4g_s^2)$  \\
+        \hline
+        \hline
+        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
+        M. Pellen    &  {\sc Recola}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
+        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
+        C. Schwan    &   Private      &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
+        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No  \
+    \end{tabularx}
+    \caption{\label{tab:codes} Summary of the different properties of the codes employed in the comparison.}
+\end{table}
 

### 2017-06-08 Setup/report.tex
first results from MG5_AMC at LO; comparison plots done with the available codes and included in the report

@@
 \usepackage{tabularx}
+\usepackage{graphicx}
 \usepackage{caption}
@@
         C. Schwan    &   Private      &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
-        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No  \
+        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No  
     \end{tabularx}
@@
 \subsection{LO $\mathcal{O}\left(\alpha^6\right)$}
+\begin{table}[h!]
+    \begin{tabular}{c|c}
+        Code  &  $\sigma[\rm{fb}]$  \\
+        \hline
+        \hline
+        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
+        {\sc Recola}  &  $1.5503 \pm 0.0003$ \\
+        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
+        Private       &  \\
+        {\sc MG5\_aMC}&  $1.542 \pm 0.002$   
+    \end{tabular}
+    \caption{\label{tab:LOrates} LO rates within VBS cuts from the different codes.}
+\end{table}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mjj_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mll_LO.pdf}
+\caption{\label{fig:mjj-llLO}Invariant-mass of the two tagging jets (left) and of the two leptons (right).
+}
+\end{figure}
+%
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj1_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj2_LO.pdf}
+\caption{\label{fig:ptj1-2LO}Transverse momentum of the first (left) and second (right) tagging jet.
+}
+\end{figure}
+%
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj1_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj2_LO.pdf}
+\caption{\label{fig:yj1-2LO}Rapidity of the first (left) and second (right) tagging jet.
+}
+\end{figure}
+%
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ze_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/zmu_LO.pdf}
+\caption{\label{fig:zel-muLO}Zeppenfeld variable of the positron (left) and of the muon (right).
+}
+\end{figure}
 

### 2017-06-08 Results/comparison_plots/run_all_macros.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+GPL=`ls plot_*.gnuplot`
+
+
+for GP in $GPL ; do
+    gnuplot $GP
+done

### 2017-06-12 Setup/report.tex
NLO results from mg5_aMC added; macros,figures and text updated

@@
 \subsection{LO $\mathcal{O}\left(\alpha^6\right)$}
+
 \begin{table}[h!]
@@
    \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mll_LO.pdf}
-\caption{\label{fig:mjj-llLO}Invariant-mass of the two tagging jets (left) and of the two leptons (right).
+\caption{\label{fig:mjj-llLO}Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO.
 }
@@
    \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj2_LO.pdf}
-\caption{\label{fig:ptj1-2LO}Transverse momentum of the first (left) and second (right) tagging jet.
+\caption{\label{fig:ptj1-2LO}Transverse momentum of the first (left) and second (right) tagging jet, at LO.
 }
@@
    \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj2_LO.pdf}
-\caption{\label{fig:yj1-2LO}Rapidity of the first (left) and second (right) tagging jet.
+\caption{\label{fig:yj1-2LO}Rapidity of the first (left) and second (right) tagging jet, at LO.
 }
@@
    \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/zmu_LO.pdf}
-\caption{\label{fig:zel-muLO}Zeppenfeld variable of the positron (left) and of the muon (right).
+\caption{\label{fig:zel-muLO}Zeppenfeld variable of the positron (left) and of the muon (right), at LO.
 }
@@
 \subsection{NLO $\mathcal{O}\left(\alpha^6\alpha_{\rm s}\right)$}
+
+\begin{table}[h!]
+    \begin{tabular}{c|c|c|c}
+        Code  &  $\sigma[\rm{fb}]$  &  $\sigma(n_j=2)[\rm{fb}]$  &  $\sigma(n_j=3)[\rm{fb}]$\\
+        \hline
+        \hline
+        {\sc POWHEG}  &  \\
+        {\sc Recola}  &  \\
+        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
+        Private       &  \\
+        {\sc MG5\_aMC}&  $1.315 \pm 0.003$  &  $0.784 \pm  0.003$  &  $0.5313 \pm 0.0009$\\
+    \end{tabular}
+    \caption{\label{tab:NLOrates} NLO rates within VBS cuts from the different codes.}
+\end{table}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mjj_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mll_NLO.pdf}
+\caption{\label{fig:mjj-llNLO}Invariant-mass of the two tagging jets (left) and of the two leptons (right), at NLO.
+}
+\end{figure}
+%
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj1_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj2_NLO.pdf}
+\caption{\label{fig:ptj1-2NLO}Transverse momentum of the first (left) and second (right) tagging jet, at NLO.
+}
+\end{figure}
+%
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj1_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj2_NLO.pdf}
+\caption{\label{fig:yj1-2NLO}Rapidity of the first (left) and second (right) tagging jet, at NLO.
+}
+\end{figure}
+%
+\begin{figure}[h!]
+   \centering
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ze_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/zmu_NLO.pdf}
+\caption{\label{fig:zel-muNLO}Zeppenfeld variable of the positron (left) and of the muon (right), at NLO.
+}
+\end{figure}
 

### 2017-06-13 Setup/report.tex
Fix definition of the azimuthal angle difference

@@
 \author{Mathieu Pellen, Marco Zaro, \\
-Alexander Karlberg, Michael Rauch, J\"urgen Reuter}
+Alexander Karlberg, Michael Rauch, J\"urgen Reuter, Christopher Schwan}
 
@@
 \end{equation}
-with $\Delta \phi_{ij}=\phi_i-\phi_j$ being the azimuthal-angle difference and $\Delta y_{ij} = y_i-y_j$ being the rapidity difference. \\
+with
+\begin{equation}
+\Delta \phi_{ij} = \begin{cases}
+|\phi_i-\phi_j|         & \text{if} \; |\phi_i-\phi_j| < \pi \\
+2 \pi - |\phi_i-\phi_j| & \text{else}
+\end{cases}
+\end{equation}
+being the positive azimuthal-angle difference and $\Delta y_{ij} = |y_i - y_j|$ being the positive rapidity difference. \\
 %
@@
         M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
-        C. Schwan    &   Private      &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
+        C. Schwan    &  {\sc PSI}     &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
         M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No
@@
         {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
-        Private       &  \\
+        {\sc PSI}     &  $1.5524 \pm 0.0002$ \\
         {\sc MG5\_aMC}&  $1.542 \pm 0.002$   
@@
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
-        Private       &  \\
+        {\sc PSI}     &  \\
         {\sc MG5\_aMC}&  $1.315 \pm 0.003$  &  $0.784 \pm  0.003$  &  $0.5313 \pm 0.0009$\\

### 2017-06-20 Setup/report.tex
Add NLO results for PSI

@@
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
-        {\sc PSI}     &  \\
+        {\sc PSI}     &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
         {\sc MG5\_aMC}&  $1.315 \pm 0.003$  &  $0.784 \pm  0.003$  &  $0.5313 \pm 0.0009$\\

### 2017-06-23 Setup/report.tex
Rename program from PSI to BONSAY

--- 2017-06-13 Setup/report.tex
@@
         M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
-        C. Schwan    &  {\sc PSI}     &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
+        C. Schwan    &  {\sc BONSAY}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
         M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No
@@
         {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
-        {\sc PSI}     &  $1.5524 \pm 0.0002$ \\
+        {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
         {\sc MG5\_aMC}&  $1.542 \pm 0.002$   
@@
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
-        {\sc PSI}     &  \\
+        {\sc BONSAY}  &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
         {\sc MG5\_aMC}&  $1.315 \pm 0.003$  &  $0.784 \pm  0.003$  &  $0.5313 \pm 0.0009$\\

### 2017-06-26 Results/comparison_plots/run_all_macros.sh
merge

@@ -1,5 +1,5 @@
 #!/bin/bash
-GPL=`ls plot_*.gnuplot`
+GPL=`ls plot_*NLO.gnuplot`
 
 
 for GP in $GPL ; do

### 2017-06-27 Setup/report.tex
merge
updated plotss with MG5_aMC numbers

@@
     \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Contact person  &  Code  &  $\mathcal O(g_W^6)$ $s/t/u$  &  $\mathcal O(g_W^6)$ interf.  &  Off-shell  &  NF QCD  &  EW corr. to $\mathcal O(g_W^4g_s^2)$  \\
+        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Off-shell  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
         \hline
@@
         {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
-        {\sc MG5\_aMC}&  $1.542 \pm 0.002$   
+        {\sc MG5\_aMC}&  $1.547 \pm 0.001$   
     \end{tabular}
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mjj_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mll_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/mjj_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/mll_LO.pdf}
 \caption{\label{fig:mjj-llLO}Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO.
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj1_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj2_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/ptj1_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/ptj2_LO.pdf}
 \caption{\label{fig:ptj1-2LO}Transverse momentum of the first (left) and second (right) tagging jet, at LO.
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj1_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj2_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/yj1_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/yj2_LO.pdf}
 \caption{\label{fig:yj1-2LO}Rapidity of the first (left) and second (right) tagging jet, at LO.
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ze_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/zmu_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/ze_LO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/zmu_LO.pdf}
 \caption{\label{fig:zel-muLO}Zeppenfeld variable of the positron (left) and of the muon (right), at LO.
@@
         \hline
-        {\sc POWHEG}  &  \\
+        {\sc POWHEG}  &  $1.334 \pm 0.0003$  &  $0.808 \pm  0.001$  &  $0.5260 \pm 0.0005$\\
         {\sc Recola}  &  \\
@@
         {\sc BONSAY}  &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
-        {\sc MG5\_aMC}&  $1.315 \pm 0.003$  &  $0.784 \pm  0.003$  &  $0.5313 \pm 0.0009$\\
+        {\sc MG5\_aMC}&  $1.318  \pm 0.003$  &  $0.781 \pm  0.004$  &  $0.5374 \pm 0.0016$\\
     \end{tabular}
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mjj_NLO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/mll_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/mjj_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/mll_NLO.pdf}
 \caption{\label{fig:mjj-llNLO}Invariant-mass of the two tagging jets (left) and of the two leptons (right), at NLO.
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj1_NLO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ptj2_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/ptj1_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/ptj2_NLO.pdf}
 \caption{\label{fig:ptj1-2NLO}Transverse momentum of the first (left) and second (right) tagging jet, at NLO.
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj1_NLO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/yj2_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/yj1_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/yj2_NLO.pdf}
 \caption{\label{fig:yj1-2NLO}Rapidity of the first (left) and second (right) tagging jet, at NLO.
@@
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/ze_NLO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 4.cm 0.6cm 1.5cm}]{figures/zmu_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/ze_NLO.pdf}
+   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.6cm 1.cm}]{figures/zmu_NLO.pdf}
 \caption{\label{fig:zel-muNLO}Zeppenfeld variable of the positron (left) and of the muon (right), at NLO.

### 2017-06-27 Setup/report.tex
added recola NLO number in tab3

@@
         {\sc POWHEG}  &  $1.334 \pm 0.0003$  &  $0.808 \pm  0.001$  &  $0.5260 \pm 0.0005$\\
-        {\sc Recola}  &  \\
+        {\sc Recola}  &  $1.197 \pm 0.003 $ \\
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\

### 2017-06-30 Setup/report.tex
WHIZARD value for LO cross section.

@@
         {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
+        {\sc WHIZARD} &  $1.5547 \pm 0.0028$ \\
         {\sc MG5\_aMC}&  $1.547 \pm 0.001$   

### 2017-07-03 Setup/report.tex
Updated WHIZARD number with higher precision.

--- 2017-06-27 Setup/report.tex
@@
 VBF approximation \\
-\subsection{ {\sc WHIZARD}: J\"urgen Reuter}
+\subsection{ {\sc WHIZARD}: J\"urgen Reuter, Pascal Stienemeier}
 Full matrix element \\
@@
         {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
+        {\sc WHIZARD} &  $1.5539 \pm 0.0004$ \\
         {\sc MG5\_aMC}&  $1.547 \pm 0.001$   

### 2017-07-03 Setup/report.tex
Add another name from the WHIZARD side.
Modifications and furture plan decided in Split

--- 2017-06-27 Setup/report.tex
@@
 \usepackage{graphicx}
+\usepackage{color}
 \usepackage{caption}
@@
 \newcommand{\eqa}[1]{\begin{eqnarray} #1 \end{eqnarray}}
+\newcommand{\MP}[1]{{ {\color{green}{ [MP: #1]}} }}
 
@@
 \begin{align}
- \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5 .
+ \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad\Delta R_{\Pj\Pl} > 0.3.
 \end{align}
@@
 %
-- All jets in the event are required to satisfy 
+- Isolation of the lepton, all jets in the event (also the one of the real radiation) are required to satisfy 
 \begin{align}
@@
         A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
-        M. Pellen    &  {\sc Recola}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
+        M. Pellen    &  {\sc Recola}\ +{\sc MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
         M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
@@
 VBF approximation \\
-\subsection{ {\sc WHIZARD}: J\"urgen Reuter}
+\subsection{ {\sc WHIZARD}: Simon Brass, J\"urgen Reuter, Pascal Stienemeier}
 Full matrix element \\
-\subsection{ \recola: Mathieu Pellen}
+\subsection{ \recola\ +{\sc MoCaNLO}: Mathieu Pellen}
 Full matrix element \\
@@
 To be checked what is possible \\
+\subsection{{\sc Bonsai}: Christopher Schwan}
 
@@
 $z^*_\ell = |y_\ell - \left(y_{\Pj_1}+y_{\Pj_2} \right)/2|/|\Delta y_{\Pj\Pj}|$ \\
-$[0;1.5]$ with bins of size $0.05$ (30 bins).
+$[0;1.5]$ with bins of size $0.05$ (30 bins). \\
+- $|\Delta y_{\Pj \Pj}|$: $[-5;5]$ with bins of size $0.5$ (20 bins).
 
@@
         {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
-        {\sc Recola}  &  $1.5503 \pm 0.0003$ \\
+        {\sc Recola\ +{\sc MoCaNLO}}  &  $1.5503 \pm 0.0003$ \\
         {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
         {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
+        {\sc WHIZARD} &  $1.5539 \pm 0.0004$ \\
         {\sc MG5\_aMC}&  $1.547 \pm 0.001$   
@@
         {\sc POWHEG}  &  $1.334 \pm 0.0003$  &  $0.808 \pm  0.001$  &  $0.5260 \pm 0.0005$\\
-        {\sc Recola}  &  $1.197 \pm 0.003 $ \\
+        {\sc Recola}\ +{\sc MoCaNLO}  &  $1.197 \pm 0.003 $ \\
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
@@
 
+\section{Plan}
+
+The plan is: \\
+- Scan in $m_{\Pj \Pj}$ and $|\Delta y_{\Pj \Pj}|$ at LO and compute the EW, QCD and interference (for the one who can) contribution. \\
+The binning in $m_{\Pj \Pj}$ is $\left[ 0, 50, 100, ..., 450, 500, 600, 700, 800 \right] $. \\
+The binning in $|\Delta y_{\Pj \Pj}|$ is $\left[ 0, 0.5, 1.0, 1.5, ..., 4.5, 5.0 \right] $. \\
+- Based on this, define a ``control region'' and a ``signal region'' (should be the one we have identified already).
+- Compute the QCD correction to QCD-induced and EW in these two regions.
+- Add PS to these computations (for those who can).
+- Add EW on top (probably only Mathieu).
+
+\section{Remarks}
+
+- \MP{Do we want to keep the cuts as they are or do we want to update to the recomandation of WG2?} \\
+- \MP{In particular we should write the report/article as we go further in the project in order to save time.}
+
 \part{Conclusion}

### 2017-08-02 Setup/report.tex
Fix spelling mistake
Update of Mathieu numbers after bug fix

@@
 To be checked what is possible \\
-\subsection{{\sc Bonsai}: Christopher Schwan}
+\subsection{{\sc BONSAY}: Christopher Schwan}
 
@@
         {\sc POWHEG}  &  $1.334 \pm 0.0003$  &  $0.808 \pm  0.001$  &  $0.5260 \pm 0.0005$\\
-        {\sc Recola}\ +{\sc MoCaNLO}  &  $1.197 \pm 0.003 $ \\
+        {\sc Recola}\ +{\sc MoCaNLO}  &  $1.317 \pm 0.004 $ \\
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\

### 2017-08-14 Setup/report.tex
Add correct rapidity dependent NLO data for BONSAY

@@
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
-        {\sc BONSAY}  &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
+        {\sc BONSAY}  &  $1.3358 \pm 0.0008$  &  $0.8192 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
         {\sc MG5\_aMC}&  $1.318  \pm 0.003$  &  $0.781 \pm  0.004$  &  $0.5374 \pm 0.0016$\\

### 2017-08-29 Setup/report.tex
Implement correct jet definition

@@
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
-        {\sc BONSAY}  &  $1.3358 \pm 0.0008$  &  $0.8192 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
+        {\sc BONSAY}  &  $1.3469 \pm 0.0008$  &  $0.8303 \pm  0.0008$  &  $0.51662 \pm 0.00008$ \\
         {\sc MG5\_aMC}&  $1.318  \pm 0.003$  &  $0.781 \pm  0.004$  &  $0.5374 \pm 0.0016$\\

### 2017-09-11 Setup/report.tex
Update VBFNLO numbers to modified jet definition

@@
         {\sc Recola\ +{\sc MoCaNLO}}  &  $1.5503 \pm 0.0003$ \\
-        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
+        {\sc VBFNLO}  &  $1.5540 \pm 0.0002$ \\
         {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
@@
         {\sc Recola}\ +{\sc MoCaNLO}  &  $1.317 \pm 0.004 $ \\
-        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
+        {\sc VBFNLO}  &  $1.3664 \pm 0.0003$  &  $0.8394 \pm  0.0003$  &  $0.5270 \pm 0.00012$\\
         {\sc BONSAY}  &  $1.3469 \pm 0.0008$  &  $0.8303 \pm  0.0008$  &  $0.51662 \pm 0.00008$ \\

### 2017-09-25 Setup/report.tex
change in the table of codes

--- 2017-08-29 Setup/report.tex
@@
 \usepackage{graphicx}
-\usepackage{color}
 \usepackage{caption}
@@
 \newcommand{\eqa}[1]{\begin{eqnarray} #1 \end{eqnarray}}
-\newcommand{\MP}[1]{{ {\color{green}{ [MP: #1]}} }}
 
@@
 \begin{align}
- \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad\Delta R_{\Pj\Pl} > 0.3.
+ \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5 .
 \end{align}
@@
 %
-- Isolation of the lepton, all jets in the event (also the one of the real radiation) are required to satisfy 
+- All jets in the event are required to satisfy 
 \begin{align}
@@
         A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
-        M. Pellen    &  {\sc Recola}\ +{\sc MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
+        M. Pellen    &  {\sc Recola}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
         M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
         C. Schwan    &  {\sc BONSAY}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
-        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No
+        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No
     \end{tabularx}
@@
 VBF approximation \\
-\subsection{ {\sc WHIZARD}: Simon Brass, J\"urgen Reuter, Pascal Stienemeier}
+\subsection{ {\sc WHIZARD}: J\"urgen Reuter}
 Full matrix element \\
-\subsection{ \recola\ +{\sc MoCaNLO}: Mathieu Pellen}
+\subsection{ \recola: Mathieu Pellen}
 Full matrix element \\
@@
 To be checked what is possible \\
-\subsection{{\sc BONSAY}: Christopher Schwan}
 
@@
 $z^*_\ell = |y_\ell - \left(y_{\Pj_1}+y_{\Pj_2} \right)/2|/|\Delta y_{\Pj\Pj}|$ \\
-$[0;1.5]$ with bins of size $0.05$ (30 bins). \\
-- $|\Delta y_{\Pj \Pj}|$: $[-5;5]$ with bins of size $0.5$ (20 bins).
+$[0;1.5]$ with bins of size $0.05$ (30 bins).
 
@@
         {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
-        {\sc Recola\ +{\sc MoCaNLO}}  &  $1.5503 \pm 0.0003$ \\
+        {\sc Recola}  &  $1.5503 \pm 0.0003$ \\
         {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
         {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
-        {\sc WHIZARD} &  $1.5539 \pm 0.0004$ \\
         {\sc MG5\_aMC}&  $1.547 \pm 0.001$   
@@
         {\sc POWHEG}  &  $1.334 \pm 0.0003$  &  $0.808 \pm  0.001$  &  $0.5260 \pm 0.0005$\\
-        {\sc Recola}\ +{\sc MoCaNLO}  &  $1.317 \pm 0.004 $ \\
+        {\sc Recola}  &  $1.197 \pm 0.003 $ \\
         {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
-        {\sc BONSAY}  &  $1.3469 \pm 0.0008$  &  $0.8303 \pm  0.0008$  &  $0.51662 \pm 0.00008$ \\
+        {\sc BONSAY}  &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
         {\sc MG5\_aMC}&  $1.318  \pm 0.003$  &  $0.781 \pm  0.004$  &  $0.5374 \pm 0.0016$\\
@@
 
-\section{Plan}
-
-The plan is: \\
-- Scan in $m_{\Pj \Pj}$ and $|\Delta y_{\Pj \Pj}|$ at LO and compute the EW, QCD and interference (for the one who can) contribution. \\
-The binning in $m_{\Pj \Pj}$ is $\left[ 0, 50, 100, ..., 450, 500, 600, 700, 800 \right] $. \\
-The binning in $|\Delta y_{\Pj \Pj}|$ is $\left[ 0, 0.5, 1.0, 1.5, ..., 4.5, 5.0 \right] $. \\
-- Based on this, define a ``control region'' and a ``signal region'' (should be the one we have identified already).
-- Compute the QCD correction to QCD-induced and EW in these two regions.
-- Add PS to these computations (for those who can).
-- Add EW on top (probably only Mathieu).
-
-\section{Remarks}
-
-- \MP{Do we want to keep the cuts as they are or do we want to update to the recomandation of WG2?} \\
-- \MP{In particular we should write the report/article as we go further in the project in order to save time.}
-
 \part{Conclusion}

### 2017-10-17 Setup/report.tex
update of set-up

--- 2017-09-11 Setup/report.tex
@@
 \usepackage{booktabs}
-\usepackage[dvips,table]{xcolor} 
+% \usepackage[dvips,table]{xcolor} 
 \usepackage{amsmath}
@@
 \newcommand{\eqa}[1]{\begin{eqnarray} #1 \end{eqnarray}}
-\newcommand{\MP}[1]{{ {\color{green}{ [MP: #1]}} }}
+\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
 
@@
 %
-- Scales: factorisation and renormalisation scale, $\mu_R = \mu_F = \MW$. \\
+- Scales: factorisation and renormalisation scale, \MP{$\mu_R = \mu_F = \mu$. \\
+
+\begin{equation}
+\label{eq:defscale}
+ \mu = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}},
+\end{equation}
+}
 %
@@
 \begin{align}
- \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad\Delta R_{\Pj\Pl} > 0.3.
+ \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3.
 \end{align}
@@
 %
-- Isolation of the lepton, all jets in the event (also the one of the real radiation) are required to satisfy 
-\begin{align}
- \qquad\Delta R_{\Pj\Pl} > 0.3 .
-\end{align}
+
+\MP{Now the $\Delta R_{\Pj\Pl}$ cut is simply in the jet definition, it is not a requirement to be fulfilled by all the jets as before.}
+
+% - Isolation of the lepton, all jets in the event (also the one of the real radiation) are required to satisfy 
+% \begin{align}
+%  \qquad\Delta R_{\Pj\Pl} > 0.3 .
+% \end{align}
 
@@
 $[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
-- $\ptsub{\Pj_1,\Pj_2}$ and $y_{\Pj_1,\Pj_2}$ of the two tagged jets (not their sum) \\
-$\ptsub{\Pj_1,\Pj_2}$: $[0; 1\TeV]$ with bins of size $25\GeV$ (40 bins). \\
+- $\ptsub{\Pj_1,\Pj_2,\Pj_3}$ and $y_{\Pj_1,\Pj_2,\Pj_3}$ of the two tagged jets \MP{and also the third jet at NLO} (not their sum) \\
+$\ptsub{\Pj_1\Pj_2}$: $[0; 1\TeV]$ with bins of size $25\GeV$ (40 bins). \\
 $y_{\Pj_1,\Pj_2}$: $[-5;5]$ with bins of size $0.5$ (20 bins). \\

### 2017-10-18 Setup/report.tex
small precision
changes according to Alexander's suggestions

@@
 \end{equation}
-}
+%
+where the jets are the tagging jets.}
+
 %
@@
 %
-- Out of these 2/3 jets, the two hardest in pT (tagged jets)are required to have:
+- Out of these 2/3 jets, the two hardest in pT (these are the tagging jets) are required to have:
 \begin{align}
@@
 $[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
-- $\ptsub{\Pj_1,\Pj_2,\Pj_3}$ and $y_{\Pj_1,\Pj_2,\Pj_3}$ of the two tagged jets \MP{and also the third jet at NLO} (not their sum) \\
-$\ptsub{\Pj_1\Pj_2}$: $[0; 1\TeV]$ with bins of size $25\GeV$ (40 bins). \\
-$y_{\Pj_1,\Pj_2}$: $[-5;5]$ with bins of size $0.5$ (20 bins). \\
+- \MP{$\ptsub{\Pj_1,\Pj_2,\Pj_3}$ and $y_{\Pj_1,\Pj_2,\Pj_3}$ of the two tagged jets and also the third jet at NLO} (not their sum) \\
+$\ptsub{\Pj_1,\Pj_2}$: $[0; 1\TeV]$ with bins of size $25\GeV$ (40 bins). \\
+\MP{$\ptsub{\Pj_3}$: $[0; 1\TeV]$ with bins of size $10\GeV$ (100 bins).} \\
+\MP{$y_{\Pj_1,\Pj_2,\Pj_3}$: $[-5;5]$ with bins of size $0.5$ (20 bins).} \\
 - Invariant mass of the two charged leptons. \\

### 2017-10-18 Setup/report.tex
Update histogram definitions with my suggestions

@@
 \newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
+\newcommand{\MR}[1]{{ {\color{blue}{ [MR: #1]}} }}
 
@@
 $[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
-- Zeppenfeld variable for $\mu^+$ and $\Pe^+$: \\
-$z^*_\ell = |y_\ell - \left(y_{\Pj_1}+y_{\Pj_2} \right)/2|/|\Delta y_{\Pj\Pj}|$ \\
+- Zeppenfeld variable for $\mu^+$, $\Pe^+$ \MR{and $\Pj_3$}: \\
+$z^*_x = |y_x - \left(y_{\Pj_1}+y_{\Pj_2} \right)/2|/|\Delta y_{\Pj\Pj}|$ \\
 $[0;1.5]$ with bins of size $0.05$ (30 bins). \\
-- $|\Delta y_{\Pj \Pj}|$: $[-5;5]$ with bins of size $0.5$ (20 bins).
+- $|\Delta y_{\Pj \Pj}|$: \MR{$[0;10]$} with bins of size $0.5$ (20 bins).
 

### 2017-10-22 Draft/article.tex
Draft of the article

%% Main-Version Draft
\documentclass[11pt,epsf]{article}
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{hyperref}
 \usepackage{caption}
 \usepackage{tabularx}
 \usepackage
 [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
 {subcaption}

\setlength{\evensidemargin}{0cm}
\setlength{\oddsidemargin}{0cm}
\setlength{\topmargin}{0.00cm}
\setlength{\textwidth}{16.0cm}
\setlength{\textheight}{22.55cm}
\setlength{\headheight}{0cm}
\setlength{\headsep}{0cm}
\setlength{\voffset}{0cm}
\setlength{\paperheight}{27cm}

\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.5}
\renewcommand{\textfraction}{0.2}
\renewcommand{\floatpagefraction}{0.7}

%% ---------------------------------
%% | ToDo Marker - only for draft! |
%% ---------------------------------
% Remove this section for final version!
\setlength{\marginparwidth}{20mm}

\newcommand{\margtodo}
{\marginpar{\textbf{\textcolor{red}{ToDo}}}{}}

\newcommand{\todo}[1]
{{\textbf{\textcolor{red}{(\margtodo{}#1)}}}{}}

\input{macros}

\begin{document}

\title{\hfill ~\\[-30mm]
\phantom{h} \hfill\mbox{\small pre-print number if any?}
\\[1cm]
\vspace{13mm}   \textbf{Precise predictions for same sign W-bosons scattering at the LHC}}

\date{}
\author{
Michele Grossi$^{X\,}$\footnote{E-mail:
  \texttt{YY@email.com}},
Alexander Karlberg, 
Mathieu Pellen$^{3\,}$\footnote{E-mail:
  \texttt{mathieu.pellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli, 
Michael Rauch, \\
J\"urgen Reuter,
Vincent Rothe, 
Christopher Schwan,
Pascal Stienemeier,
Marco Zaro.
\\[9mm]
{\small\it
$^1$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
{\small\it
$^3$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
}

\maketitle

\begin{abstract}
\noindent
Abstract to be written here.
\end{abstract}
\thispagestyle{empty}
\vfill
\newpage
\setcounter{page}{1}

\tableofcontents
\newpage

\section{Introduction}

The measurements are \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.

In the last decade many codes capable of performing VBS simulations have appeared.
Within a network such as VBSCan it is therefore natural to perform 
a quantitative comparison of these codes, both to cross-validate the results and to assess the impact of the different approximations which are used.
In fact, already at LO, when considering the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at order $\mathcal O (\alpha^6)$, the various implementations VBS simulations are different.
They differ, for example
by the (non-)inclusion of diagrams with vector bosons in the $s$-channel or by the treatment of interferences between diagrams.
The reason of these differences is that, 
when typical signal cuts for VBS are imposed, these effects turn to be small on rates and distributions.

\section{Definition of the process}

\section{Details of the calculations}

\subsection{Description of the predictions}

In the comparison, the following codes are used:

\begin{itemize}
 \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
and matrix elements taken from several sources: Born matrix elements are
adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
processes, real matrix elements are written by Marina Billoni, and virtual
matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library
\cite{Denner:2014gla,Denner:2016kdg}.

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computationsof one-loop amplitudes are carried out by switching dynamically between 
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which 
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections 
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections, 
        only loops with QCD-interacting particles are generated.
  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.

  \item The program {\sc Recola+MoCaNLO} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
These tools have been successfully used for the computation of NLO corrections for VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

  \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
parton-level Monte Carlo for processes with electroweak bosons. It
allows the calculation of VBS processes at NLO QCD in the VBF
approximation and including the s-channel triboson contribution,
neglecting interferences between the two. Besides the SM, also anomalous
couplings of the Higgs and gauge bosons can be simulated.

  \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
event generator with the LO matrix element generator {\sc O'Mega}. It
provides FKS subtraction terms for any NLO process, while virtual matrix
elements are provided externally by {\sc
OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
(cf. above) can be used as well). {\sc Whizard} allows to simulate a
huge number of BSM models as well, in particular for new physics in
the VBS channel in terms of both higher-dimensional operators as well as explicit
resonances.

\end{itemize}

The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s-$ and $t/u-$channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorizable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}
%
\begin{table}
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
        \hline
        \hline
        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
        M. Pellen    &  {\sc Recola+MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
        C. Schwan    &  {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No \\
        V. Rothe     &  {\sc Whizard}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes \\  
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
\end{table}
%

\subsection{Input parameters}

We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
density~\cite{Ball:2014uwa}
with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alpha_s\left( \MZ \right) = 0.118$. Since
the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
scheme, consistently with what is done in NNPDF.\\
We use the following values for the mass and width of the massive particles:
% 
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}. \\
\end{equation}
We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\

Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}: 
\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
        is required to be
        \begin{align}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quark and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
        \begin{align}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
%         Finally, all jest in the event are required to be separated from charged leptons:
%         \begin{align}
%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
%         \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with 
        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
\end{itemize}

\section{Fixed order comparisons}

\subsection{Cross sections}

In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
an excellent agreement among the various tools, which confirms the fact
that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc Bonsay}  &  $1.5524 \pm 0.0002$ \\
        {\sc MG5\_aMC}&  $1.547 \pm 0.001$  \\ 
        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
        {\sc Recola+MoCaNLO}  &  $1.5503 \pm 0.0003$ \\
        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
        {\sc Whizard}&  $ 1.5539 \pm 0.0004 $   
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
\end{table}

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc Bonsay}  &  $1.3366 \pm 0.0009$  \\
        {\sc MG5\_aMC}&  $1.318  \pm 0.003$  \\
        {\sc POWHEG}  &  $1.334 \pm 0.0003$  \\
        {\sc Recola+MoCaNLO}  &  $1.317 \pm 0.004 $ \\
        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
\end{table}
At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.

\subsection{Differential distributions}

\begin{figure}[h!]
   \centering
   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
\caption{\label{fig:wg1_mjj-llLO} Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO accuracy, 
computed with the different codes used in this comparison. The inset shows the ratio over {\sc VBFNLO}.
}
\end{figure}

\section{Influence of the fiducial region}

\section{Matching to parton shower}

\section{Conclusion}

%
\bfig
  \center
%   \includegraphics[width=0.5\textwidth]{figures/ZpT.pdf}
  \caption{Caption of the plot.}
\efig

\section*{Acknowledgements}

We thank ...
Acknowledgement of VBSCAN COST action.

\appendix

\section{Appendix one}

\bibliographystyle{utphys.bst}
\bibliography{article}
\end{document}

### 2017-11-02 Draft/article.tex

@@
         only loops with QCD-interacting particles are generated.
+
+  \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
+  and $e^+e^-$ colliders at $\alpha_{ew}^6$ and $\alpha_{ew}^4\alpha_s^2$ including interferences between the two sets of diagrams.
+It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity 
+formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{BERENDS1985441} and an adaptive
+strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}.
+
   \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.

### 2017-11-13 Setup/report.tex
changes of mathieu
added setup for NLOPS matchnig

@@
 \maketitle
+\tableofcontents
 
@@
         C. Schwan    &  {\sc BONSAY}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
-        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No
+        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No
     \end{tabularx}
@@
 - Scan in $m_{\Pj \Pj}$ and $|\Delta y_{\Pj \Pj}|$ at LO and compute the EW, QCD and interference (for the one who can) contribution. \\
-The binning in $m_{\Pj \Pj}$ is $\left[ 0, 50, 100, ..., 450, 500, 600, 700, 800 \right] $. \\
-The binning in $|\Delta y_{\Pj \Pj}|$ is $\left[ 0, 0.5, 1.0, 1.5, ..., 4.5, 5.0 \right] $. \\
+The binning in $m_{\Pj \Pj}$ is $\left[ 0, 50, 100, ..., 450, 500, 550, 600, 650, 700, 750, 800 \right] $. These are 17 bins. \\
+The binning in $|\Delta y_{\Pj \Pj}|$ is $\left[ 0, 0.5, 1.0, 1.5, ..., 4.5, 5.0 \right] $. These are 11 bins. \\
 - Based on this, define a ``control region'' and a ``signal region'' (should be the one we have identified already).
@@
 
+\newpage
+\section{Matching to parton shower}
+Same setup and observables as for the fixed-order runs.\\
+
+Tools:
+\begin{itemize}
+    \item VBFNLO + Herwig7: dipole vs angular-ordered shower, check also MC@NLO  vs Powheg matching
+    \item MG5\_aMC: Pythia8 vs Herwig++
+    \item Powheg + Pythia8
+    \item Whizard + Pythia6 / Pythia8 (MLM merging)
+    \item Phantom + Pythia
+\end{itemize}
+
+Comparisons are done after shower and hadronization. Hadrons are kept stable (no $\pi \to 2\gamma$ decay, no $B$ decay) in order not to have extra photons/leptons in the final state.\\
+No underlying event is simulated.\\
+QED radiation is disabled in the shower.\\
+For Pythia8, the Monash tune (number 14) should be used.\\
+All other parameters, in particular those for which particular settings need to be employed e.g. for consistency with the matching method, are free to be changed.
+
 \part{Conclusion}

### 2017-11-13 Setup/report.tex
Added pythia8 settings

@@
 
+For Pythia8 this amounts to setting
+\begin{verbatim}
+    pythia.readString("PartonLevel:All = on"); 
+    pythia.readString("HadronLevel:All = on"); 
+    pythia.readString("HadronLevel:Decay = off");
+    pythia.readString("PartonLevel:MPI = off"); 
+    pythia.readString("BeamRemnants:primordialKT = off");
+    pythia.readString("SpaceShower:QEDshowerByQ = off"); 
+    pythia.readString("SpaceShower:QEDshowerByL = off"); 
+    pythia.readString("TimeShower:QEDshowerByQ = off"); 
+    pythia.readString("TimeShower:QEDshowerByL = off"); 
+    pythia.readString("TimeShower:QEDshowerByOther = off"); 
+    pythia.readString("TimeShower:QEDshowerByGamma = off"); 
+    pythia.readString("Tune:pp = 14"); 
+\end{verbatim}
+
 \part{Conclusion}

### 2017-11-14 Setup/RivetAnalysis/MC_VBSCAN_MCComparison.cc
Add Rivet analysis

@@ -1,0 +1,228 @@
+// -*- C++ -*-
+#include "Rivet/Analysis.hh"
+#include "Rivet/Projections/FinalState.hh"
+#include "Rivet/Projections/FastJets.hh"
+#include "Rivet/Projections/MissingMomentum.hh"
+#include "Rivet/Projections/DressedLeptons.hh"
+#include "Rivet/Projections/PromptFinalState.hh"
+#include "Rivet/Projections/VetoedFinalState.hh"
+
+namespace Rivet {
+
+
+  /// @brief Add a short analysis description here
+  class MC_VBSCAN_MCComparison : public Analysis {
+  public:
+
+    /// Constructor
+    DEFAULT_RIVET_ANALYSIS_CTOR(MC_VBSCAN_MCComparison);
+
+
+    /// @name Analysis methods
+    //@{
+
+    /// Book histograms and initialise projections before the run
+    void init() {
+
+      // Complete final state
+      FinalState fs(-MAXDOUBLE, MAXDOUBLE, 0*GeV);
+
+      // Projection for dressed electrons and muons
+      IdentifiedFinalState photons(fs);
+      photons.acceptIdPair(PID::PHOTON);
+
+      IdentifiedFinalState el_id(fs);
+      el_id.acceptIdPair(PID::ELECTRON);
+      PromptFinalState electrons(el_id);
+      addProjection(electrons, "Electrons");
+      DressedLeptons dressed_electrons(photons, electrons, 0.1, Cuts::open(), true, false);
+      addProjection(dressed_electrons, "DressedElectrons");
+
+      IdentifiedFinalState mu_id(fs);
+      mu_id.acceptIdPair(PID::MUON);
+      PromptFinalState muons(mu_id);
+      addProjection(muons, "Muons");
+      DressedLeptons dressed_muons(photons, muons, 0.1, Cuts::open(), true, false);
+      addProjection(dressed_muons, "DressedMuons");
+
+      // Jets, anti-kt 0.4
+      VetoedFinalState fsJets; //final state for jet finding: veto leptons and neutrinos
+      fsJets.vetoNeutrinos();
+      fsJets.addVetoOnThisFinalState(dressed_electrons);
+      fsJets.addVetoOnThisFinalState(dressed_muons);
+      declare(FastJets(fsJets, FastJets::ANTIKT, 0.4), "Jets");
+
+      // Missing momentum
[…]

### 2017-11-14 Draft/abstract.tex
Set-up of the draft

--- 2017-10-22 Draft/article.tex
@@
-%% Main-Version Draft
-\documentclass[11pt,epsf]{article}
-%% -------------------------------
-%% |          Packages           |
-%% -------------------------------
- \usepackage{amsmath}
- \usepackage{graphicx}
- \usepackage[merge,numbers,compress]{natbib}
- \usepackage[T1]{fontenc}
- \usepackage{booktabs}
- \usepackage{xcolor} 
- \usepackage{xspace}
- \usepackage{dcolumn}
- \usepackage{hyperref}
- \usepackage{caption}
- \usepackage{tabularx}
- \usepackage
- [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
- {subcaption}
-
-\setlength{\evensidemargin}{0cm}
-\setlength{\oddsidemargin}{0cm}
-\setlength{\topmargin}{0.00cm}
-\setlength{\textwidth}{16.0cm}
-\setlength{\textheight}{22.55cm}
-\setlength{\headheight}{0cm}
-\setlength{\headsep}{0cm}
-\setlength{\voffset}{0cm}
-\setlength{\paperheight}{27cm}
-
-\renewcommand{\topfraction}{0.8}
-\renewcommand{\bottomfraction}{0.5}
-\renewcommand{\textfraction}{0.2}
-\renewcommand{\floatpagefraction}{0.7}
-
-%% ---------------------------------
-%% | ToDo Marker - only for draft! |
-%% ---------------------------------
-% Remove this section for final version!
-\setlength{\marginparwidth}{20mm}
-
-\newcommand{\margtodo}
-{\marginpar{\textbf{\textcolor{red}{ToDo}}}{}}
-
-\newcommand{\todo}[1]
-{{\textbf{\textcolor{red}{(\margtodo{}#1)}}}{}}
-
-\input{macros}
-
-\begin{document}
-
-\title{\hfill ~\\[-30mm]
-\phantom{h} \hfill\mbox{\small pre-print number if any?}
-\\[1cm]
-\vspace{13mm}   \textbf{Precise predictions for same sign W-bosons scattering at the LHC}}
-
-\date{}
-\author{
-Michele Grossi$^{X\,}$\footnote{E-mail:
-  \texttt{YY@email.com}},
-Alexander Karlberg, 
-Mathieu Pellen$^{3\,}$\footnote{E-mail:
-  \texttt{mathieu.pellen@physik.uni-wuerzburg.de}},
-Giovanni  Pelliccioli, 
-Michael Rauch, \\
-J\"urgen Reuter,
-Vincent Rothe, 
-Christopher Schwan,
-Pascal Stienemeier,
-Marco Zaro.
-\\[9mm]
-{\small\it
-$^1$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]
-{\small\it
-$^3$Universit\"at W\"urzburg, %
-        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
-{\small\it Emil-Hilb-Weg 22, \linebreak %
-        97074 W\"urzburg, %
-        Germany}\\[3mm]
-}
-
-\maketitle
-
 \begin{abstract}
@@
 \newpage
-
-\section{Introduction}
-
-The measurements are \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
-
-In the last decade many codes capable of performing VBS simulations have appeared.
-Within a network such as VBSCan it is therefore natural to perform 
-a quantitative comparison of these codes, both to cross-validate the results and to assess the impact of the different approximations which are used.
-In fact, already at LO, when considering the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at order $\mathcal O (\alpha^6)$, the various implementations VBS simulations are different.
-They differ, for example
-by the (non-)inclusion of diagrams with vector bosons in the $s$-channel or by the treatment of interferences between diagrams.
-The reason of these differences is that, 
-when typical signal cuts for VBS are imposed, these effects turn to be small on rates and distributions.
-
-\section{Definition of the process}
-
-\section{Details of the calculations}
-
-\subsection{Description of the predictions}
-
-In the comparison, the following codes are used:
-
-\begin{itemize}
- \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
-and matrix elements taken from several sources: Born matrix elements are
-adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
-processes, real matrix elements are written by Marina Billoni, and virtual
-matrix elements by Stefan Dittmaier.
-One loop integrals are evaluated using the {\sc Collier} library
-\cite{Denner:2014gla,Denner:2016kdg}.
-
-  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
-      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
-        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
-        Frederix:2016rdc}) for regulating IR singularities. The computationsof one-loop amplitudes are carried out by switching dynamically between 
-        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
-        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which 
-        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
-        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
-        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
-\begin{verbatim}
-> set complex_mass_scheme #1
-> import model loop_qcd_qed_sm_Gmu #2
-> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
-> output #4
-\end{verbatim}
-  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
-            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections 
-        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
-        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections, 
-        only loops with QCD-interacting particles are generated.
-  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.
-It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
-For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
-
-  \item The program {\sc Recola+MoCaNLO} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
-To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
-These tools have been successfully used for the computation of NLO corrections for VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
-
-  \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
-parton-level Monte Carlo for processes with electroweak bosons. It
-allows the calculation of VBS processes at NLO QCD in the VBF
-approximation and including the s-channel triboson contribution,
-neglecting interferences between the two. Besides the SM, also anomalous
-couplings of the Higgs and gauge bosons can be simulated.
-
-  \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
-event generator with the LO matrix element generator {\sc O'Mega}. It
-provides FKS subtraction terms for any NLO process, while virtual matrix
-elements are provided externally by {\sc
-OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
-(cf. above) can be used as well). {\sc Whizard} allows to simulate a
-huge number of BSM models as well, in particular for new physics in
-the VBS channel in terms of both higher-dimensional operators as well as explicit
-resonances.
-
-\end{itemize}
-
-The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
-NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
-In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
-\begin{itemize}
-    \item all $s-$ and $t/u-$channel diagrams that lead to the considered final state are included;
-    \item interferences between diagrams are included at LO;
-    \item diagrams which do not feature two resonant vector bosons are included;
-    \item the so-called non-factorizable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
-        are included;
-    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
-        the  $\mathcal O (\alpha^6$) term.
-\end{itemize}
-%
-\begin{table}
-    \footnotesize
-    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
-        \hline
-        \hline
-        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
-        M. Pellen    &  {\sc Recola+MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
-        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
-        C. Schwan    &  {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
-        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No \\
-        V. Rothe     &  {\sc Whizard}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes \\  
-    \end{tabularx}
-    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
-\end{table}
-%
-
-\subsection{Input parameters}
-
-We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
-density~\cite{Ball:2014uwa}
-with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alpha_s\left( \MZ \right) = 0.118$. Since
-the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
-scheme, consistently with what is done in NNPDF.\\
-We use the following values for the mass and width of the massive particles:
-% 
-\begin{alignat}{2}
-                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
-                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
-                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
-                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
-\end{alignat}
-and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
-\begin{equation}
-    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
-\end{equation}
-The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
-\begin{equation}
- \alpha = 7.555310522369 \times 10^{-3}. \\
-\end{equation}
-We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\
-
-Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}: 
-\begin{itemize}
-    \item The two same-sign charged leptons are required to have
-        \begin{align}
-         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
-        \end{align}
-    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
-        is required to be
-        \begin{align}
-          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
-        \end{align}
-    \item QCD partons (quark and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
-        to have
-        \begin{align}
-         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
-        \end{align}
-        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
-        \begin{align}
-         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
-        \end{align}
-%         Finally, all jest in the event are required to be separated from charged leptons:
-%         \begin{align}
-%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
-%         \end{align}
-    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with 
-        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
-        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
-\end{itemize}
-
-\section{Fixed order comparisons}
-
-\subsection{Cross sections}
-
-In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
-for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
-figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
-an excellent agreement among the various tools, which confirms the fact
-that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $1.5524 \pm 0.0002$ \\
-        {\sc MG5\_aMC}&  $1.547 \pm 0.001$  \\ 
-        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
-        {\sc Recola+MoCaNLO}  &  $1.5503 \pm 0.0003$ \\
-        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
-        {\sc Whizard}&  $ 1.5539 \pm 0.0004 $   
-    \end{tabular}
-    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $1.3366 \pm 0.0009$  \\
-        {\sc MG5\_aMC}&  $1.318  \pm 0.003$  \\
-        {\sc POWHEG}  &  $1.334 \pm 0.0003$  \\
-        {\sc Recola+MoCaNLO}  &  $1.317 \pm 0.004 $ \\
-        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  \\
-    \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
-At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
-$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.
-
-\subsection{Differential distributions}
-
-\begin{figure}[h!]
-   \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
-\caption{\label{fig:wg1_mjj-llLO} Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO accuracy, 
-computed with the different codes used in this comparison. The inset shows the ratio over {\sc VBFNLO}.
-}
-\end{figure}
-
-\section{Influence of the fiducial region}
-
-\section{Matching to parton shower}
-
-\section{Conclusion}
-
-%
-\bfig
-  \center
-%   \includegraphics[width=0.5\textwidth]{figures/ZpT.pdf}
-  \caption{Caption of the plot.}
-\efig
-
-\section*{Acknowledgements}
-
-We thank ...
-Acknowledgement of VBSCAN COST action.
-
-\appendix
-
-\section{Appendix one}
-
-\bibliographystyle{utphys.bst}
-\bibliography{article}
-\end{document}

### 2017-11-14 Draft/acknowledgements.tex
Set-up of the draft

--- 2017-10-22 Draft/article.tex
@@
-%% Main-Version Draft
-\documentclass[11pt,epsf]{article}
-%% -------------------------------
-%% |          Packages           |
-%% -------------------------------
- \usepackage{amsmath}
- \usepackage{graphicx}
- \usepackage[merge,numbers,compress]{natbib}
- \usepackage[T1]{fontenc}
- \usepackage{booktabs}
- \usepackage{xcolor} 
- \usepackage{xspace}
- \usepackage{dcolumn}
- \usepackage{hyperref}
- \usepackage{caption}
- \usepackage{tabularx}
- \usepackage
- [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
- {subcaption}
-
-\setlength{\evensidemargin}{0cm}
-\setlength{\oddsidemargin}{0cm}
-\setlength{\topmargin}{0.00cm}
-\setlength{\textwidth}{16.0cm}
-\setlength{\textheight}{22.55cm}
-\setlength{\headheight}{0cm}
-\setlength{\headsep}{0cm}
-\setlength{\voffset}{0cm}
-\setlength{\paperheight}{27cm}
-
-\renewcommand{\topfraction}{0.8}
-\renewcommand{\bottomfraction}{0.5}
-\renewcommand{\textfraction}{0.2}
-\renewcommand{\floatpagefraction}{0.7}
-
-%% ---------------------------------
-%% | ToDo Marker - only for draft! |
-%% ---------------------------------
-% Remove this section for final version!
-\setlength{\marginparwidth}{20mm}
-
-\newcommand{\margtodo}
-{\marginpar{\textbf{\textcolor{red}{ToDo}}}{}}
-
-\newcommand{\todo}[1]
-{{\textbf{\textcolor{red}{(\margtodo{}#1)}}}{}}
-
-\input{macros}
-
-\begin{document}
-
-\title{\hfill ~\\[-30mm]
-\phantom{h} \hfill\mbox{\small pre-print number if any?}
-\\[1cm]
-\vspace{13mm}   \textbf{Precise predictions for same sign W-bosons scattering at the LHC}}
-
-\date{}
-\author{
-Michele Grossi$^{X\,}$\footnote{E-mail:
-  \texttt{YY@email.com}},
-Alexander Karlberg, 
-Mathieu Pellen$^{3\,}$\footnote{E-mail:
-  \texttt{mathieu.pellen@physik.uni-wuerzburg.de}},
-Giovanni  Pelliccioli, 
-Michael Rauch, \\
-J\"urgen Reuter,
-Vincent Rothe, 
-Christopher Schwan,
-Pascal Stienemeier,
-Marco Zaro.
-\\[9mm]
-{\small\it
-$^1$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]
-{\small\it
-$^3$Universit\"at W\"urzburg, %
-        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
-{\small\it Emil-Hilb-Weg 22, \linebreak %
-        97074 W\"urzburg, %
-        Germany}\\[3mm]
-}
-
-\maketitle
-
-\begin{abstract}
-\noindent
-Abstract to be written here.
-\end{abstract}
-\thispagestyle{empty}
-\vfill
-\newpage
-\setcounter{page}{1}
-
-\tableofcontents
-\newpage
-
-\section{Introduction}
-
-The measurements are \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
-
-In the last decade many codes capable of performing VBS simulations have appeared.
-Within a network such as VBSCan it is therefore natural to perform 
-a quantitative comparison of these codes, both to cross-validate the results and to assess the impact of the different approximations which are used.
-In fact, already at LO, when considering the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at order $\mathcal O (\alpha^6)$, the various implementations VBS simulations are different.
-They differ, for example
-by the (non-)inclusion of diagrams with vector bosons in the $s$-channel or by the treatment of interferences between diagrams.
-The reason of these differences is that, 
-when typical signal cuts for VBS are imposed, these effects turn to be small on rates and distributions.
-
-\section{Definition of the process}
-
-\section{Details of the calculations}
-
-\subsection{Description of the predictions}
-
-In the comparison, the following codes are used:
-
-\begin{itemize}
- \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
-and matrix elements taken from several sources: Born matrix elements are
-adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
-processes, real matrix elements are written by Marina Billoni, and virtual
-matrix elements by Stefan Dittmaier.
-One loop integrals are evaluated using the {\sc Collier} library
-\cite{Denner:2014gla,Denner:2016kdg}.
-
-  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
-      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
-        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
-        Frederix:2016rdc}) for regulating IR singularities. The computationsof one-loop amplitudes are carried out by switching dynamically between 
-        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
-        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which 
-        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
-        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
-        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
-\begin{verbatim}
-> set complex_mass_scheme #1
-> import model loop_qcd_qed_sm_Gmu #2
-> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
-> output #4
-\end{verbatim}
-  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
-            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections 
-        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
-        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections, 
-        only loops with QCD-interacting particles are generated.
-  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.
-It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
-For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
-
-  \item The program {\sc Recola+MoCaNLO} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
-To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
-These tools have been successfully used for the computation of NLO corrections for VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
-
-  \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
-parton-level Monte Carlo for processes with electroweak bosons. It
-allows the calculation of VBS processes at NLO QCD in the VBF
-approximation and including the s-channel triboson contribution,
-neglecting interferences between the two. Besides the SM, also anomalous
-couplings of the Higgs and gauge bosons can be simulated.
-
-  \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
-event generator with the LO matrix element generator {\sc O'Mega}. It
-provides FKS subtraction terms for any NLO process, while virtual matrix
-elements are provided externally by {\sc
-OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
-(cf. above) can be used as well). {\sc Whizard} allows to simulate a
-huge number of BSM models as well, in particular for new physics in
-the VBS channel in terms of both higher-dimensional operators as well as explicit
-resonances.
-
-\end{itemize}
-
-The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
-NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
-In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
-\begin{itemize}
-    \item all $s-$ and $t/u-$channel diagrams that lead to the considered final state are included;
-    \item interferences between diagrams are included at LO;
-    \item diagrams which do not feature two resonant vector bosons are included;
-    \item the so-called non-factorizable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
-        are included;
-    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
-        the  $\mathcal O (\alpha^6$) term.
-\end{itemize}
-%
-\begin{table}
-    \footnotesize
-    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
-        \hline
-        \hline
-        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
-        M. Pellen    &  {\sc Recola+MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
-        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
-        C. Schwan    &  {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
-        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No \\
-        V. Rothe     &  {\sc Whizard}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes \\  
-    \end{tabularx}
-    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
-\end{table}
-%
-
-\subsection{Input parameters}
-
-We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
-density~\cite{Ball:2014uwa}
-with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alpha_s\left( \MZ \right) = 0.118$. Since
-the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
-scheme, consistently with what is done in NNPDF.\\
-We use the following values for the mass and width of the massive particles:
-% 
-\begin{alignat}{2}
-                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
-                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
-                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
-                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
-\end{alignat}
-and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
-\begin{equation}
-    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
-\end{equation}
-The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
-\begin{equation}
- \alpha = 7.555310522369 \times 10^{-3}. \\
-\end{equation}
-We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\
-
-Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}: 
-\begin{itemize}
-    \item The two same-sign charged leptons are required to have
-        \begin{align}
-         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
-        \end{align}
-    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
-        is required to be
-        \begin{align}
-          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
-        \end{align}
-    \item QCD partons (quark and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
-        to have
-        \begin{align}
-         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
-        \end{align}
-        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
-        \begin{align}
-         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
-        \end{align}
-%         Finally, all jest in the event are required to be separated from charged leptons:
-%         \begin{align}
-%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
-%         \end{align}
-    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with 
-        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
-        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
-\end{itemize}
-
-\section{Fixed order comparisons}
-
-\subsection{Cross sections}
-
-In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
-for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
-figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
-an excellent agreement among the various tools, which confirms the fact
-that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $1.5524 \pm 0.0002$ \\
-        {\sc MG5\_aMC}&  $1.547 \pm 0.001$  \\ 
-        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
-        {\sc Recola+MoCaNLO}  &  $1.5503 \pm 0.0003$ \\
-        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
-        {\sc Whizard}&  $ 1.5539 \pm 0.0004 $   
-    \end{tabular}
-    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $1.3366 \pm 0.0009$  \\
-        {\sc MG5\_aMC}&  $1.318  \pm 0.003$  \\
-        {\sc POWHEG}  &  $1.334 \pm 0.0003$  \\
-        {\sc Recola+MoCaNLO}  &  $1.317 \pm 0.004 $ \\
-        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  \\
-    \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
-At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
-$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.
-
-\subsection{Differential distributions}
-
-\begin{figure}[h!]
-   \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
-\caption{\label{fig:wg1_mjj-llLO} Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO accuracy, 
-computed with the different codes used in this comparison. The inset shows the ratio over {\sc VBFNLO}.
-}
-\end{figure}
-
-\section{Influence of the fiducial region}
-
-\section{Matching to parton shower}
-
-\section{Conclusion}
-
-%
-\bfig
-  \center
-%   \includegraphics[width=0.5\textwidth]{figures/ZpT.pdf}
-  \caption{Caption of the plot.}
-\efig
-
-\section*{Acknowledgements}
-
  We thank ...
 Acknowledgement of VBSCAN COST action.
-
-\appendix
-
-\section{Appendix one}
-
-\bibliographystyle{utphys.bst}
-\bibliography{article}
-\end{document}

### 2017-11-14 Draft/article.tex
Set-up of the draft

--- 2017-10-22 Draft/article.tex
@@
 
+\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
+\newcommand{\MR}[1]{{ {\color{red}{ [MR: #1]}} }}
+
 %% ---------------------------------
@@
 \title{\hfill ~\\[-30mm]
-\phantom{h} \hfill\mbox{\small pre-print number if any?}
+\phantom{h} \hfill\mbox{\small DESY PREPRINT } \\
+\vspace{-10mm}
+\phantom{h} \hfill\mbox{\small KIT PREPRINT } \\
+\vspace{-10mm}
+\phantom{h} \hfill\mbox{\small NIKHEF PREPRINT } \\
+\vspace{-10mm}
+\phantom{h} \hfill\mbox{\small ZURICH PREPRINT }
 \\[1cm]
-\vspace{13mm}   \textbf{Precise predictions for same sign W-bosons scattering at the LHC}}
+% \vspace{13mm}   
+\textbf{Precise predictions for same sign W-bosons scattering at the LHC}}
 
@@
 \author{
-Michele Grossi$^{X\,}$\footnote{E-mail:
-  \texttt{YY@email.com}},
-Alexander Karlberg, 
-Mathieu Pellen$^{3\,}$\footnote{E-mail:
-  \texttt{mathieu.pellen@physik.uni-wuerzburg.de}},
-Giovanni  Pelliccioli, 
-Michael Rauch, \\
-J\"urgen Reuter,
-Vincent Rothe, 
-Christopher Schwan,
-Pascal Stienemeier,
-Marco Zaro.
+Ansgar Denner$^{1\,}$,
+Stefan Dittmaier$^{2\,}$,
+Michele Grossi$^{3\,}$,
+Alexander Karlberg$^{4\,}$, \\
+Mathieu Pellen$^{1\,}$\footnote{E-mail:
+  \texttt{mpellen@physik.uni-wuerzburg.de}},
+Giovanni  Pelliccioli$^{5\,}$,
+Michael Rauch$^{6\,}$,
+J\"urgen Reuter$^{7\,}$,
+Vincent Rothe$^{7\,}$, \\
+Christopher Schwan$^{2\,}$,
+Pascal Stienemeier$^{7\,}$,
+Marco Zaro$^{8\,}$\footnote{E-mail:
+  \texttt{m.zaro@nikhef.nl}}.
 \\[9mm]
 {\small\it
-$^1$University X, %
+$^1$Universit\"at W\"urzburg, %
+        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
+{\small\it Emil-Hilb-Weg 22, \linebreak %
+        97074 W\"urzburg, %
+        Germany}\\[3mm]
+        %
+$^2${\small\it
+Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
+{\small\it Hermann-Herder-Str.\ 3, \linebreak %
+         79104 Freiburg, Germany}\\[3mm]
+        %
+{\small\it
+$^3$University X, %
         Institut Y,} \\ %
@@
         Country}\\[3mm]
+        %
 {\small\it
-$^3$Universit\"at W\"urzburg, %
-        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
-{\small\it Emil-Hilb-Weg 22, \linebreak %
-        97074 W\"urzburg, %
-        Germany}\\[3mm]
+$^4$Department of Physics, University of Z\"urich,} \\ %
+{\small\it CH-8057
+Z\"urich, Switzerland}\\[3mm]
+        %
+{\small\it
+$^5$University X, %
+        Institut Y,} \\ %
+{\small\it Street X, \linebreak %
+        XXXX city, %
+        Country}\\[3mm]
+        %
+{\small\it
+$^6$Institute for Theoretical Physics, Karlsruhe Institute of
+Technology (KIT), 
+,} \\ %
+{\small\it Karlsruhe, Germany}\\[3mm]
+        %
+{\small\it
+$^7$University X, %
+        Institut Y,} \\ %
+{\small\it Street X, \linebreak %
+        XXXX city, %
+        Country}\\[3mm]
+        %
+{\small\it
+$^8$University X, %
+        Institut Y,} \\ %
+{\small\it Street X, \linebreak %
+        XXXX city, %
+        Country}\\[3mm]
         }
@@
 
-\begin{abstract}
-\noindent
-Abstract to be written here.
-\end{abstract}
-\thispagestyle{empty}
-\vfill
 \newpage
-\setcounter{page}{1}
 
-\tableofcontents
-\newpage
+\input{abstract}
 
@@
 
-The measurements are \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
-
-In the last decade many codes capable of performing VBS simulations have appeared.
-Within a network such as VBSCan it is therefore natural to perform 
-a quantitative comparison of these codes, both to cross-validate the results and to assess the impact of the different approximations which are used.
-In fact, already at LO, when considering the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at order $\mathcal O (\alpha^6)$, the various implementations VBS simulations are different.
-They differ, for example
-by the (non-)inclusion of diagrams with vector bosons in the $s$-channel or by the treatment of interferences between diagrams.
-The reason of these differences is that, 
-when typical signal cuts for VBS are imposed, these effects turn to be small on rates and distributions.
+\input{introduction}
 
@@
 
-In the comparison, the following codes are used:
-
-\begin{itemize}
- \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
-and matrix elements taken from several sources: Born matrix elements are
-adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
-processes, real matrix elements are written by Marina Billoni, and virtual
-matrix elements by Stefan Dittmaier.
-One loop integrals are evaluated using the {\sc Collier} library
-\cite{Denner:2014gla,Denner:2016kdg}.
-
-  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
-      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
-        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
-        Frederix:2016rdc}) for regulating IR singularities. The computationsof one-loop amplitudes are carried out by switching dynamically between 
-        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
-        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which 
-        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
-        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
-        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
-\begin{verbatim}
-> set complex_mass_scheme #1
-> import model loop_qcd_qed_sm_Gmu #2
-> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
-> output #4
-\end{verbatim}
-  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
-            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections 
-        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
-        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections, 
-        only loops with QCD-interacting particles are generated.
-  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.
-It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
-For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
-
-  \item The program {\sc Recola+MoCaNLO} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
-To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
-These tools have been successfully used for the computation of NLO corrections for VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
-
-  \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
-parton-level Monte Carlo for processes with electroweak bosons. It
-allows the calculation of VBS processes at NLO QCD in the VBF
-approximation and including the s-channel triboson contribution,
-neglecting interferences between the two. Besides the SM, also anomalous
-couplings of the Higgs and gauge bosons can be simulated.
-
-  \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
-event generator with the LO matrix element generator {\sc O'Mega}. It
-provides FKS subtraction terms for any NLO process, while virtual matrix
-elements are provided externally by {\sc
-OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
-(cf. above) can be used as well). {\sc Whizard} allows to simulate a
-huge number of BSM models as well, in particular for new physics in
-the VBS channel in terms of both higher-dimensional operators as well as explicit
-resonances.
-
-\end{itemize}
-
-The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
-NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
-In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
-\begin{itemize}
-    \item all $s-$ and $t/u-$channel diagrams that lead to the considered final state are included;
-    \item interferences between diagrams are included at LO;
-    \item diagrams which do not feature two resonant vector bosons are included;
-    \item the so-called non-factorizable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
-        are included;
-    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
-        the  $\mathcal O (\alpha^6$) term.
-\end{itemize}
-%
-\begin{table}
-    \footnotesize
-    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
-        \hline
-        \hline
-        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
-        M. Pellen    &  {\sc Recola+MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
-        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
-        C. Schwan    &  {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
-        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No \\
-        V. Rothe     &  {\sc Whizard}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes \\  
-    \end{tabularx}
-    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
-\end{table}
-%
+\input{description}
 
@@
 
-We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
-density~\cite{Ball:2014uwa}
-with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alpha_s\left( \MZ \right) = 0.118$. Since
-the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
-scheme, consistently with what is done in NNPDF.\\
-We use the following values for the mass and width of the massive particles:
-% 
-\begin{alignat}{2}
-                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
-                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
-                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
-                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
-\end{alignat}
-and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
-\begin{equation}
-    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
-\end{equation}
-The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
-\begin{equation}
- \alpha = 7.555310522369 \times 10^{-3}. \\
-\end{equation}
-We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\
-
-Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}: 
-\begin{itemize}
-    \item The two same-sign charged leptons are required to have
-        \begin{align}
-         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
-        \end{align}
-    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
-        is required to be
-        \begin{align}
-          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
-        \end{align}
-    \item QCD partons (quark and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
-        to have
-        \begin{align}
-         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
-        \end{align}
-        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
-        \begin{align}
-         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
-        \end{align}
-%         Finally, all jest in the event are required to be separated from charged leptons:
-%         \begin{align}
-%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
-%         \end{align}
-    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with 
-        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
-        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
-\end{itemize}
+\input{input}
 
@@
 
-In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
-for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
-figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
-an excellent agreement among the various tools, which confirms the fact
-that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $1.5524 \pm 0.0002$ \\
-        {\sc MG5\_aMC}&  $1.547 \pm 0.001$  \\ 
-        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
-        {\sc Recola+MoCaNLO}  &  $1.5503 \pm 0.0003$ \\
-        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
-        {\sc Whizard}&  $ 1.5539 \pm 0.0004 $   
-    \end{tabular}
-    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $1.3366 \pm 0.0009$  \\
-        {\sc MG5\_aMC}&  $1.318  \pm 0.003$  \\
-        {\sc POWHEG}  &  $1.334 \pm 0.0003$  \\
-        {\sc Recola+MoCaNLO}  &  $1.317 \pm 0.004 $ \\
-        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  \\
-    \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
-At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
-$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.
+\input{crosssection}
 
@@
 
-\begin{figure}[h!]
-   \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
-\caption{\label{fig:wg1_mjj-llLO} Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO accuracy, 
-computed with the different codes used in this comparison. The inset shows the ratio over {\sc VBFNLO}.
-}
-\end{figure}
+\input{distributions}
 
@@
 
+\input{shower}
+
 \section{Conclusion}
-
-%
-\bfig
-  \center
-%   \includegraphics[width=0.5\textwidth]{figures/ZpT.pdf}
-  \caption{Caption of the plot.}
-\efig
 
@@
 
-We thank ...
-Acknowledgement of VBSCAN COST action.
+\input{acknowledgements}
 

### 2017-11-14 Draft/crosssection.tex
Set-up of the draft

 In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
an excellent agreement among the various tools, which confirms the fact
that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X \pm 0.0002$ \\
        {\sc MG5\_aMC}&  $X \pm 0.001$  \\ 
        {\sc MoCaNLO+Recola}  &  $X \pm 0.0003$ \\
        {\sc PHANTOM}&  $X \pm 0.0004 $  \\
        {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\
        {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
        {\sc Whizard}&  $X \pm 0.0004 $
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
\end{table}

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X \pm 0.0009$  \\
        {\sc MG5\_aMC}&  $X  \pm 0.003$  \\
        {\sc MoCaNLO+Recola}  &  $X \pm 0.0003$ \\
        {\sc POWHEG}  &  $1.3556 \pm 0.0009$  \\
        {\sc VBFNLO}  &  $1.3916 \pm 0.0001$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
\end{table}
At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.

### 2017-11-14 Draft/description.tex
Set-up of the draft

In the comparison, the following codes are used:

\begin{itemize}
 \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
and matrix elements taken from several sources: Born matrix elements are
adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
processes, real matrix elements are written by Marina Billoni, and virtual
matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library
\cite{Denner:2014gla,Denner:2016kdg}.

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computationsof one-loop amplitudes are carried out by switching dynamically between 
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which 
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections 
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections, 
        only loops with QCD-interacting particles are generated.

  \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
  and $e^+e^-$ colliders at $\alpha_{ew}^6$ and $\alpha_{ew}^4\alpha_s^2$ including interferences between the two sets of diagrams.
It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity 
formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{BERENDS1985441} and an adaptive
strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}.

  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
\MP{Mention the non-clustering for the scale as well as the different running of alphas at NLO.}

  \item The program {\sc Recola+MoCaNLO} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
These tools have been successfully used for the computation of NLO corrections for VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

  \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
parton-level Monte Carlo for processes with electroweak bosons. It
allows the calculation of VBS processes at NLO QCD in the VBF
approximation and including the s-channel triboson contribution,
neglecting interferences between the two. Besides the SM, also anomalous
couplings of the Higgs and gauge bosons can be simulated.

  \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
event generator with the LO matrix element generator {\sc O'Mega}. It
provides FKS subtraction terms for any NLO process, while virtual matrix
elements are provided externally by {\sc
OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
(cf. above) can be used as well). {\sc Whizard} allows to simulate a
huge number of BSM models as well, in particular for new physics in
the VBS channel in terms of both higher-dimensional operators as well as explicit
resonances.

\end{itemize}

The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s-$ and $t/u-$channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorizable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}
%
\begin{table}
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
        \hline
        \hline
        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
        M. Pellen    &  {\sc Recola+MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
        C. Schwan    &  {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No \\
        V. Rothe     &  {\sc Whizard}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes \\  
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
\end{table}
%

### 2017-11-14 Draft/input.tex
Set-up of the draft

We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
density~\cite{Ball:2014uwa}
with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alpha_s\left( \MZ \right) = 0.118$. Since
the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
scheme, consistently with what is done in NNPDF.\\
We use the following values for the mass and width of the massive particles:
% 
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}. \\
\end{equation}
We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\

Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}: 
\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
        is required to be
        \begin{align}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quark and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
        \begin{align}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
%         Finally, all jest in the event are required to be separated from charged leptons:
%         \begin{align}
%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
%         \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with 
        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
\end{itemize}

### 2017-11-14 Draft/introduction.tex
Set-up of the draft

The measurements are \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.

In the last decade many codes capable of performing VBS simulations have appeared.
Within a network such as VBSCan it is therefore natural to perform 
a quantitative comparison of these codes, both to cross-validate the results and to assess the impact of the different approximations which are used.
In fact, already at LO, when considering the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at order $\mathcal O (\alpha^6)$, the various implementations VBS simulations are different.
They differ, for example
by the (non-)inclusion of diagrams with vector bosons in the $s$-channel or by the treatment of interferences between diagrams.
The reason of these differences is that, 
when typical signal cuts for VBS are imposed, these effects turn to be small on rates and distributions.

### 2017-11-14 Draft/shower.tex
Set-up of the draft

 \begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
%         {\sc Bonsay}  &  $X \pm 0.0009$  \\
        {\sc MG5\_aMC}&  $X  \pm 0.003$  \\
        {\sc POWHEG}  &  $1.3633 \pm 0.0004$  \\
%         {\sc Recola+MoCaNLO}  &  $X \pm 0.004 $ \\
        {\sc VBFNLO}  &  $X \pm 0.0003$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
\end{table}

### 2017-11-14 Draft/crosssection.tex
update of the recola numbers

@@
         {\sc MG5\_aMC}&  $X \pm 0.001$  \\ 
-        {\sc MoCaNLO+Recola}  &  $X \pm 0.0003$ \\
+        {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
         {\sc PHANTOM}&  $X \pm 0.0004 $  \\
@@
         {\sc MG5\_aMC}&  $X  \pm 0.003$  \\
-        {\sc MoCaNLO+Recola}  &  $X \pm 0.0003$ \\
+        {\sc MoCaNLO+Recola}  &  $ 1.382 \pm 0.002$ \\
         {\sc POWHEG}  &  $1.3556 \pm 0.0009$  \\

### 2017-11-14 Draft/article.tex
Add package `lmodern` for nicer fonts
Update article.tex
changes in the scan and draft

@@
  \usepackage{tabularx}
+ \usepackage{lmodern}
  \usepackage
@@
 \author{
-Ansgar Denner$^{1\,}$,
-Stefan Dittmaier$^{2\,}$,
-Michele Grossi$^{3\,}$,
-Alexander Karlberg$^{4\,}$, \\
-Mathieu Pellen$^{1\,}$\footnote{E-mail:
+Simon Brass$^{1\,}$,
+Ansgar Denner$^{2\,}$,
+Stefan Dittmaier$^{3\,}$,
+Michele Grossi$^{4\,}$, \\
+Alexander Karlberg$^{5\,}$, 
+Mathieu Pellen$^{2\,}$\footnote{E-mail:
   \texttt{mpellen@physik.uni-wuerzburg.de}},
-Giovanni  Pelliccioli$^{5\,}$,
-Michael Rauch$^{6\,}$,
-J\"urgen Reuter$^{7\,}$,
-Vincent Rothe$^{7\,}$, \\
-Christopher Schwan$^{2\,}$,
-Pascal Stienemeier$^{7\,}$,
-Marco Zaro$^{8\,}$\footnote{E-mail:
+Giovanni  Pelliccioli$^{6\,}$,
+Michael Rauch$^{7\,}$,
+J\"urgen Reuter$^{8\,}$, \\
+Vincent Rothe$^{8\,}$, 
+Christopher Schwan$^{3\,}$,
+Pascal Stienemeier$^{8\,}$,
+Marco Zaro$^{9\,}$\footnote{E-mail:
   \texttt{m.zaro@nikhef.nl}}.
@@
 {\small\it
-$^1$Universit\"at W\"urzburg, %
+$^1$Universit\"at Siegen, Department Physik,} \\ %
+{\small\it Walter-Flex-Str.3, \linebreak %
+        57068 Siegen, Germany}\\[3mm]
+        %
+{\small\it
+$^2$Universit\"at W\"urzburg, %
         Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
@@
         %
-$^2${\small\it
+$^3${\small\it
 Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
@@
 {\small\it
-$^3$University X, %
+$^4$University X, %
         Institut Y,} \\ %
@@
 {\small\it
-$^4$Department of Physics, University of Z\"urich,} \\ %
+$^5$Department of Physics, University of Z\"urich,} \\ %
 {\small\it CH-8057
@@
 {\small\it
-$^5$University X, %
+$^6$University X, %
         Institut Y,} \\ %
@@
 {\small\it
-$^6$Institute for Theoretical Physics, Karlsruhe Institute of
-Technology (KIT), 
-,} \\ %
+$^7$Institute for Theoretical Physics, Karlsruhe Institute of
+Technology (KIT),} \\ %
 {\small\it Karlsruhe, Germany}\\[3mm]
@@
 {\small\it
-$^7$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]
+$^8$DESY Theory Group,} \\ %
+{\small\it Notkestr. 85, \linebreak %
+        D-22607 Hamburg, Germany}\\[3mm]
         %
 {\small\it
-$^8$University X, %
+$^9$University X, %
         Institut Y,} \\ %

### 2017-11-14 Draft/article.tex
Update article.tex

--- 2017-11-14 Draft/article.tex
@@
 Stefan Dittmaier$^{2\,}$,
-Michele Grossi$^{3\,}$,
+Michele Grossi$^{3\,}{9\,}
 Alexander Karlberg$^{4\,}$, \\
@@
 {\small\it
-$^3$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]
+$^3$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
+{\small\it Via A. Bassi 6, \linebreak %
+        27100 Pavia, %
+        Italy}\\[3mm]
         %
@@
         %
-{\small\it
-$^5$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]
+$^5${\small\it
+Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
+{\small\it Via P. Giuria 1, \linebreak %
+        10125 Torino, %
+        Italy}\\[3mm]
         %
@@
         }
+$^9$ IBM Italia s.p.a.} \\ %
+{\small\it Circonvallazione Idroscalo , \linebreak %
+        20090 Segrate (MI), %
+        Italy}\\[3mm]
+        %
 

### 2017-11-14 Draft/article.tex
Update article.tex

@@
 Stefan Dittmaier$^{2\,}$,
-Michele Grossi$^{3\,}{9\,}
+Michele Grossi$^{{3\,},{9\,}}$
 Alexander Karlberg$^{4\,}$, \\

### 2017-11-14 Draft/article.tex
fix of the affiliation

--- 2017-11-14 Draft/article.tex
@@
 Stefan Dittmaier$^{3\,}$,
-Michele Grossi$^{4\,}$, \\
-Alexander Karlberg$^{5\,}$, 
+Michele Grossi$^{4,5\,}$, \\
+Alexander Karlberg$^{6\,}$, 
 Mathieu Pellen$^{2\,}$\footnote{E-mail:
   \texttt{mpellen@physik.uni-wuerzburg.de}},
-Giovanni  Pelliccioli$^{6\,}$,
-Michael Rauch$^{7\,}$,
-J\"urgen Reuter$^{8\,}$, \\
-Vincent Rothe$^{8\,}$, 
+Giovanni  Pelliccioli$^{7\,}$,
+Michael Rauch$^{8\,}$,
+J\"urgen Reuter$^{9\,}$, \\
+Vincent Rothe$^{9\,}$, 
 Christopher Schwan$^{3\,}$,
-Pascal Stienemeier$^{8\,}$,
-Marco Zaro$^{9\,}$\footnote{E-mail:
+Pascal Stienemeier$^{9\,}$,
+Marco Zaro$^{10\,}$\footnote{E-mail:
   \texttt{m.zaro@nikhef.nl}}.
@@
 {\small\it
-$^4$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]
+$^4$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
+{\small\it Via A. Bassi 6, \linebreak %
+        27100 Pavia, %
+        Italy}\\[3mm]
 %        
 {\small\it
-$^5$Department of Physics, University of Z\"urich,} \\ %
+$^{5}$IBM Italia s.p.a.} \\ %
+{\small\it Circonvallazione Idroscalo , \linebreak %
+        20090 Segrate (MI), %
+        Italy}\\[3mm]
+        %
+{\small\it
+$^6$Department of Physics, University of Z\"urich,} \\ %
 {\small\it CH-8057
@@
         %
-{\small\it
-$^6$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]
+$^7${\small\it
+Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
+{\small\it Via P. Giuria 1, \linebreak %
+        10125 Torino, %
+        Italy}\\[3mm]
         %
 {\small\it
-$^7$Institute for Theoretical Physics, Karlsruhe Institute of
+$^8$Institute for Theoretical Physics, Karlsruhe Institute of
 Technology (KIT),} \\ %
@@
 {\small\it
-$^8$DESY Theory Group,} \\ %
+$^9$DESY Theory Group,} \\ %
 {\small\it Notkestr. 85, \linebreak %
@@
 {\small\it
-$^9$University X, %
+$^{10}$University X, %
         Institut Y,} \\ %

### 2017-11-14 Draft/crosssection.tex
WHIZZARD numbers

@@
         {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
-        {\sc PHANTOM}&  $X \pm 0.0004 $  \\
+        {\sc PHANTOM}&  $1.4363 \pm 0.0009 $  \\
         {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\

### 2017-11-14 Draft/crosssection.tex
WHIZZARD numbers

--- 2017-11-14 Draft/crosssection.tex
@@
         {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
-        {\sc Whizard}&  $X \pm 0.0004 $
+        {\sc Whizard}&  $1.4363 \pm 0.0009 $
     \end{tabular}

### 2017-11-14 Setup/RivetAnalysis/MC_VBSCAN_MCComparison.cc
Fix Zeppenfeld variable definition
add absolute value in front of it

@@ -158,17 +158,17 @@ namespace Rivet {
         // z_e+
         double avgj12 = (filterjets[0].eta()+filterjets[1].eta())/2.;
         double norm12 = abs(filterjets[0].eta()-filterjets[1].eta());
-        double z = ( electrons[0].eta() - avgj12 ) / norm12;
+        double z = abs( electrons[0].eta() - avgj12 ) / norm12;
         _h_fiducial21->fill(z, event.weight());
         // z_mu
-        z = ( muons[0].eta() - avgj12 ) / norm12;
+        z = abs( muons[0].eta() - avgj12 ) / norm12;
         _h_fiducial22->fill(z, event.weight());
         if (filterjets.size() > 2) {
           // pT_j3, y_j3
           _h_fiducial23->fill(filterjets[2].perp(), event.weight());
           _h_fiducial24->fill(filterjets[2].eta(), event.weight());
           // z_j3
-          z = ( filterjets[2].eta() - avgj12 ) / norm12;
+          z = abs( filterjets[2].eta() - avgj12 ) / norm12;
           _h_fiducial25->fill(z, event.weight());
         }
 

### 2017-11-14 Setup/RivetAnalysis/MC_VBSCAN_MCComparison.cc
More improvements to Rivet analysis
* generate cross section histogram with unit bin width
* use linear histograms for cross section plots

@@ -56,7 +56,7 @@ namespace Rivet {
       declare(MissingMomentum(), "MET");
 
       // Histograms
-      _h_fiducial11 = bookHisto1D("crosssection", 1, 0, 1e6);
+      _h_fiducial11 = bookHisto1D("crosssection", 1, 12999.5, 13000.5);
       _h_fiducial12 = bookHisto1D("jetsinclusive", 7, -0.5, 6.5);
       _h_fiducial13 = bookHisto1D("jetsexclusive", 7, -0.5, 6.5);
       _h_fiducial14 = bookHisto1D("m_jj", 40, 0, 4000);

### 2017-11-15 Draft/crosssection.tex

--- 2017-11-14 Draft/crosssection.tex
@@
         {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
-        {\sc PHANTOM}&  $X \pm 0.0004 $  \\
+        {\sc PHANTOM}&  $1.4374 \pm 0.0006 $  \\
         {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\
         {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
-        {\sc Whizard}&  $X \pm 0.0004 $
+        {\sc Whizard}&  $1.4363 \pm 0.0009 $
     \end{tabular}

### 2017-11-16 Results/VBFNLO/internal2flat.py
Add script to convert from dat files to flat fmt
currently VBFNLO-specific, but adapting to other codes should be easy

@@ -1,0 +1,60 @@
+#! /usr/bin/python
+
+dataconversion = {
+    "jetsinclusive" : "hist.njetincl.dat",
+    "jetsexclusive" : "hist.njetexcl.dat",
+    "pT_j1"         : "hist.ptj1.dat",
+    "y_j1"          : "hist.yj1.dat",
+    "pT_j2"         : "hist.ptj2.dat",
+    "y_j2"          : "hist.yj2.dat",
+    "pT_j3"         : "hist.ptj3.dat",
+    "y_j3"          : "hist.yj3.dat",
+    "m_ll"          : "hist.mll.dat",
+    "m_jj"          : "hist.mjj.dat",
+    "Deltay_jj"     : "hist.yjj.dat",
+    "z_e"           : "hist.ze.dat",
+    "z_mu"          : "hist.zmu.dat",
+    "z_j3"          : "hist.zj3.dat"
+    }
+
+fout = open("LHC.dat",'w')
+
+cs = 0
+cserr = 0
+
+for key in dataconversion:
+  fout.write("""
+# BEGIN HISTO1D /MC_VBSCAN_MCComparison/{0}
+Path=/MC_VBSCAN_MCComparison/{0}
+ScaledBy=1
+Title=
+XLabel=
+YLabel=
+# xlow   xhigh   val     errminus        errplus
+""".format(key))
+  fin = open(dataconversion[key],'r')
+  for l in fin:
+    entries = l.split()
+    fout.write("{0}   {1}   {2}   {3}   {3}\n".format(entries[0],entries[1],entries[2],entries[3]))
+    if key == "jetsinclusive" and float(entries[0]) == 1.5:
+      cs = float(entries[2])
+      cserr = float(entries[3])
+  fout.write("# END HISTO1D\n")
+  fin.close()
+
+fout.write("""
+# BEGIN HISTO1D /MC_VBSCAN_MCComparison/crosssection
+Path=/MC_VBSCAN_MCComparison/crosssection
+ScaledBy=1
+Title=
+XLabel=
+YLabel=
+# xlow   xhigh   val     errminus        errplus
+0.000000e+00    1.000000e+06   {0}   {1}   {1}
+# END HISTO1D
+""".format(str(cs*1e-6),str(cserr*1e-6)))
+
+fout.close()
+
+
+

### 2017-11-16 parton-shower/rivetplot.sh
Add script for Rivet plots

@@ -1,0 +1,24 @@
+#! /bin/sh
+
+rivet-mkhtml \
+  NLO.yoda\
+:"Title=NLO"\
+:"ErrorBands=1"\
+:"ErrorBandColor=red"\
+:"RatioPlotErrorBandColor=red"\
+:"ErrorBandOpacity=0.3"\
+  Powheg.yoda\
+:"Title=Powheg+Pythia 8"\
+:"LineColor=green"\
+:"ErrorBands=1"\
+:"ErrorBandColor=green"\
+:"RatioPlotErrorBandColor=green"\
+:"ErrorBandOpacity=0.3"\
+  Herwig.yoda\
+:"Title=VBFNLO 3+Herwig 7"\
+:"LineColor=brown"\
+:"ErrorBands=1"\
+:"ErrorBandColor=brown"\
+:"RatioPlotErrorBandColor=brown"\
+:"ErrorBandOpacity=0.3"\
+

### 2017-11-16 parton-shower/rivetplot.sh
Adjust to new yoda file locations

@@ -1,20 +1,20 @@
 #! /bin/sh
 
 rivet-mkhtml \
-  NLO.yoda\
+  VBFNLO/VBFNLO-NLO.yoda\
 :"Title=NLO"\
 :"ErrorBands=1"\
 :"ErrorBandColor=red"\
 :"RatioPlotErrorBandColor=red"\
 :"ErrorBandOpacity=0.3"\
-  Powheg.yoda\
+  Powheg/Powheg.yoda\
 :"Title=Powheg+Pythia 8"\
 :"LineColor=green"\
 :"ErrorBands=1"\
 :"ErrorBandColor=green"\
 :"RatioPlotErrorBandColor=green"\
 :"ErrorBandOpacity=0.3"\
-  Herwig.yoda\
+  VBFNLO/Herwig-MCatNLO-DipoleShower.yoda\
 :"Title=VBFNLO 3+Herwig 7"\
 :"LineColor=brown"\
 :"ErrorBands=1"\

### 2017-11-16 Draft/process.tex
modifications of the drafts

- Explanation on the of the process \\

- Details on the description starting from the VBS approximation \\

### 2017-11-16 parton-shower/rivetplot.sh
Added powheg-lhef

@@ -21,4 +21,11 @@ rivet-mkhtml \
 :"ErrorBandColor=brown"\
 :"RatioPlotErrorBandColor=brown"\
 :"ErrorBandOpacity=0.3"\
+  Powheg/lhef.yoda\
+:"Title=Powheg-lhef"\
+:"LineColor=blue"\
+:"ErrorBands=1"\
+:"ErrorBandColor=blue"\
+:"RatioPlotErrorBandColor=blue"\
+:"ErrorBandOpacity=0.3"\
 

### 2017-11-28 Draft/fidregion.tex
Update fidregion.tex

\subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{../analyses/forthedraft/mjj_full.pdf}
\includegraphics[scale=0.395]{../analyses/forthedraft/dyjj_full.pdf}
\caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{PHANTOM} calculations.} \label{fig:mjjdyjj_1d}
\end{figure}
\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{../analyses/forthedraft/scan_ew6.pdf}
\includegraphics[scale=0.395]{../analyses/forthedraft/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{../analyses/forthedraft/scan_ew4qcd2.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
\end{figure}

\begin{figure}[hbt]
\centering
%\includegraphics[scale=0.39]{blank.pdf}
FIGURE
\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics. Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}
\newpage
\subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_tu.pdf}
\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_stu.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{PHANTOM} (full) calculations.}\label{fig:ratio2d_LO}
\end{figure}

\begin{figure}[hbt]
\centering
%\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_tu.pdf}
%\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_stu.pdf}
FIGURE
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{XXX} (full) calculations.}\label{fig:ratio2d_NLO}
\end{figure}

### 2017-11-28 Draft/fiducialregion.tex
Update fidregion.tex

--- 2017-11-28 Draft/fidregion.tex
@@
 \centering
-\includegraphics[scale=0.395]{../analyses/forthedraft/mjj_full.pdf}
-\includegraphics[scale=0.395]{../analyses/forthedraft/dyjj_full.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
 \caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics.
@@
 \centering
-\includegraphics[scale=0.395]{../analyses/forthedraft/scan_ew6.pdf}
-\includegraphics[scale=0.395]{../analyses/forthedraft/scan_ew5qcd1.pdf}
-\includegraphics[scale=0.395]{../analyses/forthedraft/scan_ew4qcd2.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
 \caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics.
@@
 \centering
-%\includegraphics[scale=0.39]{blank.pdf}
+%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
 FIGURE
@@
 \centering
-\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_tu.pdf}
-\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_stu.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
 \caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
@@
 \centering
-%\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_tu.pdf}
-%\includegraphics[scale=0.395]{../analyses/forthedraft/ratio_stu.pdf}
+%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
+%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
 FIGURE

### 2017-11-29 parton-shower/rivetplot_PHANTOM.sh
Upload New File

@@ -1,0 +1,39 @@
+#! /bin/sh
+
+rivet-mkhtml \
+VBFNLO/VBFNLO-NLO.yoda\
+:"Title=NLO"\
+:"ErrorBands=1"\
+:"ErrorBandColor=red"\
+:"RatioPlotErrorBandColor=red"\
+:"ErrorBandOpacity=0.3"\
+Powheg/Powheg.yoda\
+:"Title=Powheg+Pythia 8"\
+:"LineColor=green"\
+:"ErrorBands=1"\
+:"ErrorBandColor=green"\
+:"RatioPlotErrorBandColor=green"\
+:"ErrorBandOpacity=0.3"\
+VBFNLO/Herwig-MCatNLO-DipoleShower.yoda\
+:"Title=VBFNLO 3+Herwig 7"\
+:"LineColor=brown"\
+:"ErrorBands=1"\
+:"ErrorBandColor=brown"\
+:"RatioPlotErrorBandColor=brown"\
+:"ErrorBandOpacity=0.3"\
+Powheg/lhef.yoda\
+:"Title=Powheg-lhef"\
+:"LineColor=blue"\
+:"ErrorBands=1"\
+:"ErrorBandColor=blue"\
+:"RatioPlotErrorBandColor=blue"\
+:"ErrorBandOpacity=0.3"\
+PHANTOM/plots_loose_cuts/PHANTOM_5M.yoda\
+:"Title=PHANTOM"\
+:"LineColor=magenta"\
+:"ErrorBands=1"\
+:"ErrorBandColor=magenta"\
+:"RatioPlotErrorBandColor=magenta"\
+:"ErrorBandOpacity=0.3"\
+
+

### 2017-12-07 Draft/fiducialregion.tex
Update fiducialregion.tex

@@
 \end{figure}
+
+\begin{figure}[hbt]
+\centering %jjpeak_diag
+\includegraphics[scale=0.19]{figures/scanfigures/jjpeak_diag.png}
+\caption{Tree--level $\mathcal{O}(\alpha_{ew}^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
+\end{figure}
+
 \begin{figure}[ht]
@@
 \newpage
+
 \subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
+
+The VBS approximation [?] is frequently employed for VBS computations and we aim at the identification of kinematical regions where it provides trustworthy prediction for the $W^+W^+$ scattering.
+At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha_{ew}^6)$, the approximations consists in:
+\begin{itemize}
+\item discarding interferences between $t$ and $u$ channel diagrams, which are expected to be suppressed in the fiducial volume, after VBF cuts;
+\item discarding $s$--channel diagrams shown in \autoref{fig:jjpeak_diag}, which contain $q\bar{q}'$ annihilations ($W^-\rightarrow q \bar{q}'$); with a hard cut on the $jj$--pair invariant mass, these contributions are strongly suppressed.
+\end{itemize}
+
 \begin{figure}[hbt]
@@
 \centering
+\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-FIGURE
 \caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-Results of \texttt{VBFNLO} (approximated) and \texttt{XXX} (full) calculations.}\label{fig:ratio2d_NLO}
+Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations.
+RIGHT SIDE FIG.
+IN PREPARATION.
+QUESTION: is RECOLA calc.
+'exact' ?}\label{fig:ratio2d_NLO}
 \end{figure}

### 2017-12-08 Draft/abstract.tex
First attempt of Mathieu on draft, to be continued

@@
 \noindent
-Abstract to be written here.
+
+In this article, a detailed study of the vector-boson scattering of two positively charged W bosons is presented.
+In particular, a comparison between the full NLO QCD corrections against several approximations is carried out.
+This study is not only performed in the usual fiducial region used by experimental collaborations but also in a more inclusive set-up.
+This allows to infer precisely the quality of such approximations.
+Finally, NLO predictions matched to various parton shower are discussed.
+This study allows thus to infer the systematics related to vector-boson scattering at the NLO-QCD level and beyond.
+
 \end{abstract}

### 2017-12-08 Draft/article.tex
Update article.tex
First attempt of Mathieu on draft, to be continued

@@
 \author{
-Simon Brass$^{1\,}$,
-Ansgar Denner$^{2\,}$,
+Benedikt Biedermann$^{1\,}$,
+Simon Brass$^{2\,}$,
+Ansgar Denner$^{1\,}$,
 Stefan Dittmaier$^{3\,}$,
@@
 Alexander Karlberg$^{6\,}$, 
-Mathieu Pellen$^{2\,}$\footnote{E-mail:
+Mathieu Pellen$^{1\,}$\footnote{E-mail:
   \texttt{mpellen@physik.uni-wuerzburg.de}},
@@
 {\small\it
-$^1$Universit\"at Siegen, Department Physik,} \\ %
-{\small\it Walter-Flex-Str.3, \linebreak %
-        57068 Siegen, Germany}\\[3mm]
-        %
-{\small\it
-$^2$Universit\"at W\"urzburg, %
+$^1$Universit\"at W\"urzburg, %
         Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
@@
         Germany}\\[3mm]
+        %
+{\small\it
+$^2$Universit\"at Siegen, Department Physik,} \\ %
+{\small\it Walter-Flex-Str.3, \linebreak %
+        57068 Siegen, Germany}\\[3mm]
         %
@@
 \section{Definition of the process}
+\label{sec:definition}
+
+\input{definition}
 
 \section{Details of the calculations}
+\label{sec:details}
+
+\subsection{Several descriptions for one process}
+
+\input{process}
 
@@
 
-\section{Fixed order comparisons}
+\section{Leading-order study}
+\label{sec:LO}
 
-\subsection{Cross sections}
+\subsection{Scan}
 
-\input{crosssection}
+\input{scanLO}
 
-\subsection{Differential distributions}
+\subsection{Comparison in the fiducial region}
 
-\input{distributions}
+\input{crosssectionLO}
 
-\section{Influence of the fiducial region}
+\input{distributionsLO}
+
+\section{Next-to-leading order QCD}
+\label{sec:NLO}
+
+\subsection{ScanNLO}
+
+\input{scanNLO}
+
+\subsection{Comparison in the fiducial region}
+
+\input{crosssectionNLO}
+
+\input{distributionsNLO}
 
 \section{Matching to parton shower}
+\label{sec:matching}
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
+
+\input{conclusion}
 

### 2017-12-08 Draft/conclusion.tex
First attempt of Mathieu on draft, to be continued

- Sum-up of the study. \\

\MP{This might deserve a section on its own.} \\
Recommendations to experimental collaborations: \\
- Combinations with EW NLO corrections. \\
- Missing higher EW order: $\pm \delta^2_{\rm NLO EW}$ \\
- Systematics when using NLO QCD approximation \\
- Systematics of different parton shower \\
- Combined measurement including  EW, QCD, and interference \\
- Move to NLO predictions / generators \\
- Comment on the irreducible QCD background \\

### 2017-12-08 Draft/definition.tex
First attempt of Mathieu on draft, to be continued

--- 2017-11-28 Draft/fiducialregion.tex
@@
-\subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
+Defintion of the process. \\
+Explaining the various contributions. \\
+Show few Feynman diagrams and explain that it possesses also tri-boson contribuitions in the s-channel. \\
+
+% \subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
+
 \begin{figure}[hbt]
@@
 \end{figure}
-
-\begin{figure}[hbt]
-\centering
-%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
-FIGURE
-\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics.
-Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
-\end{figure}
-\newpage
-\subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
-\begin{figure}[hbt]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-Results of \texttt{VBFNLO} (approximated) and \texttt{PHANTOM} (full) calculations.}\label{fig:ratio2d_LO}
-\end{figure}
-
-\begin{figure}[hbt]
-\centering
-%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-FIGURE
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-Results of \texttt{VBFNLO} (approximated) and \texttt{XXX} (full) calculations.}\label{fig:ratio2d_NLO}
-\end{figure}

### 2017-12-08 Draft/distributionsLO.tex
First attempt of Mathieu on draft, to be continued

 \begin{figure}[h!]
   \centering
   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
\caption{\label{fig:wg1_mjj-llLO} Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO accuracy, 
computed with the different codes used in this comparison. The inset shows the ratio over {\sc VBFNLO}.
}
\end{figure}

### 2017-12-08 Draft/introduction.tex
First attempt of Mathieu on draft, to be continued

@@
-The measurements are \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
+The vector-boson scattering (VBS) process with two positively charged W boson is just starting to be measured at the LHC~\cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
+A whole class of new processes will therefore be measured during Run~II at the Large Hadron Collider (LHC).
+For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
+On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematics.
 
-In the last decade many codes capable of performing VBS simulations have appeared.
-Within a network such as VBSCan it is therefore natural to perform 
-a quantitative comparison of these codes, both to cross-validate the results and to assess the impact of the different approximations which are used.
-In fact, already at LO, when considering the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at order $\mathcal O (\alpha^6)$, the various implementations VBS simulations are different.
-They differ, for example
-by the (non-)inclusion of diagrams with vector bosons in the $s$-channel or by the treatment of interferences between diagrams.
-The reason of these differences is that, 
-when typical signal cuts for VBS are imposed, these effects turn to be small on rates and distributions.
+The $\PW^+\PW^+$ scattering is probably the simplest VBS processes to compute and to measure due to its particular charge structure and low background, respectively.
+Therefore, it is an ideal example for a detailed study of various theoretical predictions.
+In the last few years, several (N)LO computations become available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background
+process~\cite{Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Rauch:2016pai}.
+These computations all relied on approximations while recently the complete NLO corrections became available \cite{Biedermann:2017bss}.
+It is therefore interesting to infer in details the quality of the various approximations.
+Indeed, apart from Ref.~\cite{Biedermann:2017bss} \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
+
+The hadronic process is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ and it posses three contributions at leading order (LO) 
+[$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$].
+They are refer to as EW, interference, and QCD contributions respectively.
+The EW contribution is sometimes referred to as the VBS contribution even it possesses not-VBS contributions.
+Therefore, we start with a LO study of these contributions as a function of typical VBS cuts.
+This allows to understand the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
+This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.
+
+At NLO, the process possesses four contributions of orders 
+$\mathcal{O}{\left(\alpha^{7}\right)}$,
+$\mathcal{O}{\left(\alphas\alpha^{6}\right)}$,
+$\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and
+$\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
+The largest one is the EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ \cite{Biedermann:2016yds,Biedermann:2017bss}.
+The contribution of order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution.
+It is often referred as the QCD corrections to the VBS process.
+In the following, this order is the one where our comparisons are focused on.
+It is therefore usually referred to as simply \emph{NLO}.
+As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
+
+Finally, several predictions featuring parton shower are compared.
+This allows to infer systematics differences between the various predictions.
+This is the first time in the literature that such an analysis has been carried out \MP{True?}.
+
+Obviously all VBS processes deserve such a study but the present article sets the standard for inferring systematics related to NLO corrections and beyond.
+
+The article is organised as follow:
+in the first part (section~\ref{sec:definition}), the process studied is defined.
+Then, various approximation at LO and NLO are described in section~\ref{sec:details}.
+It is followed by a presentation of the various programs used for the simulations.
+Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
+Section~\ref{sec:matching} deals with the matching to parton shower.
+The last section (section \ref{sec:conclusion}) consists in concluding remarks and recommendations.

### 2017-12-08 Draft/scanLO.tex
First attempt of Mathieu on draft, to be continued

--- 2017-12-07 Draft/fiducialregion.tex
@@
-\subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
-\begin{figure}[hbt]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
-\caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics.
-Results of full matrix element \texttt{PHANTOM} calculations.} \label{fig:mjjdyjj_1d}
-\end{figure}
-
-\begin{figure}[hbt]
-\centering %jjpeak_diag
-\includegraphics[scale=0.19]{figures/scanfigures/jjpeak_diag.png}
-\caption{Tree--level $\mathcal{O}(\alpha_{ew}^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics.
-Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
-\end{figure}
-
 \begin{figure}[hbt]
@@
 
-\subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
+% \subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
 

### 2017-12-10 Draft/contributions.tex
new changes on the draft (very long train ride thanks to DB...)

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential distribution in the di-jet invariant mass (left) and the difference of the jet rapidity (right) at LO.
No cuts on the di-jet invariant mass and the different of the jet rapidity are applied.}
\label{fig:mjjdyjj_1d}
\end{figure}

One can also see this in three different plots in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.

\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alpha^5\alphas)$ (top right), and $\mathcal{O}(\alpha^4 \alphas^2)$ (bottom).}
\label{fig:mjjdyjj_2d_LO}
\end{figure}

### 2017-12-10 Draft/crosssectionLO.tex
new changes on the draft (very long train ride thanks to DB...)

--- 2017-11-15 Draft/crosssection.tex
@@
 \end{table}
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $X \pm 0.0009$  \\
-        {\sc MG5\_aMC}&  $X  \pm 0.003$  \\
-        {\sc MoCaNLO+Recola}  &  $ 1.382 \pm 0.002$ \\
-        {\sc POWHEG}  &  $1.3556 \pm 0.0009$  \\
-        {\sc VBFNLO}  &  $1.3916 \pm 0.0001$  \\
-    \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
-At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
-$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.

### 2017-12-10 Draft/crosssectionNLO.tex
new changes on the draft (very long train ride thanks to DB...)

--- 2017-11-14 Draft/crosssection.tex
@@
- In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
-for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
-figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
-an excellent agreement among the various tools, which confirms the fact
-that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $X \pm 0.0002$ \\
-        {\sc MG5\_aMC}&  $X \pm 0.001$  \\ 
-        {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
-        {\sc PHANTOM}&  $X \pm 0.0004 $  \\
-        {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\
-        {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
-        {\sc Whizard}&  $1.4363 \pm 0.0009 $
-    \end{tabular}
-    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
-\end{table}
+Cross secitons at NLO
 

### 2017-12-10 Draft/definition.tex
new changes on the draft (very long train ride thanks to DB...)

@@
-Defintion of the process. \\
+Definition of the process. \\
 Explaining the various contributions. \\
-Show few Feynman diagrams and explain that it possesses also tri-boson contribuitions in the s-channel. \\
+Show few Feynman diagrams and explain that it possesses also tri-boson contributions in the s-channel. \\
+This is explained in some details in Ref.~\cite{Biedermann:2017bss}.
 
-% \subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
-
-\begin{figure}[hbt]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
-\caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics.
-Results of full matrix element \texttt{PHANTOM} calculations.} \label{fig:mjjdyjj_1d}
+\begin{figure}[t]
+\begin{center}
+          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
+          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
+          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
+\end{center}
+        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
+        In addition to typical VBS contribution (left), this order also possesses $s$-channel (middle) and tri-boson contributions (right). }
+\label{diag:LO}
 \end{figure}
-
-\begin{figure}[hbt]
-\centering %jjpeak_diag
-\includegraphics[scale=0.19]{figures/scanfigures/jjpeak_diag.png}
-\caption{Tree--level $\mathcal{O}(\alpha_{ew}^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics.
-Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
-\end{figure}

### 2017-12-10 Draft/description.tex
new changes on the draft (very long train ride thanks to DB...)

@@
         only loops with QCD-interacting particles are generated.
+        \MP{Detail of the approximation done, divergent part, assumed to cancel etc.}
 
@@
 
-  \item The program {\sc Recola+MoCaNLO} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
+  \item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
 To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
@@
 
-The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
+% The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
 NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
@@
 \begin{itemize}
-    \item all $s-$ and $t/u-$channel diagrams that lead to the considered final state are included;
+    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
     \item interferences between diagrams are included at LO;
     \item diagrams which do not feature two resonant vector bosons are included;
-    \item the so-called non-factorizable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
+    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
         are included;
@@
     \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
+        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
         \hline
         \hline
-        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
-        M. Pellen    &  {\sc Recola+MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
-        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
-        C. Schwan    &  {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
-        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No \\
-        V. Rothe     &  {\sc Whizard}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes \\  
+        {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  & Yes & No  &  No  \\
+        {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  Yes & No  &  No  \\
+        {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  & Yes & No  &  No \\
+        {\sc MoCaNLO+Recola}  &  Yes  &  Yes  &  Yes  &  Yes & Yes  &  Yes  \\
+        {\sc PHANTOM}  &  Yes  &  Yes  &  Yes  & No & - & - \\  
+        {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  Yes & No  &  No  \\
+        {\sc Whizard}  &  Yes  &  Yes  &  Yes  & No & - & - \\  
     \end{tabularx}

### 2017-12-10 Draft/process.tex
new changes on the draft (very long train ride thanks to DB...)

@@
-- Explanation on the of the process \\
+Describe the physics and mention the code that simulate these cases. \\
+Start with LO (one paragraph each). \\
 
-- Details on the description starting from the VBS approximation \\
+- Details on the description starting from the VBS approximation which we define as the t-u approximation (other names in the litterature) \\
+Start from the idea of two independent protons etc. (POWHEG) \\
+- adding $s$-channel contributions, explain why this is possible to add them separately (VBFNLO)\\
+- Full computation (MG, MoCaNLO-Recola, Phantom) \\
+
+Move to NLO (one paragraph each). \\
+
+- VBS approximation at NLO (POWHEG) \\
+- VBS approximation at NLO + DPA for virt (Bonsay) \\
+- VBS approximation + $s$-channel (VBS NLO) \\
+- Hybrid VBS approximation (MG) \\
+- Explanation why EW corrections are needed in the full computation (Recola) \\
+
+\MP{Part written by Giovanni to be included}
+
+The VBS approximation [?] is frequently employed for VBS computations and we aim at the identification of kinematical regions where it provides trustworthy prediction for the $W^+W^+$ scattering.
+At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha_{ew}^6)$, the approximations consists in:
+\begin{itemize}
+\item discarding interferences between $t$ and $u$ channel diagrams, which are expected to be suppressed in the fiducial volume, after VBF cuts;
+\item discarding $s$--channel diagrams shown in \autoref{fig:jjpeak_diag}, which contain $q\bar{q}'$ annihilations ($W^-\rightarrow q \bar{q}'$); with a hard cut on the $jj$--pair invariant mass, these contributions are strongly suppressed.
+\end{itemize}

### 2017-12-10 Draft/scanLO.tex
new changes on the draft (very long train ride thanks to DB...)

@@
-\begin{figure}[hbt]
-\centering
-%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
-FIGURE
-\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics.
-Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
-\end{figure}
-\newpage
-
 % \subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
-
-The VBS approximation [?] is frequently employed for VBS computations and we aim at the identification of kinematical regions where it provides trustworthy prediction for the $W^+W^+$ scattering.
-At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha_{ew}^6)$, the approximations consists in:
-\begin{itemize}
-\item discarding interferences between $t$ and $u$ channel diagrams, which are expected to be suppressed in the fiducial volume, after VBF cuts;
-\item discarding $s$--channel diagrams shown in \autoref{fig:jjpeak_diag}, which contain $q\bar{q}'$ annihilations ($W^-\rightarrow q \bar{q}'$); with a hard cut on the $jj$--pair invariant mass, these contributions are strongly suppressed.
-\end{itemize}
 
@@
 \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-Results of \texttt{VBFNLO} (approximated) and \texttt{PHANTOM} (full) calculations.}\label{fig:ratio2d_LO}
+\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ at order $\mathcal{O}(\alpha^6)$.
+Ratio of approximated squared amplitudes over the full matrix element.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).}
+\label{fig:ratio2d_LO}
 \end{figure}
-
-\begin{figure}[hbt]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
-%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations.
-RIGHT SIDE FIG.
-IN PREPARATION.
-QUESTION: is RECOLA calc.
-'exact' ?}\label{fig:ratio2d_NLO}
-\end{figure}

### 2017-12-10 Draft/scanNLO.tex
new changes on the draft (very long train ride thanks to DB...)

--- 2017-11-28 Draft/fiducialregion.tex
@@
-\subsection{Scan in $M_{jj}$ and $\Delta y_{jj}$: fiducial region}\label{subsec:scan_full}
-\begin{figure}[hbt]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
-\caption{Differential cross--sections (fb) in $M_{jj}$ (left) and $\Delta y_{jj}$ (right) for the leading perturbative orders, without any cut on the $jj$ pair kinematics.
-Results of full matrix element \texttt{PHANTOM} calculations.} \label{fig:mjjdyjj_1d}
-\end{figure}
-\begin{figure}[ht]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics.
-Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
-\end{figure}
+Scan at NLO
 
@@
 \end{figure}
-\newpage
-\subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
-\begin{figure}[hbt]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-Results of \texttt{VBFNLO} (approximated) and \texttt{PHANTOM} (full) calculations.}\label{fig:ratio2d_LO}
-\end{figure}
 

### 2017-12-12 Draft/article.tex
new changes on the draft (very long train ride thanks to DB...)
added EPJC template

@@
 %% Main-Version Draft
-\documentclass[11pt,epsf]{article}
+\documentclass[twocolumn,epjc3]{svjour3} % use the EPJC template, two columns
+%%\documentclass[epjc3]{svjour3} % use the EPJC template, one column
+\smartqed  % flush right qed marks, e.g. at end of proof
 %% -------------------------------
@@
  \usepackage{lmodern}
- \usepackage
- [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
- {subcaption}
+% \usepackage
+% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
+% {subcaption}
 
-\setlength{\evensidemargin}{0cm}
-\setlength{\oddsidemargin}{0cm}
-\setlength{\topmargin}{0.00cm}
-\setlength{\textwidth}{16.0cm}
-\setlength{\textheight}{22.55cm}
-\setlength{\headheight}{0cm}
-\setlength{\headsep}{0cm}
-\setlength{\voffset}{0cm}
-\setlength{\paperheight}{27cm}
+%\setlength{\evensidemargin}{0cm}
+%\setlength{\oddsidemargin}{0cm}
+%\setlength{\topmargin}{0.00cm}
+%\setlength{\textwidth}{16.0cm}
+%\setlength{\textheight}{22.55cm}
+%\setlength{\headheight}{0cm}
+%\setlength{\headsep}{0cm}
+%\setlength{\voffset}{0cm}
+%\setlength{\paperheight}{27cm}
 
-\renewcommand{\topfraction}{0.8}
-\renewcommand{\bottomfraction}{0.5}
-\renewcommand{\textfraction}{0.2}
-\renewcommand{\floatpagefraction}{0.7}
+%\renewcommand{\topfraction}{0.8}
+%\renewcommand{\bottomfraction}{0.5}
+%\renewcommand{\textfraction}{0.2}
+%\renewcommand{\floatpagefraction}{0.7}
 
@@
 % Remove this section for final version!
-\setlength{\marginparwidth}{20mm}
+%\setlength{\marginparwidth}{20mm}
 
@@
 \input{macros}
-
+%
+\journalname{PREPRINT NUMBERS HERE}
+%
 \begin{document}
 
-\title{\hfill ~\\[-30mm]
-\phantom{h} \hfill\mbox{\small DESY PREPRINT } \\
-\vspace{-10mm}
-\phantom{h} \hfill\mbox{\small KIT PREPRINT } \\
-\vspace{-10mm}
-\phantom{h} \hfill\mbox{\small NIKHEF PREPRINT } \\
-\vspace{-10mm}
-\phantom{h} \hfill\mbox{\small ZURICH PREPRINT }
-\\[1cm]
-% \vspace{13mm}   
-\textbf{Precise predictions for same sign W-bosons scattering at the LHC}}
+\title{Precise predictions for same-sign W-bosons scattering at the LHC}
 
-\date{}
-\author{
-Benedikt Biedermann$^{1\,}$,
-Simon Brass$^{2\,}$,
-Ansgar Denner$^{1\,}$,
-Stefan Dittmaier$^{3\,}$,
-Michele Grossi$^{4,5\,}$, \\
-Alexander Karlberg$^{6\,}$, 
-Mathieu Pellen$^{1\,}$\footnote{E-mail:
-  \texttt{mpellen@physik.uni-wuerzburg.de}},
-Giovanni  Pelliccioli$^{7\,}$,
-Michael Rauch$^{8\,}$,
-J\"urgen Reuter$^{9\,}$, \\
-Vincent Rothe$^{9\,}$, 
-Christopher Schwan$^{3\,}$,
-Pascal Stienemeier$^{9\,}$,
-Marco Zaro$^{10\,}$\footnote{E-mail:
-  \texttt{m.zaro@nikhef.nl}}.
-\\[9mm]
-{\small\it
-$^1$Universit\"at W\"urzburg, %
-        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
-{\small\it Emil-Hilb-Weg 22, \linebreak %
+\author{Benedikt Biedermann\thanksref{wurz}
+\and
+Simon Brass\thanksref{sieg}
+\and
+Ansgar Denner\thanksref{wurz}
+\and
+Stefan Dittmaier\thanksref{frei}
+\and
+Michele Grossi\thanksref{pavia,ibm}
+\and
+Alexander Karlberg\thanksref{uzh} 
+\and
+Mathieu Pellen\thanksref{wurz,e1}
+\and
+Giovanni  Pelliccioli\thanksref{unito}
+\and
+Michael Rauch\thanksref{kit}
+\and
+J\"urgen Reuter\thanksref{desy}
+\and
+Vincent Rothe\thanksref{desy} 
+\and
+Christopher Schwan\thanksref{frei}
+\and
+Pascal Stienemeier\thanksref{desy}
+\and
+Marco Zaro\thanksref{nikh,e2}
+}
+
+\thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
+\thankstext{e2}{e-mail: m.zaro@nikhef.nl}
+
+\institute{Universit\"at W\"urzburg, %
+Institut f\"ur Theoretische Physik und Astrophysik,  %
+Emil-Hilb-Weg 22, %
 97074 W\"urzburg, %
-        Germany}\\[3mm]
-        %
-{\small\it
-$^2$Universit\"at Siegen, Department Physik,} \\ %
-{\small\it Walter-Flex-Str.3, \linebreak %
-        57068 Siegen, Germany}\\[3mm]
-        %
-$^3${\small\it
-Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
-{\small\it Hermann-Herder-Str.\ 3, \linebreak %
-         79104 Freiburg, Germany}\\[3mm]
-        %
-{\small\it
-$^4$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
-{\small\it Via A. Bassi 6, \linebreak %
+Germany\label{wurz} 
+\and
+Universit\"at Siegen, Department Physik, %
+ Walter-Flex-Str.3, %
+57068 Siegen, Germany\label{sieg}
+\and
+Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut, %
+ Hermann-Herder-Str.\ 3, %
+79104 Freiburg, Germany\label{frei}
+\and
+Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia, %
+Via A. Bassi 6, %
 27100 Pavia, %
-        Italy}\\[3mm]
-%        
-{\small\it
-$^{5}$IBM Italia s.p.a.} \\ %
-{\small\it Circonvallazione Idroscalo , \linebreak %
+Italy\label{pavia}
+\and
+IBM Italia s.p.a. %
+Circonvallazione Idroscalo , %
 20090 Segrate (MI), %
-        Italy}\\[3mm]
-        %
-{\small\it
-$^6$Department of Physics, University of Z\"urich,} \\ %
-{\small\it CH-8057
-Z\"urich, Switzerland}\\[3mm]
-        %
-$^7${\small\it
-Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
-{\small\it Via P. Giuria 1, \linebreak %
+Italy\label{ibm}
+\and
+Department of Physics, University of Z\"urich, %
+CH-8057 Z\"urich, 
+Switzerland\label{uzh}
+\and
+Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino, %
+Via P. Giuria 1, %
 10125 Torino, %
-        Italy}\\[3mm]
-        %
-{\small\it
-$^8$Institute for Theoretical Physics, Karlsruhe Institute of
-Technology (KIT),} \\ %
-{\small\it Karlsruhe, Germany}\\[3mm]
-        %
-{\small\it
-$^9$DESY Theory Group,} \\ %
-{\small\it Notkestr. 85, \linebreak %
-        D-22607 Hamburg, Germany}\\[3mm]
-        %
-{\small\it
-$^{10}$University X, %
-        Institut Y,} \\ %
-{\small\it Street X, \linebreak %
-        XXXX city, %
-        Country}\\[3mm]        
+Italy\label{unito}
+\and
+Institute for Theoretical Physics, Karlsruhe Institute of
+Technology (KIT), %
+Karlsruhe, 
+Germany\label{kit}
+\and
+DESY Theory Group, %
+Notkestr. 85, %
+D-22607 Hamburg, 
+Germany\label{desy}
+\and
+Nikhef,
+Science Park 105,
+1098XG Amsterdam,
+The Netherlancs\label{nikh}
 }
@@
 \maketitle
-
-\newpage
 
@@
 
-\subsection{Scan}
+\subsection{Three contributions}
+
+\input{contributions}
+
+\subsection{Inclusive comparison}
 
@@
 
-\subsection{ScanNLO}
+\subsection{Inclusive comparision}
 

### 2017-12-12 Draft/description.tex
added EPJC template

@@
+\begin{table*}[ht!]
+    \footnotesize
+    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
+        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
+        \hline
+        \hline
+        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
+        {\sc POWHEG}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
+        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
+        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
+        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
+    \end{tabularx}
+    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
+\end{table*}
+
 In the comparison, the following codes are used: 
-
 \begin{itemize}
@@
 %
-\begin{table}
-    \footnotesize
-    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
-        \hline
-        \hline
-        {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  & Yes & No  &  No  \\
-        {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  Yes & No  &  No  \\
-        {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  & Yes & No  &  No \\
-        {\sc MoCaNLO+Recola}  &  Yes  &  Yes  &  Yes  &  Yes & Yes  &  Yes  \\
-        {\sc PHANTOM}  &  Yes  &  Yes  &  Yes  & No & - & - \\  
-        {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  Yes & No  &  No  \\
-        {\sc Whizard}  &  Yes  &  Yes  &  Yes  & No & - & - \\  
-    \end{tabularx}
-    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
-\end{table}
 %

### 2017-12-15 Draft/scanLO.tex
Updated scanLO.tex

@@
 Ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).}
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (rightl).}
 \label{fig:ratio2d_LO}

### 2017-12-15 Draft/contributions.tex
added EPJC template
contributions.tex: text added

@@
-\begin{figure}[hbt]
+At tree--level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha_{ew}^6)$, the QCD background $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ and the interference $\mathcal{O}(\alpha_s\alpha_{ew}^5)$.\\
+Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ diagrams only involve $t/u$--channel virtual gluons.\\
+
+The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
+\begin{figure*}[hbt]
 \centering
@@
 \includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
-\caption{Differential distribution in the di-jet invariant mass (left) and the difference of the jet rapidity (right) at LO.
-No cuts on the di-jet invariant mass and the different of the jet rapidity are applied.}
+\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO.
+EW contribution in red, QCD in green, interference in gray and sum in blue.
+No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied.}
 \label{fig:mjjdyjj_1d}
-\end{figure}
+\end{figure*}
+The interference between EW and QCD contributions is small [to be commented further]
 

### 2017-12-16 Draft/contributions.tex
LO scan : text added

--- 2017-12-10 Draft/contributions.tex
@@
-\begin{figure}[hbt]
+At tree--level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha_{ew}^6)$, the QCD background $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ and the interference $\mathcal{O}(\alpha_s\alpha_{ew}^5)$.\\
+The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
+\begin{figure*}[hbt]
 \centering
@@
 \includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
-\caption{Differential distribution in the di-jet invariant mass (left) and the difference of the jet rapidity (right) at LO.
-No cuts on the di-jet invariant mass and the different of the jet rapidity are applied.}
+\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO.
+EW contribution in red, QCD in green, interference in gray and sum in blue.
+No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied.
+Results of full LO matrix element simulation.}
 \label{fig:mjjdyjj_1d}
-\end{figure}
-
+\end{figure*}
+Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed.
+The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).
+The LO cross--section for the three perturbative orders are shown in table~\ref{tab:LOscanXsec}.
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|c|c|c}
+        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha_{ew}^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alpha_s^2\alpha_{ew}^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alpha_s\alpha_{ew}^5))$ \\
+        \hline
+        \hline
+        {\sc Phantom}  &  $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
+        {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
+    \end{tabular}
+    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process: these results concern the setup described in section~\ref{subsec:inputpar}, apart from the $M_{jj}$ and $|\Delta y_{jj}|$ cuts which have been dropped.}
+\end{table}
+The EW, QCD and interference amount respectively to 57\%, 37\% and 6\% of the total inclusive cross section.
+In the presence of typical VBS cuts, the EW contribution is strongly enhanced, as shown in section~\ref{subsec:LOfiducial}.\\
+The EW contribution to the $M_{jj}$ distribution (red curve in Fig.~\ref{fig:mjjdyjj_1d}) shows a huge peak around the $W$ mass: this is due to the possibility for the two jets to be decay products of a $W^-$ boson.
+Note that this effect doesn't arise in calculations which employ VBS approximation (see VBS approx.
+description in section [ref.]).
 One can also see this in three different plots in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
-
 \begin{figure}[ht]

### 2018-01-08 Draft/contributions.tex
small typos fixed

@@
-At tree--level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha_{ew}^6)$, the QCD background $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ and the interference $\mathcal{O}(\alpha_s\alpha_{ew}^5)$.\\
+At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the QCD background $\mathcal{O}(\alphas^2\alpha^4)$ and the interference $\mathcal{O}(\alphas\alpha^5)$.\\
 The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
@@
 \end{figure*}
-Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed.
+Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed.
 The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).
@@
     \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha_{ew}^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alpha_s^2\alpha_{ew}^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alpha_s\alpha_{ew}^5))$ \\
+        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas^2\alpha^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas\alpha^5))$ \\
         \hline

### 2018-01-08 Draft/description.tex
typocorr2
small typos fixed

@@
     \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
+        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
         \hline
@@
   \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
-  and $e^+e^-$ colliders at $\alpha_{ew}^6$ and $\alpha_{ew}^4\alpha_s^2$ including interferences between the two sets of diagrams.
+  and $e^+e^-$ colliders at $\alpha_{ew}^6$ and $\alpha_{ew}^4\alphas^2$ including interferences between the two sets of diagrams.
 It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity 
 formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{BERENDS1985441} and an adaptive
-strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}.
+strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}
 
@@
 % The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
-NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
+NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alphas)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
 In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
@@
         are included;
-    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
+    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
         the  $\mathcal O (\alpha^6$) term.

### 2018-01-08 Draft/fiducialregion.tex
small typos fixed

@@
 \includegraphics[scale=0.19]{figures/scanfigures/jjpeak_diag.png}
-\caption{Tree--level $\mathcal{O}(\alpha_{ew}^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
+\caption{Tree--level $\mathcal{O}(\alpha^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
 \end{figure}
@@
 \includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics.
+\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha^6)$, $\mathcal{O}(\alpha^5\alphas)$ and $\mathcal{O}(\alpha^4 \alphas^2)$, without any cut on the $jj$ pair kinematics.
 Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
@@
 FIGURE
-\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics.
+\caption{Cross section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics.
 Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
@@
 The VBS approximation [?] is frequently employed for VBS computations and we aim at the identification of kinematical regions where it provides trustworthy prediction for the $W^+W^+$ scattering.
-At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha_{ew}^6)$, the approximations consists in:
+At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha^6)$, the approximations consists in:
 \begin{itemize}
@@
 \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
+\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
@@
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
+\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).

### 2018-01-08 Draft/input.tex
new changes on the draft (very long train ride thanks to DB...)
small typos fixed

@@
 density~\cite{Ball:2014uwa}
-with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alpha_s\left( \MZ \right) = 0.118$. Since
+with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alphas\left( \MZ \right) = 0.118$. Since
 the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
@@
 We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\
+
+The renormalisation and factorisation scales are set dynamically as
+%
+\begin{equation}
+\label{eq:defscale}
+ \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}},
+\end{equation}
 

### 2018-01-08 Draft/scanNLO.tex
Update scanNLO.tex
small typos fixed

@@
 \centering
-%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
+\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}
 FIGURE
-\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics.
+\caption{Cross section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics.
 Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}

### 2018-01-09 Draft/shower.tex
some edits for the shower part

@@
+We now turn to discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
+a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
+matching schemes, PS employed and of the other details of the matching (such as the choice of the shower initial scale). Among
+the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG} and {\sc VBFNLO}
+can also provide results at (N)LO+PS accuracy. Besides, also {\sc PHANTOM} is employed for LO+PS results.\\
+{\sc MG5\_aMC},
+which
+employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3) 
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the omonymous matching procedure is 
+employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} 
+{\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
+matching, in both cases together with {\sc Herwig7}~\cite{}. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8}.
+Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\
+
+Results will be presented within the cuts described in Section~\ref{subsec:inputpar}, applied after shower and hadronization (this implies that jets
+are obtained by clustering stable hadrons, and not QCD partons). This implies that at the event-generation level, looser cuts (or no cuts at all) 
+must be emplouyed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
+
+A slightly different setup has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full 
+${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is anyway dominated by doubly-resonant contribution, the 
+events are produced for the process with two stable W$^+$ bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and these W$^+$ bosons
+are decayed with {\sc MadSpin}~\cite{Artoisenet:2012st} (keeping spin correlations) before the PS. Since {\sc MadSpin}\ computes 
+the partial and total decay width of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed, 
+a small effect (6\%) on the normalisation of distribution is induced. Finally, when the renormalisation
+and factorisation scales are set, the $\Delta R_{\Pj\Pl}$ cut is not imposed during the jet-clustering procedure, but this has no visible effect 
+on the results.
+
+We now turn to present the results:
+
 \begin{table}[h!]

### 2018-01-11 Draft/shower.tex
updated phantom plots and rates in the text

@@
         \hline
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 (1.368) \pm 0.$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 (1.363) \pm 0.$  \\
+        {\sc POWHEG}  &  $1.3633 \pm 0.0004$  \\
+        {\sc VBFNLO}  &  $X \pm 0.0003$  \\
         \hline
-%         {\sc Bonsay}  &  $X \pm 0.0009$  \\
-        {\sc MG5\_aMC}&  $X  \pm 0.003$  \\
-        {\sc POWHEG}  &  $1.3633 \pm 0.0004$  \\
-%         {\sc Recola+MoCaNLO}  &  $X \pm 0.004 $ \\
-        {\sc VBFNLO}  &  $X \pm 0.0003$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275) \pm 0.$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $X  \pm 0.$  \\
+        {\sc PHANTOM} &  $1.235  \pm 0.$  \\
     \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
+    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison, 
+    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin}, see the text for details.}
+
+{\bf MZ: MC uncertainties???}
 \end{table}

### 2018-01-11 Draft/abstract.tex
added EPJC template

--- 2017-11-14 Draft/abstract.tex
@@
 \noindent
-Abstract to be written here.
+
+In this article, a detailed study of the vector-boson scattering for two positively charged W bosons is presented.
+In particular, a comparison between the full next-to-leading (NLO) QCD corrections against several approximations is carried out.
+This study is not only performed in the usual fiducial region used by experimental collaborations but also in a more inclusive set-up.
+This allows to infer precisely the quality of such approximations.
+Finally, NLO predictions matched to various parton shower are discussed.
+This study allows thus to infer the systematic errors related to vector-boson scattering at the NLO-QCD level and beyond.
+
 \end{abstract}
@@
 
-\tableofcontents
+%\tableofcontents
 \newpage

### 2018-01-11 Draft/definition.tex
added EPJC template

@@
-Definition of the process. \\
-Explaining the various contributions. \\
-Show few Feynman diagrams and explain that it possesses also tri-boson contributions in the s-channel. \\
-This is explained in some details in Ref.~\cite{Biedermann:2017bss}.
+The scattering of two positively charge W bosons is proceeding at the LHC through the partonic process:
+%
+\begin{equation}
+ {\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}.
+\end{equation}
 
-\begin{figure}[t]
+This process possesses three LO contributions of different orders.
+The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ is referred to as EW contributions.
+In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
+These type of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
+Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO})
+The VBS diagrams typically dominate the full process.
+But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.
+
+The process can also be mediated via a gluon connecting the two quark lines while the W bosons are radiated from the quark lines.
+These contributions are of order $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$ and usually feature different kinematic behaviours than the EW contribution.
+Nonetheless they share the same final state and therefore constitute an irreducible background.
+
+Finally, due to the specific colour structure of these two classes of amplitudes, there exists non-zero interferences.
+These are of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$ and are usually small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
+
+Usually, in experimental measurements, special VBS-cuts are designed in order to enhance the EW contribution over the QCD one.
+These cuts are based on the fact that the two contributions have rather different kinematic.
+The EW contribution is characterised by two jets with large rapidity in the peripheral region as well as a large invariant mass.
+The two W bosons are mostly produced centrally.
+This is in opposition with the QCD component which favour jets in the central region.
+Therefore, the event selection usually involve rapidity-difference and invariance mass cuts for the jets.
+This will also be discussed in Section \ref{subsec:contributions}.
+
+\begin{figure*}[t]
 \begin{center}
@@
 \label{diag:LO}
-\end{figure}
+\end{figure*}

### 2018-01-11 Draft/description.tex

@@
   \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
-  and $e^+e^-$ colliders at $\alpha_{ew}^6$ and $\alpha_{ew}^4\alphas^2$ including interferences between the two sets of diagrams.
+  and $e^+e^-$ colliders at $\alpha^6$ and $\alpha^4\alphas^2$ including interferences between the two sets of diagrams.
 It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity 

### 2018-01-11 Draft/introduction.tex

@@
-The vector-boson scattering (VBS) process with two positively charged W boson is just starting to be measured at the LHC~\cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
+The vector-boson scattering (VBS) process with two positively charged W boson is now starting to be measured at the LHC~\cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
 A whole class of new processes will therefore be measured during Run~II at the Large Hadron Collider (LHC).
 For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
-On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematics.
+On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.
 
-The $\PW^+\PW^+$ scattering is probably the simplest VBS processes to compute and to measure due to its particular charge structure and low background, respectively.
+The $\PW^+\PW^+$ scattering is the simplest VBS processes to compute theoretically and to measure experimentally due to its particular charge structure and low background, respectively.
 Therefore, it is an ideal example for a detailed study of various theoretical predictions.
-In the last few years, several (N)LO computations become available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background
+In the last few years, several leading order (LO) and next-to-leading order (NLO) computations become available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background
 process~\cite{Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Rauch:2016pai}.
@@
 It is therefore interesting to infer in details the quality of the various approximations.
-Indeed, apart from Ref.~\cite{Biedermann:2017bss} \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
+Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
 
-The hadronic process is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ and it posses three contributions at leading order (LO) 
-[$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$].
-They are refer to as EW, interference, and QCD contributions respectively.
-The EW contribution is sometimes referred to as the VBS contribution even it possesses not-VBS contributions.
-Therefore, we start with a LO study of these contributions as a function of typical VBS cuts.
-This allows to understand the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
+The hadronic process is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ and it posses three contributions at leading order.
+The orders of the contributions are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
+They are refer to as electroweak (EW), interference, and QCD contributions respectively.
+\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
+Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
+This allows to identify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
 This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.
@@
 The contribution of order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution.
-It is often referred as the QCD corrections to the VBS process.
+It is often referred to as the QCD corrections to the VBS process.
 In the following, this order is the one where our comparisons are focused on.
@@
 As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
+In particular, this allows to infer the accuracy of the so-called VBS approximation.
+To our knowledge, such a detailed study was still missing.
 
 Finally, several predictions featuring parton shower are compared.
-This allows to infer systematics differences between the various predictions.
+This allows to infer systematic differences between the various predictions.
 This is the first time in the literature that such an analysis has been carried out \MP{True?}.
@@
 Section~\ref{sec:matching} deals with the matching to parton shower.
-The last section (section \ref{sec:conclusion}) consists in concluding remarks and recommendations.
+The last section (section \ref{sec:conclusion}) consists in concluding remarks and recommendations for experimental collaborations.

### 2018-01-11 Draft/scanNLO.tex

@@
 FIGURE
-\caption{Cross section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics.
-Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
+\caption{Cross section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$.
+Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations.}\label{fig:mjjdyjj_2d_NLO}
 \end{figure}
@@
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations.
-RIGHT SIDE FIG.
-IN PREPARATION.
-QUESTION: is RECOLA calc.
-'exact' ?}\label{fig:ratio2d_NLO}
+\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$.
+Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations.}\label{fig:ratio2d_NLO}
 \end{figure}

### 2018-01-11 parton-shower/rivetplot.sh
Update parton-shower plot script and add new plots

@@ -1,11 +1,18 @@
 #! /bin/sh
 
-rivet-mkhtml \
+rivet-mkhtml -o rivet-NLOPS \
   VBFNLO/VBFNLO-NLO.yoda\
 :"Title=NLO"\
 :"ErrorBands=1"\
 :"ErrorBandColor=red"\
 :"RatioPlotErrorBandColor=red"\
+:"ErrorBandOpacity=0.3"\
+  VBFNLO/Herwig-MCatNLO-DipoleShower.yoda\
+:"Title=VBFNLO 3+Herwig 7"\
+:"LineColor=blue"\
+:"ErrorBands=1"\
+:"ErrorBandColor=blue"\
+:"RatioPlotErrorBandColor=blue"\
 :"ErrorBandOpacity=0.3"\
   Powheg/Powheg.yoda\
 :"Title=Powheg+Pythia 8"\
@@ -14,24 +21,51 @@ rivet-mkhtml \
 :"ErrorBandColor=green"\
 :"RatioPlotErrorBandColor=green"\
 :"ErrorBandOpacity=0.3"\
-  VBFNLO/Herwig-MCatNLO-DipoleShower.yoda\
-:"Title=VBFNLO 3+Herwig 7"\
+  Powheg/lhef.yoda\
+:"Title=Powheg-no shower"\
+:"LineColor=green"\
+:"LineStyle=dashed"\
+  MG5_aMC/run_HWPP_5M_NLOPS.yoda\
+:"Title=MG5_aMC+Herwig 2.7.1"\
+:"LineColor=magenta"\
+:"ErrorBands=1"\
+:"ErrorBandColor=magenta"\
+:"RatioPlotErrorBandColor=magenta"\
+:"ErrorBandOpacity=0.3"\
+  MG5_aMC/run_PY8_10M_NLOPS.yoda\
+:"Title=MG5_aMC+Pythia 8"\
 :"LineColor=brown"\
 :"ErrorBands=1"\
 :"ErrorBandColor=brown"\
 :"RatioPlotErrorBandColor=brown"\
 :"ErrorBandOpacity=0.3"\
-  Powheg/lhef.yoda\
-:"Title=Powheg-lhef"\
+
+
+rivet-mkhtml -o rivet-LOPS \
+  VBFNLO/VBFNLO-NLO.yoda\
+:"Title=NLO"\
+:"ErrorBands=1"\
+:"ErrorBandColor=red"\
[…]

### 2018-01-11 Draft/shower.tex
added figures to the PS part; text to be added

@@
     are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin}, see the text for details.}
-
 {\bf MZ: MC uncertainties???}
 \end{table}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/jetsexclusive.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
+\caption{Exclusive jet multiplicity from predictions matched to parton shower, at LO (left) or NLO (right) accuracy, compared with the fixed-NLO result
+    computed with \sc{VBFNLO}}
+\label{fig:PSnjet}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/m_jj.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/m_jj.pdf}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\label{fig:PSmjj}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/Deltay_jj.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/Deltay_jj.pdf}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the rapidity separation of the two tagging jets.}
+\label{fig:PSdyjj}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j1.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\label{fig:PSpt1}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j2.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\label{fig:PSpt2}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j3.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j3.pdf}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\label{fig:PSy3}
+\end{figure*}

### 2018-01-11 Draft/description.tex
Writting further paragraphs for the first part

@@
-\begin{table*}[ht!]
-    \footnotesize
-    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
-        \hline
-        \hline
-        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
-        {\sc POWHEG}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
-        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
-        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
-        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
-        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
-        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
-    \end{tabularx}
-    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
-\end{table*}
-
 In the comparison, the following codes are used: 
@@
 
-% The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
-NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alphas)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
-In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
-\begin{itemize}
-    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
-    \item interferences between diagrams are included at LO;
-    \item diagrams which do not feature two resonant vector bosons are included;
-    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
-        are included;
-    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
-        the  $\mathcal O (\alpha^6$) term.
-\end{itemize}
 %

### 2018-01-11 Draft/process.tex
Writting further paragraphs for the first part

--- 2017-11-16 Draft/process.tex
@@
-- Explanation on the of the process \\
+As mentioned previously, the EW contribution is dominated by the scattering of two W gauge bosons.
+Therefore it is justified to approximate the full EW contributions simply by the VBS contributions.
+Nonetheless, this set of contributions is not gauge invariant.
+To make it gauge-invariant, one should project on-shell the incoming W boson.
+Unfortunately, this momentum is space-like and thus a simple on-shell projection is not possible.
+Instead, one can keep the W boson leg connected to the external quark line off-shell while the one connected to the scattering is put on-shell.
+Then the polarisation of the gauge boson is accommodated following the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
+Such an approximation is usually called effective vector-boson approximation (EVBA).
 
-- Details on the description starting from the VBS approximation \\
+A more refined approximation consists in considering all $t$- and $u$- diagrams and square them separately.
+Nonetheless, different type of diagrams are not squared which amounts to neglecting interferences.
+These interferences are expected to be small in the VBS fiducial region.
+The $s$-channel contributions can still be left out.
+This approximation is often called $t$-/$u$- approximation or even VBS approximation.
+We will adopt the latter denomination in the following of the article.
+Such an approximation is implemented at LO in the computer codes {\sc Bonsay} and {\sc Powheg}.
+The physical origin of this approximation is that each proton emitting a quark represent two independent copies of $SU_c\left(3\right)$ gauge group.
+
+The squared matrix element of the $s$-channel contributions can then be added but all interferences between different kinematic channels are neglected.
+This is what is done in {\sc VBFNLO}.
+
+All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard}) consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
+Note that the final W boson can always be considered either on-shell or off-shell without affecting the previous discussion.
+All the codes mentioned here are described in details in the following sub-section.
+
+Moving on to NLO accuracy, one can extend the approximation presented at LO.
+The VBS approximation at NLO is simply extending the same approximation to real as well as to virtual corrections.
+This is implemented in {\sc POWHEG}.
+This approximation can be used in combination with a double-pole approximation [REF] for the virtual contribution.
+This require the computation of factorisable as well as non-factorisable corrections \cite{Dittmaier:2015bfe} separately.
+Such an approximation is implemented in {\sc Bonsay}.
+In {\sc VBFNLO}, the VBS approximation at NLO with $s$-channel contributions is implemented.
+
+A further refinement is to consider the full real contributions as well as part of the virtual \MP{I cannot remember exactly what is included}.
+This assumes a cancellation of infrared poles.
+Such predictions are provided by {\sc MG5\_aMC}.
+
+Finally the full computation implies to also consider EW corrections in the virtual as well as real corrections \cite{Biedermann:2017bss}.
+Such full predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
+
+In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
+\begin{itemize}
+    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
+    \item interferences between diagrams are included at LO;
+    \item diagrams which do not feature two resonant vector bosons are included;
+    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
+        are included;
+    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
+        the  $\mathcal O (\alpha^6$) term.
+\end{itemize}
+
+\begin{table*}[ht!]
+    \footnotesize
+    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
+        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
+        \hline
+        \hline
+        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
+        {\sc POWHEG}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
+        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
+        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
+        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
+    \end{tabularx}
+    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
+\end{table*}

### 2018-01-12 Draft/article.tex
LO scan : text added
Add Simon as author
Addition of some paragraphs
minimal changes
Add a motivation and extend the introduction
- added a motivation (first paragraph)
- extended or added some explanations
- changed the process to include the `+ X`, since we are inclusive;
  TODO: make sure this is also used in the remaining document
- changes `section` and `Section` to `Sec.` if they are not at the
  beginning of a sentence (in `macros.tex` there are abbreviations for
  it so I assume that is the "correct" style)
- corrected some spelling mistakes

@@
  \usepackage{hyperref}
+%  \usepackage[draft]{hyperref}
  \usepackage{caption}
@@
  \usepackage{lmodern}
+ \usepackage{siunitx}
 % \usepackage
@@
 \and
+Pietro Govoni\thanksref{mila}
+\and
 Michele Grossi\thanksref{pavia,ibm}
@@
 \and
-Mathieu Pellen\thanksref{wurz,e1}
+Mathieu Pellen\thanksref{wurz}
 \and
 Giovanni  Pelliccioli\thanksref{unito}
+\and
+Simon Pl\"atzer\thanksref{wien}
 \and
@@
 \and
-Marco Zaro\thanksref{nikh,e2}
+Marco Zaro\thanksref{nikh}
 }
 
-\thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
-\thankstext{e2}{e-mail: m.zaro@nikhef.nl}
+% \thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
+% \thankstext{e2}{e-mail: m.zaro@nikhef.nl}
 
@@
 79104 Freiburg, Germany\label{frei}
+\and
+Milan, Italy\label{mila}
 \and
@@
 \and
+Particle Physics, Faculty of Physics, University of Vienna, %
+Vienna, %
+Austria\label{wien}
+\and
 Institute for Theoretical Physics, Karlsruhe Institute of
@@
 1098XG Amsterdam,
-The Netherlancs\label{nikh}
+The Netherlands\label{nikh}
 }
@@
 \subsection{Input parameters}
+\label{subsec:inputpar}
 
@@
 \subsection{Three contributions}
+\label{subsec:contributions}
 
@@
 \subsection{Comparison in the fiducial region}
+\label{subsec:LOfiducial}
 

### 2018-01-12 Draft/introduction.tex
Writting further paragraphs for the first part
Add a motivation and extend the introduction
- added a motivation (first paragraph)
- extended or added some explanations
- changed the process to include the `+ X`, since we are inclusive;
  TODO: make sure this is also used in the remaining document
- changes `section` and `Section` to `Sec.` if they are not at the
  beginning of a sentence (in `macros.tex` there are abbreviations for
  it so I assume that is the "correct" style)
- corrected some spelling mistakes

@@
-The vector-boson scattering (VBS) process with two positively charged W boson is now starting to be measured at the LHC~\cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
-A whole class of new processes will therefore be measured during Run~II at the Large Hadron Collider (LHC).
+Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
+It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs and can be longitudinally polarized.
+The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge- and unitarity cancellations that strongly depend on the actual form of the Higgs-sector.
+A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-standard model Higgs bosons.
+
+The process with two positively charged W boson is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
 For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
@@
 
-The $\PW^+\PW^+$ scattering is the simplest VBS processes to compute theoretically and to measure experimentally due to its particular charge structure and low background, respectively.
-Therefore, it is an ideal example for a detailed study of various theoretical predictions.
-In the last few years, several leading order (LO) and next-to-leading order (NLO) computations become available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background
-process~\cite{Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Rauch:2016pai}.
-These computations all relied on approximations while recently the complete NLO corrections became available \cite{Biedermann:2017bss}.
+The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because the double-charge structure of the leptonic final state limits the number of partonic processes and total number of Feynman diagrams for each process.
+It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg $\PW^+\PW^-$ scattering, which has the largest cross section.
+Therefore, it is an ideal candidate for a detailed study of various theoretical predictions.
+
+In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
+These computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
 It is therefore interesting to infer in details the quality of the various approximations.
 Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
+Preliminary results have already been made public in Ref.~[proceedings Split].
 
-The hadronic process is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ and it posses three contributions at leading order.
-The orders of the contributions are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
-They are refer to as electroweak (EW), interference, and QCD contributions respectively.
+The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
+This final state possesses three contributions at LO whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
+They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
 \footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
 Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
-This allows to identify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
+This allows to identify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
 This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.
 
-At NLO, the process possesses four contributions of orders 
-$\mathcal{O}{\left(\alpha^{7}\right)}$,
-$\mathcal{O}{\left(\alphas\alpha^{6}\right)}$,
-$\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and
-$\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
-The largest one is the EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ \cite{Biedermann:2016yds,Biedermann:2017bss}.
-The contribution of order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution.
-It is often referred to as the QCD corrections to the VBS process.
-In the following, this order is the one where our comparisons are focused on.
-It is therefore usually referred to as simply \emph{NLO}.
+At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
+The largest one are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
+The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
+In the following, this order is the one where our comparisons are focused on; in this article we will refer to it as simply \emph{NLO}.
 As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
-In particular, this allows to infer the accuracy of the so-called VBS approximation.
+In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in later.
 To our knowledge, such a detailed study was still missing.
@@
 The article is organised as follow:
-in the first part (section~\ref{sec:definition}), the process studied is defined.
-Then, various approximation at LO and NLO are described in section~\ref{sec:details}.
-It is followed by a presentation of the various programs used for the simulations.
+In Sec.~\ref{sec:definition} the studied process is defined.
+Various approximation at LO and NLO are described in Sec.~\ref{sec:details}.
+This is followed by a presentation of the programs used for the computations.
 Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
 Section~\ref{sec:matching} deals with the matching to parton shower.
-The last section (section \ref{sec:conclusion}) consists in concluding remarks and recommendations for experimental collaborations.
+The last section consists in concluding remarks and recommendations for experimental collaborations.

### 2018-01-15 parton-shower/rivetplot.sh
Update PS plots
includes new MG5_aMC LOPS with Herwig and fixed z distributions for PHANTOM

@@ -62,8 +62,15 @@ rivet-mkhtml -o rivet-LOPS \
 :"ErrorBandColor=brown"\
 :"RatioPlotErrorBandColor=brown"\
 :"ErrorBandOpacity=0.3"\
-  PHANTOM/plots_loose_cuts2/phantom_norm.yoda\
-:"Title=PHANTOM+???"\
+  MG5_aMC/run_HWPP_1M_LOPS.yoda\
+:"Title=MG5_aMC+Herwig 2.7.1"\
+:"LineColor=magenta"\
+:"ErrorBands=1"\
+:"ErrorBandColor=magenta"\
+:"RatioPlotErrorBandColor=magenta"\
+:"ErrorBandOpacity=0.3"\
+  PHANTOM/plots_loose_cuts2/phantom_norm-scaled.yoda\
+:"Title=PHANTOM+Pythia 8"\
 :"LineColor=cyan"\
 :"ErrorBands=1"\
 :"ErrorBandColor=cyan"\

### 2018-01-18 Draft/contributions.tex
Update WHIZARD LO cross section in the Draft
also fix typos in shower.tex and contributions.tex.

@@
 \end{figure*}
-Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed.
+Concerning the QCD contribution, it is worth noticing that for quantum number conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed.
 The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).

### 2018-01-18 Draft/crosssectionLO.tex
some edits for the shower part
Update WHIZARD LO cross section in the Draft
also fix typos in shower.tex and contributions.tex.

@@
  In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
-for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
+for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both cases we show the absolute distributions in the main frame of the 
 figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
 an excellent agreement among the various tools, which confirms the fact
-that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
+that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region. We have checked 
+that the same level of agreement holds for many other differential distributions.
 \begin{table}[h!]
@@
         {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
-        {\sc Whizard}&  $1.4363 \pm 0.0009 $
+        {\sc Whizard}&  $1.4360 \pm 0.0005 $
     \end{tabular}

### 2018-01-18 Draft/shower.tex
Update WHIZARD LO cross section in the Draft
also fix typos in shower.tex and contributions.tex.

@@
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3) 
-and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the omonymous matching procedure is 
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the anonymous matching procedure is 
 employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} 
@@
 are obtained by clustering stable hadrons, and not QCD partons). This implies that at the event-generation level, looser cuts (or no cuts at all) 
-must be emplouyed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
+must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
 

### 2018-01-19 Draft/shower.tex
edits in shower.tex

--- 2018-01-11 Draft/shower.tex
@@
         {\sc POWHEG}  &  $1.3633 \pm 0.0004$  \\
-        {\sc VBFNLO}  &  $X \pm 0.0003$  \\
+        {\sc VBFNLO}  &  $1.339 \pm 0.$  \\
         \hline
         {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275) \pm 0.$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $X  \pm 0.$  \\
-        {\sc PHANTOM} &  $1.235  \pm 0.$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 (1.267)  \pm 0.$  \\
+        {\sc PHANTOM}+{\sc Pythia8} &  $1.235  \pm 0.$  \\
     \end{tabular}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the transverse momentum of the hardest jet.}
 \label{fig:PSpt1}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the transverse momentum of the second-hardest jet.}
 \label{fig:PSpt2}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j2.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j2.pdf}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the rapidity of the second-hardest jet.}
+\label{fig:PSy2}
 \end{figure*}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j3.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the rapidity of the third-hardest jet.}
 \label{fig:PSy3}
 \end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/z_j3.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/z_j3.pdf}
+\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the $z$ variable of the third-hardest jet.}
+\label{fig:PSz3}
+\end{figure*}

### 2018-01-22 Draft/contributions.tex
fix a bunch of typos

@@
-At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the QCD background $\mathcal{O}(\alphas^2\alpha^4)$ and the interference $\mathcal{O}(\alphas\alpha^5)$.\\
-The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
+At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$ and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.\\
+The three contributions to the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
 \begin{figure*}[hbt]

### 2018-01-22 Draft/definition.tex
Add a motivation and extend the introduction
- added a motivation (first paragraph)
- extended or added some explanations
- changed the process to include the `+ X`, since we are inclusive;
  TODO: make sure this is also used in the remaining document
- changes `section` and `Section` to `Sec.` if they are not at the
  beginning of a sentence (in `macros.tex` there are abbreviations for
  it so I assume that is the "correct" style)
- corrected some spelling mistakes
fix a bunch of typos

@@
-The scattering of two positively charge W bosons is proceeding at the LHC through the partonic process:
+The scattering of two positively charged W bosons is proceeding at the LHC through the partonic process:
 %
 \begin{equation}
- {\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}.
+\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}.
 \end{equation}
@@
 In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
-These type of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
-Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO})
+These types of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
+Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
 The VBS diagrams typically dominate the full process.
@@
 
-Finally, due to the specific colour structure of these two classes of amplitudes, there exists non-zero interferences.
+Finally, due to the specific colour structure of these two classes of amplitudes, there exist non-zero interferences.
 These are of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$ and are usually small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
@@
 The two W bosons are mostly produced centrally.
-This is in opposition with the QCD component which favour jets in the central region.
-Therefore, the event selection usually involve rapidity-difference and invariance mass cuts for the jets.
+This is in opposition with the QCD component which favours jets in the central region.
+Therefore, the event selection usually involves rapidity-difference and invariance mass cuts for the jets.
 This will also be discussed in Section \ref{subsec:contributions}.

### 2018-01-22 Draft/description.tex
fix a bunch of typos

@@
         Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
-        Frederix:2016rdc}) for regulating IR singularities. The computationsof one-loop amplitudes are carried out by switching dynamically between 
+        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
         two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
@@
 
-  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for mathcing NLO-QCD calculations with parton showers.
+  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for matching NLO-QCD calculations with parton showers.
 It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.

### 2018-01-22 Draft/input.tex
fix a bunch of typos

@@
 with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alphas\left( \MZ \right) = 0.118$. Since
-the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
+the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularities are factorised with the  ${\overline{\rm MS}}$
 scheme, consistently with what is done in NNPDF.\\
@@
         \end{align}
-    \item QCD partons (quark and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
+    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
         to have

### 2018-01-22 Draft/introduction.tex
fix a bunch of typos

@@
 The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge- and unitarity cancellations that strongly depend on the actual form of the Higgs-sector.
-A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-standard model Higgs bosons.
+A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-Standard Model Higgs bosons.
 
-The process with two positively charged W boson is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
+The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
 For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
@@
 As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
-In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in later.
+In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more detail later.
 To our knowledge, such a detailed study was still missing.

### 2018-01-22 Draft/process.tex
fix a bunch of typos

@@
 Such an approximation is implemented at LO in the computer codes {\sc Bonsay} and {\sc Powheg}.
-The physical origin of this approximation is that each proton emitting a quark represent two independent copies of $SU_c\left(3\right)$ gauge group.
+The physical origin of this approximation is that each proton emitting a quark represents two independent copies of the $SU_c\left(3\right)$ gauge group.
 
@@
 This approximation can be used in combination with a double-pole approximation [REF] for the virtual contribution.
-This require the computation of factorisable as well as non-factorisable corrections \cite{Dittmaier:2015bfe} separately.
+This requires the computation of factorisable as well as non-factorisable corrections \cite{Dittmaier:2015bfe} separately.
 Such an approximation is implemented in {\sc Bonsay}.

### 2018-01-24 Draft/scanNLO.tex
scanNLO.tex: written intro, added plots and total Xsec

@@
-Scan at NLO
+We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha^6\alpha_s)$.\\
+According to the results shown in sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{jj} < 200$ GeV, $|\Delta y_{jj}| < 2$; moreover, we would like to validate this approximation (and its extension to $s$--channels inclusion) at the NLO accuracy.
+Thus, we impose the same kinematic cuts shown in sec.~\ref{subsec:inputpar} relaxing the VBF cuts and asking for
+\begin{equation}
+	m_{jj} > 200 \,\textrm{GeV}\,,\qquad |\Delta y_{jj}| > 2\,.
+\end{equation}
+We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc Vbfnlo} adds the $s--$channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha^5\alpha_s)$ interference.
+The total cross--sections within the above mentioned kinematic cuts are shown in table~\ref{tab:crosssecINCLUSIVE}
+\begin{table}[h!]
+\centering
+\begin{tabular}{c|c|c} 
+\bf Matrix--element & $\sigma_{\textrm{tot}}\,[\textrm{fb}]$ & $\delta$ \\
+\hline
+\hline
+full &  1.8120 $\pm$ 0.0144 & - \\
+\hline
+$|t|^2 + |u|^2$ & 1.6292 $\pm$ 0.0001  &  -10 \% \\
+\hline
+$|s|^2 + |t|^2 + |u|^2$ & 1.7780 $\pm$ 0.0001  & -2 \%
+\end{tabular}
+\caption{Total cross--sections at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, with $m_{jj}>200$ GeV, $|\Delta y_{jj}|>2$.}
+\end{table}\label{tab:crosssecINCLUSIVE}
 
+{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ distributions, mainly in the region $200 < m_{jj} < 500$ and $2<|\Delta y_{jj}|<2.5$.}
 \begin{figure}[hbt]
 \centering
-\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}
-FIGURE
-\caption{Cross section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$.
-Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations.}\label{fig:mjjdyjj_2d_NLO}
+{\includegraphics[scale=0.35]{mjj_nlo.pdf}}
+{\includegraphics[scale=0.35]{dyjj_nlo.pdf}}
+\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_1}
+\end{figure}
+
+{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ 2D scan: s--channels yes/no, left discrepancies after s--channel inclusion.}
+\begin{figure}[h]
+\centering
+{\includegraphics[scale=0.39]{a6as_vbfnloVSrecola_tu.pdf}} 
+%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
+\caption{Cross sections (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$.
+Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:ratio2d_NLO}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
-%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$.
-Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations.}\label{fig:ratio2d_NLO}
+{\includegraphics[scale=0.39]{a6as_vbfnloVSrecola_stu.pdf}}
+\caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$.
+Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:mjjdyjj_2d_NLO}
 \end{figure}
+
+{\bf GP: Comment on the other distributions: all the plots ?}
+\begin{figure}[hbt]
+\centering
+{\includegraphics[scale=0.35]{ptj1_nlo.pdf}}
+{\includegraphics[scale=0.35]{ptj2_nlo.pdf}}
+\caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_2}
+\end{figure}
+
+\begin{figure}[hbt]
+\centering
+\fbox{\includegraphics[scale=0.35]{ptj3_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{yj1_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{yj2_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{mll_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{zel_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{zmu_nlo.pdf}}
+\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
+\end{figure}
+
+{\bf GP: Maybe a separate subsection for the analysis of the third jet kinematics with LO accuracy ?}

### 2018-01-25 Draft/scanNLO.tex
Update scanNLO.tex

@@
 \centering
-{\includegraphics[scale=0.35]{mjj_nlo.pdf}}
-{\includegraphics[scale=0.35]{dyjj_nlo.pdf}}
+{\includegraphics[scale=0.35]{figures/scanfigures/mjj_nlo.pdf}}
+{\includegraphics[scale=0.35]{figures/scanfigures/dyjj_nlo.pdf}}
 \caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_1}
@@
 \centering
-{\includegraphics[scale=0.39]{a6as_vbfnloVSrecola_tu.pdf}} 
+{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}} 
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
@@
 \centering
-{\includegraphics[scale=0.39]{a6as_vbfnloVSrecola_stu.pdf}}
+{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
 \caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
@@
 \centering
-{\includegraphics[scale=0.35]{ptj1_nlo.pdf}}
-{\includegraphics[scale=0.35]{ptj2_nlo.pdf}}
+{\includegraphics[scale=0.35]{figures/scanfigures/ptj1_nlo.pdf}}
+{\includegraphics[scale=0.35]{figures/scanfigures/ptj2_nlo.pdf}}
 \caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_2}
@@
 \centering
-\fbox{\includegraphics[scale=0.35]{ptj3_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{yj1_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{yj2_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{mll_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{zel_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{zmu_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
+\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
 \caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}

### 2018-01-26 Draft/introduction.tex
Remove usepackage{siunitx} as it seems not be a default package. Replace in the introduction TeV

@@
 
-The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
+The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \TeV data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \TeV data.
 For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.

### 2018-01-26 Draft/abstract.tex
series of imporvements, corrections from the beginning up to section 3.3

@@
 This allows to infer precisely the quality of such approximations.
-Finally, NLO predictions matched to various parton shower are discussed.
-This study allows thus to infer the systematic errors related to vector-boson scattering at the NLO-QCD level and beyond.
+Finally, NLO predictions matched to various parton shower are also discussed.
+Thanks to this, it is thus possible to infer the systematic errors related to vector-boson scattering at the NLO-QCD level and beyond.
 

### 2018-01-26 Draft/definition.tex
series of imporvements, corrections from the beginning up to section 3.3

@@
 This process possesses three LO contributions of different orders.
-The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ is referred to as EW contributions.
+The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as EW contributions.
 In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
@@
 This is in opposition with the QCD component which favours jets in the central region.
-Therefore, the event selection usually involves rapidity-difference and invariance mass cuts for the jets.
+Therefore, the event selection usually involves rapidity-difference and invariance-mass cuts for the jets.
 This will also be discussed in Section \ref{subsec:contributions}.

### 2018-01-26 Draft/description.tex
series of imporvements, corrections from the beginning up to section 3.3

@@
 
-  \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
-  and $e^+e^-$ colliders at $\alpha^6$ and $\alpha^4\alphas^2$ including interferences between the two sets of diagrams.
-It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity
-formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{BERENDS1985441} and an adaptive
-strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}
+  \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states at $\Pp \Pp,\, \Pp\bar{\Pp}$
+  and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alpha^4\alphas^2$ including interferences between the two sets of diagrams.
+It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:2006ic} computed via the modular helicity
+formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive
+strategy~\cite{Lepage:1977sw}. {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of BSM theories.
 
@@
 
-  \item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
-To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
-These tools have been successfully used for the computation of NLO corrections for VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
+\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
+The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
+The IR divergences appearing in the real corrections are handles with the help of the Cantani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
+To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
+These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particlar VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
 

### 2018-01-26 Draft/process.tex
series of imporvements, corrections from the beginning up to section 3.3

@@
 
-A further refinement is to consider the full real contributions as well as part of the virtual \MP{I cannot remember exactly what is included}.
-This assumes a cancellation of infrared poles.
+A further refinement is to consider the full real contributions as well as part of the virtual.
+In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and assuming a cancellation of the infrared (IR) poles.
+\MP{True?
+I cannot remember exactly what is included}.
 Such predictions are provided by {\sc MG5\_aMC}.
 
-Finally the full computation implies to also consider EW corrections in the virtual as well as real corrections \cite{Biedermann:2017bss}.
-Such full predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
+Finally the full $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ computation consists also of EW corrections in the virtual as well as real corrections \cite{Biedermann:2017bss}.
+Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
 

### 2018-01-26 Draft/description.tex
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

@@
 In the comparison, the following codes are used:
+
 \begin{itemize}
- \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
-and matrix elements taken from several sources: Born matrix elements are
-adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
-processes, real matrix elements are written by Marina Billoni, and virtual
-matrix elements by Stefan Dittmaier.
-One loop integrals are evaluated using the {\sc Collier} library
-\cite{Denner:2014gla,Denner:2016kdg}.
+
+ \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator and matrix elements taken from several sources.
+ Born matrix elements are adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic processes, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
+One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
 
@@
 
-  \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states at $\Pp \Pp,\, \Pp\bar{\Pp}$
-  and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alpha^4\alphas^2$ including interferences between the two sets of diagrams.
-It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:2006ic} computed via the modular helicity
-formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive
-strategy~\cite{Lepage:1977sw}. {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of BSM theories.
+  \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states 
+  at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alphas^2\alpha^4$ including interferences between the two sets of diagrams.
+It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
+The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
+{\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of BSM theories.
 
@@
 
-\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
+\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
 The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
@@
 \end{itemize}
-
-%
-%

### 2018-01-26 Draft/input.tex
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

@@
-We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton
-density~\cite{Ball:2014uwa}
-with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alphas\left( \MZ \right) = 0.118$. Since
-the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularities are factorised with the  ${\overline{\rm MS}}$
-scheme, consistently with what is done in NNPDF.\\
-We use the following values for the mass and width of the massive particles:
+The VBS production mechanism is simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$. 
+The five flavour scheme is used and the NNPDF~3.0 parton density~\cite{Ball:2014uwa} with NLO QCD evolution is employed and strong coupling constant $\alphas\left( \MZ \right) = 0.118$.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
+Since the employed PDF set has no photonic density, photon-induced processes are not considered.
+Initial-state collinear singularities are factorised with the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
+
+For the mass and width of the massive particles, the following values are used:
 %
@@
 \end{alignat}
-and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
+%
+and the EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
+%
 \begin{equation}
@@
 \end{equation}
-The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is
+%
+The numerical value of $\alpha$, corresponding to the choice of input parameters, is
+%
 \begin{equation}
- \alpha = 7.555310522369 \times 10^{-3}. \\
+ \alpha = 7.555310522369 \times 10^{-3}.
 \end{equation}
-We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\
+%
+The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.
 
-The renormalisation and factorisation scales are set dynamically as
+The renormalisation and factorisation scales are set dynamically to
 %
@@
 \label{eq:defscale}
- \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}},
+ \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}.
 \end{equation}
+%
+This choice of scale has been shown to provide stable NLO predictions \cite{Denner:2012dz}.
 
-Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}:
+The cross sections and distribution are computed within the following event selecton.
+These are inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}.
+
 \begin{itemize}

### 2018-01-26 Draft/introduction.tex
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

@@
 Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
-It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs and can be longitudinally polarized.
-The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge- and unitarity cancellations that strongly depend on the actual form of the Higgs-sector.
-A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-Standard Model Higgs bosons.
+It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarized.
+The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual form of the Higgs sector.
+A detailed study of this class of processes will therefore further constrain the Higgs couplings and hint at or exclude non-Standard Model Higgs bosons.
 
-The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \TeV data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \TeV data.
+The process with two positively charged W bosons is the VBS process with the largest signal-to-background ratio at the LHC, for which evidence has been found in $8 \TeV$ data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in $13\TeV$ data.
 For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
@@
 
-The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because the double-charge structure of the leptonic final state limits the number of partonic processes and total number of Feynman diagrams for each process.
-It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg $\PW^+\PW^-$ scattering, which has the largest cross section.
-Therefore, it is an ideal candidate for a detailed study of various theoretical predictions.
+The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because of the double-charge structure of the leptonic final state that limits the number of partonic processes and total number of Feynman diagrams for each process.
+It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg to $\PW^+\PW^-$ scattering, which has the largest cross section.
+Therefore, the $\PW^+\PW^+$ scattering is an ideal candidate for a detailed study of various theoretical predictions.
 
@@
 Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
-Preliminary results have already been made public in Ref.~[proceedings Split].
+Preliminary results have already been made public in %Ref.~\cite{Anders:2018gfr}.
 
@@
 Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
-This allows to identify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
+This allows to quantify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
 This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.
@@
 The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
-In the following, this order is the one where our comparisons are focused on; in this article we will refer to it as simply \emph{NLO}.
+In the following, this order is the one where our comparisons are focused on.
+In this article we will refer to it as simply \emph{NLO}.
 As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
@@
 
-Obviously all VBS processes deserve such a study but the present article sets the standard for inferring systematics related to NLO corrections and beyond.
+Obviously all VBS processes deserve such a detailed study but the present article sets standards for inferring systematics related to NLO corrections and beyond.
 
 The article is organised as follow:
-In Sec.~\ref{sec:definition} the studied process is defined.
+in Sec.~\ref{sec:definition} the studied process is defined.
 Various approximation at LO and NLO are described in Sec.~\ref{sec:details}.

### 2018-01-26 Draft/shower.tex
fix a bunch of typos
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

--- 2018-01-19 Draft/shower.tex
@@
 {\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
-matching, in both cases together with {\sc Herwig7}~\cite{}. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8}.
+matching, in both cases together with {\sc Herwig7}~CITEREF. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8}.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\
@@
 are obtained by clustering stable hadrons, and not QCD partons). This implies that at the event-generation level, looser cuts (or no cuts at all)
-must be emplouyed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
+must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
 

### 2018-01-28 Draft/contributions.tex
Some further work on the draft. Note that the hyperref package is commented as it seems that is was the origin of the problems I had. We will put it back at the end before we submit.

@@
-At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$ and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.\\
-The three contributions to the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
+At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$ and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
+In the present section, the cross sections and distributions are obtained without applying the typical VBS cuts $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
+In Table~\ref{tab:LOscanXsec}, the cross section of the three contributions are displayed.
+The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
+The QCD contribution does not posses external gluons due to charge conservation.
+Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchanged in the $t/u$-channel between the quark lines.
+This results in a small contributions although the VBS cuts have not been imposed.
+The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|c|c|c}
+        Order & $ \mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
+        \hline
+        \hline
+        $\sigma[\rm{fb}]$ & $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
+%         {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
+    \end{tabular}
+    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.
+    These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}
+\end{table}
+
+In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
+Interestingly, the EW contributions peaks around and invariant mass of about $80\GeV$.
+These are due to contributions where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
+Note that these contributions are not present in calculation relying on the VBS approximation.
+Also, the EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$ and for jet rapidity difference larger than $2.5$.
+
 \begin{figure*}[hbt]
@@
 \includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
-\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO.
-EW contribution in red, QCD in green, interference in gray and sum in blue.
-No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied.
-Results of full LO matrix element simulation.}
+\caption{Differential distribution in the di-jet invariant mass $m_{\Pj\Pj}$ (left) and the difference of the jet rapidities $|\Delta y_{\Pj\Pj}|$ (right) at LO.
+The EW contribution is in red, the QCD one in green, and the interference in grey.
+The sum of all the contributions is in blue.
+No cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
+\MP{On the plots: it should be $\alpha$ and not $\alpha_{em}$ and $m_{\Pj\Pj}$ instead of $M_{jj}$. And we have the convention to put $\alphas$ before $\alpha$.}}
 \label{fig:mjjdyjj_1d}
 \end{figure*}
-Concerning the QCD contribution, it is worth noticing that for quantum number conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed.
-The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).
-The LO cross--section for the three perturbative orders are shown in table~\ref{tab:LOscanXsec}.
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas^2\alpha^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas\alpha^5))$ \\
-        \hline
-        \hline
-        {\sc Phantom}  &  $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
-        {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
-    \end{tabular}
-    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process: these results concern the setup described in section~\ref{subsec:inputpar}, apart from the $M_{jj}$ and $|\Delta y_{jj}|$ cuts which have been dropped.}
-\end{table}
-The EW, QCD and interference amount respectively to 57\%, 37\% and 6\% of the total inclusive cross section.
-In the presence of typical VBS cuts, the EW contribution is strongly enhanced, as shown in section~\ref{subsec:LOfiducial}.\\
-The EW contribution to the $M_{jj}$ distribution (red curve in Fig.~\ref{fig:mjjdyjj_1d}) shows a huge peak around the $W$ mass: this is due to the possibility for the two jets to be decay products of a $W^-$ boson.
-Note that this effect doesn't arise in calculations which employ VBS approximation (see VBS approx.
-description in section [ref.]).
-One can also see this in three different plots in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
+
+This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a function of the di-jet invariant mass and jet rapidity difference.
+Again, it is obvious that the region with low di-jet invariant mass and low jet-rapidity difference should be avoided.
+This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study.
+Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
+This is particularly explicit in Sec.~\ref{subsec:LOfiducial}.
+
 \begin{figure}[ht]
@@
 \includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
-\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alpha^5\alphas)$ (top right), and $\mathcal{O}(\alpha^4 \alphas^2)$ (bottom).}
+\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top), $\mathcal{O}(\alphas\alpha^5)$ (middle), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
+\MP{On the plots: it should be $\alpha$ and not $\alpha_{em}$ and $m_{\Pj\Pj}$ instead of $M_{jj}$. And we have the convention to put $\alphas$ before $\alpha$.}}
 \label{fig:mjjdyjj_2d_LO}

### 2018-01-28 Draft/crosssectionLO.tex
Some further work on the draft. Note that the hyperref package is commented as it seems that is was the origin of the problems I had. We will put it back at the end before we submit.

@@
- In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
-for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both cases we show the absolute distributions in the main frame of the 
-figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
-an excellent agreement among the various tools, which confirms the fact
-that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region. We have checked 
-that the same level of agreement holds for many other differential distributions.
+In Table~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts (Eq.~\ref{cut:4}).
+This is the order $\mathcal{O}(\alpha^6)$.
+
 \begin{table}[h!]

### 2018-01-28 Draft/distributionsLO.tex
Some further work on the draft. Note that the hyperref package is commented as it seems that is was the origin of the problems I had. We will put it back at the end before we submit.

@@
+In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass of the tagging-jet (left) and lepton-pair (right).
+In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over {\sc VBFNLO}.
+For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
+We have checked that the same level of agreement holds for many other differential distributions.
+
  \begin{figure}[h!]
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
+   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
+   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
 \caption{\label{fig:wg1_mjj-llLO} Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO accuracy, 

### 2018-01-28 Draft/input.tex
Some further work on the draft. Note that the hyperref package is commented as it seems that is was the origin of the problems I had. We will put it back at the end before we submit.

@@
 The VBS production mechanism is simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$. 
-The five flavour scheme is used and the NNPDF~3.0 parton density~\cite{Ball:2014uwa} with NLO QCD evolution is employed and strong coupling constant $\alphas\left( \MZ \right) = 0.118$.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
+The NNPDF~3.0 parton density~\cite{Ball:2014uwa} with five flavour scheme, NLO QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ is employed.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
 Since the employed PDF set has no photonic density, photon-induced processes are not considered.
@@
                 \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
-                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
+                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
 \end{alignat}
 %
-and the EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
+The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
 %
@@
 %
-The numerical value of $\alpha$, corresponding to the choice of input parameters, is
+The numerical value of $\alpha$, corresponding to the choice of input parameters is
 %
@@
 
-The cross sections and distribution are computed within the following event selecton.
-These are inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}.
+Following experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}, the event selection used in the present study is:
 
@@
         \begin{align}
+        \label{cut:1}
          \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
         \end{align}
-    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
-        is required to be
+    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
         \begin{align}
+        \label{cut:2}
           \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
@@
         \begin{align}
+        \label{cut:3}
          \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
         \end{align}
-        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
+        Typically, on the two jets with largest transverse-momentum VBS cuts are applied.
+        These are an invariant-mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
+        The nominal value of these cuts if not stated explicitly read:
         \begin{align}
+        \label{cut:4}
          m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
         \end{align}
-%         Finally, all jest in the event are required to be separated from charged leptons:
-%         \begin{align}
-%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
-%         \end{align}
     \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
-        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
-        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
+        radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
 \end{itemize}

### 2018-01-28 Draft/description.tex
small typos fixed

@@
 The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
-The IR divergences appearing in the real corrections are handles with the help of the Cantani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
+The IR divergences appearing in the real corrections are handles with the help of the Catani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
 To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
-These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particlar VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
+These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particular VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
 

### 2018-01-29 parton-shower/rivetplot.sh
Redo parton shower plots

@@ -8,11 +8,18 @@ rivet-mkhtml -o rivet-NLOPS \
 :"RatioPlotErrorBandColor=red"\
 :"ErrorBandOpacity=0.3"\
   VBFNLO/Herwig-MCatNLO-DipoleShower.yoda\
-:"Title=VBFNLO 3+Herwig 7"\
+:"Title=VBFNLO 3+Herwig 7-Dipole"\
 :"LineColor=blue"\
 :"ErrorBands=1"\
 :"ErrorBandColor=blue"\
 :"RatioPlotErrorBandColor=blue"\
+:"ErrorBandOpacity=0.3"\
+  VBFNLO/Herwig-MCatNLO-DefaultShower.yoda\
+:"Title=VBFNLO 3+Herwig 7-QTilde"\
+:"LineColor=cyan"\
+:"ErrorBands=1"\
+:"ErrorBandColor=cyan"\
+:"RatioPlotErrorBandColor=cyan"\
 :"ErrorBandOpacity=0.3"\
   Powheg/Powheg.yoda\
 :"Title=Powheg+Pythia 8"\
@@ -63,7 +70,7 @@ rivet-mkhtml -o rivet-LOPS \
 :"RatioPlotErrorBandColor=brown"\
 :"ErrorBandOpacity=0.3"\
   MG5_aMC/run_HWPP_1M_LOPS.yoda\
-:"Title=MG5_aMC+Herwig 2.7.1"\
+:"Title=MG5_aMC+Herwig++ 2.7.1"\
 :"LineColor=magenta"\
 :"ErrorBands=1"\
 :"ErrorBandColor=magenta"\
@@ -75,4 +82,11 @@ rivet-mkhtml -o rivet-LOPS \
 :"ErrorBands=1"\
 :"ErrorBandColor=cyan"\
 :"RatioPlotErrorBandColor=cyan"\
+:"ErrorBandOpacity=0.3"\
+  PHANTOM/plots_loose_cuts2/phantom_norm_hwpp-scaled.yoda\
+:"Title=PHANTOM+Herwig++ 2.7.1"\
+:"LineColor=green"\
+:"ErrorBands=1"\
+:"ErrorBandColor=green"\
+:"RatioPlotErrorBandColor=green"\
 :"ErrorBandOpacity=0.3"\

### 2018-01-29 Draft/scanNLO.tex
fix typos in article and apply convention to put alphas before alpha.

@@
-We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha^6\alpha_s)$.\\
+We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha_s\alpha^6)$.\\
 According to the results shown in sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{jj} < 200$ GeV, $|\Delta y_{jj}| < 2$; moreover, we would like to validate this approximation (and its extension to $s$--channels inclusion) at the NLO accuracy.
@@
 \end{equation}
-We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc Vbfnlo} adds the $s--$channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha^5\alpha_s)$ interference.
-The total cross--sections within the above mentioned kinematic cuts are shown in table~\ref{tab:crosssecINCLUSIVE}
+We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc Vbfnlo} adds the s--channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha_s\alpha^5)$ interference.
+The total cross sections within the above mentioned kinematic cuts are shown in table~\ref{tab:crosssecINCLUSIVE}
 \begin{table}[h!]
@@
 \end{tabular}
-\caption{Total cross--sections at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, with $m_{jj}>200$ GeV, $|\Delta y_{jj}|>2$.}
+\caption{Total cross--sections at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, with $m_{jj}>200$ GeV, $|\Delta y_{jj}|>2$.}
 \end{table}\label{tab:crosssecINCLUSIVE}
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/dyjj_nlo.pdf}}
-\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_1}
+\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_1}
 \end{figure}
@@
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-\caption{Cross sections (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
+\caption{Cross sections (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$.
@@
 {\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-\caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
+\caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$.
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/ptj2_nlo.pdf}}
-\caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_2}
+\caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
 \end{figure}

### 2018-01-29 Draft/contributions.tex

@@
 The QCD contribution does not posses external gluons due to charge conservation.
-Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchanged in the $t/u$-channel between the quark lines.
-This results in a small contributions although the VBS cuts have not been imposed.
+Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchange in the $t/u$-channel between the quark lines.
+This results in a small contribution although the VBS cuts have not been imposed.
 The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).

### 2018-01-29 Draft/crosssectionLO.tex

@@
         {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
-        {\sc PHANTOM}&  $1.4374 \pm 0.0006 $  \\
+        {\sc PHANTOM} &  $1.4374 \pm 0.0006 $  \\
         {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\
         {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
-        {\sc Whizard}&  $1.4360 \pm 0.0005 $
+        {\sc Whizard} &  $1.4381 \pm 0.0002 $
     \end{tabular}

### 2018-01-30 Draft/scanNLO.tex
commented some plots in scanNLO.tex

@@
 
-\begin{figure}[hbt]
-\centering
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
-\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
-\end{figure}
+%\begin{figure}[hbt]
+%\centering
+%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
+%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
+%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
+%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
+%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
+%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
+%\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
+%\end{figure}
 

### 2018-01-31 parton-shower/rivetplot.sh
Use LO file for MG5_PY8 LO distribs

@@ -62,7 +62,7 @@ rivet-mkhtml -o rivet-LOPS \
 :"ErrorBandColor=blue"\
 :"RatioPlotErrorBandColor=blue"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_PY8_10M_NLOPS.yoda\
+  MG5_aMC/run_PY8_1M_LOPS.yoda\
 :"Title=MG5_aMC+Pythia 8"\
 :"LineColor=brown"\
 :"ErrorBands=1"\

### 2018-01-31 Draft/scanNLO.tex
scanNLO: plots modifications and selection

--- 2018-01-29 Draft/scanNLO.tex
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/ptj1_nlo.pdf}}
-{\includegraphics[scale=0.35]{figures/scanfigures/ptj2_nlo.pdf}}
-\caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
+{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
+\caption{NLO QCD inclusive study: transverse momentum and rapidity distributions of the leading jet, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
 \end{figure}
@@
 \centering
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
-\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
-\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
+{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
+{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
+\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
 \end{figure}

### 2018-01-31 Draft/shower.tex

@@
 on the results.
-
-We now turn to present the results:
-
+%
 \begin{table}[h!]
@@
         {\sc PHANTOM}+{\sc Pythia8} &  $1.235  \pm 0.$  \\
+        {\sc PHANTOM}+{\sc Herwig++} &  $1.260  \pm 0.$  \\
     \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
+    \caption{\label{tab:PSrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
     for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
@@
 \end{table}
+%
+We now turn to present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in in Table~\ref{tab:PSrates}, both at LO and NLO 
+accuracy. For {\sc MG5\_aMC}, the number in parentheses are rescaled to take into account the width effects described in the above paragraph. Once this effect is taken into
+account, total rates from different tools agree within few percents. Larger discrepancies however will appear for differential observables, which we are going to discuss in 
+the following. For any observable, results will be presented in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown 
+with different colours in the main frame. In the inset, these predictions are compared in both cases with the fixed-order prediciton at NLO accuracy (obtained with 
+{\sc VBFNLO}). For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.\\
+
+The first observable we invesigate is the exclusive jet multiplicity, shown in Figure~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
+main effects are driven by the parton shower that is employed {\sc Herwig++/7} or {\sc Pythia8}, with the clear tendency of producing more radiation for the latter, 
+leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
+initial scale of the shower. The main effect of NLO corrections for this (rather inclusive) observable is to stabilize the predictions for the two-jet bin, where discrepancies 
+among tools are reduced to about 10\%. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
+{\sc MG5\_aMC}, while the smallest by {\sc Powheg}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
+is different among the two tools. In particular, for {\sc Powheg}, the first emission is generated with an internal Sudakov form factor (the
+prediction dubbed {\sc Powheg-no shower} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
+interplay between the real-emission matrix element and the shower emission. \\
+The next observable that we study is the invariant mass of the two tagging jets, shown in Figure~\ref{fig:PSmjj}. For this observable, both at LO+PS and NLO+PS,
+the spread of predictions matched with parton shower is rather small
+($\lesssim 10\%$, if one compensates for the 6\% width effect for {\sc MG5\_aMC}); LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of 
+about -30\% at the end of the displayed range. At NLO+PS, this effect is much mitigated, owing to the better description of the first QCD emission which is now driven by  
+ the real-emission matrix element.\\
+The rapidity difference between the two tagging jets, shown in Figure~\ref{fig:PSdyjj} has some similarities to the invariant-mass distribution: at LO+PS all predictions, 
+except for {\sc VBFNLO3+Herwig7} where the effect is mitigated, show the tendency to deplete the large-separation region with respect to the fixed-order predicion, in a 
+quantitatively similar way. At NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable 
+exception is the {\sc Powheg} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
+it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the 
+{\sc MG5\_aMC+Herwig++} prediction (although with rather large statistical uncertainties).\\
+The transverse momentum of the hardest and second-hardest jets are shown in Figures~\ref{fig:PSpt1} and~\ref{fig:PSpt2} respectively. In general, for both observables, 
+predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transvers-momentum spectra are softer than
+the fixed-NLO one, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
+effect is mitigated by NLO corrections. The only feature that it may be worth to notice among the NLO+PS predictions is the tendency of {\sc Powheg} to suppress the
+hardest-jet spectrum at low transverse momentum ($p_T<100 \GeV$).\\
+If we consider the rapidity of the second jet, Figure~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general 
+stabilization at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions 
+obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; {\sc Powheg}\ displays an enhancement of the central region, and a consequent suppression in the
+peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being 
+at most 10\%.\\
+Finally, we conclude the list of differential observable with two observables related to the third jet, the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}. 
+{\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper sectiomn. Otherwise define it here} 
+In general, for observables which involve the third jet, one 
+can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The rapidity and $z$ variable
+are a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation (corresponding to low values of $z$) 
+is clearly visible; it is interesting to notice that
+this effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+Pythia8}. If it is true that the central enhancement
+is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC} with the fixed-NLO prediciton), however even at NLO+PS the central region 
+($z_{j_3}<0.5$) is cursed by huge differences between tools. Large differences, reaching a factor 2, persist also away from the central region. \\
+
+In conclusion, the comparison of tools including matching with parton-shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
+effectively at NLO accuracy differences between tools are at (or below) the 10\% level. {\bf MZ compare this number with scale uncertainties} 
+Some exceptions exist, e.g. the rapidity separation of the two tagging jets, which
+on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it still worth to investigate more in details the way QCD radiation is 
+generated {\bf MZ cite here H VBF at NNLO?}.
+Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
+experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory uncertainties. In order to improve the
+description of these observables, a simulation of VBS+j at NLO, currently unavailable but within the reach of modern automated tools, is certainly desirable.
 

### 2018-01-31 parton-shower/cpfigures.sh
Update figures in article

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-FIGS="jetsexclusive m_jj pT_j1 pT_j2 Deltay_jj y_j3"
+FIGS="jetsexclusive m_jj pT_j1 pT_j2 y_j2 Deltay_jj y_j3 z_j3"
 
 for ORD in LOPS NLOPS; do
     for F in $FIGS; do

### 2018-02-01 Draft/shower.tex
small changes in shower.tex

@@
 this effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+Pythia8}. If it is true that the central enhancement
-is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC} with the fixed-NLO prediciton), however even at NLO+PS the central region 
+is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediciton), however even at NLO+PS the central region 
 ($z_{j_3}<0.5$) is cursed by huge differences between tools. Large differences, reaching a factor 2, persist also away from the central region. \\
@@
 Some exceptions exist, e.g. the rapidity separation of the two tagging jets, which
-on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it still worth to investigate more in details the way QCD radiation is 
+on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is 
 generated {\bf MZ cite here H VBF at NNLO?}.

### 2018-02-01 Draft/shower.tex
Update small correction shower.tex

@@
 {\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
-matching, in both cases together with {\sc Herwig7}~CITEREF. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8}.
+matching, in both cases together with {\sc Herwig7}~CITEREF. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\
@@
 Results will be presented within the cuts described in Section~\ref{subsec:inputpar}, applied after shower and hadronization (this implies that jets
-are obtained by clustering stable hadrons, and not QCD partons). This implies that at the event-generation level, looser cuts (or no cuts at all)
+are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or no cuts at all)
 must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
@@
 
-The first observable we invesigate is the exclusive jet multiplicity, shown in Figure~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
+The first observable we investigate is the exclusive jet multiplicity, shown in Figure~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
 main effects are driven by the parton shower that is employed {\sc Herwig++/7} or {\sc Pythia8}, with the clear tendency of producing more radiation for the latter, 
@@
 at most 10\%.\\
-Finally, we conclude the list of differential observable with two observables related to the third jet, the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}. 
-{\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper sectiomn. Otherwise define it here} 
+Finally, focusing on the third jet, we conclude the list of differential observable with the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}. 
+{\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper section. Otherwise define it here} 
 In general, for observables which involve the third jet, one 

### 2018-02-01 Draft/scanNLO.tex
scanNLO.tex: text added and refined

@@
 \end{equation}
-We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc Vbfnlo} adds the s--channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha_s\alpha^5)$ interference.
+We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc VBFNLO} adds the s--channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha_s\alpha^5)$ interference.
 The total cross sections within the above mentioned kinematic cuts are shown in table~\ref{tab:crosssecINCLUSIVE}
@@
 \end{tabular}
-\caption{Total cross--sections at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, with $m_{jj}>200$ GeV, $|\Delta y_{jj}|>2$.}
-\end{table}\label{tab:crosssecINCLUSIVE}
-
-{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ distributions, mainly in the region $200 < m_{jj} < 500$ and $2<|\Delta y_{jj}|<2.5$.}
+\caption{\label{tab:crosssecINCLUSIVE}Total cross--sections at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, with $m_{jj}>200$ GeV, $|\Delta y_{jj}|>2$.}
+\end{table}
+The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) gives a negative discrepancy of about 10 \% w.r.t the full calculation; the inclusion of $s$--channel diagrams improves the approximate prediction up to a 2 \% discrepancy.\\
+These discrepancies are much more evident in differential cross--sections.\\
+In fig.~\ref{fig:mjjdyjj_1d_1} we show the distributions in the jet--jet invariant mass $m_{jj}$ and rapidity separation $\Delta y_{jj}$: at large $m_{jj}$ and large $\Delta y_{jj}$ the VBS approximation and its $s$--channel extension agree with the full calculation within few percents.
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/dyjj_nlo.pdf}}
-\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_1}
+\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_1}
 \end{figure}
-
-{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ 2D scan: s--channels yes/no, left discrepancies after s--channel inclusion.}
+Focussing on the region  $200 \GeV < m_{jj} < 500 \GeV$ and $2<|\Delta y_{jj}|<2.5$, the negative discrepancy between the $t|^2 + |u|^2$ approximation and the full computation is enhanced by up to 30 \%.
+The inclusion of $s$--channels cures the discrepancy in these regions; still, in the very low $m_{jj}$ a small discrepancy ($\approx$ 5 \%) becomes positive pointing out that also interferences (GP: and non--factorizable QCD corrections ?) are needed.\\
+In order to investigate further the jet pair kinematics, we divide the $m_{jj},\Delta y_{jj}$ plane in 2--dimensional bins and analyze the cross--sections: in particular we compute in each bin the ratio of the approximated cross--section over the full one.
+In fig.~\ref{fig:ratio2d_NLO} and fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.
 \begin{figure}[h]
 \centering
-{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}}
+{\includegraphics[scale=0.39]{figures/scanfigures/a6as_VBFNLOVSrecola_tu.pdf}}
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
@@
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$.
-Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:ratio2d_NLO}
+Results of {\sc Bonsay} (approximated) and {\sc Recola} (full) calculations.
+{\bf GP: notation to be changed, Mjj > mjj, alphas alpha} }\label{fig:ratio2d_NLO}
 \end{figure}
-
 \begin{figure}[hbt]
 \centering
-{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
+{\includegraphics[scale=0.39]{figures/scanfigures/a6as_VBFNLOVSrecola_stu.pdf}}
 \caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$.
-Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:mjjdyjj_2d_NLO}
+Results of {\sc VBFNLO} (approximated) and {\sc Recola} (full) calculations.
+{\bf GP: notation to be changed, Mjj > mjj, alphas alpha}}\label{fig:mjjdyjj_2d_NLO}
 \end{figure}
-
-{\bf GP: Comment on the other distributions: all the plots ?}
+As expected, in the low invariant mass--low rapidity separation region of the jet--jet pair the VBS approximation fails badly (up to 40 \% discrepancies) and the $s$--channel inclusion lead to discrepancies of at most 5 \%.
+However, the positive discrepancy shown in the low $m_{jj}$ region (black curve, fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{jj}$, large $\Delta y_{jj}$ region of fig.~\ref{fig:mjjdyjj_2d_NLO}, where the two leading jets have soft transverse momenta, according to
+\[
+m_{jj}^2 = 2\,p_t^{j_1}p_t^{j_2}\,(\cosh \Delta y_{jj} - \cos \Delta\phi_{jj}) \approx 2\,p_t^{j_1}p_t^{j_2}\,\cosh \Delta y_{jj} \,\,.
+\]
+The same positive discrepancy of the $|s|^2 + |t|^2 + |u|^2$ approximation, in fact, can be seen in the low $p_t$ region of the leading jet in the left panel of fig.~\ref{fig:mjjdyjj_1d_2}.\\
+In the large invariant mass--small rapidity separation region of fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the 15 \% level are left: this can be traced back to the large $p_t$ and central rapidity region of the leading jets kinematics, shown in fig.~\ref{fig:mjjdyjj_1d_2}.
+For such distributions, despite the $s$--channel inclusion, the discrepancy between the approximated and full result is about 5-10 \%.\\
+In the VBS signal region the VBS approximation it shows a good agreement with the full calculation.
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
-\caption{NLO QCD inclusive study: transverse momentum and rapidity distributions of the leading jet, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
+\caption{NLO QCD inclusive study: transverse momentum and rapidity distributions of the leading jet, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
 \end{figure}
 
+Concerning leptonic kinematcs, we show in fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton--lepton invariant mass and of the Zeppenfeld variable of the electron.
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
-\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
+\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
 \end{figure}
+{\bf GP: leptonic variables, comment further.}
 
-{\bf GP: Maybe a separate subsection for the analysis of the third jet kinematics with LO accuracy ?}
+In conclusion, both the loose minimum $jj$ invariant mass cut and the inclusion of QCD radiative correction make the $s$--channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
+Nevertheless, interferences and non--factorizable QCD corrections should be included to reduce the discrepancies down to the $\approx$ 1 \%  level, mainly in inclusive analyses.\\
+Instead, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($M_{jj} \gtrsim 600 \GeV$, $\Delta y_{jj} \gtrsim 3$), concerning both total cross--section and distributions.

### 2018-02-02 parton-shower/analysis_scpdfunc/MC_VBSCAN_MCComparison_scpdfunc.cc
added analysis with scale and PDF uncertainties

@@ -1,0 +1,285 @@
+// -*- C++ -*-
+#include "Rivet/Analysis.hh"
+#include "Rivet/Projections/FinalState.hh"
+#include "Rivet/Projections/FastJets.hh"
+#include "Rivet/Projections/MissingMomentum.hh"
+#include "Rivet/Projections/DressedLeptons.hh"
+#include "Rivet/Projections/PromptFinalState.hh"
+#include "Rivet/Projections/VetoedFinalState.hh"
+#include "YODA/Histo1D.h"
+
+namespace Rivet {
+
+  //MZ Make the histo array global
+  Rivet::Histo1DPtr  _h_fiducial[26][112];
+
+  /// @brief Add a short analysis description here
+  class MC_VBSCAN_MCComparison : public Analysis {
+  public:
+
+    /// Constructor
+    DEFAULT_RIVET_ANALYSIS_CTOR(MC_VBSCAN_MCComparison);
+
+
+    /// @name Analysis methods
+    //@{
+
+    /// Book histograms and initialise projections before the run
+    void init() {
+
+      // Complete final state
+      FinalState fs(-MAXDOUBLE, MAXDOUBLE, 0*GeV);
+
+      // Projection for dressed electrons and muons
+      IdentifiedFinalState photons(fs);
+      photons.acceptIdPair(PID::PHOTON);
+
+      IdentifiedFinalState el_id(fs);
+      el_id.acceptIdPair(PID::ELECTRON);
+      PromptFinalState electrons(el_id);
+      addProjection(electrons, "Electrons");
+      DressedLeptons dressed_electrons(photons, electrons, 0.1, Cuts::open(), true, false);
+      addProjection(dressed_electrons, "DressedElectrons");
+
+      IdentifiedFinalState mu_id(fs);
+      mu_id.acceptIdPair(PID::MUON);
+      PromptFinalState muons(mu_id);
+      addProjection(muons, "Muons");
+      DressedLeptons dressed_muons(photons, muons, 0.1, Cuts::open(), true, false);
+      addProjection(dressed_muons, "DressedMuons");
+
+      // Jets, anti-kt 0.4
[…]

### 2018-02-02 Draft/input.tex
Conversion pole/OS mass
Extend and correct descriptions in Secs. 2 and 3
- updated writing rules, use Sec.~\ref{X1} for consistency reasons
- defined what s-, t-, and u-channels are
- added explanation for the VBS approximation for the reals
- no non-factorisable corrections for the O(a^6 as) virtuals
- added sentence about CKM matrix

@@
 %
+The measured on-shell (OS) values for the masses and widths of the W and Z bosons are converted into pole values for the gauge bosons ($V=\PW,\PZ$) according to Ref.~\cite{Bardin:1988xt},
+%
+\begin{equation}
+\begin{split}
+        M_V &= \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,, \\
+   \Gamma_V &= \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
+\end{split}
+\end{equation}
+%
 The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
@@
 \end{equation}
+The CKM-Matrix is assumed to be diagonal, meaning that we neglect mixing between different quark families.
 %
@@
 
-The renormalisation and factorisation scales are set dynamically to
+The renormalisation and factorisation scales are set to the dynamical scale
 %

### 2018-02-02 Draft/scanNLO.tex
Extend and correct descriptions in Secs. 2 and 3
- updated writing rules, use Sec.~\ref{X1} for consistency reasons
- defined what s-, t-, and u-channels are
- added explanation for the VBS approximation for the reals
- no non-factorisable corrections for the O(a^6 as) virtuals
- added sentence about CKM matrix

@@
-We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha_s\alpha^6)$.\\
-According to the results shown in sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{jj} < 200$ GeV, $|\Delta y_{jj}| < 2$; moreover, we would like to validate this approximation (and its extension to $s$--channels inclusion) at the NLO accuracy.
-Thus, we impose the same kinematic cuts shown in sec.~\ref{subsec:inputpar} relaxing the VBF cuts and asking for
+We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha_s\alpha^6)$.
+
+According to the results shown in Sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{jj} < 200$ GeV, $|\Delta y_{jj}| < 2$; moreover, we would like to validate this approximation (and its extension to $s$--channels inclusion) at the NLO accuracy.
+Thus, we impose the same kinematic cuts shown in sec.~\ref{subsec:inputpar} relaxing the VBS cuts and asking for
 \begin{equation}
@@
 We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc VBFNLO} adds the s--channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha_s\alpha^5)$ interference.
-The total cross sections within the above mentioned kinematic cuts are shown in table~\ref{tab:crosssecINCLUSIVE}
+The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
 \begin{table}[h!]
@@
 These discrepancies are much more evident in differential cross--sections.\\
-In fig.~\ref{fig:mjjdyjj_1d_1} we show the distributions in the jet--jet invariant mass $m_{jj}$ and rapidity separation $\Delta y_{jj}$: at large $m_{jj}$ and large $\Delta y_{jj}$ the VBS approximation and its $s$--channel extension agree with the full calculation within few percents.
+In Fig.~\ref{fig:mjjdyjj_1d_1} we show the distributions in the jet--jet invariant mass $m_{jj}$ and rapidity separation $\Delta y_{jj}$: at large $m_{jj}$ and large $\Delta y_{jj}$ the VBS approximation and its $s$--channel extension agree with the full calculation within few percents.
 \begin{figure}[hbt]
@@
 \end{figure}
-Focussing on the region  $200 \GeV < m_{jj} < 500 \GeV$ and $2<|\Delta y_{jj}|<2.5$, the negative discrepancy between the $t|^2 + |u|^2$ approximation and the full computation is enhanced by up to 30 \%.
+Focussing on the region  $200 \GeV < m_{jj} < 500 \GeV$ and $2<|\Delta y_{jj}|<2.5$, the negative discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation is enhanced by up to 30 \%.
 The inclusion of $s$--channels cures the discrepancy in these regions; still, in the very low $m_{jj}$ a small discrepancy ($\approx$ 5 \%) becomes positive pointing out that also interferences (GP: and non--factorizable QCD corrections ?) are needed.\\
 In order to investigate further the jet pair kinematics, we divide the $m_{jj},\Delta y_{jj}$ plane in 2--dimensional bins and analyze the cross--sections: in particular we compute in each bin the ratio of the approximated cross--section over the full one.
-In fig.~\ref{fig:ratio2d_NLO} and fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.
+In Fig.~\ref{fig:ratio2d_NLO} and Fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.
 \begin{figure}[h]
@@
 As expected, in the low invariant mass--low rapidity separation region of the jet--jet pair the VBS approximation fails badly (up to 40 \% discrepancies) and the $s$--channel inclusion lead to discrepancies of at most 5 \%.
-However, the positive discrepancy shown in the low $m_{jj}$ region (black curve, fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{jj}$, large $\Delta y_{jj}$ region of fig.~\ref{fig:mjjdyjj_2d_NLO}, where the two leading jets have soft transverse momenta, according to
-\[
-m_{jj}^2 = 2\,p_t^{j_1}p_t^{j_2}\,(\cosh \Delta y_{jj} - \cos \Delta\phi_{jj}) \approx 2\,p_t^{j_1}p_t^{j_2}\,\cosh \Delta y_{jj} \,\,.
-\]
-The same positive discrepancy of the $|s|^2 + |t|^2 + |u|^2$ approximation, in fact, can be seen in the low $p_t$ region of the leading jet in the left panel of fig.~\ref{fig:mjjdyjj_1d_2}.\\
-In the large invariant mass--small rapidity separation region of fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the 15 \% level are left: this can be traced back to the large $p_t$ and central rapidity region of the leading jets kinematics, shown in fig.~\ref{fig:mjjdyjj_1d_2}.
+However, the positive discrepancy shown in the low $m_{jj}$ region (black curve, Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{jj}$, large $\Delta y_{jj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, where the two leading jets have soft transverse momenta, according to the following approximation
+\begin{equation}
+\begin{split}
+m_{jj}^2 &= 2\,p_t^{j_1}p_t^{j_2}\,(\cosh \Delta y_{jj} - \cos \Delta\phi_{jj})
+&\approx 2\,p_t^{j_1}p_t^{j_2}\,\cosh \Delta y_{jj} \,\,.
+\end{split}
+\end{equation}
+The same positive discrepancy of the $|s|^2 + |t|^2 + |u|^2$ approximation, in fact, can be seen in the low $p_t$ region of the leading jet in the left panel of Fig.~\ref{fig:mjjdyjj_1d_2}.\\
+In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the 15 \% level are left: this can be traced back to the large $p_t$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
 For such distributions, despite the $s$--channel inclusion, the discrepancy between the approximated and full result is about 5-10 \%.\\
-In the VBS signal region the VBS approximation it shows a good agreement with the full calculation.
+In the VBS signal region the VBS approximation shows a good agreement with the full calculation.
 \begin{figure}[hbt]
@@
 
-Concerning leptonic kinematcs, we show in fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton--lepton invariant mass and of the Zeppenfeld variable of the electron.
+Concerning leptonic kinematcs, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton--lepton invariant mass and of the Zeppenfeld variable of the electron.
 \begin{figure}[hbt]

### 2018-02-02 Draft/scanNLO.tex
scanNLO.tex: modified wrong figure names

--- 2018-02-01 Draft/scanNLO.tex
@@
 \centering
-{\includegraphics[scale=0.39]{figures/scanfigures/a6as_VBFNLOVSrecola_tu.pdf}}
+{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}}
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
@@
 \centering
-{\includegraphics[scale=0.39]{figures/scanfigures/a6as_VBFNLOVSrecola_stu.pdf}}
+{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
 \caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.

### 2018-02-02 Draft/crosssectionLO.tex
Work on the draft, mainly improvements and corrections

@@
-In Table~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts (Eq.~\ref{cut:4}).
-This is the order $\mathcal{O}(\alpha^6)$.
+In Table~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
+The order considered here is the order $\mathcal{O}(\alpha^6)$.
 

### 2018-02-02 Draft/scanNLO.tex
Work on the draft, mainly improvements and corrections

@@
-We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha_s\alpha^6)$.
+We now present the inclusive study performed at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$.
 
-According to the results shown in Sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{jj} < 200$ GeV, $|\Delta y_{jj}| < 2$; moreover, we would like to validate this approximation (and its extension to $s$--channels inclusion) at the NLO accuracy.
-Thus, we impose the same kinematic cuts shown in sec.~\ref{subsec:inputpar} relaxing the VBS cuts and asking for
-\begin{equation}
-	m_{jj} > 200 \,\textrm{GeV}\,,\qquad |\Delta y_{jj}| > 2\,.
-\end{equation}
-We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc VBFNLO} adds the s--channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha_s\alpha^5)$ interference.
+According to the results shown in Sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
+For the inclusive region (see Eq.~\eqref{eq:inclusive}), this approximation is good up to $\pm10\%$ apart for large di-jet differences and low di-jet invariant mass.
+It is therefore interesting to check how good this approximation is at NLO.
+Thus, we impose the same kinematic cuts shown in Sec.~\ref{subsec:inputpar} and apply the VBS cuts of Eq.~\eqref{eq:inclusive}.
+
+We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$) while {\sc VBFNLO} adds the $s$-channel contributions ($|s|^2+|t|^2+|u|^2$).
+On the other hand {\sc Recola} employs full matrix elements, adding also $t/u$ interferences, factorisable, and non-factorisable QCD corrections to the order $\mathcal{O}(\alpha^6)$.
+This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.
 The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
+
 \begin{table}[h!]
@@
 \begin{tabular}{c|c|c}
-\bf Matrix--element & $\sigma_{\textrm{tot}}\,[\textrm{fb}]$ & $\delta$ \\
+Prediction & $\sigma_{\textrm{tot}}\,[\textrm{fb}]$ & $\delta$ \\
 \hline
 \hline
-full &  1.8120 $\pm$ 0.0144 & - \\
+full &  $1.8120 \pm 0.0144$ & - \\
 \hline
-$|t|^2 + |u|^2$ & 1.6292 $\pm$ 0.0001  &  -10 \% \\
+$|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-10\%$ \\
 \hline
-$|s|^2 + |t|^2 + |u|^2$ & 1.7780 $\pm$ 0.0001  & -2 \%
+$|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $-2\%$
 \end{tabular}
-\caption{\label{tab:crosssecINCLUSIVE}Total cross--sections at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, with $m_{jj}>200$ GeV, $|\Delta y_{jj}|>2$.}
+\caption{\label{tab:crosssecINCLUSIVE} Total cross sections at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ GeV, $|\Delta y_{\Pj\Pj}|>2$.}
 \end{table}
-The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) gives a negative discrepancy of about 10 \% w.r.t the full calculation; the inclusion of $s$--channel diagrams improves the approximate prediction up to a 2 \% discrepancy.\\
-These discrepancies are much more evident in differential cross--sections.\\
-In Fig.~\ref{fig:mjjdyjj_1d_1} we show the distributions in the jet--jet invariant mass $m_{jj}$ and rapidity separation $\Delta y_{jj}$: at large $m_{jj}$ and large $\Delta y_{jj}$ the VBS approximation and its $s$--channel extension agree with the full calculation within few percents.
+
+The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) gives a negative discrepancy of about $10\%$ with respect to the full calculation.
+The inclusion of $s$-channel diagrams improves the approximate prediction down to a $2\%$ discrepancy.
+
+These discrepancies are much more evident in differential distributions.
+In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $\Delta y_{\Pj\Pj}$.
+For large $m_{\Pj\Pj}$ and large $\Delta y_{\Pj\Pj}$, as expected, the VBS approximation is performing well and its $s$-channel extension agree with the full calculation within few per cents.
+% On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
+% In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
+This is in contrast to the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation goes up to $30\%$.
+The inclusion of $s$-channels cures partly the discrepancy in these regions.
+Still, for the very low $m_{\Pj\Pj}$ a small discrepancy of about $5\%$ remains.
+This might indicate that also interferences (GP: and non--factorizable QCD corrections ? \MP{I don't know, we have to think about it}) are needed in this phase-space region.
+
+In order to investigate further the jet pair kinematics, we divide the $m_{\Pj\Pj},\Delta y_{\Pj\Pj}$ plane in 2-dimensional bins and analyse the cross sections.
+In particular we compute in each bin the ratio of the approximated cross sections over the full one.
+In Fig.~\ref{fig:ratio2d_NLO} and Fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.
+
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/dyjj_nlo.pdf}}
-\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_1}
+\caption{NLO QCD inclusive study: distributions in $m_{\Pj\Pj}$ (left) and $\Delta y_{\Pj\Pj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_1}
 \end{figure}
-Focussing on the region  $200 \GeV < m_{jj} < 500 \GeV$ and $2<|\Delta y_{jj}|<2.5$, the negative discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation is enhanced by up to 30 \%.
-The inclusion of $s$--channels cures the discrepancy in these regions; still, in the very low $m_{jj}$ a small discrepancy ($\approx$ 5 \%) becomes positive pointing out that also interferences (GP: and non--factorizable QCD corrections ?) are needed.\\
-In order to investigate further the jet pair kinematics, we divide the $m_{jj},\Delta y_{jj}$ plane in 2--dimensional bins and analyze the cross--sections: in particular we compute in each bin the ratio of the approximated cross--section over the full one.
-In Fig.~\ref{fig:ratio2d_NLO} and Fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.
+
 \begin{figure}[h]
@@
 %\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-\caption{Cross sections (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
+\caption{Cross sections (fb) per bin of $(m_{\Pj\Pj},\,\Delta y_{\Pj\Pj})$ at NLO QCD $\mathcal{O}(\alphas\alpha^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$.
@@
 {\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-\caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_s\alpha^6)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
+\caption{Cross section (fb) per bin of $(m_{\Pj\Pj},\,\Delta y_{\Pj\Pj})$ at NLO QCD $\mathcal{O}(\alphas\alpha^6)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$.
@@
 \end{figure}
-As expected, in the low invariant mass--low rapidity separation region of the jet--jet pair the VBS approximation fails badly (up to 40 \% discrepancies) and the $s$--channel inclusion lead to discrepancies of at most 5 \%.
-However, the positive discrepancy shown in the low $m_{jj}$ region (black curve, Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{jj}$, large $\Delta y_{jj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, where the two leading jets have soft transverse momenta, according to the following approximation
+
+As expected, in the low invariant mass--low rapidity separation region of the jet pair the VBS approximation fails badly (up to $40\%$ discrepancies).
+The inclusion of the $s$-channel brings down to at most $5\%$.
+However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}.
+In this region, the two leading jets have soft transverse momenta, according to the following low-angle approximation
+
 \begin{equation}
 \begin{split}
-m_{jj}^2 &= 2\,p_t^{j_1}p_t^{j_2}\,(\cosh \Delta y_{jj} - \cos \Delta\phi_{jj})
-&\approx 2\,p_t^{j_1}p_t^{j_2}\,\cosh \Delta y_{jj} \,\,.
+m_{\Pj_i\Pj_j}^2 &= 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,(\cosh \Delta y_{\Pj_i\Pj_j} - \cos \Delta\phi_{\Pj_i\Pj_j}) \\
+&\approx 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,\cosh \Delta y_{\Pj_i\Pj_j} \,\,.
 \end{split}
 \end{equation}
-The same positive discrepancy of the $|s|^2 + |t|^2 + |u|^2$ approximation, in fact, can be seen in the low $p_t$ region of the leading jet in the left panel of Fig.~\ref{fig:mjjdyjj_1d_2}.\\
-In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the 15 \% level are left: this can be traced back to the large $p_t$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
-For such distributions, despite the $s$--channel inclusion, the discrepancy between the approximated and full result is about 5-10 \%.\\
-In the VBS signal region the VBS approximation shows a good agreement with the full calculation.
+
+The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low $\pt$ region of the leading jet in the left panel of Fig.~\ref{fig:mjjdyjj_1d_2}.
+In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the level of $15\%$ are present.
+This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
+For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about 5-10 \%.\\
+In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.
+
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
-\caption{NLO QCD inclusive study: transverse momentum and rapidity distributions of the leading jet, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
+\caption{NLO QCD inclusive study: transverse momentum and rapidity distributions of the leading jet, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
 \end{figure}
 
-Concerning leptonic kinematcs, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton--lepton invariant mass and of the Zeppenfeld variable of the electron.
+Concerning leptonic kinematics, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron \MP{We should defined the Zep var.
+somewhere}.
+
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
-\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
+\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
 \end{figure}
@@
 
-In conclusion, both the loose minimum $jj$ invariant mass cut and the inclusion of QCD radiative correction make the $s$--channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
-Nevertheless, interferences and non--factorizable QCD corrections should be included to reduce the discrepancies down to the $\approx$ 1 \%  level, mainly in inclusive analyses.\\
-Instead, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($M_{jj} \gtrsim 600 \GeV$, $\Delta y_{jj} \gtrsim 3$), concerning both total cross--section and distributions.
+In conclusion, both the loose minimum di-jet invariant mass cut and the inclusion of QCD radiative correction make the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
+Nevertheless, interferences and non-factorizable QCD corrections should be included to reduce the discrepancies down to the $\approx 1\%$  level, mainly in inclusive analyses.
+Instead, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($M_{\Pj\Pj} \gtrsim 600 \GeV$, $\Delta y_{\Pj\Pj} \gtrsim 3$), for both total cross section and differential distributions.

### 2018-02-03 Draft/contributions.tex

@@
 At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$ and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
-In the present section, the cross sections and distributions are obtained without applying the typical VBS cuts $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
-In Table~\ref{tab:LOscanXsec}, the cross section of the three contributions are displayed.
+In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
+In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are displayed.
 The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
@@
 In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
-Interestingly, the EW contributions peaks around and invariant mass of about $80\GeV$.
-These are due to contributions where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
+The EW contribution peaks around an invariant mass of about $80\GeV$.
+These are due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
 Note that these contributions are not present in calculation relying on the VBS approximation.

### 2018-02-03 Draft/definition.tex

@@
 This process possesses three LO contributions of different orders.
-The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as EW contributions.
-In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
-These types of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
-Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
+The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as EW contribution.
+In addition to typical VBS contributions, as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
+Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines.
+The $s$-channels will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
+Some of them take the form of decay chains, for example the diagram represented in the middle of Fig.~\ref{diag:LO}, while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
 The VBS diagrams typically dominate the full process.
@@
 
-The process can also be mediated via a gluon connecting the two quark lines while the W bosons are radiated from the quark lines.
-These contributions are of order $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$ and usually feature different kinematic behaviours than the EW contribution.
+The process can also be mediated via a gluon connecting the two quark lines while the W bosons are radiated off the quark lines.
+These contributions are of order $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$ and feature different kinematical behaviours than the EW contribution.
 Nonetheless they share the same final state and therefore constitute an irreducible background.
 
-Finally, due to the specific colour structure of these two classes of amplitudes, there exist non-zero interferences.
+Finally, due to the specific colour structure of these two classes of amplitudes, there exist non-zero interferences if only one quark family is involved.
 These are of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$ and are usually small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
 
-Usually, in experimental measurements, special VBS-cuts are designed in order to enhance the EW contribution over the QCD one.
-These cuts are based on the fact that the two contributions have rather different kinematic.
-The EW contribution is characterised by two jets with large rapidity in the peripheral region as well as a large invariant mass.
+In experimental measurements, special VBS-cuts are designed to enhance the EW contribution over the QCD one.
+These cuts are based on the fact that the two contributions have different kinematical behaviour.
+The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
 The two W bosons are mostly produced centrally.
-This is in opposition with the QCD component which favours jets in the central region.
+This is in contrast to the QCD contribution which favours jets in the central region.
 Therefore, the event selection usually involves rapidity-difference and invariance-mass cuts for the jets.
-This will also be discussed in Section \ref{subsec:contributions}.
+This will also be discussed in Sec.~\ref{subsec:contributions}.
 

### 2018-02-03 Draft/process.tex
References added

@@
 Then the polarisation of the gauge boson is accommodated following the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
-Such an approximation is usually called effective vector-boson approximation (EVBA).
+Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
 
-A more refined approximation consists in considering all $t$- and $u$- diagrams and square them separately.
-Nonetheless, different type of diagrams are not squared which amounts to neglecting interferences.
+A less crude approximation consists in considering all $t$- and $u$- diagrams and squaring them separately and neglecting their interferences.
 These interferences are expected to be small in the VBS fiducial region.
-The $s$-channel contributions can still be left out.
-This approximation is often called $t$-/$u$- approximation or even VBS approximation.
+The $s$-channel squared diagrams and interferences with $s$-channels are left out as well.
+This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
 We will adopt the latter denomination in the following of the article.
 Such an approximation is implemented at LO in the computer codes {\sc Bonsay} and {\sc Powheg}.
-The physical origin of this approximation is that each proton emitting a quark represents two independent copies of the $SU_c\left(3\right)$ gauge group.
+This approximation is gauge-invariant, which can be seen by considering the quark coming from different protons belonging to different $SU \left(3\right)$ gauge groups.
 
-The squared matrix element of the $s$-channel contributions can then be added but all interferences between different kinematic channels are neglected.
+The squared matrix element of the $s$-channel contributions can added back, but all interferences between different kinematic channels are still neglected.
 This is what is done in {\sc VBFNLO}.
@@
 
-Moving on to NLO accuracy, one can extend the approximation presented at LO.
-The VBS approximation at NLO is simply extending the same approximation to real as well as to virtual corrections.
+Moving on to NLO accuracy, one can extend the approximations presented at LO.
+The VBS approximation at NLO is straightforward for the virtual contributions, for the real-contributions one must be careful about gluon-initiated processes\footnote{The initial gluon must not couple to the other initial quark, otherwise there are infrared divergences proportional to $s$-channels which do not match with the ones found in the virtual contributions.
+The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument as presented above.
+}.
 This is implemented in {\sc POWHEG}.
-This approximation can be used in combination with a double-pole approximation [REF] for the virtual contribution.
-This requires the computation of factorisable as well as non-factorisable corrections \cite{Dittmaier:2015bfe} separately.
+This approximation can be used in combination with a double-pole approximation \cite{Dittmaier:2015bfe} for the virtual contribution.
 Such an approximation is implemented in {\sc Bonsay}.

### 2018-02-03 Draft/contributions.tex

@@
-At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$ and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
+At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
 In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
@@
 These are due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
-Note that these contributions are not present in calculation relying on the VBS approximation.
+Note that these contributions are not present in calculations relying on the VBS approximation.
 Also, the EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$ and for jet rapidity difference larger than $2.5$.
@@
 Again, it is obvious that the region with low di-jet invariant mass and low jet-rapidity difference should be avoided.
-This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study.
+This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
 Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
-This is particularly explicit in Sec.~\ref{subsec:LOfiducial}.
+This is are the cuts used in Sec.~\ref{subsec:LOfiducial}.
 

### 2018-02-03 Draft/crosssectionLO.tex

@@
     \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison,
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
+    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.
+    \MP{Please add or check your respective numbers}}
 \end{table}
+
+We note that several full predictions are not in statistical agreement.
+These are possibly due to too aggressive estimations of statistical uncertainty or ... \MP{To be added}
+Nonetheless, all these predictions agree within less than $0.5\%$.
+At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
+This simply means that the various VBS approximations are not worth than $0.5\%$ at the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.

### 2018-02-03 Draft/crosssectionNLO.tex
Work on the draft, mainly improvements and corrections

@@
-Cross secitons at NLO
+Cross sections at NLO
 
@@
     \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
+    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.
+    \MP{Please add or check your respective numbers}}
 \end{table}
-At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
-$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.
+
+At NLO, the rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}.
+This is most likely due to low di-jet invariant-mass configurations, where $s$-channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.

### 2018-02-03 Draft/distributionsLO.tex

@@
 In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over {\sc VBFNLO}.
-For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
+For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
 We have checked that the same level of agreement holds for many other differential distributions.

### 2018-02-03 Draft/scanLO.tex
typocorr
Work on the draft, mainly improvements and corrections

--- 2017-12-10 Draft/scanLO.tex
@@
-% \subsection{Validity of the VBS approximation}\label{subsec:VBSapprox}
+As explained previously, the low di-jet invariant mass and low jet rapidity separation is dominated by tri-bosons production.
+Therefore a comparison of the various approximation in an \emph{inclusive} phase-space volume.
+To that end, we have chosen for the inclusive fiducial volume to take the following values for the VBS cuts
+
+\begin{equation}
+\label{eq:inclusive}
+	m_{jj} > 200\GeV\,,\qquad |\Delta y_{jj}| > 2 .
+\end{equation}
+
+The figure is Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
+Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
+In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
+The low rapidity difference region possesses remnants of the tri-bosons contributions.
+It is therefore expected that the $|t|^2 + |u|^2$ approximations fails in this region.
+The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
+The full calculation is approximated at the level of $\pm10\%$ everywhere apart in the upper left corner where the inclusion of $s$-channel contributions did not improve the approximation.
+This is due to ...
 

### 2018-02-04 Draft/acknowledgements.tex
Some changes in sections 4.3 and 5.2

@@
- We thank ...
-Acknowledgement of VBSCAN COST action.
+The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
+Moreover, this work was supported by a STSM Grant from COST Action CA16108.
+
+BB, AD, and MP acknowledges financial support by the
+German Federal Ministry for Education and Research (BMBF) under
+contract no.~05H15WWCA1 and the German Science Foundation (DFG) under
+reference number DE 623/6-1.

### 2018-02-04 Draft/conclusion.tex
Some changes in sections 4.3 and 5.2

@@
 - Comment on the irreducible QCD background \\
+- Uncertainties related to PDF.
+Some of us have already presented preliminary results on this subjetc \cite{}. % Radcor proceedings from Christopher.
+A forthcoming article will addresses related questions.

### 2018-02-04 Draft/crosssectionLO.tex
Some changes in sections 4.3 and 5.2

@@
-In Table~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
+In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
 The order considered here is the order $\mathcal{O}(\alpha^6)$.
+We note that several full predictions are not in statistical agreement.
+These are possibly due to too aggressive estimations of statistical uncertainty or ... \MP{To be added}
+Nonetheless, all these predictions agree within less than $0.5\%$.
+At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
+This simply means that the various VBS approximations are not worth than $0.5\%$ at the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
 
@@
     \end{tabular}
-    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison,
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.
+    \caption{\label{tab:wg1_LOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
+    The uncertainties shown refers to the estimated statistical error of the Monte Carlo programs.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
     \MP{Please add or check your respective numbers}}
 \end{table}
-
-We note that several full predictions are not in statistical agreement.
-These are possibly due to too aggressive estimations of statistical uncertainty or ... \MP{To be added}
-Nonetheless, all these predictions agree within less than $0.5\%$.
-At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
-This simply means that the various VBS approximations are not worth than $0.5\%$ at the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.

### 2018-02-04 Draft/crosssectionNLO.tex
Some changes in sections 4.3 and 5.2

--- 2017-12-10 Draft/crosssectionNLO.tex
@@
-Cross secitons at NLO
+In Tab.~\ref{tab:wg1_NLOrates}, the cross sections of the various tools at NLO QCD accuracy are presented.
+The order considered is $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions seems to visibly differing according to the approximations used already at the level of the fiducial cross section.
 
@@
     \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD accuracy within VBS cuts obtained with the different codes used in this comparison, 
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
+    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha^6)$.
+    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
+    \MP{Please add or check your respective numbers.}}
 \end{table}
-At NLO, rates show slightly larger discrepancies, as it can be observed in Tab.~\ref{tab:wg1_NLOrates}. This is most likely due to low dijet invariant-mass configurations, where
-$s-$channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.
+
+The first observation is that the predictions featuring two versions of the VBS approximation ({\sc Bonsay} and {\sc POWHEG}) are close.
+This means that the double-pole approximation on the two W bosons used in {\sc Bonsay} constitutes a good approximation of the VBS-approximated virtual corrections implemented in {\sc POWHEG}.
+Both predictions differ by about $2\%$ with respect to the full computation ({\sc MoCaNLO+Recola}).
+The second observation is that the inclusion of $s$-channel contributions seems to have a significant impact.
+Indeed, its inclusion (as done in {\sc VBFNLO}) approximates the full computation by less than a per-cent ($0.7\%$).
+This behaviour is most likely due to low di-jet invariant-mass configurations, where $s$-channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.
+\MP{To be developed with more physics insight}.

### 2018-02-04 Draft/distributionsLO.tex
Some changes in sections 4.3 and 5.2

--- 2017-12-08 Draft/distributionsLO.tex
@@
+In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (top) and the rapidity difference of the two tagging jets (bottom) which are key observables for VBS measurements.
+In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over {\sc VBFNLO} \MP{To be changed to Recola}.
+For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.
+In general, the agreement is at the level of $1\%$ or below for each bin.
+We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, transverse momentum.
+This means that at LO, in the fiducial volume, the VBS approximation is good to a per cent.
+
  \begin{figure}[h!]
    \centering
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mjj_LO.pdf}
-   \includegraphics[width=0.49\textwidth,angle=0,clip=true,trim={0.4cm 2.5cm 0.cm 1.cm}]{figures/mll_LO.pdf}
-\caption{\label{fig:wg1_mjj-llLO} Invariant-mass of the two tagging jets (left) and of the two leptons (right), at LO accuracy, 
-computed with the different codes used in this comparison. The inset shows the ratio over {\sc VBFNLO}.
+   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/mjj_LO.pdf}
+   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
+\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (top) and rapidity difference of the two tagging jets (bottom).
+The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
+The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
+The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
+\MP{MG statistics should be improved and the baseline changed to Recola.}
 }

### 2018-02-04 Draft/scanNLO.tex
Reorganise the figure folder and fixed some merged problems

@@
 \caption{Cross sections (fb) per bin of $(m_{\Pj\Pj},\,\Delta y_{\Pj\Pj})$ at NLO QCD $\mathcal{O}(\alphas\alpha^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$.
-Results of {\sc Bonsay} (approximated) and {\sc Recola} (full) calculations.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$. Results of {\sc Bonsay} (approximated) and {\sc Recola} (full) calculations. 
 {\bf GP: notation to be changed, Mjj > mjj, alphas alpha} }\label{fig:ratio2d_NLO}
@@
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$. 
-Results of {\sc VBFNLO} (approximated) and {\sc Recola} (full) calculations.
-{\bf GP: notation to be changed, Mjj > mjj, alphas alpha}}\label{fig:mjjdyjj_2d_NLO}
+Results of {\sc VBFNLO} (approximated) and {\sc Recola} (full) calculations. {\bf GP: notation to be changed, Mjj > mjj, alphas alpha}}\label{fig:mjjdyjj_2d_NLO}
 \end{figure}
@@
 somewhere}.
-
 \begin{figure}[hbt]
@@
 \end{figure}
-{\bf GP: leptonic variables, comment further.}
+The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees pretty well with the full curve, generated with {\sc Recola}; the {\sc Bonsay} curve is about 10 \% smaller.
+The discrepancies are roughly constant over the whole specrum.\\
+Instead, the right panel of fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$--channels, with increasing discrepancy w.r.t.
+the full result at large values.
+The muon variable $z_{\mu}$ behaviour is almost identical to $z_e$.\\
 

### 2018-02-04 Draft/distributionsNLO.tex
First text and distributions for the NLO comparison.

In Figs.~(\ref{fig:distNLO1}-\ref{fig:distNLO3}), several differential distributions are shown.
All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
\MP{Physics and conclusion on interference/non-factorisable etc.\ effects are not addresses yet in the discussion.}

We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (top) and the rapidity separation (bottom) of the two tagging jets.
For high invariant mass, all predictions agree rather well.
On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
The VBS-approximated predictions ({\sc BONSAY} and {\sc POWHEG}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC@NLO}.
Finally, {\sc VBFNLO} which include as well $s$-channel contributions provides larger predictions at low invariant mass.
For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.

 \begin{figure}[h!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mjj_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
\caption{\label{fig:distNLO1} Differential distributions in the invariant mass (top) and rapidity difference of the two tagging jets (bottom).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure}

Concerning the transverse momentum (top) and rapidity (bottom) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
While {\sc MadGraph5\_aMC@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
This is in contrast with ({\sc BONSAY} and {\sc POWHEG}) which approximate the full computation reasonably well over the whole range and in particular the the high transverse-momentum region.
Finally, {\sc VBFNLO} predicts higher rates over the whole range apart around $200\GeV$ where it is in perfect agreement with the complete calculation.
Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $\pm3$.
For larger rapidity, the other codes constitute a better description of the full process at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.

 \begin{figure}[h!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/ptj1_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
\caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (top) and rapidity of the hardest jet (bottom).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure}

The last set of differential distributions are the invariant mass of the two charged lepton (top) and the Zeppenfeld variable for the anti-muon (bottom).
Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
Indeed, the hierarchy mentioned previously is here respected and enhanced towards high invariant mass or high Zeppenfeld variable.
{\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
The other three VBS approximations seem to be close to each other.

 \begin{figure}[h!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mll_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
\caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (top) and Zeppenfeld variable for the muon (bottom).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure}

### 2018-02-07 Draft/distributionsNLO.tex
Minor changes on draft, mostly typos

@@
 While {\sc MadGraph5\_aMC@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
-This is in contrast with ({\sc BONSAY} and {\sc POWHEG}) which approximate the full computation reasonably well over the whole range and in particular the the high transverse-momentum region.
+This is in contrast with {\sc BONSAY} and {\sc POWHEG} which approximate the full computation reasonably well over the whole range and in particular the high transverse-momentum region.
 Finally, {\sc VBFNLO} predicts higher rates over the whole range apart around $200\GeV$ where it is in perfect agreement with the complete calculation.
-Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $\pm3$.
+Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
 For larger rapidity, the other codes constitute a better description of the full process at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
@@
 
-The last set of differential distributions are the invariant mass of the two charged lepton (top) and the Zeppenfeld variable for the anti-muon (bottom).
+The last set of differential distributions is the invariant mass of the two charged lepton (top) and the Zeppenfeld variable for the anti-muon (bottom).
 Concerning the comparison of the predictions, both distributions display a rather similar behaviour.

### 2018-02-07 Draft/introduction.tex
small typos fixed
Minor changes on draft, mostly typos

@@
 Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
-Preliminary results have already been made public in %Ref.~\cite{Anders:2018gfr}.
+Preliminary results have already been made public in Ref.~\cite{Anders:2018gfr}.
 
@@
 At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
-The largest one are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
+The largest ones are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
 The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.

### 2018-02-07 Draft/scanLO.tex
Minor changes on draft, mostly typos

@@
-As explained previously, the low di-jet invariant mass and low jet rapidity separation is dominated by tri-bosons production.
-Therefore a comparison of the various approximation in an \emph{inclusive} phase-space volume.
+As explained previously, the low di-jet invariant mass and low jet rapidity separation is dominated by tri-boson production.
+Therefore a comparison of the various approximations in an \emph{inclusive} phase-space volume is performed.
 To that end, we have chosen for the inclusive fiducial volume to take the following values for the VBS cuts
-
 \begin{equation}
@@
 
-The figure is Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
+The figure showing this is Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
 Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
@@
 The low rapidity difference region possesses remnants of the tri-bosons contributions.
-It is therefore expected that the $|t|^2 + |u|^2$ approximations fails in this region.
+It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
 The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
@@
 Ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).}
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (top) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (bottom).}
 \label{fig:ratio2d_LO}

### 2018-02-07 Draft/scanNLO.tex
Minor changes on draft, mostly typos

@@
 The discrepancies are roughly constant over the whole specrum.\\
-Instead, the right panel of fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$--channels, with increasing discrepancy w.r.t.
+Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$--channels, with increasing discrepancy w.r.t.
 the full result at large values.

### 2018-02-07 Draft/shower.tex
Minor changes on draft, mostly typos

@@
 on the results.
-%
+
 \begin{table}[h!]
@@
 \end{table}
-%
-We now turn to present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in in Table~\ref{tab:PSrates}, both at LO and NLO 
-accuracy. For {\sc MG5\_aMC}, the number in parentheses are rescaled to take into account the width effects described in the above paragraph. Once this effect is taken into
+
+We now turn to present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Table~\ref{tab:PSrates}, both at LO and NLO
+accuracy. For {\sc MG5\_aMC}, the numbers in parentheses are rescaled to take into account the width effects described in the above paragraph. Once this effect is taken into
 account, total rates from different tools agree within few percents. Larger discrepancies however will appear for differential observables, which we are going to discuss in
@@
 among tools are reduced to about 10\%. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
-{\sc MG5\_aMC}, while the smallest by {\sc Powheg}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
+{\sc MG5\_aMC}, while the smallest rate is predicted by {\sc Powheg}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
 is different among the two tools. In particular, for {\sc Powheg}, the first emission is generated with an internal Sudakov form factor (the
@@
 at most 10\%.\\
-Finally, focusing on the third jet, we conclude the list of differential observable with the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}. 
+Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}.
 {\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper section. Otherwise define it here}

### 2018-02-07 Draft/definition.tex
added comments

@@
 
-This process possesses three LO contributions of different orders.
+{\bf MR: This process possesses three LO contributions of different orders.
 The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as EW contribution.
@@
 The VBS diagrams typically dominate the full process.
-But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.
+But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.}
 

### 2018-02-08 Draft/abstract.tex
Add my corrections

@@
 
-In this article, a detailed study of the vector-boson scattering for two positively charged W bosons is presented.
-In particular, a comparison between the full next-to-leading (NLO) QCD corrections against several approximations is carried out.
-This study is not only performed in the usual fiducial region used by experimental collaborations but also in a more inclusive set-up.
+  Vector-boson scattering processes are of great importance for the
+  current run-2 and future runs at design energy of the Large Hadron
+  Collider. The presence of triple and quartic gauge couplings gives
+  access to tests of the gauge sector and possible new-physics
+  contributions there. For this, a precise knowledge of the Standard
+  Model contributions is necessary, which at least matches the
+  experimental uncertainties.
+
+  In this article, we present a detailed study of the vector-boson
+  scattering process with two positively charged leptons and missing
+  transverse momentum in the final state, mediated predominantly by
+  same-sign production of two W bosons with positive charge.
+In particular, we carry out a comparison between the full NLO QCD corrections against several approximations.
+This study is not only performed in the usual fiducial region used by experimental collaborations, but also in a more inclusive set-up.
 This allows to infer precisely the quality of such approximations.
-Finally, NLO predictions matched to various parton shower are also discussed.
+Finally, we discuss NLO predictions matched to various parton showers.
 Thanks to this, it is thus possible to infer the systematic errors related to vector-boson scattering at the NLO-QCD level and beyond.

### 2018-02-08 Draft/article.tex
Update article.tex: subsec. labels
Remove usepackage{siunitx} as it seems not be a default package. Replace in the introduction TeV
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.
Some further work on the draft. Note that the hyperref package is commented as it seems that is

@@
  \usepackage{amsmath}
+ \usepackage{amssymb}
  \usepackage{graphicx}
@@
  \usepackage{dcolumn}
- \usepackage{hyperref}
-%  \usepackage[draft]{hyperref}
+%  \usepackage{hyperref}
+  \usepackage[draft]{hyperref}
  \usepackage{caption}
@@
  \usepackage{lmodern}
- \usepackage{siunitx}
+ \usepackage{url}
+%  \usepackage{siunitx}
 % \usepackage
@@
 % {subcaption}
+\hyphenation{quan-ti-ta-tive-ly}
 
@@
 
-\author{Benedikt Biedermann\thanksref{wurz}
+\author{Alessandro Ballestrero\thanksref{infnto}
+\and
+Benedikt Biedermann\thanksref{wurz}
 \and
@@
 \and
+Ezio Maina\thanksref{infnto,unito}
+\and
 Mathieu Pellen\thanksref{wurz}
 \and
-Giovanni  Pelliccioli\thanksref{unito}
+Giovanni Pelliccioli\thanksref{infnto,unito}
 \and
@@
 Michael Rauch\thanksref{kit}
+\and
+Daniela Rebuzzi\thanksref{pavia}
 \and
@@
 \and
-Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino, %
+INFN, Sezione di Torino, %
+Via P. Giuria 1, %
+10125 Torino, %
+Italy\label{infnto}
+\and
+Universit\`a di Torino, Dipartimento di Fisica, %
 Via P. Giuria 1, %
@@
 Technology (KIT), %
-Karlsruhe, 
+76131 Karlsruhe,
 Germany\label{kit}
@@
 \subsection{Description of the predictions}
+\label{subsec:codedescr}
 
@@
 \subsection{Inclusive comparison}
+\label{subsec:LOinclusive}
 
@@
 \subsection{Inclusive comparision}
+\label{subsec:NLOinclusive}
 
@@
 
-\bibliographystyle{utphys.bst}
+\bibliographystyle{utphys}
 \bibliography{article}
+
 \end{document}

### 2018-02-08 Draft/crosssectionLO.tex
Add my corrections

@@
     \centering
-    \begin{tabular}{c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
+    \begin{tabular}{c|r@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
         \hline
         \hline
-        {\sc Bonsay}  &  $X \pm 0.0002$ \\
-        {\sc MG5\_aMC}&  $X \pm 0.001$  \\
-        {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
-        {\sc PHANTOM} &  $1.4374 \pm 0.0006 $  \\
-        {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\
-        {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
-        {\sc Whizard} &  $1.4381 \pm 0.0002 $
+        {\sc Bonsay}  &  $X$ & $0.0002$ \\
+        {\sc MG5\_aMC}&  $X$ & $0.001$  \\
+        {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\
+        {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
+        {\sc POWHEG}  &  $1.44092$ & $0.00009$ \\
+        {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
+        {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $
     \end{tabular}

### 2018-02-08 Draft/crosssectionNLO.tex
Add my corrections

@@
     \centering
-    \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
+    \begin{tabular}{c|r@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
         \hline
         \hline
-        {\sc Bonsay}  &  $X \pm 0.0009$  \\
-        {\sc MG5\_aMC}&  $X  \pm 0.003$  \\
-        {\sc MoCaNLO+Recola}  &  $ 1.382 \pm 0.002$ \\
-        {\sc POWHEG}  &  $1.3556 \pm 0.0009$  \\
-        {\sc VBFNLO}  &  $1.3916 \pm 0.0001$  \\
+        {\sc Bonsay}  &  $X$ & $0.0009$  \\
+        {\sc MG5\_aMC}&  $X $ & $0.003$  \\
+        {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
+        {\sc POWHEG}  &  $1.3556$ & $0.0009$  \\
+        {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
     \end{tabular}
@@
     \MP{Please add or check your respective numbers.}}
+    \MR{My $t$-/$u$-channel-only number is $1.3703(1)$, so something additionally must be going on with Powheg, which we should comment on.}
 \end{table}
@@
 Indeed, its inclusion (as done in {\sc VBFNLO}) approximates the full computation by less than a per-cent ($0.7\%$).
-This behaviour is most likely due to low di-jet invariant-mass configurations, where $s$-channel diagrams and interferences are less suppressed than at LO, because of the presence of extra QCD radiation.
-\MP{To be developed with more physics insight}.
+The main source of the $s$-channel diagrams thereby consists of
+real-emission contributions, where one of the two leading jets is formed
+by one quark, or possibly also both quarks, originating from the $W$
+decay, and the second one by the extra radiation emitted from the
+initial state. In such configurations, the hadronically decaying W boson
+can become on-shell and hence yield larger contributions than at LO, where the
+invariant mass cut on the two jets forces the boson into the far
+off-shell region.

### 2018-02-08 Draft/definition.tex
Add my corrections

--- 2018-02-03 Draft/definition.tex
@@
 In addition to typical VBS contributions, as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
-Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines.
+Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.} $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.
 The $s$-channels will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
 Some of them take the form of decay chains, for example the diagram represented in the middle of Fig.~\ref{diag:LO}, while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
-The VBS diagrams typically dominate the full process.
-But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.
+When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results.
+We will discuss the commonly-used possible choices in detail in the next section.
 

### 2018-02-08 Draft/description.tex
Add my corrections

@@
     parton-level Monte Carlo for processes with electroweak bosons. It
-allows the calculation of VBS processes at NLO QCD in the VBF
-approximation and including the s-channel triboson contribution,
-neglecting interferences between the two. Besides the SM, also anomalous
-couplings of the Higgs and gauge bosons can be simulated.
+    allows the calculation of VBS processes at NLO QCD in the VBS
+    approximation, with process IDs between 200 and 290. The corresponding
+    s-channel contributions are available separately as triboson processes with
+    semi-leptonic decays, with process IDs in the 400 range. These can simply
+    be added on top of the VBS contribution, as interferences between the two are neglected.
+    The usage of leptonic tensors in the calculation, pioneered in
+    Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
+    automatically generated code.  Besides the SM, also a variety of
+    new-physics models including anomalous couplings of the Higgs and gauge
+    bosons can be simulated.
 

### 2018-02-08 Draft/introduction.tex
Add my corrections

@@
-Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
+Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and triple and quartic gauge couplings.
 It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarized.
@@
 
-In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
-These computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
+In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
+The VBS computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
 It is therefore interesting to infer in details the quality of the various approximations.
@@
 This allows to infer systematic differences between the various predictions.
-This is the first time in the literature that such an analysis has been carried out \MP{True?}.
+A first study for the $\PW^+ \PW^- \Pj \Pj$ VBS process has been presented in
+Ref.~\cite{Rauch:2016upa}, comparing the angular-ordered default shower and the dipole
+shower and both{\sc MC@NLO}-like~\cite{Frixione:2002ik} and {\sc POWHEG}-like~\cite{Nason:2004rx,Frixione:2007vw} matching as implemented
+in {\sc Herwig 7}~\cite{Bellm:2015jjp}, also showing scale-variation uncertainties.
+This is the first time in the literature that NLO QCD calculations for VBS processed matched to parton shower are compared between different generators.
 
@@
 
-The article is organised as follow:
-in Sec.~\ref{sec:definition} the studied process is defined.
+The article is organised as follows:
+First, we define the process under study in Sec.~\ref{sec:definition}.
 Various approximation at LO and NLO are described in Sec.~\ref{sec:details}.
 This is followed by a presentation of the programs used for the computations.
-Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
-Section~\ref{sec:matching} deals with the matching to parton shower.
+Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study at fixed order, respectively.
+Section~\ref{sec:matching} then adds the effect of parton showers and hadronization to the fixed-order results by matching the two.
 The last section consists in concluding remarks and recommendations for experimental collaborations.

### 2018-02-08 Draft/process.tex
Add my corrections

@@
-As mentioned previously, the EW contribution is dominated by the scattering of two W gauge bosons.
-Therefore it is justified to approximate the full EW contributions simply by the VBS contributions.
-Nonetheless, this set of contributions is not gauge invariant.
-To make it gauge-invariant, one should project on-shell the incoming W boson.
-Unfortunately, this momentum is space-like and thus a simple on-shell projection is not possible.
-Instead, one can keep the W boson leg connected to the external quark line off-shell while the one connected to the scattering is put on-shell.
+As mentioned previously, the contribution of main interest in our process is
+the scattering of two W gauge bosons, which includes the quartic gauge-boson vertex.
+Therefore it is justified to approximate the full EW contributions simply by only these contributions which contain the $2\rightarrow 2$ scattering process as a subpart.
+However, this set of contributions is not gauge invariant.
+To make it gauge invariant, one should perform an on-shell projection of the incoming W bosons.
+Unfortunately, these momenta are space-like and thus a simple on-shell projection is not possible.
+Instead, one can keep the W boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
 Then the polarisation of the gauge boson is accommodated following the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
@@
 
-A less crude approximation consists in considering all $t$- and $u$- diagrams and squaring them separately and neglecting their interferences.
-These interferences are expected to be small in the VBS fiducial region.
-The $s$-channel squared diagrams and interferences with $s$-channels are left out as well.
+A less crude approximation consists in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two.
+These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed.
+The $s$-channel squared diagrams and any interferences with $s$-channels are left out as well.
 This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
@@
 Such an approximation is implemented at LO in the computer codes {\sc Bonsay} and {\sc Powheg}.
-This approximation is gauge-invariant, which can be seen by considering the quark coming from different protons belonging to different $SU \left(3\right)$ gauge groups.
+This approximation is gauge-invariant, which can be seen by considering that the two protons and therefore the two incoming quarks belong to two different, but otherwise identical, copies of the $SU \left(3\right)$ gauge group.
 
-The squared matrix element of the $s$-channel contributions can added back, but all interferences between different kinematic channels are still neglected.
-This is what is done in {\sc VBFNLO}.
+The squared matrix element of the $s$-channel contributions can be added in addition, but all interferences between different kinematic channels are still neglected.
+This is the level of simulation available in {\sc VBFNLO}.
 
@@
 The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument as presented above.
+This approach is also fully consistent with the picture of two separate SU(3) copies.
 }.
@@
 Such an approximation is implemented in {\sc Bonsay}.
-In {\sc VBFNLO}, the VBS approximation at NLO with $s$-channel contributions is implemented.
+In {\sc VBFNLO}, the $s$-channel contributions are available as well and can be
+added on top of the VBS approximation. For the real emission diagrams, thereby
+as simplification the gluon emission is fully modelled only for initial-state
+radiation. The effect of final-state radiation together with the corresponding
+virtual contributions is included as a $K$-factor.
 
@@
 I cannot remember exactly what is included}.
+\MR{What about gauge invariance? A comment about that would be useful as well.}
 Such predictions are provided by {\sc MG5\_aMC}.

### 2018-02-08 Draft/scanNLO.tex
Add my corrections

@@
 
-Concerning leptonic kinematics, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron \MP{We should defined the Zep var.
-somewhere}.
+Concerning leptonic kinematics, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron. 
+It is defined as
+\begin{equation}
+  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj1}+y_{\Pj2}}2}{|y_{\Pj1}-y_{\Pj2}|} \,.
+  \label{eq:Zeppenfeld}
+\end{equation}
+Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
 \begin{figure}[hbt]

### 2018-02-08 Draft/shower.tex
Add my corrections

@@
 the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG} and {\sc VBFNLO}
-can also provide results at (N)LO+PS accuracy. Besides, also {\sc PHANTOM} is employed for LO+PS results.\\
+can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO}, we
+restrict ourselves to showing results only in the VBS approximation,
+{\emph i.e.} the $s$-channel contributions are neglected here. Besides,
+also {\sc PHANTOM} is employed for LO+PS results.\\
 {\sc MG5\_aMC},
@@
 employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8}
-{\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
-matching, in both cases together with {\sc Herwig7}~CITEREF. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.
+{\bf MZ VERSION? if same as MG5, put it at the end together with the
+tune}. {\sc VBFNLO} serves as a matrix-element and phase-space provider
+for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
+Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the BLHA
+interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
+possible to choose between {\sc MC@NLO}-like and {\sc POWHEG}-like
+matching. As parton shower, both the default angular-ordered shower as
+well as the dipole shower can be employed.
+Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\
@@
     \centering
-    \begin{tabular}{c|c|c|c}
-        Code  &  $\sigma[\rm{fb}]$  \\
+    \begin{tabular}{c|r@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+        \hline\hline
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 (1.368)$ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 (1.363)$ & $0.004$  \\
+        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389$ & $0.0006$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
         \hline
-        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 (1.368) \pm 0.$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 (1.363) \pm 0.$  \\
-        {\sc POWHEG}  &  $1.3633 \pm 0.0004$  \\
-        {\sc VBFNLO}  &  $1.339 \pm 0.$  \\
-        \hline
-        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275) \pm 0.$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 (1.267)  \pm 0.$  \\
-        {\sc PHANTOM}+{\sc Pythia8} &  $1.235  \pm 0.$  \\
-        {\sc PHANTOM}+{\sc Herwig++} &  $1.260  \pm 0.$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275)$ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 (1.267)$ & $ 0.003$  \\
+        {\sc PHANTOM}+{\sc Pythia8} &  $1.235\phantom{0} $ & $0.001$  \\
+        {\sc PHANTOM}+{\sc Herwig++} &  $1.260\phantom{0} $ & $0.001$  \\
+        {\sc VBFNLO}+{\sc Herwig7} (LO) &  $1.3001$ & $0.0002$  \\
     \end{tabular}
@@
     are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin}, see the text for details.}
-{\bf MZ: MC uncertainties???}
 \end{table}
@@
 at most 10\%.\\
-Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}.
+Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}.
 {\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper section. Otherwise define it here}

### 2018-02-09 Draft/acknowledgements.tex
Lots of corrections and improvements

--- 2017-11-14 Draft/acknowledgements.tex
@@
- We thank ...
-Acknowledgement of VBSCAN COST action.
+The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
+Moreover, this work was supported by sveral STSM Grant from the COST Action CA16108.
+
+BB, AD, and MP acknowledge financial support by the
+German Federal Ministry for Education and Research (BMBF) under
+contract no.~05H15WWCA1 and the German Science Foundation (DFG) under
+reference number DE 623/6-1.

### 2018-02-09 Draft/contributions.tex
Some changes in sections 4.3 and 5.2
Minor changes on draft, mostly typos
Lots of corrections and improvements

@@
 In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
-In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are displayed.
+In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are reported.
 The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
@@
     \begin{tabular}{c|c|c|c}
-        Order & $ \mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
+        Order & $\mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
         \hline
@@
     \end{tabular}
-    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.
+    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
     These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}
@@
 In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
-The EW contribution peaks around an invariant mass of about $80\GeV$.
+In the distributions in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
 These are due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
 Note that these contributions are not present in calculations relying on the VBS approximation.
-Also, the EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$ and for jet rapidity difference larger than $2.5$.
+Also, the EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
+The same holds true for jet rapidity difference larger than $2.5$ (right).
+This clearly explains why these two observables are used to enhanced the EW contribution over the QCD one.
+In particular, in order to have a large EW contribution, rather exclusive cuts are required.
 
@@
 Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
-This is are the cuts used in Sec.~\ref{subsec:LOfiducial}.
+These are the cuts used in Sec.~\ref{subsec:LOfiducial}.
 

### 2018-02-09 Draft/crosssectionLO.tex
Lots of corrections and improvements

@@
-In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
+In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
 The order considered here is the order $\mathcal{O}(\alpha^6)$.

### 2018-02-09 Draft/crosssectionNLO.tex
Lots of corrections and improvements

@@
-In Tab.~\ref{tab:wg1_NLOrates}, the cross sections of the various tools at NLO QCD accuracy are presented.
-The order considered is $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
-In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions seems to visibly differing according to the approximations used already at the level of the fiducial cross section.
+In Tab.~\ref{tab:wg1_NLOrates}, the cross sections of the various tools at NLO-QCD accuracy are presented.
+The order considered is again the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$ and the fiducial volume is the one described in Sec.~\ref{subsec:inputpar}.
+In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions are visibly differ according to the approximations used.
 

### 2018-02-09 Draft/definition.tex
Lots of corrections and improvements

@@
 The two W bosons are mostly produced centrally.
-This is in contrast to the QCD contribution which favours jets in the central region.
+This is in contrast with the QCD contribution which favours jets in the central region.
 Therefore, the event selection usually involves rapidity-difference and invariance-mass cuts for the jets.
-This will also be discussed in Sec.~\ref{subsec:contributions}.
+This will be further discussed in Sec.~\ref{subsec:contributions}.
 

### 2018-02-09 Draft/description.tex
Lots of corrections and improvements

@@
         in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
-        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
+        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, \MP{Is Collier not missing here?
+I think it made it to one of the default if I am correct} together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
         The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
@@
   \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for matching NLO-QCD calculations with parton showers.
-It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
+It relies on the user providing the matrix elements and Born phase space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
 For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
@@
 
-\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
-The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
-The IR divergences appearing in the real corrections are handles with the help of the Catani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
-To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
-These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particular VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
+\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
+It can compute arbitrary processes for the LHC at both NLO QCD and EW accuracy in the Standard Model.
+This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the Standard Model.
+To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
+In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
+The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
+In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained from this tool.
+One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
 

### 2018-02-09 Draft/distributionsLO.tex
Lots of corrections and improvements

@@
 In general, the agreement is at the level of $1\%$ or below for each bin.
-We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, transverse momentum.
+We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
 This means that at LO, in the fiducial volume, the VBS approximation is good to a per cent.
+\MP{Add some comment with respect to the 2D scan.}
 

### 2018-02-09 Draft/distributionsNLO.tex
Lots of corrections and improvements

@@
 While {\sc MadGraph5\_aMC@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
-This is in contrast with {\sc BONSAY} and {\sc POWHEG} which approximate the full computation reasonably well over the whole range and in particular the high transverse-momentum region.
+This is in contrast with {\sc BONSAY} and {\sc POWHEG} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
 Finally, {\sc VBFNLO} predicts higher rates over the whole range apart around $200\GeV$ where it is in perfect agreement with the complete calculation.
@@
 {\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
-The other three VBS approximations seem to be close to each other.
+The other three VBS approximations are close to each other within few per cent.
 

### 2018-02-09 Draft/input.tex
Lots of corrections and improvements

@@
 \end{equation}
-The CKM-Matrix is assumed to be diagonal, meaning that we neglect mixing between different quark families.
-%
+The CKM-Matrix is assumed to be diagonal, meaning that the mixing between different quark families is neglected.
 The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.
@@
 %
-This choice of scale has been shown to provide stable NLO predictions \cite{Denner:2012dz}.
+This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.
 

### 2018-02-09 Draft/introduction.tex
Lots of corrections and improvements

@@
 Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and triple and quartic gauge couplings.
-It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarized.
-The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual form of the Higgs sector.
+It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarised.
+The scattering of longitudinally polarised bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual structure of the Higgs sector.
 A detailed study of this class of processes will therefore further constrain the Higgs couplings and hint at or exclude non-Standard Model Higgs bosons.
@@
 The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because of the double-charge structure of the leptonic final state that limits the number of partonic processes and total number of Feynman diagrams for each process.
-It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg to $\PW^+\PW^-$ scattering, which has the largest cross section.
+It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg $\PW^+\PW^-$ scattering, which has the largest cross section.
 Therefore, the $\PW^+\PW^+$ scattering is an ideal candidate for a detailed study of various theoretical predictions.
 
-In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
+In the last few years, several next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
 The VBS computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
@@
 Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
-Preliminary results have already been made public in Ref.~\cite{Anders:2018gfr}.
+Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
 
 The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
-This final state possesses three contributions at LO whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
+This final state possesses three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
 They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
@@
 In this article we will refer to it as simply \emph{NLO}.
-As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
-In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more detail later.
+As for the LO study, the various predictions are compared at the level of the cross section and differential distributions now at NLO accuracy.
+In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more details later.
 To our knowledge, such a detailed study was still missing.

### 2018-02-09 Draft/process.tex
Lots of corrections and improvements

@@
 Instead, one can keep the W boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
-Then the polarisation of the gauge boson is accommodated following the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
+Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
 Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
@@
 
-Finally the full $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ computation consists also of EW corrections in the virtual as well as real corrections \cite{Biedermann:2017bss}.
+Finally, when considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ and its corresponding real QCD radiation, other contributions have to be added.
+Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
+The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones.\footnote{For more details, the reader is referred to Ref.~\cite{Biedermann:2017bss}.}
 Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

### 2018-02-09 Draft/scanLO.tex
Lots of corrections and improvements

@@
 As explained previously, the low di-jet invariant mass and low jet rapidity separation is dominated by tri-boson production.
-Therefore a comparison of the various approximations in an \emph{inclusive} phase-space volume is performed.
-To that end, we have chosen for the inclusive fiducial volume to take the following values for the VBS cuts
+Therefore, a comparison of the various approximations in an \emph{inclusive} phase-space volume should exclude the region where tri-boson contributions are dominating.
+To that end, we have chosen for the inclusive fiducial volume to take the following values for the VBS cuts:
+%
 \begin{equation}
 \label{eq:inclusive}
-	m_{jj} > 200\GeV\,,\qquad |\Delta y_{jj}| > 2 .
+	m_{jj} > 200\GeV\, \qquad {\rm and} \qquad |\Delta y_{jj}| > 2 .
 \end{equation}
 
-The figure showing this is Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
+In Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
 Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
@@
 The full calculation is approximated at the level of $\pm10\%$ everywhere apart in the upper left corner where the inclusion of $s$-channel contributions did not improve the approximation.
-This is due to ...
+This is due to ... \MP{Ideas?}
 
@@
 \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ at order $\mathcal{O}(\alpha^6)$.
+\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at order $\mathcal{O}(\alpha^6)$.
 Ratio of approximated squared amplitudes over the full matrix element.

### 2018-02-09 Draft/scanNLO.tex
Lots of corrections and improvements

--- 2018-02-07 Draft/scanNLO.tex
@@
-We now present the inclusive study performed at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$.
+We now present an inclusive study performed at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$.
 
@@
 For the inclusive region (see Eq.~\eqref{eq:inclusive}), this approximation is good up to $\pm10\%$ apart for large di-jet differences and low di-jet invariant mass.
-It is therefore interesting to check how good this approximation is at NLO.
+It is therefore interesting to check how good this approximation performs at NLO.
 Thus, we impose the same kinematic cuts shown in Sec.~\ref{subsec:inputpar} and apply the VBS cuts of Eq.~\eqref{eq:inclusive}.
 
-We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$) while {\sc VBFNLO} adds the $s$-channel contributions ($|s|^2+|t|^2+|u|^2$).
-On the other hand {\sc Recola} employs full matrix elements, adding also $t/u$ interferences, factorisable, and non-factorisable QCD corrections to the order $\mathcal{O}(\alpha^6)$.
-This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.
+We compare three different predictions at NLO QCD: 
+the VBS approximation ($|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions ($|s|^2+|t|^2+|u|^2$) from {\sc VBFNLO}, and the full computation.
+The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable, and non-factorisable QCD corrections as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^6)$ are included.
+% This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.
 The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
@@
 \end{tabular}
-\caption{\label{tab:crosssecINCLUSIVE} Total cross sections at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ GeV, $|\Delta y_{\Pj\Pj}|>2$.}
+\caption{
+Total cross sections at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
+\label{tab:crosssecINCLUSIVE}
 \end{table}
 
-The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) gives a negative discrepancy of about $10\%$ with respect to the full calculation.
-The inclusion of $s$-channel diagrams improves the approximate prediction down to a $2\%$ discrepancy.
+The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) is lower by about $10\%$ with respect to the full calculation.
+The inclusion of $s$-channel diagrams improves the approximate prediction down to a $2\%$-level.
 
-These discrepancies are much more evident in differential distributions.
-In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $\Delta y_{\Pj\Pj}$.
-For large $m_{\Pj\Pj}$ and large $\Delta y_{\Pj\Pj}$, as expected, the VBS approximation is performing well and its $s$-channel extension agree with the full calculation within few per cents.
+These differences are much more evident in differential distributions.
+In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
+For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agree with the full calculation within $10\%$ per cent.
 % On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
 % In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
-This is in contrast to the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation goes up to $30\%$.
-The inclusion of $s$-channels cures partly the discrepancy in these regions.
-Still, for the very low $m_{\Pj\Pj}$ a small discrepancy of about $5\%$ remains.
+This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation goes up to $30\%$.
+The inclusion of $s$-channels cures partly the discrepancy in this region.
+Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains.
 This might indicate that also interferences (GP: and non--factorizable QCD corrections ? \MP{I don't know, we have to think about it}) are needed in this phase-space region.
 
-In order to investigate further the jet pair kinematics, we divide the $m_{\Pj\Pj},\Delta y_{\Pj\Pj}$ plane in 2-dimensional bins and analyse the cross sections.
-In particular we compute in each bin the ratio of the approximated cross sections over the full one.
-In Fig.~\ref{fig:ratio2d_NLO} and Fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.
+In order to investigate further the jet-pair kinematics, we look at the double-differential distribution in the variables $m_{\Pj\Pj}$ and $\Delta y_{\Pj\Pj}$.
+In particular, we compute in each bin the ratio of the approximated cross sections over the full one.
+In Fig.~\ref{fig:ratio2d_NLO} and Fig.~\ref{fig:mjjdyjj_2d_NLO} we show the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$, respectively.
 
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/dyjj_nlo.pdf}}
-\caption{NLO QCD inclusive study: distributions in $m_{\Pj\Pj}$ (left) and $\Delta y_{\Pj\Pj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_1}
+\caption{
+Differential distributions in $m_{\Pj\Pj}$ (left) and $|\Delta y_{\Pj\Pj}|$ (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+\label{fig:mjjdyjj_1d_1}
 \end{figure}
@@
 {\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}}
-%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
-\caption{Cross sections (fb) per bin of $(m_{\Pj\Pj},\,\Delta y_{\Pj\Pj})$ at NLO QCD $\mathcal{O}(\alphas\alpha^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$. Results of {\sc Bonsay} (approximated) and {\sc Recola} (full) calculations.
-{\bf GP: notation to be changed, Mjj > mjj, alphas alpha} }\label{fig:ratio2d_NLO}
+\caption{Ratio of cross sections (fb) per bin of $(m_{\Pj\Pj},\,|\Delta y_{\Pj\Pj}|)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
+{\bf GP: notation to be changed, Mjj -> mjj, alphas alpha} }
+\label{fig:ratio2d_NLO}
 \end{figure}
+%
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-\caption{Cross section (fb) per bin of $(m_{\Pj\Pj},\,\Delta y_{\Pj\Pj})$ at NLO QCD $\mathcal{O}(\alphas\alpha^6)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$.
-Results of {\sc VBFNLO} (approximated) and {\sc Recola} (full) calculations. {\bf GP: notation to be changed, Mjj > mjj, alphas alpha}}\label{fig:mjjdyjj_2d_NLO}
+\caption{Ratio of cross sections (fb) per bin of $(m_{\Pj\Pj},\,|\Delta y_{\Pj\Pj}|)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation with $s$-channel contributions over the full computation.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
+{\bf GP: notation to be changed, Mjj -> mjj, alphas alpha} }
+\label{fig:mjjdyjj_2d_NLO}
 \end{figure}
 
-As expected, in the low invariant mass--low rapidity separation region of the jet pair the VBS approximation fails badly (up to $40\%$ discrepancies).
-The inclusion of the $s$-channel brings down to at most $5\%$.
-However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}.
+As expected, in the low invariant mass--low rapidity separation region of the jet pair the VBS approximation fails significantly (up to $40\%$ discrepancies).
+The inclusion of the $s$-channel brings the difference down to at most $5\%$.
+However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}.
 In this region, the two leading jets have soft transverse momenta, according to the following low-angle approximation
@@
 
-The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low $\pt$ region of the leading jet in the left panel of Fig.~\ref{fig:mjjdyjj_1d_2}.
+The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low $\pt$ region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
 In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the level of $15\%$ are present.
 This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
-For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about 5-10 \%.\\
+For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is of about $5-10\%$.
 In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
-\caption{NLO QCD inclusive study: transverse momentum and rapidity distributions of the leading jet, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
+\caption{Differential distributions in the transverse momentum and rapidity of the hardest tagging jet at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+\label{fig:mjjdyjj_1d_2}
 \end{figure}
 
-Concerning leptonic kinematics, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron \MP{We should defined the Zep var.
-somewhere}.
+Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron. 
+It is defined as
+%
+\begin{equation}
+  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
+  \label{eq:Zeppenfeld}
+\end{equation}
+%
+Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
+%
 \begin{figure}[hbt]
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
-\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
+\caption{Differential distributions in the lepton-lepton invariant mass and the electron Zeppenfeld variable at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+\label{fig:mjjdyjj_1d_3}
 \end{figure}
-The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees pretty well with the full curve, generated with {\sc Recola}; the {\sc Bonsay} curve is about 10 \% smaller.
-The discrepancies are roughly constant over the whole specrum.\\
-Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$--channels, with increasing discrepancy w.r.t.
-the full result at large values.
-The muon variable $z_{\mu}$ behaviour is almost identical to $z_e$.\\
+%
+The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees rather well with the full curve, obtained from {\sc MoCaNLO+Recola}.
+The prediction from {\sc Bonsay} is about $10\%$ lower.
+The discrepancies are roughly constant over the whole spectrum.
+Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$-channels, with increasing discrepancy with respect to the full result at large values.
+The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.
 
 In conclusion, both the loose minimum di-jet invariant mass cut and the inclusion of QCD radiative correction make the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
-Nevertheless, interferences and non-factorizable QCD corrections should be included to reduce the discrepancies down to the $\approx 1\%$  level, mainly in inclusive analyses.
-Instead, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($M_{\Pj\Pj} \gtrsim 600 \GeV$, $\Delta y_{\Pj\Pj} \gtrsim 3$), for both total cross section and differential distributions.
+Nevertheless, interferences and non-factorizable QCD corrections should be included to reduce the discrepancies down to about $1\%$, mainly in inclusive analyses.
+Instead, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($M_{\Pj\Pj} \gtrsim 600 \GeV$, $|\Delta y_{\Pj\Pj}| \gtrsim 3$), for both total cross section and differential distributions.

### 2018-02-09 Draft/shower.tex
Lots of corrections and improvements

@@
-We now turn to discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
+We now discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
 a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
-matching schemes, PS employed and of the other details of the matching (such as the choice of the shower initial scale). Among
-the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG} and {\sc VBFNLO}
+matching schemes, parton shower employed and of other details of the matching (such as the choice of the parton shower initial scale). Among
+the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG}, and {\sc VBFNLO}
 can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO}, we
 restrict ourselves to showing results only in the VBS approximation,
-{\emph i.e.} the $s$-channel contributions are neglected here. Besides,
+{\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
 also {\sc PHANTOM} is employed for LO+PS results.\\
-{\sc MG5\_aMC},
-which
+{\sc MG5\_aMC}, which
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3)
-and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the omonymous matching procedure is
-employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8}
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
+For {\sc POWHEG}, the homonymous \MP{Is it the correct word?
+Because it would mean that the work ``Powheg'' has different meaning.
+Isn't it?}
+matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8}
 {\bf MZ VERSION? if same as MG5, put it at the end together with the
@@
 Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.
-Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\
+Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.
 
-Results will be presented within the cuts described in Section~\ref{subsec:inputpar}, applied after shower and hadronization (this implies that jets
-are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or no cuts at all)
-must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
+Results will be presented within the cuts described in Sec.~\ref{subsec:inputpar}, applied after shower and hadronisation (this implies that jets
+are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
+must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.
 
-A slightly different setup has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
+Compared to the fixed order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
 ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is anyway dominated by doubly-resonant contribution, the
@@
 and factorisation scales are set, the $\Delta R_{\Pj\Pl}$ cut is not imposed during the jet-clustering procedure, but this has no visible effect
-on the results.
+on the results \MP{Is it true? Because I remember some numbers from Christopher with $1\%$ or so}.
 
@@
     for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
-    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin}, see the text for details.}
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).}
 \end{table}
 
-We now turn to present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Table~\ref{tab:PSrates}, both at LO and NLO
+We now present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Table~\ref{tab:PSrates}, both at LO and NLO
 accuracy. For {\sc MG5\_aMC}, the numbers in parentheses are rescaled to take into account the width effects described in the above paragraph. Once this effect is taken into
-account, total rates from different tools agree within few percents. Larger discrepancies however will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within few per cent. Larger discrepancies however will appear for differential observables, which we are going to discuss in
 the following. For any observable, results will be presented in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
-with different colours in the main frame. In the inset, these predictions are compared in both cases with the fixed-order prediciton at NLO accuracy (obtained with
-{\sc VBFNLO}). For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.\\
+with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
+{\sc VBFNLO} \emph{i.e.}\ the VBS approximation with $s$-channel contributions).
+For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
 
-The first observable we investigate is the exclusive jet multiplicity, shown in Figure~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
+The first observable we investigate is the exclusive jet multiplicity, shown in Fig.~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
 main effects are driven by the parton shower that is employed {\sc Herwig++/7} or {\sc Pythia8}, with the clear tendency of producing more radiation for the latter,
 leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
-initial scale of the shower. The main effect of NLO corrections for this (rather inclusive) observable is to stabilize the predictions for the two-jet bin, where discrepancies
-among tools are reduced to about 10\%. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
+initial scale of the parton shower. The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
+among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
 {\sc MG5\_aMC}, while the smallest rate is predicted by {\sc Powheg}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
@@
 prediction dubbed {\sc Powheg-no shower} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
-interplay between the real-emission matrix element and the shower emission. \\
-The next observable that we study is the invariant mass of the two tagging jets, shown in Figure~\ref{fig:PSmjj}. For this observable, both at LO+PS and NLO+PS,
-the spread of predictions matched with parton shower is rather small
-($\lesssim 10\%$, if one compensates for the 6\% width effect for {\sc MG5\_aMC}); LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
-about -30\% at the end of the displayed range. At NLO+PS, this effect is much mitigated, owing to the better description of the first QCD emission which is now driven by
- the real-emission matrix element.\\
-The rapidity difference between the two tagging jets, shown in Figure~\ref{fig:PSdyjj} has some similarities to the invariant-mass distribution: at LO+PS all predictions,
-except for {\sc VBFNLO3+Herwig7} where the effect is mitigated, show the tendency to deplete the large-separation region with respect to the fixed-order predicion, in a
-quantitatively similar way. At NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
-exception is the {\sc Powheg} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
-it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
-{\sc MG5\_aMC+Herwig++} prediction (although with rather large statistical uncertainties).\\
-The transverse momentum of the hardest and second-hardest jets are shown in Figures~\ref{fig:PSpt1} and~\ref{fig:PSpt2} respectively. In general, for both observables,
-predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transvers-momentum spectra are softer than
-the fixed-NLO one, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
-effect is mitigated by NLO corrections. The only feature that it may be worth to notice among the NLO+PS predictions is the tendency of {\sc Powheg} to suppress the
-hardest-jet spectrum at low transverse momentum ($p_T<100 \GeV$).\\
-If we consider the rapidity of the second jet, Figure~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
-stabilization at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions
-obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; {\sc Powheg}\ displays an enhancement of the central region, and a consequent suppression in the
-peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
-at most 10\%.\\
-Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}.
-{\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper section. Otherwise define it here}
-In general, for observables which involve the third jet, one
-can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The rapidity and $z$ variable
-are a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation (corresponding to low values of $z$)
-is clearly visible; it is interesting to notice that
-this effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+Pythia8}. If it is true that the central enhancement
-is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediciton), however even at NLO+PS the central region
-($z_{j_3}<0.5$) is cursed by huge differences between tools. Large differences, reaching a factor 2, persist also away from the central region. \\
-
-In conclusion, the comparison of tools including matching with parton-shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
-effectively at NLO accuracy differences between tools are at (or below) the 10\% level. {\bf MZ compare this number with scale uncertainties}
-Some exceptions exist, e.g. the rapidity separation of the two tagging jets, which
-on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is
-generated {\bf MZ cite here H VBF at NNLO?}.
-Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
-experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory uncertainties. In order to improve the
-description of these observables, a simulation of VBS+j at NLO, currently unavailable but within the reach of modern automated tools, is certainly desirable.
+interplay between the real-emission matrix element and the shower emission.
 
@@
 \end{figure*}
+
+The next observable that we study is the invariant mass of the two tagging jets, shown in Fig.~\ref{fig:PSmjj}. For this observable, both at LO+PS and NLO+PS,
+the spread of predictions matched with parton shower is rather small
+($\lesssim 10\%$, if one compensates for the 6\% width effect for {\sc MG5\_aMC}); LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
+about -30\% at the end of the displayed range.
+At NLO+PS, this effect is much more mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
+
+The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj} has some similarities to the invariant-mass distribution: at LO+PS all predictions,
+except for {\sc VBFNLO3+Herwig7} where the effect is mitigated, show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
+quantitatively similar way. At NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
+exception is the {\sc Powheg} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
+it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
+{\sc MG5\_aMC+Herwig++} prediction (although with rather large statistical uncertainties).
+
+The transverse momentum of the hardest and second-hardest jets are shown in Figures~\ref{fig:PSpt1} and~\ref{fig:PSpt2} respectively. In general, for both observables,
+predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transverse-momentum spectra are softer than
+the fixed-NLO ones, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
+effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of {\sc Powheg} to suppress the
+hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).\\
+If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
+stabilisation at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions
+obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; {\sc Powheg}\ displays an enhancement of the central region, and a consequent suppression in the
+peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
+at most $10\%$.
+
+Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}.
+{\bf MZ the rapidity can be dropped (check also the following discussion in case)}
+In general, for observables which involve the third jet, one
+can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The rapidity and Zeppenfeld variable $z$
+are a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation (corresponding to low values of $z$)
+is clearly visible; it is interesting to notice that
+this effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+Pythia8}. If it is true that the central enhancement
+is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
+($z_{j_3}<0.5$) is cursed by huge differences between tools. Large differences, reaching a factor 2, persist also away from the central region. \\
+
+In conclusion, the comparison of tools including matching with parton-shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
+effectively at NLO accuracy differences between tools are at (or below) the $10\%$ level. {\bf MZ compare this number with scale uncertainties}
+Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
+on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is
+generated {\bf MZ cite here H VBF at NNLO?}.
+Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
+experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory uncertainties. In order to improve the
+description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern automated tools, is certainly desirable.
 

### 2018-02-12 Draft/crosssectionLO.tex
some improvements in the draft

@@
 The order considered here is the order $\mathcal{O}(\alpha^6)$.
-We note that several full predictions are not in statistical agreement.
-These are possibly due to too aggressive estimations of statistical uncertainty or ... \MP{To be added}
-Nonetheless, all these predictions agree within less than $0.5\%$.
+We note that several full predictions are not in statistical agreement. These are possibly due to Monte-Carlo 
+integrators performing too aggressive estimations of statistical uncertainties. Nonetheless, all these predictions agree within less than $0.5\%$.
 At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
-This simply means that the various VBS approximations are not worth than $0.5\%$ at the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
+This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
+the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
 
@@
         {\sc Bonsay}  &  $X$ & $0.0002$ \\
-        {\sc MG5\_aMC}&  $X$ & $0.001$  \\
+        {\sc MG5\_aMC}&  $1.435$ & $0.004$ TO BE UPDATED  \\
         {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\

### 2018-02-12 Draft/crosssectionNLO.tex
some improvements in the draft

@@
         {\sc Bonsay}  &  $X$ & $0.0009$  \\
-        {\sc MG5\_aMC}&  $X $ & $0.003$  \\
+        {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
         {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\

### 2018-02-12 Draft/description.tex
some improvements in the draft

@@
         in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
-        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, \MP{Is Collier not missing here?
-I think it made it to one of the default if I am correct} together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
+        Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
+        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweigthing
+        at zero additional CPU cost~\cite{Frederix:2011ss}.\\
         The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
@@
         and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections,
-        only loops with QCD-interacting particles are generated.
-        \MP{Detail of the approximation done, divergent part, assumed to cancel etc.}
+        only loops with QCD-interacting particles are generated. As it has been already mentioned, such an approximation is equivalent to the assumption that the finite part of
+        those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
+        pole-cancelation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
+        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards/FKS\_params.dat} file to -1.
 

### 2018-02-12 Draft/shower.tex
some improvements in the draft

@@
         \hline\hline
-        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 (1.368)$ & $0.004$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 (1.363)$ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 \, (1.368)$ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 \, (1.363)$ & $0.004$  \\
         {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
@@
         \hline
-        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275)$ & $0.003$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 (1.267)$ & $ 0.003$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 \, (1.275)$ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 \, (1.267)$ & $ 0.003$  \\
         {\sc PHANTOM}+{\sc Pythia8} &  $1.235\phantom{0} $ & $0.001$  \\

### 2018-02-12 Draft/shower.tex
some more edits in shower.tex

@@
 are a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation (corresponding to low values of $z$)
-is clearly visible; it is interesting to notice that
-this effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+Pythia8}. If it is true that the central enhancement
+is clearly visible\footnote{The effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF/S-type processes,
+can be mitigated by setting {\tt SpaceShower:dipoleRecoil = on} in the {\sc Pythia8} input file (this requires version $\ge8.230$). 
+However, such a setting is not compatible with the matching
+in {\sc MG5\_aMC}, and has other effects, though smaller, on the rapidity spectrum of the two hardest jets.}; it is interesting to notice that
+this effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+Pythia8}. A similar
+behaviour of {\sc Pythia8}
+has been also observed in the study of EW production of a Z boson in association with two jets (see the recent CMS measurement, 
+Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}. 
+If it is true that the central enhancement
 is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
@@
 Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
-experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory uncertainties. In order to improve the
-description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern automated tools, is certainly desirable.
+experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory 
+uncertainties. On the one hand, un order to improve the
+description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern 
+automated tools, is certainly desirable; on the other hand, measurements of processes with similar 
+color flow (EW production of a single vector boson plus jets,
+ VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data.
 

### 2018-02-13 parton-shower/MG5_aMC/envelope.py
Process variation for MG5_aMC
rescale as the diagrams seem to contain a factor 1e4
split into variations PDF-only, scale-only and both
(hat tip to Johannes Bellm for the basis of the script)

@@ -1,0 +1,128 @@
+#!/usr/bin/python
+
+## import modules
+import os
+import yoda
+import glob
+####################
+
+## declare modes
+# generate yodas
+# generate rivet-mkhtml command
+####################
+
+import  optparse, sys, math
+
+parser = optparse.OptionParser(usage=__doc__)
+parser.add_option('-o', '--output', default='-', dest='OUTPUT_FILE')
+#parser.add_option('-c', '--central', default='-', dest='CENTRAL_FILE')
+opts, fileargs = parser.parse_args()
+            
+####################
+
+## Put the incoming objects into a dict from each path to a list of histos and scalings
+
+filenames = []
+for fa in fileargs:
+  filenames += [fa]
+
+# check for at least one input file
+if len(filenames) < 1:
+  print "need at least one input file"
+  exit(1)
+
+## generate all variations
+if True:
+  # from yoda-manipulate:
+  scatters_all = {}
+  scatters_pdf = {}
+  scatters_scale = {}
+  scatters_central = {}
+  for filename in filenames:
+    # print filename
+    for p, ao in yoda.readYODA(filename).iteritems():
+      if isinstance(ao, yoda.Scatter2D):
+        scatter = ao
+      elif isinstance(ao, yoda.Histo1D):
+        scatter = yoda.Scatter2D(ao.path, ao.title)
+        for bin in ao.bins:
+          scatter.addPoint(yoda.Point2D(bin.xMid, bin.height, 0.5*bin.xWidth, bin.heightErr))
+      else:
+        print "cannot treat ", ao
+        continue
+      path = ao.path.split()
+      scatter.path = path[0]
+      if path[1] == "PDF=":
+        scatters_all.setdefault(path[0], []).append(scatter)
+        scatters_pdf.setdefault(path[0], []).append(scatter)
+        if path[2] == "260000":
+          scatters_central.setdefault(path[0], []).append(scatter)
+      elif path[1] == "dyn=":
+        scatters_all.setdefault(path[0], []).append(scatter)
+        scatters_scale.setdefault(path[0], []).append(scatter)
+      elif path[1] == "0":
+        pass # ignore
+      elif path[1] == "central":
+        pass # ignore
+      else:
+        print "Unknown path object: ", ao.path
+
+  # write out
+  scatters_outall = {}
+  scatters_outpdf = {}
+  scatters_outscale = {}
+
+  ## all
+  for p, scatters in scatters_all.iteritems():
[…]

### 2018-02-13 parton-shower/rivetplot_scale.sh
Add variation script and output
scale and PDF variation from MG5aMC
scale variation from VBFNLO

@@ -1,0 +1,112 @@
+#! /bin/sh
+
+rivet-mkhtml -o rivet-NLOPSvariation_scale \
+  VBFNLO/VBFNLO-NLO.yoda\
+:"Title=NLO"\
+:"ErrorBands=1"\
+:"ErrorBandColor=red"\
+:"RatioPlotErrorBandColor=red"\
+:"ErrorBandOpacity=0.3"\
+  VBFNLO/Herwig-MCatNLO-DipoleShower_scale.yoda\
+:"Title=VBFNLO 3+H7-Dipole"\
+:"LineColor=blue"\
+:"ErrorBands=1"\
+:"ErrorBandColor=blue"\
+:"RatioPlotErrorBandColor=blue"\
+:"ErrorBandOpacity=0.3"\
+  MG5_aMC/run_PY8_10M_NLOPS.yoda\
+:"Title=MG5_aMC+Pythia 8"\
+:"LineColor=brown"\
+:"ErrorBands=1"\
+:"ErrorBandColor=brown"\
+:"RatioPlotErrorBandColor=brown"\
+:"ErrorBandOpacity=0.3"\
+  MG5_aMC/run_PY8_5M_NLOPS_error_scale.yoda\
+:"Title=MG5_aMC+Pythia 8(scale)"\
+:"LineColor=green"\
+:"ErrorBands=1"\
+:"ErrorBandColor=green"\
+:"RatioPlotErrorBandColor=green"\
+:"ErrorBandOpacity=0.3"\
+
+rivet-mkhtml -o rivet-NLOPSvariation_VBFNLOscale \
+  VBFNLO/VBFNLO-NLO.yoda\
+:"Title=NLO"\
+:"ErrorBands=1"\
+:"ErrorBandColor=red"\
+:"RatioPlotErrorBandColor=red"\
+:"ErrorBandOpacity=0.3"\
+  VBFNLO/Herwig-MCatNLO-DipoleShower_scale.yoda\
+:"Title=VBFNLO 3+H7-Dipole"\
+:"LineColor=blue"\
+:"ErrorBands=1"\
+:"ErrorBandColor=blue"\
+:"RatioPlotErrorBandColor=blue"\
+:"ErrorBandOpacity=0.3"\
+
+rivet-mkhtml -o rivet-NLOPSvariation_MG5aMCscale \
+  VBFNLO/VBFNLO-NLO.yoda\
+:"Title=NLO"\
[…]

### 2018-02-14 Draft/shower.tex
fixed some issues in yoda file with scale and PDF uncertainties from MG5_aMC

@@
 {\sc MG5\_aMC}, which
-employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3)
+employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
 and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).

### 2018-02-14 parton-shower/MG5_aMC/envelope.py
Additionally take stat uncertainty into account

@@ -15,14 +15,14 @@ import  optparse, sys, math
 
 parser = optparse.OptionParser(usage=__doc__)
 parser.add_option('-o', '--output', default='-', dest='OUTPUT_FILE')
-#parser.add_option('-c', '--central', default='-', dest='CENTRAL_FILE')
+parser.add_option('-c', '--central', default='-', dest='CENTRAL_FILE')
 opts, fileargs = parser.parse_args()
             
 ####################
 
 ## Put the incoming objects into a dict from each path to a list of histos and scalings
 
-filenames = []
+filenames = [opts.CENTRAL_FILE]
 for fa in fileargs:
   filenames += [fa]
 
@@ -52,20 +52,26 @@ if True:
         continue
       path = ao.path.split()
       scatter.path = path[0]
-      if path[1] == "PDF=":
+      if len(path) <= 1: #central
+        scatters_central.setdefault(path[0], []).append(scatter)
         scatters_all.setdefault(path[0], []).append(scatter)
         scatters_pdf.setdefault(path[0], []).append(scatter)
-        if path[2] == "260000":
-          scatters_central.setdefault(path[0], []).append(scatter)
-      elif path[1] == "dyn=":
-        scatters_all.setdefault(path[0], []).append(scatter)
         scatters_scale.setdefault(path[0], []).append(scatter)
-      elif path[1] == "0":
-        pass # ignore
-      elif path[1] == "central":
-        pass # ignore
       else:
-        print "Unknown path object: ", ao.path
+        if path[1] == "PDF=":
+          scatters_all.setdefault(path[0], []).append(scatter)
+          scatters_pdf.setdefault(path[0], []).append(scatter)
+          #if path[2] == "260000":
+          #  scatters_central.setdefault(path[0], []).append(scatter)
+        elif path[1] == "dyn=":
+          scatters_all.setdefault(path[0], []).append(scatter)
+          scatters_scale.setdefault(path[0], []).append(scatter)
+        elif path[1] == "0":
+          pass # ignore
+        elif path[1] == "central":
+          pass # ignore
+        else:
+          print "Unknown path object: ", ao.path
 
   # write out
   scatters_outall = {}
@@ -73,6 +79,7 @@ if True:
   scatters_outscale = {}
 
   ## all
+  ### scale
   for p, scatters in scatters_all.iteritems():
     for pcentral, scattercentral in scatters_central.iteritems():
[…]

### 2018-02-14 parton-shower/rivetplot_scale.sh

@@ -14,19 +14,19 @@ rivet-mkhtml -o rivet-NLOPSvariation_scale \
 :"ErrorBandColor=blue"\
 :"RatioPlotErrorBandColor=blue"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_PY8_10M_NLOPS.yoda\
-:"Title=MG5_aMC+Pythia 8"\
-:"LineColor=brown"\
-:"ErrorBands=1"\
-:"ErrorBandColor=brown"\
-:"RatioPlotErrorBandColor=brown"\
-:"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_PY8_5M_NLOPS_error_scale.yoda\
-:"Title=MG5_aMC+Pythia 8(scale)"\
+  MG5_aMC/run_PY8_5M_NLOPS_error_scalestat.yoda\
+:"Title=MG5_aMC+Pythia 8(scale+stat)"\
 :"LineColor=green"\
 :"ErrorBands=1"\
 :"ErrorBandColor=green"\
 :"RatioPlotErrorBandColor=green"\
+:"ErrorBandOpacity=0.3"\
+  MG5_aMC/run_PY8_5M_NLOPS_error_scale.yoda\
+:"Title=MG5_aMC+Pythia 8(scale)"\
+:"LineColor=brown"\
+:"ErrorBands=1"\
+:"ErrorBandColor=brown"\
+:"RatioPlotErrorBandColor=brown"\
 :"ErrorBandOpacity=0.3"\
 
 rivet-mkhtml -o rivet-NLOPSvariation_VBFNLOscale \
@@ -51,19 +51,19 @@ rivet-mkhtml -o rivet-NLOPSvariation_MG5aMCscale \
 :"ErrorBandColor=red"\
 :"RatioPlotErrorBandColor=red"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_PY8_10M_NLOPS.yoda\
-:"Title=MG5_aMC+Pythia 8"\
-:"LineColor=brown"\
-:"ErrorBands=1"\
-:"ErrorBandColor=brown"\
-:"RatioPlotErrorBandColor=brown"\
-:"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_PY8_5M_NLOPS_error_scale.yoda\
-:"Title=MG5_aMC+Pythia 8(scale)"\
[…]

### 2018-02-15 parton-shower/MG5_aMC/envelope.py
Update parton-shower plots

@@ -78,44 +78,6 @@ if True:
   scatters_outpdf = {}
   scatters_outscale = {}
 
-  ## all
-  ### scale
-  for p, scatters in scatters_all.iteritems():
-    for pcentral, scattercentral in scatters_central.iteritems():
-      if pcentral == p:
-        scatters_outall[scattercentral[0].path] = scattercentral[0].clone()
-    for i, point in enumerate(scatters_outall[scatters[0].path].points):
-      upper = float('-inf')
-      lower = float('inf')
-      for scatter in scatters:
-        val = scatter.points[i].y;
-        if val > upper:
-          upper = val
-        if val < lower:
-          lower = val
-        point.yErrs = (point.y-lower, upper-point.y)
-  # write envelopes
-  outname = opts.OUTPUT_FILE.replace(".yoda","_all.yoda")
-  yoda.write(scatters_outall.values(), outname)
-  ### scale + stat
-  for p, scatters in scatters_all.iteritems():
-    for pcentral, scattercentral in scatters_central.iteritems():
-      if pcentral == p:
-        scatters_outall[scattercentral[0].path] = scattercentral[0].clone()
-    for i, point in enumerate(scatters_outall[scatters[0].path].points):
-      upper = float('-inf')
-      lower = float('inf')
-      for scatter in scatters:
-        val = scatter.points[i].yMax;
-        if val > upper:
-          upper = val
-        val = scatter.points[i].yMin;
-        if val < lower:
-          lower = val
-        point.yErrs = (point.y-lower, upper-point.y)
-  # write envelopes
-  outname = opts.OUTPUT_FILE.replace(".yoda","_allstat.yoda")
-  yoda.write(scatters_outall.values(), outname)
   ## pdf
   for p, scatters in scatters_pdf.iteritems():
     for pcentral, scattercentral in scatters_central.iteritems():
@@ -134,25 +96,25 @@ if True:
   # write envelopes
   outname = opts.OUTPUT_FILE.replace(".yoda","_pdf.yoda")
   yoda.write(scatters_outpdf.values(), outname)
-  ## pdf + stat
-  for p, scatters in scatters_pdf.iteritems():
-    for pcentral, scattercentral in scatters_central.iteritems():
-      if pcentral == p:
-        scatters_outpdf[scattercentral[0].path] = scattercentral[0].clone()
-    for i, point in enumerate(scatters_outpdf[scatters[0].path].points):
[…]

### 2018-02-15 parton-shower/rivetplot.sh

@@ -3,90 +3,112 @@
 rivet-mkhtml -o rivet-NLOPS \
   VBFNLO/VBFNLO-NLO.yoda\
 :"Title=NLO"\
-:"ErrorBands=1"\
-:"ErrorBandColor=red"\
-:"RatioPlotErrorBandColor=red"\
+:"LineColor={[rgb]{0.40,0.40,0.40}}"\
+:"LineStyle=solid"\
+:"ErrorBands=0"\
+:"ErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"ErrorBandOpacity=0.3"\
-  VBFNLO/Herwig-MCatNLO-DipoleShower.yoda\
-:"Title=VBFNLO 3+H7-Dipole"\
-:"LineColor=blue"\
-:"ErrorBands=1"\
-:"ErrorBandColor=blue"\
-:"RatioPlotErrorBandColor=blue"\
+  MG5_aMC/run_HWPP_5M_NLOPS.yoda\
+:"Title=MG5_aMC+H++ 2.7.1"\
+:"LineColor={[rgb]{0.46,0.44,0.70}}"\
+:"LineStyle=solid"\
+:"ErrorBands=0"\
+:"ErrorBandColor={[rgb]{0.46,0.44,0.70}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.46,0.44,0.70}}"\
 :"ErrorBandOpacity=0.3"\
-  VBFNLO/Herwig-MCatNLO-DefaultShower.yoda\
-:"Title=VBFNLO 3+H7-QTilde"\
-:"LineColor=cyan"\
+  MG5_aMC/run_PY8_5M_NLOPS_error_all.yoda\
+:"Title=MG5_aMC+Pythia 8"\
+:"LineColor={[rgb]{0.91,0.16,0.54}}"\
+:"LineStyle=solid"\
 :"ErrorBands=1"\
-:"ErrorBandColor=cyan"\
-:"RatioPlotErrorBandColor=cyan"\
+:"ErrorBandColor={[rgb]{0.91,0.16,0.54}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.91,0.16,0.54}}"\
 :"ErrorBandOpacity=0.3"\
+  MG5_aMC/run_PY8_5M_NLOPS_error_scale.yoda\
+:"Title="\
[…]

### 2018-02-15 Draft/abstract.tex
direct modifications in the gitlab, please check!

@@
   current run-2 and future runs at design energy of the Large Hadron
-  Collider. The presence of triple and quartic gauge couplings gives
-  access to tests of the gauge sector and possible new-physics
-  contributions there. For this, a precise knowledge of the Standard
-  Model contributions is necessary, which at least matches the
-  experimental uncertainties.
+  Collider. The presence of triple and quartic gauge couplings in the process
+  gives access the gauge sector of the Standard Model and possible new-physics
+  contributions there. 
+  To test this hypothesis, a precise knowledge of the Standard
+  Model contributions is necessary, 
+  with a precision which at least matches the
+  experimental uncertainties
+  of existing and forthcoming measurements.
 
@@
   same-sign production of two W bosons with positive charge.
-In particular, we carry out a comparison between the full NLO QCD corrections against several approximations.
-This study is not only performed in the usual fiducial region used by experimental collaborations, but also in a more inclusive set-up.
-This allows to infer precisely the quality of such approximations.
-Finally, we discuss NLO predictions matched to various parton showers.
-Thanks to this, it is thus possible to infer the systematic errors related to vector-boson scattering at the NLO-QCD level and beyond.
+In particular, 
+we carry out a comparison between the full fixed-order NLO QCD corrections 
+against several approximations.
+This study is performed in the usual fiducial region used by experimental collaborations, 
+as well as in a more inclusive phase space,
+where the importance of the approximations can be infered.
+Eventually, we discuss NLO predictions matched to various parton showers.
+In summary, from the distributions presented it is thus possible to infer 
+the systematic unertainties due to missing higher orders in the calculations
+at the NLO + NLL QCD level.
 

### 2018-02-15 Draft/abstract.tex
updated figures of draft. Edited intro and abstract

@@
   of existing and forthcoming measurements.
-
   In this article, we present a detailed study of the vector-boson
-  scattering process with two positively charged leptons and missing
+  scattering process with two positively-charged leptons and missing
   transverse momentum in the final state, mediated predominantly by
   same-sign production of two W bosons with positive charge.
-In particular, 
-we carry out a comparison between the full fixed-order NLO QCD corrections 
-against several approximations.
-This study is performed in the usual fiducial region used by experimental collaborations, 
-as well as in a more inclusive phase space,
-where the importance of the approximations can be infered.
-Eventually, we discuss NLO predictions matched to various parton showers.
-In summary, from the distributions presented it is thus possible to infer 
-the systematic unertainties due to missing higher orders in the calculations
-at the NLO + NLL QCD level.
+  In particular, we first carry out a systematic comparison of the various 
+  approximations that are usually performed for this kind of process against the complete calculation, 
+  at LO and NLO QCD accuracy. Such  a study is performed both 
+  in the usual fiducial region used by experimental collaborations and in a more inclusive phase space,
+  where the differences among the various approximations lead to more sizeable effects.
+  Afterwards, we turn ourselves to predictions matched to parton showers, at LO and NLO: we show that on the
+  one hand, the inclusion of NLO QCD corrections leads to more stable predictions, but on the other the details 
+  of the matching and of the parton-shower programs lead to differences which are considerably larger than those
+  observed at fixed-order, even in the experimental fiducial region. 
+  We conclude with some recommendations for experimental studies of vector-boson scattering processes.
 

### 2018-02-15 Draft/introduction.tex
updated figures of draft. Edited intro and abstract

@@
-Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and triple and quartic gauge couplings.
-It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarised.
-The scattering of longitudinally polarised bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual structure of the Higgs sector.
+Vector-boson scattering (VBS) is a class of processes that make it possible 
+to probe the nature of Higgs-vector-vector couplings and triple and quartic gauge couplings.
+It is usually understood that VBS refers to the scattering of massive vector bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarised.
+The scattering of longitudinally-polarised bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual structure of the Higgs sector.
 A detailed study of this class of processes will therefore further constrain the Higgs couplings and hint at or exclude non-Standard Model Higgs bosons.
 
-The process with two positively charged W bosons is the VBS process with the largest signal-to-background ratio at the LHC, for which evidence has been found in $8 \TeV$ data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in $13\TeV$ data.
-For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
+The process with two positively charged $\PW$ bosons is the VBS process with the largest signal-to-background ratio at the LHC, for which evidence has been found in $8 \TeV$ data~\cite{Aad:2014zda,Khachatryan:2014sta} and has been subsequently
+observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in $13\TeV$ data. At present 
+the measurements of VBS processes are limited by statistics but the situation will change in a near future.
 On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.
@@
 
-The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
+The hadronic process ito be considered is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
 This final state possesses three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
@@
 The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
-In the following, this order is the one where our comparisons are focused on.
-In this article we will refer to it as simply \emph{NLO}.
+In the following, this order is the one where our comparisons are focused on and we will refer to it as simply \emph{NLO}.
 As for the LO study, the various predictions are compared at the level of the cross section and differential distributions now at NLO accuracy.
-In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more details later.
+In particular, this makes it possible to infer the accuracy of the so-called VBS approximation, which we will define in more details later.
 To our knowledge, such a detailed study was still missing.
 
-Finally, several predictions featuring parton shower are compared.
-This allows to infer systematic differences between the various predictions.
+Finally, several predictions featuring parton shower are compared, giving the possibility to infer systematic differences between the various predictions.
 A first study for the $\PW^+ \PW^- \Pj \Pj$ VBS process has been presented in
@@
 shower and both{\sc MC@NLO}-like~\cite{Frixione:2002ik} and {\sc POWHEG}-like~\cite{Nason:2004rx,Frixione:2007vw} matching as implemented
-in {\sc Herwig 7}~\cite{Bellm:2015jjp}, also showing scale-variation uncertainties.
+in {\sc Herwig 7}~\cite{Bellm:2015jjp}, also showing scale-variation uncertainties. In this work we extend such a comparison by presenting 
+results obtained by {\sc MadGrap5\_aMC@NLO}, {\sc Powheg} and {\sc Phantom} {\bf CITES}, possibly matched with different parton-showers.
 This is the first time in the literature that NLO QCD calculations for VBS processed matched to parton shower are compared between different generators.
-
-Obviously all VBS processes deserve such a detailed study but the present article sets standards for inferring systematics related to NLO corrections and beyond.
 

### 2018-02-15 Draft/introduction.tex
fixed a tupo

@@
 in {\sc Herwig 7}~\cite{Bellm:2015jjp}, also showing scale-variation uncertainties. In this work we extend such a comparison by presenting 
-results obtained by {\sc MadGrap5\_aMC@NLO}, {\sc Powheg} and {\sc Phantom} {\bf CITES}, possibly matched with different parton-showers.
+results obtained by {\sc MadGraph5\_aMC@NLO}, {\sc Powheg} and {\sc Phantom} {\bf CITES}, possibly matched with different parton-showers.
 This is the first time in the literature that NLO QCD calculations for VBS processed matched to parton shower are compared between different generators.

### 2018-02-15 Draft/abstract.tex
further small changes

@@
   transverse momentum in the final state, mediated predominantly by
-  same-sign production of two W bosons with positive charge.
+  same-sign production of two $\PW$ bosons with positive charge.
   In particular, we first carry out a systematic comparison of the various 

### 2018-02-15 Draft/definition.tex
further small changes

@@
-The scattering of two positively charged W bosons is proceeding at the LHC through the partonic process:
+The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay proceeds at the LHC through the partonic process:
 %
@@
 
-The process can also be mediated via a gluon connecting the two quark lines while the W bosons are radiated off the quark lines.
+The process can also be mediated via a gluon connecting the two quark lines while the $\PW$ bosons are radiated off the quark lines.
 These contributions are of order $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$ and feature different kinematical behaviours than the EW contribution.
@@
 The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
-The two W bosons are mostly produced centrally.
+The two $\PW$ bosons are mostly produced centrally.
 This is in contrast with the QCD contribution which favours jets in the central region.
-Therefore, the event selection usually involves rapidity-difference and invariance-mass cuts for the jets.
+Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
 This will be further discussed in Sec.~\ref{subsec:contributions}.

### 2018-02-15 Draft/process.tex
some improvements in the draft
further small changes

@@
 As mentioned previously, the contribution of main interest in our process is
-the scattering of two W gauge bosons, which includes the quartic gauge-boson vertex.
+the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex.
 Therefore it is justified to approximate the full EW contributions simply by only these contributions which contain the $2\rightarrow 2$ scattering process as a subpart.
-However, this set of contributions is not gauge invariant.
-To make it gauge invariant, one should perform an on-shell projection of the incoming W bosons.
+However, this set of contributions is not gauge invariant. In order to make it gauge invariant, one 
+should perform an on-shell projection of the incoming and outgoing $\PW$ bosons {\bf MZ: it is incoming and outgoing, right? in case modify what follows}.
 Unfortunately, these momenta are space-like and thus a simple on-shell projection is not possible.
-Instead, one can keep the W boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
+Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
 Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
@@
 These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed.
-The $s$-channel squared diagrams and any interferences with $s$-channels are left out as well.
+The $s$-channel squared diagrams and any interferences with $s$-channels are also discarded.
 This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
@@
 
-The squared matrix element of the $s$-channel contributions can be added in addition, but all interferences between different kinematic channels are still neglected.
-This is the level of simulation available in {\sc VBFNLO}.
+A further refinement is to add the squared matrix element of the $s$-channel contributions, still neglecting 
+all interferences between different kinematic channels, as it is implemented in in {\sc VBFNLO}.
 
 All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard}) consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
-Note that the final W boson can always be considered either on-shell or off-shell without affecting the previous discussion.
+Note that the final $\PW$ boson can always be considered either on-shell or off-shell without affecting the previous discussion.
 All the codes mentioned here are described in details in the following sub-section.
@@
 A further refinement is to consider the full real contributions as well as part of the virtual.
-In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and assuming a cancellation of the infrared (IR) poles.
-\MP{True?
-I cannot remember exactly what is included}.
-\MR{What about gauge invariance? A comment about that would be useful as well.}
-Such predictions are provided by {\sc MG5\_aMC}.
+In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and 
+assuming a cancellation of the infrared (IR) poles. Such an approximation is implemented by {\sc MG5\_aMC}.
 

### 2018-02-15 Draft/shower.tex
further edits in shower.tex

@@
         \hline\hline
-        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 \, (1.368)$ & $0.004$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 \, (1.363)$ & $0.004$  \\
-        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
-        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389$ & $0.0006$  \\
-        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
-        \hline
-        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 \, (1.275)$ & $0.003$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 \, (1.267)$ & $ 0.003$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.352 $ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.343 $ & $ 0.003$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.275$ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.267$ & $ 0.003$  \\
         {\sc PHANTOM}+{\sc Pythia8} &  $1.235\phantom{0} $ & $0.001$  \\
         {\sc PHANTOM}+{\sc Herwig++} &  $1.260\phantom{0} $ & $0.001$  \\
-        {\sc VBFNLO}+{\sc Herwig7} (LO) &  $1.3001$ & $0.0002$  \\
+        {\sc VBFNLO}+{\sc Herwig7} &  $1.3001$ & $0.0002$  \\
     \end{tabular}
-    \caption{\label{tab:PSrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
+    \caption{\label{tab:PSratesLO} Rates at LO-QCD accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
+    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
     are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).}
@@
 
-We now present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Table~\ref{tab:PSrates}, both at LO and NLO
-accuracy. For {\sc MG5\_aMC}, the numbers in parentheses are rescaled to take into account the width effects described in the above paragraph. Once this effect is taken into
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|r@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+        \hline\hline
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+XX}_{-YY} {}^{+XX}_{-YY} $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.368$ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
+        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0.0}_{-1.0}$ & $0.0006$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
+    \end{tabular}
+    \caption{\label{tab:PSratesNLO} Rates at NLO-QCD  accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
+    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties is shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
+are respectively the nine-point scale uncertainty and the PDF one. Theory uncertainties are in percent.}
+\end{table}
+
+We now present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
+\ref{tab:PSratesNLO}, at LO and NLO
+accuracy respectively. For {\sc MG5\_aMC}, 
+the numbers whith $\Gamma_{\rm resc}$ are rescaled to 
+take into account the width effects described in the above paragraph.d  At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}, we also quote
+theoretical uncertainties: for the former, we show both PDF and scale uncertainties, obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
+scale by a factor 2 around its central value, Eq.~\ref{eq:defscale} (nine-point variations); for the latter, we show the 
+three-point scale uncertainties, obtained by considering correlated variations of the renormalization and factorization scales. 
+We observe that, once the width effect is taken into
 account, total rates from different tools agree within few per cent. Larger discrepancies however will appear for differential observables, which we are going to discuss in
@@
 For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
+As for the table, we show theoretical uncertainties for the NLO+PS samples
+obtained with {\sc VBFNLO} and {\sc MG5\_aMC}: 
+again, for the first the band corresponds to three-point variations, while for the second the darker (lighter) band corresponds to nine-point 
+scale variations (plus PDF uncertainties, linearly added).
 
@@
 In conclusion, the comparison of tools including matching with parton-shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
-effectively at NLO accuracy differences between tools are at (or below) the $10\%$ level. {\bf MZ compare this number with scale uncertainties}
+effectively at NLO accuracy differences between tools are at (or below) the $10\%$ level. 
 Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
 on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is
-generated {\bf MZ cite here H VBF at NNLO?}.
+generated {\bf MZ cite here H VBF at NNLO?}. It is remarkable the fact that, even for those observables that display small discrepancies,
+the theoretical uncertainty estimated via scale variations systematically underestimates the spread of predictions. Again, this stresses the need
+ to employ at least two different tools in order to have a conservative estimate of theoretical uncertainties.
 Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that

### 2018-02-15 Draft/shower.tex
edit shower.tex

@@
         \hline\hline
-        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+XX}_{-YY} {}^{+XX}_{-YY} $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+2\%}_{-1\%} {}^{+5\%}_{-6\%} $ & $0.004$  \\
         {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
@@
         {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
-        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0.0}_{-1.0}$ & $0.0006$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0\%}_{-1\%}$ & $0.0006$  \\
         {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
@@
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties is shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
-are respectively the nine-point scale uncertainty and the PDF one. Theory uncertainties are in percent.}
+are respectively the nine-point scale uncertainty and the PDF one.}
 \end{table}
@@
 the numbers whith $\Gamma_{\rm resc}$ are rescaled to 
-take into account the width effects described in the above paragraph.d  At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}, we also quote
+take into account the width effects described in the above paragraph.d  At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
 theoretical uncertainties: for the former, we show both PDF and scale uncertainties, obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
@@
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within few per cent. Larger discrepancies however will appear for differential observables, which we are going to discuss in
-the following. For any observable, results will be presented in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
+account, total rates from different tools agree within few per cent, both at LO and NLO. Larger discrepancies however will appear for differential observables, which we are going to discuss in
+the following. Before turning to the differential observables, we point out the smallness of the theory uncertainties due to the scale variations, both when
+scales are varied independently and when they are varied in a correlated manner. On the other hand PDF uncertainties are larger, at the level of 
+$\pm 5\%$. Concerning differential kinematic distributions, for each observable we will display results two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
 with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with

### 2018-02-16 Draft/introduction.tex
updated figures with PDF uncertainties fixed, uptated shower.tex implemented suggestions by PG in the intro

@@
-Vector-boson scattering (VBS) is a class of processes that make it possible 
-to probe the nature of Higgs-vector-vector couplings and triple and quartic gauge couplings.
-It is usually understood that VBS refers to the scattering of massive vector bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarised.
-The scattering of longitudinally-polarised bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual structure of the Higgs sector.
-A detailed study of this class of processes will therefore further constrain the Higgs couplings and hint at or exclude non-Standard Model Higgs bosons.
+Vector-boson scattering (VBS) at a hadron collider 
+usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
+irradiated by partons (quarks) of the incoming protons, 
+which in turn are deflected from the beam direction 
+and enter the volume of the particle detectors.
+As a consequence, the typical signature of VBS events
+is characterised by two energetic jets 
+and four fermions,
+originating from the decay of the two vector bosons.
+Among the possible diagrams,
+the scattering process can be mediated also by a Higgs boson
+and involve in particular their longitudinal component.
+The interaction of of longitudinally polarised bosons is of particular interest, 
+because the corresponding matrix elements feature both gauge and unitarity cancellations 
+that strongly depend on the actual structure of the Higgs sector.
+A detailed study of this class of processes will therefore further constrain the Higgs couplings 
+at a very different energy scale with respect to the Higgs boson mass,
+and hint at, or exclude, non-Standard Model behaviours.
 
-The process with two positively charged $\PW$ bosons is the VBS process with the largest signal-to-background ratio at the LHC, for which evidence has been found in $8 \TeV$ data~\cite{Aad:2014zda,Khachatryan:2014sta} and has been subsequently
-observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in $13\TeV$ data. At present 
-the measurements of VBS processes are limited by statistics but the situation will change in a near future.
-On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.
+The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio at the LHC:
+evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
+and it has been recently observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} 
+at $13\TeV$ as well.
+Presently, the measurements of VBS processes are limited by statistics, but the situation will change in a near future.
+On the theoretical side, 
+it is thus of prime importance to provide predictions with systematic uncertainties
+at least comparable to the current and experimental precisions~\cite{CMS:2016rcn}.
 
-The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because of the double-charge structure of the leptonic final state that limits the number of partonic processes and total number of Feynman diagrams for each process.
-It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg $\PW^+\PW^-$ scattering, which has the largest cross section.
-Therefore, the $\PW^+\PW^+$ scattering is an ideal candidate for a detailed study of various theoretical predictions.
+The $\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
+because the double-charge structure of the leptonic final state 
+limits the number of partonic processes and total number of Feynman diagrams for each process.
+Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.
 
@@
 
-The hadronic process ito be considered is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
-This final state possesses three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
+The full gauge-invariant process including the $\PW^+\PW^+$ scattering 
+ is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
+This final state receives three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
 They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
-\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
+\footnote{The EW contribution is sometimes referred to as the VBS contribution, even it involves also non-VBS contributions.}
 Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
@@
 The article is organised as follows:
-First, we define the process under study in Sec.~\ref{sec:definition}.
-Various approximation at LO and NLO are described in Sec.~\ref{sec:details}.
+first, we define the process under study in Sec.~\ref{sec:definition}.
+The various approximation which are provided by the different computer codes at LO and NLO are described in Sec.~\ref{sec:details}.
 This is followed by a presentation of the programs used for the computations.
 Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study at fixed order, respectively.
-Section~\ref{sec:matching} then adds the effect of parton showers and hadronization to the fixed-order results by matching the two.
+Section~\ref{sec:matching} complements our study by comparing predictions at LO and LO which include the effect of parton showers and hadronization.
 The last section consists in concluding remarks and recommendations for experimental collaborations.

### 2018-02-16 Draft/shower.tex
updated figures with PDF uncertainties fixed, uptated shower.tex implemented suggestions by PG in the intro

@@
         \hline\hline
-        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+2\%}_{-1\%} {}^{+5\%}_{-6\%} $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+2\%}_{-1\%} {}^{+2\%}_{-2\%} $ & $0.004$  \\
         {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
@@
 the following. Before turning to the differential observables, we point out the smallness of the theory uncertainties due to the scale variations, both when
-scales are varied independently and when they are varied in a correlated manner. On the other hand PDF uncertainties are larger, at the level of 
-$\pm 5\%$. Concerning differential kinematic distributions, for each observable we will display results two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
+scales are varied independently and when they are varied in a correlated manner, as well as those due to PDF.  
+Concerning differential kinematic distributions, for each observable we will display results two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
 with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with

### 2018-02-16 Draft/article.tex
Lots of corrections and improvements
some improvements in the draft
Updated affiliations and added a preprint number

@@
  \usepackage{url}
+ \usepackage{morefloats}
 %  \usepackage{siunitx}
@@
 \newcommand{\MR}[1]{{ {\color{red}{ [MR: #1]}} }}
+\newcommand{\AK}[1]{{ {\color{pink}{ [AK: #1]}} }}
 
@@
 %
-\journalname{PREPRINT NUMBERS HERE}
+\journalname{ZU-TH-08/18} % Preprint numbers here
 %
@@
 Michele Grossi\thanksref{pavia,ibm}
+\and
+Barbara J\"ager\thanksref{tub}
 \and
@@
 Pascal Stienemeier\thanksref{desy}
+\and
+Giulia Zanderighi\thanksref{cern}
 \and
@@
 \and
-Department of Physics, University of Z\"urich, %
+Physik-Institut,
+Universit\"at Z\"urich,
+Winterthurerstrasse 190,
 CH-8057 Z\"urich,
@@
 Notkestr. 85, %
-D-22607 Hamburg,
+22607 Hamburg,
 Germany\label{desy}
@@
 The Netherlands\label{nikh}
+\and
+CERN,
+Theoretical Physics Department,
+CH-1211, Geneva 23,
+Switzerland\label{cern}
+\and
+Institute for Theoretical Physics,
+University of T\"ubingen,
+Auf der Morgenstelle 14,
+72076 T\"bingen,
+Germany\label{tub}
 }
@@
 \section{Introduction}
-
 \input{introduction}
@@
     \label{sec:definition}
-
     \input{definition}
@@
     \label{sec:details}
-
     \subsection{Several descriptions for one process}
-
         \input{process}
-
     \subsection{Description of the predictions}
         \label{subsec:codedescr}
-
         \input{description}
-
     \subsection{Input parameters}
         \label{subsec:inputpar}
-
         \input{input}
@@
     \label{sec:LO}
-
     \subsection{Three contributions}
         \label{subsec:contributions}
-
         \input{contributions}
-
     \subsection{Inclusive comparison}
         \label{subsec:LOinclusive}
-
         \input{scanLO}
-
     \subsection{Comparison in the fiducial region}
         \label{subsec:LOfiducial}
-
         \input{crosssectionLO}
-
         \input{distributionsLO}
@@
     \label{sec:NLO}
-
     \subsection{Inclusive comparision}
         \label{subsec:NLOinclusive}
-
         \input{scanNLO}
-
     \subsection{Comparison in the fiducial region}
-
         \input{crosssectionNLO}
-
         \input{distributionsNLO}
@@
     \label{sec:matching}
-
     \input{shower}

### 2018-02-16 Draft/abstract.tex
Fixed a typo in abstract

--- 2018-02-15 Draft/abstract.tex
@@
   current run-2 and future runs at design energy of the Large Hadron
-  Collider. The presence of triple and quartic gauge couplings in the process
-  gives access the gauge sector of the Standard Model and possible new-physics
-  contributions there. 
-  To test this hypothesis, a precise knowledge of the Standard
-  Model contributions is necessary, 
-  with a precision which at least matches the
-  experimental uncertainties
-  of existing and forthcoming measurements.
-  In this article, we present a detailed study of the vector-boson
-  scattering process with two positively-charged leptons and missing
-  transverse momentum in the final state, mediated predominantly by
-  same-sign production of two W bosons with positive charge.
-  In particular, we first carry out a systematic comparison of the various 
-  approximations that are usually performed for this kind of process against the complete calculation, 
-  at LO and NLO QCD accuracy. Such  a study is performed both 
-  in the usual fiducial region used by experimental collaborations and in a more inclusive phase space,
-  where the differences among the various approximations lead to more sizeable effects.
-  Afterwards, we turn ourselves to predictions matched to parton showers, at LO and NLO: we show that on the
-  one hand, the inclusion of NLO QCD corrections leads to more stable predictions, but on the other the details 
-  of the matching and of the parton-shower programs lead to differences which are considerably larger than those
-  observed at fixed-order, even in the experimental fiducial region. 
-  We conclude with some recommendations for experimental studies of vector-boson scattering processes.
+  Collider. The presence of triple and quartic gauge couplings in the
+  process gives access to the gauge sector of the Standard Model and
+  possible new-physics contributions there.  To test this hypothesis,
+  precise knowledge of the Standard Model contributions is necessary,
+  with a precision which at least matches the experimental
+  uncertainties of existing and forthcoming measurements.  In this
+  article we present a detailed study of the vector-boson scattering
+  process with two positively-charged leptons and missing transverse
+  momentum in the final state, mediated predominantly by same-sign
+  production of two $\PW$ bosons with positive charge.  In particular,
+  we first carry out a systematic comparison of the various
+  approximations that are usually performed for this kind of process
+  against the complete calculation, at LO and NLO QCD accuracy. Such a
+  study is performed both in the usual fiducial region used by
+  experimental collaborations and in a more inclusive phase space,
+  where the differences among the various approximations lead to more
+  sizeable effects.  Afterwards, we turn ourselves to predictions
+  matched to parton showers, at LO and NLO: we show that on the one
+  hand, the inclusion of NLO QCD corrections leads to more stable
+  predictions, but on the other the details of the matching and of the
+  parton-shower programs lead to differences which are considerably
+  larger than those observed at fixed-order, even in the experimental
+  fiducial region.  We conclude with some recommendations for
+  experimental studies of vector-boson scattering processes.
 

### 2018-02-16 Draft/introduction.tex
Updated introduction and inserted some comments

@@
 usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
-irradiated by partons (quarks) of the incoming protons, 
+radiated by partons (quarks) of the incoming protons, 
 which in turn are deflected from the beam direction 
@@
 and involve in particular their longitudinal component.
-The interaction of of longitudinally polarised bosons is of particular interest, 
+The interaction of longitudinally polarised bosons is of particular interest, 
 because the corresponding matrix elements feature both gauge and unitarity cancellations 
@@
 
-The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio at the LHC:
+The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio at the LHC of all the VBS processes:
 evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
@@
 at $13\TeV$ as well.
-Presently, the measurements of VBS processes are limited by statistics, but the situation will change in a near future.
+Presently, the measurements of VBS processes are limited by statistics, but the situation will change in the near future.
 On the theoretical side, 
@@
 
-The $\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
+$\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
 because the double-charge structure of the leptonic final state 
@@
 Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.
+\AK{Could one not argue the opposite?
+That because it is easy and only has a certain class of diagrams it doesn't capture all the differences one might find between different simulation programs?
+This sentence is not very convincing to me.}
 
-In the last few years, several next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
-The VBS computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
-It is therefore interesting to infer in details the quality of the various approximations.
-Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
+In the last few years, several next-to-leading order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
+These VBS computations all rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Oleari:2003tc}.
+Recently the complete NLO corrections to $\PW^+\PW^+$ have been performed in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations used in most tools.
+\AK{I have changed this sentence a bit, as I felt it didn't convey the message strongly enough.
+I also added a reference to Oleari and Zeppenfeld which have a statement about the VBS approximation being accurate at the 0.3\% level at LO.
+}
+
+Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}\AK{As stated above this paper has a statement on the LO approximation.
+As far as I can see all further papers cite this one as the reason why the VBS approximation is good enough.}.
 Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
@@
 Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
-This allows to quantify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
-This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.
+This allows us to quantify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
+It is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.
 
@@
 The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
-In the following, this order is the one where our comparisons are focused on and we will refer to it as simply \emph{NLO}.
+The main focus of the paper is the comparison of these corrections, and we will henceforth refer to this order simply as \emph{NLO}.
 As for the LO study, the various predictions are compared at the level of the cross section and differential distributions now at NLO accuracy.
 In particular, this makes it possible to infer the accuracy of the so-called VBS approximation, which we will define in more details later.
-To our knowledge, such a detailed study was still missing.
+To our knowledge, such a detailed study was still missing. \AK{Vague statement. It is either missing or not. I suggest simply removing the sentence.}
 
-Finally, several predictions featuring parton shower are compared, giving the possibility to infer systematic differences between the various predictions.
-A first study for the $\PW^+ \PW^- \Pj \Pj$ VBS process has been presented in
-Ref.~\cite{Rauch:2016upa}, comparing the angular-ordered default shower and the dipole
-shower and both{\sc MC@NLO}-like~\cite{Frixione:2002ik} and {\sc POWHEG}-like~\cite{Nason:2004rx,Frixione:2007vw} matching as implemented
-in {\sc Herwig 7}~\cite{Bellm:2015jjp}, also showing scale-variation uncertainties. In this work we extend such a comparison by presenting 
-results obtained by {\sc MadGraph5\_aMC@NLO}, {\sc Powheg} and {\sc Phantom} {\bf CITES}, possibly matched with different parton-showers.
-This is the first time in the literature that NLO QCD calculations for VBS processed matched to parton shower are compared between different generators.
+Finally, several parton shower matched predictions are compared, giving the possibility to infer systematic differences between the various parton showers and matching prescriptions.
+A similar study for the $\PW^+ \PW^- \Pj \Pj$ VBS process has been presented in
+Ref.~\cite{Rauch:2016upa}. Here a comparison of the default angular-ordered shower and the dipole
+shower  in {\sc Herwig 7}~\cite{Bellm:2015jjp} was carried out.
+Both {\sc MC@NLO}-like~\cite{Frixione:2002ik} and {\sc POWHEG}-like~\cite{Nason:2004rx,Frixione:2007vw} matching was studied.
+In this work we extend such a comparison by presenting
+results obtained by {\sc MadGraph5\_aMC@NLO}, {\sc Powheg} and {\sc Phantom} {\bf CITES} for the $\PW^+ \PW^+ \Pj \Pj$ VBS process, possibly\AK{Why possibly?} matched with different parton-showers.
+This is the first time in the literature that NLO QCD calculations for VBS processes matched to parton shower are compared between different generators.
 
 The article is organised as follows:
-first, we define the process under study in Sec.~\ref{sec:definition}.
+In Sec.~\ref{sec:definition}, we define the VBS process.
 The various approximation which are provided by the different computer codes at LO and NLO are described in Sec.~\ref{sec:details}.
@@
 Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study at fixed order, respectively.
-Section~\ref{sec:matching} complements our study by comparing predictions at LO and LO which include the effect of parton showers and hadronization.
-The last section consists in concluding remarks and recommendations for experimental collaborations.
+Section~\ref{sec:matching} complements our study by comparing predictions at LO and NLO which include the effect of parton showers and hadronization.
+The last section consists of concluding remarks and recommendations for experimental collaborations.

### 2018-02-16 Draft/definition.tex
Updated definitions section

@@
-The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay proceeds at the LHC through the partonic process:
+The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay proceeds at the LHC through the partonic process\AK{This is only one such process...}:
 %
@@
 This process possesses three LO contributions of different orders.
-The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as EW contribution.
+The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as the EW contribution.
 In addition to typical VBS contributions, as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
-Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.} $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.
+Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.} $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.\AK{This sentence makes no sense to me.
+How about: ``Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the quark lines.
+$s$-channel denotes all the diagrams where the final state quarks are produced from the decay of a vector boson.'' Or am I missing something?}
 The $s$-channels will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
@@
 The two $\PW$ bosons are mostly produced centrally.
-This is in contrast with the QCD contribution which favours jets in the central region.
+This is in contrast to the QCD contribution which favours jets in the central region.
 Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
 This will be further discussed in Sec.~\ref{subsec:contributions}.
-
+\AK{Should we also discuss the definition of the process at NLO - ie point out that at this level one can no longer distinguish EW/QCD production?}
 \begin{figure*}[t]
@@
         \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
-        In addition to typical VBS contribution (left), this order also possesses $s$-channel (middle) and tri-boson contributions (right). }
+        In addition to typical VBS contribution (left), this order also possesses $s$-channel (middle) and tri-boson contributions (right).
+\AK{The text here is in conflict with the main text.
+Reading this it looks as if s-channel and tri-boson production are two different classifications, but in the main text we say both decay chains and tri-boson production belongs to s-channel.}}
 \label{diag:LO}

### 2018-02-16 Draft/process.tex
Updated processes section

@@
 However, this set of contributions is not gauge invariant. In order to make it gauge invariant, one 
-should perform an on-shell projection of the incoming and outgoing $\PW$ bosons {\bf MZ: it is incoming and outgoing, right? in case modify what follows}.
+should perform an on-shell projection of the incoming and outgoing $\PW$ bosons \MZ{it is incoming and outgoing, right? in case modify what follows}.
 Unfortunately, these momenta are space-like and thus a simple on-shell projection is not possible.
 Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
-Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
+Then the polarisation of the gauge boson is accommodated for following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
 Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
@@
 A less crude approximation consists in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two.
-These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed.
+These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
 The $s$-channel squared diagrams and any interferences with $s$-channels are also discarded.
@@
 We will adopt the latter denomination in the following of the article.
-Such an approximation is implemented at LO in the computer codes {\sc Bonsay} and {\sc Powheg}.
+Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
 This approximation is gauge-invariant, which can be seen by considering that the two protons and therefore the two incoming quarks belong to two different, but otherwise identical, copies of the $SU \left(3\right)$ gauge group.
@@
 A further refinement is to add the squared matrix element of the $s$-channel contributions, still neglecting 
-all interferences between different kinematic channels, as it is implemented in in {\sc VBFNLO}.
+all interferences between different kinematic channels, as it is implemented in in {\sc VBFNLO}\AK{CITATIONS}.
 
-All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard}) consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
+All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard})\AK{CITATIONS} consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
 Note that the final $\PW$ boson can always be considered either on-shell or off-shell without affecting the previous discussion.
@@
 }.
-This is implemented in {\sc POWHEG}.
+This is implemented in the {\sc Powheg-Box}.
 This approximation can be used in combination with a double-pole approximation \cite{Dittmaier:2015bfe} for the virtual contribution.
@@
 as simplification the gluon emission is fully modelled only for initial-state
-radiation. The effect of final-state radiation together with the corresponding
+radiation\AK{I don't understand this sentence. What does 'thereby' refer to?}. The effect of final-state radiation together with the corresponding
 virtual contributions is included as a $K$-factor.
@@
 Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
-The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones.\footnote{For more details, the reader is referred to Ref.~\cite{Biedermann:2017bss}.}
+The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones.\footnote{For more details, the reader is referred to Ref.~\cite{Biedermann:2017bss}.\AK{Do we need this footnote given that the next sentence gives the reference?}}
 Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
@@
         {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
-        {\sc POWHEG}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
         {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\

### 2018-02-16 Draft/description.tex
Updated description section

@@
 
-  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for matching NLO-QCD calculations with parton showers.
+  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw,Nason:2006hfa} is a framework for matching NLO-QCD calculations with parton showers.
 It relies on the user providing the matrix elements and Born phase space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
 For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
-\MP{Mention the non-clustering for the scale as well as the different running of alphas at NLO.}
+The {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_s$.
+The renormalisation and factorisation scale used differ slightly from \eqref{eq:defscale}, as rather than constructing the jets the {\sc Powheg-Box} uses the transverse momentum of the two final-state quarks in the underlying Born event.
 

### 2018-02-16 Draft/input.tex
Updated input section

@@
         \end{align}
-        Typically, on the two jets with largest transverse-momentum VBS cuts are applied.
-        These are an invariant-mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
+        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated.
+        These are an in\-vari\-ant mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
         The nominal value of these cuts if not stated explicitly read:

### 2018-02-16 Draft/contributions.tex
some improvements in the draft
Updated contributions section

@@
-At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
+At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$ \AK{We have mentioned this many times at this point.
+Perhaps not worth repeating again?}.
 In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
@@
 
-\begin{figure}[ht]
+\begin{figure*}[hbt]
 \centering
@@
 \label{fig:mjjdyjj_2d_LO}
-\end{figure}
+\end{figure*}

### 2018-02-16 Draft/scanLO.tex
Updated contributions and scanLO section

@@
-As explained previously, the low di-jet invariant mass and low jet rapidity separation is dominated by tri-boson production.
+As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.
 Therefore, a comparison of the various approximations in an \emph{inclusive} phase-space volume should exclude the region where tri-boson contributions are dominating.
@@
 
-In Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
+In Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
 Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
@@
 The full calculation is approximated at the level of $\pm10\%$ everywhere apart in the upper left corner where the inclusion of $s$-channel contributions did not improve the approximation.
-This is due to ... \MP{Ideas?}
+This is due to ...
+\MP{Ideas?} \AK{The upper left corner looks fine, did you mean lower right?
+:) What are the MC error on these plots?
+Also, in the text it says we are applying a delta yjj cut, so why is this plot showing [0:4]?
+}
 
@@
 Ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (top) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (bottom).}
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (top) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (bottom).\AK{I think the caption should also state the cuts and that this is LO.}}
 \label{fig:ratio2d_LO}

### 2018-02-16 Draft/crosssectionNLO.tex
Updated crosssssssssectionNLO section and powheg numbers

--- 2018-02-09 Draft/crosssectionNLO.tex
@@
 The order considered is again the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$ and the fiducial volume is the one described in Sec.~\ref{subsec:inputpar}.
-In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions are visibly differ according to the approximations used.
+In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions differ visibly according to the approximations used.
 
@@
         {\sc Bonsay}  &  $X$ & $0.0009$  \\
-        {\sc MG5\_aMC}&  $X $ & $0.003$  \\
+        {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
         {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
-        {\sc POWHEG}  &  $1.3556$ & $0.0009$  \\
+        {\sc Powheg-Box}  &  $1.362$   $0.003$   \\
         {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
@@
     \MR{My $t$-/$u$-channel-only number is $1.3703(1)$, so something additionally must be going on with Powheg, which we should comment on.}
+    \AK{The number here was wrong. I have updated the table and plots. I am also running some more statistics... }
 \end{table}
 
-The first observation is that the predictions featuring two versions of the VBS approximation ({\sc Bonsay} and {\sc POWHEG}) are close.
-This means that the double-pole approximation on the two W bosons used in {\sc Bonsay} constitutes a good approximation of the VBS-approximated virtual corrections implemented in {\sc POWHEG}.
+The first observation is that the predictions featuring two versions of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are close.
+This means that the double-pole approximation on the two W bosons used in {\sc Bonsay} constitutes a good approximation of the VBS-approximated virtual corrections implemented in the {\sc Powheg-Box}.
 Both predictions differ by about $2\%$ with respect to the full computation ({\sc MoCaNLO+Recola}).

### 2018-02-16 Draft/distributionsNLO.tex
some improvements in the draft
Updated distributionsNLO section

@@
 On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
-The VBS-approximated predictions ({\sc BONSAY} and {\sc POWHEG}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
-The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC@NLO}.
-Finally, {\sc VBFNLO} which include as well $s$-channel contributions provides larger predictions at low invariant mass.
+The VBS-approximated predictions ({\sc BONSAY} and the {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
+The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
+Finally, {\sc VBFNLO} which includes as well $s$-channel contributions provides larger predictions at low invariant mass.
 For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.
 
- \begin{figure}[h!]
+ \begin{figure*}[hbt!]
    \centering
@@
 }
-\end{figure}
+\end{figure*}
 
 Concerning the transverse momentum (top) and rapidity (bottom) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
-While {\sc MadGraph5\_aMC@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
+While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
 This is in contrast with {\sc BONSAY} and {\sc POWHEG} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
-Finally, {\sc VBFNLO} predicts higher rates over the whole range apart around $200\GeV$ where it is in perfect agreement with the complete calculation.
+Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.
 Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
@@
 
- \begin{figure}[h!]
+ \begin{figure*}[hbt!]
    \centering
@@
 }
-\end{figure}
+\end{figure*}
 
@@
 }
-\end{figure}
+\end{figure*}

### 2018-02-16 Draft/acknowledgements.tex
some improvements in the draft
Updated last sections

@@
+We would like to thank \ldots \\
+the {\sc Pythia8} authors, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
+discussions and clarifications about the third-jet rapidity spectrum.
+
 The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
@@
 reference number DE 623/6-1.
+
+AK acknowledge financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595

### 2018-02-16 Draft/article.tex
Updated last sections

@@
 \newcommand{\MR}[1]{{ {\color{red}{ [MR: #1]}} }}
-\newcommand{\AK}[1]{{ {\color{pink}{ [AK: #1]}} }}
+\newcommand{\AK}[1]{{ {\color{magenta}{ [AK: #1]}} }}
 
@@
 \maketitle
-
+\AK{Some general comments: We don't write the names of programs consistently everywhere. I think the nicest is to use}
+\begin{verbatim} 
+{\sc Generator}
+\end{verbatim}
+\AK{Ie captial first letter and lower-case everywhere else for generator names instead of all capital. But this is a matter of taste of course...}
+\AK{We may want to make it more clear in the abstract/introduction why this study is worth publishing.
+So focus on the large contributions from non-VBS approxiamtion at NLO which until now has been reproted as small, and the large discrepancies in the NLO+PS predictions.
+That plus the recommendations we give should be the main selling point, I think.}
 \input{abstract}

### 2018-02-16 Draft/crosssectionLO.tex
Updated crossssssssssssssectionLO section
Updated last sections

@@
 This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
-the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
+the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations. This is in agreement with the findings of Ref.~\cite{Oleari:2003tc}.
 
@@
         {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
-        {\sc POWHEG}  &  $1.44092$ & $0.00009$ \\
+        {\sc Powheg-Box}  &  $1.44092$ & $0.00009$ \\
         {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\

### 2018-02-16 Draft/shower.tex
Updated last sections

@@
 matching schemes, parton shower employed and of other details of the matching (such as the choice of the parton shower initial scale). Among
-the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG}, and {\sc VBFNLO}
+the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
 can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO}, we
@@
 and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
-For {\sc POWHEG}, the homonymous \MP{Is it the correct word?
+For the {\sc Powheg-Box}, the eponymous \MP{Is it the correct word?
 Because it would mean that the work ``Powheg'' has different meaning.
-Isn't it?}
-matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8}
-{\bf MZ VERSION? if same as MG5, put it at the end together with the
-tune}. {\sc VBFNLO} serves as a matrix-element and phase-space provider
+Isn't it?} \AK{Changed to epononymous.
+Although still not correct as the powheg-box takes its name from the powheg mathcing and not the other way around....
+:)}
+matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
 for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
@@
 interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
-possible to choose between {\sc MC@NLO}-like and {\sc POWHEG}-like
+possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
 matching. As parton shower, both the default angular-ordered shower as
 well as the dipole shower can be employed.
-Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.
+Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.\AK{versions??}
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.
@@
 are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
-must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.
+must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?} \AK{In powheg the separation is done after shower. So it's really the jet.}.
 
@@
         {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
-        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
+        {\sc Powheg-Box}  & $1.3642$ & $0.0004$  \\
         {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0\%}_{-1\%}$ & $0.0006$  \\
@@
 accuracy respectively. For {\sc MG5\_aMC}, 
-the numbers whith $\Gamma_{\rm resc}$ are rescaled to 
-take into account the width effects described in the above paragraph.d  At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
+the numbers with $\Gamma_{\rm resc}$ are rescaled to 
+take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
 theoretical uncertainties: for the former, we show both PDF and scale uncertainties, obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
@@
 scales are varied independently and when they are varied in a correlated manner, as well as those due to PDF.  
-Concerning differential kinematic distributions, for each observable we will display results two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
+Concerning differential kinematic distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
 with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
@@
 among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
-{\sc MG5\_aMC}, while the smallest rate is predicted by {\sc Powheg}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
-is different among the two tools. In particular, for {\sc Powheg}, the first emission is generated with an internal Sudakov form factor (the
+{\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
+is different among the two tools. In particular, for the {\sc Powheg-Box}, the first emission is generated with an internal Sudakov form factor (the
 prediction dubbed {\sc Powheg-no shower} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
@@
 quantitatively similar way. At NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
-exception is the {\sc Powheg} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
+exception is the the {\sc Powheg-Box} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
 it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
@@
 the fixed-NLO ones, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
-effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of {\sc Powheg} to suppress the
-hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).\\
+effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of the {\sc Powheg-Box} to suppress the
+hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).\AK{This effect seems to be cured by the dipole shower.}\\
 If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
 stabilisation at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions
-obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; {\sc Powheg}\ displays an enhancement of the central region, and a consequent suppression in the
+obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; the {\sc Powheg-Box}\ displays an enhancement of the central region, and a consequent suppression in the
 peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
-at most $10\%$.
+at most $10\%$ \AK{This effect again seems to be evened out by the dipole shower}.
 
@@
 behaviour of {\sc Pythia8}
-has been also observed in the study of EW production of a Z boson in association with two jets (see the recent CMS measurement, 
+has also been observed in the study of EW production of a Z boson in association with two jets (see the recent CMS measurement, 
 Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}. 
-If it is true that the central enhancement
+It is true that the central enhancement
 is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
@@
 on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is
-generated {\bf MZ cite here H VBF at NNLO?}. It is remarkable the fact that, even for those observables that display small discrepancies,
+generated {\bf MZ cite here H VBF at NNLO?} \AK{I agree! :)}. It is a remarkable fact that, even for those observables that display small discrepancies,
 the theoretical uncertainty estimated via scale variations systematically underestimates the spread of predictions. Again, this stresses the need
@@
 Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
-experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory 
-uncertainties. On the one hand, un order to improve the
+experimental analyses should rely as little as possible on those observables and, in any case, use conservative estimate of the theory 
+uncertainties.\AK{Are there any current analyses with a central jet veto in VBS? The experimentalists might take this statement a little too literal.} On the one hand, in order to improve the
 description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern 
@@
 color flow (EW production of a single vector boson plus jets,
- VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data.
+ VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data. \AK{Include some references here?}
 

### 2018-02-16 Draft/abstract.tex
First corrections

@@
   Vector-boson scattering processes are of great importance for the
-  current run-2 and future runs at design energy of the Large Hadron
+  current run-II and future runs of the Large Hadron
   Collider. The presence of triple and quartic gauge couplings in the
@@
   where the differences among the various approximations lead to more
-  sizeable effects.  Afterwards, we turn ourselves to predictions
+  sizeable effects.  Afterwards, we turn to predictions
   matched to parton showers, at LO and NLO: we show that on the one

### 2018-02-16 Draft/crosssectionLO.tex
Add BONSAY integrated cross sections

@@
         \hline
-        {\sc Bonsay}  &  $X$ & $0.0002$ \\
+        {\sc Bonsay}  &  $1.43636 \pm 0.00002$ \\
         {\sc MG5\_aMC}&  $1.435$ & $0.004$ TO BE UPDATED  \\

### 2018-02-16 Draft/crosssectionNLO.tex
Add BONSAY integrated cross sections

@@
         \hline
-        {\sc Bonsay}  &  $X$ & $0.0009$  \\
+        {\sc Bonsay}  &  $1.35039 \pm 0.00006$  \\
         {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
         {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
-        {\sc Powheg-Box}  &  $1.362$   $0.003$   \\
+        {\sc Powheg-Box}  &  $1.362$  & $0.003$   \\
         {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\

### 2018-02-16 Draft/definition.tex
definition

@@
-The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay proceeds at the LHC through the partonic process\AK{This is only one such process...}:
+The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay with different flavours can proceed at the LHC through the partonic process:
+\AK{This is only one such process...}
+\MP{I added ``with different flavours'' and ``can''.}
 %
@@
 In addition to typical VBS contributions, as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
-Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.} $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.\AK{This sentence makes no sense to me.
+Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.}\ $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.\AK{This sentence makes no sense to me.
 How about: ``Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the quark lines.
 $s$-channel denotes all the diagrams where the final state quarks are produced from the decay of a vector boson.'' Or am I missing something?}
-The $s$-channels will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
+The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
 Some of them take the form of decay chains, for example the diagram represented in the middle of Fig.~\ref{diag:LO}, while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
@@
 The process can also be mediated via a gluon connecting the two quark lines while the $\PW$ bosons are radiated off the quark lines.
-These contributions are of order $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$ and feature different kinematical behaviours than the EW contribution.
+These contributions are of order $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$ and feature different kinematical behaviours than the EW contributions.
 Nonetheless they share the same final state and therefore constitute an irreducible background.
@@
 This will be further discussed in Sec.~\ref{subsec:contributions}.
+Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes the separation between EW and QCD production becomes meaningless.
+Hence, combined measurements which are well defined theoretically should be rather performed by the experimental collaborations at the LHC.
 \AK{Should we also discuss the definition of the process at NLO - ie point out that at this level one can no longer distinguish EW/QCD production?}
+\MP{I added two sentences, I guess we should develop in the conclusion/recommendation part}
+
 \begin{figure*}[t]

### 2018-02-16 Draft/definition.tex
processes and definiton

@@
         \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
-        In addition to typical VBS contribution (left), this order also possesses $s$-channel (middle) and tri-boson contributions (right).
-\AK{The text here is in conflict with the main text.
-Reading this it looks as if s-channel and tri-boson production are two different classifications, but in the main text we say both decay chains and tri-boson production belongs to s-channel.}}
+        In addition to typical VBS contribution (left), this order also possesses $s$-channel contributions such as decay chain (middle) and tri-boson contributions (right).}
 \label{diag:LO}

### 2018-02-16 Draft/process.tex
processes and definiton

@@
 However, this set of contributions is not gauge invariant. In order to make it gauge invariant, one 
-should perform an on-shell projection of the incoming and outgoing $\PW$ bosons \MZ{it is incoming and outgoing, right? in case modify what follows}.
-Unfortunately, these momenta are space-like and thus a simple on-shell projection is not possible.
+should perform an on-shell projection of the incoming and outgoing $\PW$ bosons.
+Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
 Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
@@
 Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
-This approximation is gauge-invariant, which can be seen by considering that the two protons and therefore the two incoming quarks belong to two different, but otherwise identical, copies of the $SU \left(3\right)$ gauge group.
+This approximation is gauge-invariant, which can be seen by considering that the two protons and therefore the two incoming quarks belong to two different, but otherwise identical, copies of the SU(3) gauge group.
 
@@
 
-All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard})\AK{CITATIONS} consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
+All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard})\AK{CITATIONS} \MP{No ref.
+for MoCaNLO+Recola} consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
 Note that the final $\PW$ boson can always be considered either on-shell or off-shell without affecting the previous discussion.
@@
 In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and 
-assuming a cancellation of the infrared (IR) poles. Such an approximation is implemented by {\sc MG5\_aMC}.
+assuming a cancellation of the infrared (IR) poles.
+Such an approximation is implemented by {\sc MG5\_aMC}.
+\MP{I think this is not a gauge invariant approximation. If not, this should be commented on.}
 
@@
 Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
-The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones.\footnote{For more details, the reader is referred to Ref.~\cite{Biedermann:2017bss}.\AK{Do we need this footnote given that the next sentence gives the reference?}}
+The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones. 
 Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
@@
     \item diagrams which do not feature two resonant vector bosons are included;
-    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
+    \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
         are included;

### 2018-02-16 Draft/contributions.tex
Updated contributions and scanLO section
various modifications

@@
 The sum of all the contributions is in blue.
-No cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
-\MP{On the plots: it should be $\alpha$ and not $\alpha_{em}$ and $m_{\Pj\Pj}$ instead of $M_{jj}$. And we have the convention to put $\alphas$ before $\alpha$.}}
+The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.}
 \label{fig:mjjdyjj_1d}
@@
 This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a function of the di-jet invariant mass and jet rapidity difference.
-Again, it is obvious that the region with low di-jet invariant mass and low jet-rapidity difference should be avoided.
-This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
+Again, it is obvious that the region with low di-jet invariant mass should be avoided as it is dominated by tri-boson contributions.
+% This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
+This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and for our LO inclusive study (see below).
 Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
@@
 \caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top), $\mathcal{O}(\alphas\alpha^5)$ (middle), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
-\MP{On the plots: it should be $\alpha$ and not $\alpha_{em}$ and $m_{\Pj\Pj}$ instead of $M_{jj}$. And we have the convention to put $\alphas$ before $\alpha$.}}
+The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
+}
 \label{fig:mjjdyjj_2d_LO}

### 2018-02-16 Draft/description.tex
various modifications

@@
 
+\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
+It can compute arbitrary processes for the LHC at both NLO QCD and EW accuracy in the Standard Model.
+This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the Standard Model.
+To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
+In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
+The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
+In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained from this tool.
+One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
+
   \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states 
@@
 For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
-The {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_s$.
-The renormalisation and factorisation scale used differ slightly from \eqref{eq:defscale}, as rather than constructing the jets the {\sc Powheg-Box} uses the transverse momentum of the two final-state quarks in the underlying Born event.
-
-\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
-It can compute arbitrary processes for the LHC at both NLO QCD and EW accuracy in the Standard Model.
-This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the Standard Model.
-To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
-In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
-The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
-In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained from this tool.
-One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
+The {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.
+The renormalisation and factorisation scale used differ slightly from one defined in Eq.~\eqref{eq:defscale}, as rather than constructing the jets the {\sc Powheg-Box} uses the transverse momentum of the two final-state quarks in the underlying Born event.
 

### 2018-02-16 Draft/scanLO.tex
various modifications

@@
-As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.
-Therefore, a comparison of the various approximations in an \emph{inclusive} phase-space volume should exclude the region where tri-boson contributions are dominating.
-To that end, we have chosen for the inclusive fiducial volume to take the following values for the VBS cuts:
+In Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
+Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
+In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
+The low rapidity difference region possesses remnants of the tri-bosons contributions that peek at the an di-jet invariant mass around the W-boson mass.
+It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
+The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
+The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
+\AK{What are the MC error on these plots?}
+\MP{@AK: I changed some stuffs in the text to justify the plot range}
+
+\begin{figure}[hbt]
+\centering
+\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
+\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
+\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
+Ratio of approximated squared amplitudes over the full matrix element.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (top) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (bottom).
+The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
+\label{fig:ratio2d_LO}
+\end{figure}
+% As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.
+
+Therefore, the \emph{inclusive} study at NLO is only performed in the region 
 %
@@
 \end{equation}
+%
+Hence, the differences arising at NLO in this fiducial region originate solely from NLO effects.
 
-In Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
-Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
-In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
-The low rapidity difference region possesses remnants of the tri-bosons contributions.
-It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
-The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
-The full calculation is approximated at the level of $\pm10\%$ everywhere apart in the upper left corner where the inclusion of $s$-channel contributions did not improve the approximation.
-This is due to ...
-\MP{Ideas?} \AK{The upper left corner looks fine, did you mean lower right?
-:) What are the MC error on these plots?
-Also, in the text it says we are applying a delta yjj cut, so why is this plot showing [0:4]?
-}
-
-\begin{figure}[hbt]
-\centering
-\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
-\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at order $\mathcal{O}(\alpha^6)$.
-Ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (top) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (bottom).\AK{I think the caption should also state the cuts and that this is LO.}}
-\label{fig:ratio2d_LO}
-\end{figure}
+% As explained previously, the low di-jet invariant mass are dominated by tri-boson production.
+% Therefore, a comparison of the various approximations in an \emph{inclusive} phase-space volume should exclude the region where tri-boson contributions are dominating.
+% To that end, we have chosen for the inclusive fiducial volume to take the following values for the VBS cuts:
+%

### 2018-02-16 Draft/crosssectionNLO.tex
some extra corrections. Start of the WE for Mathieu

--- 2018-02-16 Draft/crosssectionNLO.tex
@@
         {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
-        {\sc Powheg-Box}  &  $1.362$   $0.003$   \\
+        {\sc Powheg-Box}  &  $1.362$  & $0.003$   \\
         {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\

### 2018-02-16 Draft/distributionsLO.tex
some improvements in the draft
Updated distributionsLO section
some extra corrections. Start of the WE for Mathieu

@@
 We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
-This means that at LO, in the fiducial volume, the VBS approximation is good to a per cent.
-\MP{Add some comment with respect to the 2D scan.}
+This means that at LO, in the fiducial volume and for energies relevant to the LHC, the VBS approximation is good to a per cent.
+This is in agreement with the findings of section \ref{subsec:LOinclusive} as the present comparison completely exclude the region where tri-boson contributions could have a noticeable impact.
 
- \begin{figure}[h!]
+ \begin{figure*}[htb!]
    \centering

### 2018-02-16 Draft/shower.tex
some extra corrections. Start of the WE for Mathieu

@@
 For the {\sc Powheg-Box}, the eponymous \MP{Is it the correct word?
-Because it would mean that the work ``Powheg'' has different meaning.
+Because it would mean that the word ``Powheg'' has different meaning.
 Isn't it?} \AK{Changed to epononymous.
-Although still not correct as the powheg-box takes its name from the powheg mathcing and not the other way around....
+Although still not correct as the powheg-box takes its name from the powheg matching and not the other way around...
 :)}

### 2018-02-19 Draft/acknowledgements.tex
Add acknowledgment
added acknowledgments

@@
 The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
-Moreover, this work was supported by sveral STSM Grant from the COST Action CA16108.
+Moreover, this work was supported by several STSM Grant from the COST Action CA16108. Many authors acknowledge
+hospitality from Nikhef, where part of this work was performed.
 
@@
 
-AK acknowledge financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595
+MZ is supported
+ by the Netherlands National Organisation for Scientific
+ Research (NWO),

### 2018-02-19 Draft/acknowledgements.tex

@@
 
+AK acknowledge financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
+MR acknowledges funding from the European Union's Horizon 2020 research and innovation programme as part of the Marie Sklodowska-Curie Innovative Training Network MCnetITN3 (grant agreement no.
+722104).
 MZ is supported

### 2018-02-19 Draft/conclusion.tex

@@
-- Sum-up of the study. \\
+In the present article, a detailed study of the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC has been presented.
+The main focus is the electroweak (EW) production of such a final state where vector-boson (VBS) occurs.
+So far, all NLO computations have been performed in the so-called VBS approximation.
+Only recently a full computation became available \cite{Biedermann:2017bss}.
+Therefore, various theoretical predictions have been compared to the full computation.
+This has not only been performed in a typical VBS fiducial region but also in more inclusive volumes.
+We quantify precisely the differences that arise for several physical observables and in particular for the di-jet invariant mass and the rapidity-separation of the leading two jets.
+This is the first time that such a in-depth study is performed and should be representative of the quality of the approximations for other VBS signatures.
+In addition to fixed order predictions we have also investigated the impact of parton-shower.
+To that end, several fixed-order computations matched to parton shower have been used.
+It turns out that very large differences can appear for certain observables in the central region.
+These differences appear in the central region where for VBS, colour-recombination plays a significant role.
+These finding are new and should trigger further investigations in the theoretical community as well as by experimental collaborations.
+Indeed, measurements of such observables should allow for a better understanding of colour-recombination in parton shower.
+\MP{It might be too strong a statement.}
+The results presented here are exclusively theoretical.
+Nonetheless, they should raise significant interests in the experimental collaborations.
+Therefore, to supplement this summary, we provide several recommendations for the use of theoretical predictions for the quest of measuring VBS processes precisely.
 
@@
 Recommendations to experimental collaborations: \\
+- Stress that this is only for W+W+ but that qualitative results should apply to other VBS signatures with massive gauge bosons.
 - Combinations with EW NLO corrections. \\

### 2018-02-19 Draft/distributionsNLO.tex

@@
 On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
-The VBS-approximated predictions ({\sc BONSAY} and the {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
+The VBS-approximated predictions ({\sc Bonsay} and the {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
 The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
@@
 While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
-This is in contrast with {\sc BONSAY} and {\sc POWHEG} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
+This is in contrast with {\sc Bonsay} and {\sc Powheg} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
 Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.

### 2018-02-19 Draft/introduction.tex

@@
 Among the possible diagrams,
-the scattering process can be mediated also by a Higgs boson
+the scattering process can be mediated by a Higgs boson
 and involve in particular their longitudinal component.
@@
 it is thus of prime importance to provide predictions with systematic uncertainties
-at least comparable to the current and experimental precisions~\cite{CMS:2016rcn}.
+at least comparable to the current and envisaged experimental precisions~\cite{CMS:2016rcn}.
 
@@
 limits the number of partonic processes and total number of Feynman diagrams for each process.
+Nonetheless, it posses all features of VBS at the LHC and is thus representative of other VBS signature.
 Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.
@@
 This sentence is not very convincing to me.}
+\MP{I added ``Nontheless [...]'' but I am not sure it is more convincing...}
 
@@
 shower  in {\sc Herwig 7}~\cite{Bellm:2015jjp} was carried out.
-Both {\sc MC@NLO}-like~\cite{Frixione:2002ik} and {\sc POWHEG}-like~\cite{Nason:2004rx,Frixione:2007vw} matching was studied.
+Both {\sc MC@NLO}-like~\cite{Frixione:2002ik} and {\sc Powheg}-like~\cite{Nason:2004rx,Frixione:2007vw} matching was studied.
 In this work we extend such a comparison by presenting
@@
 Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study at fixed order, respectively.
-Section~\ref{sec:matching} complements our study by comparing predictions at LO and NLO which include the effect of parton showers and hadronization.
+Section~\ref{sec:matching} complements our study by comparing predictions at LO and NLO which include the effect of parton showers and hadronisation.
 The last section consists of concluding remarks and recommendations for experimental collaborations.

### 2018-02-19 Draft/scanNLO.tex
some improvements in the draft
Updated scanNLO section

@@
 \begin{tabular}{c|c|c}
-Prediction & $\sigma_{\textrm{tot}}\,[\textrm{fb}]$ & $\delta$ \\
+Prediction & $\sigma_{\textrm{tot}}\,[\textrm{fb}]$ & $\delta [\%]$ \\
 \hline
@@
 \hline
-$|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-10\%$ \\
+$|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-10$ \\
 \hline
-$|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $-2\%$
+$|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $-2$
 \end{tabular}
@@
 
-\begin{figure}[h]
+\begin{figure}[hbt]
 \centering
@@
 \caption{Ratio of cross sections (fb) per bin of $(m_{\Pj\Pj},\,|\Delta y_{\Pj\Pj}|)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
-{\bf GP: notation to be changed, Mjj -> mjj, alphas alpha} }
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
 \label{fig:ratio2d_NLO}
@@
 \caption{Ratio of cross sections (fb) per bin of $(m_{\Pj\Pj},\,|\Delta y_{\Pj\Pj}|)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation with $s$-channel contributions over the full computation.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
-{\bf GP: notation to be changed, Mjj -> mjj, alphas alpha} }
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
 \label{fig:mjjdyjj_2d_NLO}
@@
 \begin{equation}
-  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
+%  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
+  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
   \label{eq:Zeppenfeld}
@@
 %
-The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees rather well with the full curve, obtained from {\sc MoCaNLO+Recola}.
+The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
 The prediction from {\sc Bonsay} is about $10\%$ lower.

### 2018-02-19 Draft/shower.tex

@@
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
-For the {\sc Powheg-Box}, the eponymous \MP{Is it the correct word?
-Because it would mean that the word ``Powheg'' has different meaning.
-Isn't it?} \AK{Changed to epononymous.
-Although still not correct as the powheg-box takes its name from the powheg matching and not the other way around...
-:)}
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For the {\sc Powheg-Box}, the eponymous 
+\MP{Is it the correct word? Because it would mean that the word ``Powheg'' has different meaning. Isn't it?} 
+\AK{Changed to epononymous. Although still not correct as the powheg-box takes its name from the powheg matching and not the other way around... :)}
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
 \caption{Exclusive jet multiplicity from predictions matched to parton shower, at LO (left) or NLO (right) accuracy, compared with the fixed-NLO result
-    computed with \sc{VBFNLO}}
+    computed with \sc{VBFNLO}. \MP{The plots themselves should probably have the label LO and NLO for the FO+PS predictions. One should also describe how the bands are obtaineds.}}
 \label{fig:PSnjet}

### 2018-02-19 Draft/abstract.tex
various changes following the vidyo discussion, up to 3.2 (included)

@@
   possible new-physics contributions there.  To test this hypothesis,
-  precise knowledge of the Standard Model contributions is necessary,
+  sound knowledge of the Standard Model contributions is necessary,
   with a precision which at least matches the experimental

### 2018-02-19 Draft/definition.tex
various changes following the vidyo discussion, up to 3.2 (included)

@@
-The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay with different flavours can proceed at the LHC through the partonic process:
-\AK{This is only one such process...}
-\MP{I added ``with different flavours'' and ``can''.}
-%
-\begin{equation}
-\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}.
-\end{equation}
-
-This process possesses three LO contributions of different orders.
-The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as the EW contribution.
-In addition to typical VBS contributions, as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
-Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.}\ $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.\AK{This sentence makes no sense to me.
-How about: ``Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the quark lines.
-$s$-channel denotes all the diagrams where the final state quarks are produced from the decay of a vector boson.'' Or am I missing something?}
-The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
-Some of them take the form of decay chains, for example the diagram represented in the middle of Fig.~\ref{diag:LO}, while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
-When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results.
-We will discuss the commonly-used possible choices in detail in the next section.
-
-The process can also be mediated via a gluon connecting the two quark lines while the $\PW$ bosons are radiated off the quark lines.
-These contributions are of order $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$ and feature different kinematical behaviours than the EW contributions.
-Nonetheless they share the same final state and therefore constitute an irreducible background.
-
-Finally, due to the specific colour structure of these two classes of amplitudes, there exist non-zero interferences if only one quark family is involved.
-These are of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$ and are usually small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
-
-In experimental measurements, special VBS-cuts are designed to enhance the EW contribution over the QCD one.
-These cuts are based on the fact that the two contributions have different kinematical behaviour.
-The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
-The two $\PW$ bosons are mostly produced centrally.
-This is in contrast to the QCD contribution which favours jets in the central region.
-Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
-This will be further discussed in Sec.~\ref{subsec:contributions}.
-Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes the separation between EW and QCD production becomes meaningless.
-Hence, combined measurements which are well defined theoretically should be rather performed by the experimental collaborations at the LHC.
-\AK{Should we also discuss the definition of the process at NLO - ie point out that at this level one can no longer distinguish EW/QCD production?}
-\MP{I added two sentences, I guess we should develop in the conclusion/recommendation part}
-
 \begin{figure*}[t]
@@
 \end{figure*}
+
+The scattering of two positively-charged $\PW$ bosons with their subsequent decay into different-flavour leptons 
+can proceed at the LHC through the partonic process:
+%
+\begin{equation}
+\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}.
+\end{equation}
+
+This process possesses three LO contributions of different orders.
+At LO, this process can proceed via three different coupling-order combinations:
+$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$ and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
+The first, commonly referred to as EW contribution or VBS~\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
+of vector bosons}, receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
+in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
+(center diagram) or from
+triple-boson production (right diagram).
+Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines. $s$-channel 
+denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, 
+and $u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
+The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
+
+When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results.
+We will discuss the commonly-used possible choices in detail in the next section.
+
+The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
+radiated off the quark lines. Because of the different colour structure, this contribution features
+different kinematical behaviours than VBS. Nonetheless they share the same final state and therefore constitute an irreducible background.
+
+Finally, the third contribution is the interference of diagrams belonging to the first with those belonging to the second. It is non-zero only for
+those partonic subprocesses which involve only one quark family. Such a contribution is typically small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
+
+In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
+These cuts are based on the different kinematical behaviour of the two contributions.
+The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
+The two $\PW$ bosons are mostly produced centrally.
+This is in contrast to the QCD contribution which favours jets in the central region.
+Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
+Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes, the separation between EW and QCD production becomes ill
+defined.
+Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.

### 2018-02-19 Draft/description.tex
various changes following the vidyo discussion, up to 3.2 (included)

@@
-In the comparison, the following codes are used:
+\begin{table*}[ht!]
+    \footnotesize
+    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
+        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
+        \hline
+        \hline
+        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
+        {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
+        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
+        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
+        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
+    \end{tabularx}
+    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
+\end{table*}
+
+In the following, the codes employed throughout this paper and the approximations implemented in each of them will be discussed:
 
@@
 
- \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator and matrix elements taken from several sources.
+    \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator. It implements the VBS approximation at LO and NLO, with
+        the exception of the virtual matrix elements, which are computed in the EVBA. Matrix elements are taken from several sources.
  Born matrix elements are adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic processes, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
@@
         with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
-        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections,
-        only loops with QCD-interacting particles are generated. As it has been already mentioned, such an approximation is equivalent to the assumption that the finite part of
+        and written to disk {\tt \#4}. No approximation is performed for the Born and real-emission matrix elements. 
+        For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
+        only loops with QCD-interacting particles are generated. Such an approximation is equivalent to the assumption that the finite part of
         those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
@@
         {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards/FKS\_params.dat} file to -1.
+        {\bf MZ what exactly needs to be clarified here? perhaps I am just too used to this that I do not see problems here}
 
@@
 One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
+In {\sc MoCaNLO+Recola} no approximation is performed at LO as well as at NLO, and, in particular, also contributions stemming from EW corrections to the interference are computed.
 
@@
 For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
+{\bf MZ : I would move these sentences in the setup part, possibly as footnotes}
 The {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.
@@
   \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
-event generator with the LO matrix element generator {\sc O'Mega}. It
+      event generator with the LO matrix element generator {\sc O'Mega}.
+{\bf MZ: if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
 provides FKS subtraction terms for any NLO process, while virtual matrix
@@
 \end{itemize}
+
+We conclude this section by summarizing the details of the various codes in Tab.~\ref{tab:wg1_codes}. In particular, it is specified whether
+\begin{itemize}
+    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
+    \item interferences between diagrams are included at LO;
+    \item diagrams which do not feature two resonant vector bosons are included;
+    \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
+        are included;
+    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
+        the  $\mathcal O (\alpha^6$) term.
+\end{itemize}

### 2018-02-19 Draft/introduction.tex
various changes following the vidyo discussion, up to 3.2 (included)

@@
 The interaction of longitudinally polarised bosons is of particular interest, 
-because the corresponding matrix elements feature both gauge and unitarity cancellations 
+because the corresponding matrix elements feature unitarity cancellations 
 that strongly depend on the actual structure of the Higgs sector.
@@
 limits the number of partonic processes and total number of Feynman diagrams for each process.
-Nonetheless, it posses all features of VBS at the LHC and is thus representative of other VBS signature.
+Nonetheless, it posseses all features of VBS at the LHC and is thus representative of other VBS signatures.
 Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.
-\AK{Could one not argue the opposite?
-That because it is easy and only has a certain class of diagrams it doesn't capture all the differences one might find between different simulation programs?
-This sentence is not very convincing to me.}
-\MP{I added ``Nontheless [...]'' but I am not sure it is more convincing...}
 
 In the last few years, several next-to-leading order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
-These VBS computations all rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Oleari:2003tc}.
-Recently the complete NLO corrections to $\PW^+\PW^+$ have been performed in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations used in most tools.
-\AK{I have changed this sentence a bit, as I felt it didn't convey the message strongly enough.
-I also added a reference to Oleari and Zeppenfeld which have a statement about the VBS approximation being accurate at the 0.3\% level at LO.
-}
+All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Oleari:2003tc,Denner:2012dz}.
+Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations used in most tools.
 
-Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}\AK{As stated above this paper has a statement on the LO approximation.
-As far as I can see all further papers cite this one as the reason why the VBS approximation is good enough.}.
-Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
+{\bf MZ: we can remove the following sentence, up to the citation of Oleari}
+Apart from Ref.~\cite{Biedermann:2017bss}, no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}.
 
+\iffalse
 The full gauge-invariant process including the $\PW^+\PW^+$ scattering 
@@
 \footnote{The EW contribution is sometimes referred to as the VBS contribution, even it involves also non-VBS contributions.}
-Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
-This allows us to quantify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
-It is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.
+\fi
+After having defined the VBS process in Sec.~\ref{sec:definition} and having described the approximations of the various computer 
+codes in Sec.~\ref{sec:details}, in Sec.~\ref{sec:LO} a leading-order (LO) study 
+of the different contributions which lead to the production of two same-sign $\PW$ bosons and 
+two jets is performed, as a function of typical VBS cuts. In the same section predictions for VBS from different tools are compared
+the level of the cross section and differential distributions. The article continues in Sec.~\ref{sec:NLO} where the comparison is extended to the
+NLO corrections to VBS. The effect of the inclusion of matching LO and NLO computations to parton-shower (PS) is 
+discussed in Sec.~\ref{sec:matching}. Finally,
+Sec.~\ref{sec:conclusion} contains concluding remarks and recommendations for experimental collaborations.
 
+Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
+
+\iffalse
 At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
@@
 The last section consists of concluding remarks and recommendations for experimental collaborations.
+\fi

### 2018-02-19 Draft/process.tex
various modifications
various changes following the vidyo discussion, up to 3.2 (included)

@@
-As mentioned previously, the contribution of main interest in our process is
-the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex.
-Therefore it is justified to approximate the full EW contributions simply by only these contributions which contain the $2\rightarrow 2$ scattering process as a subpart.
-However, this set of contributions is not gauge invariant. In order to make it gauge invariant, one 
-should perform an on-shell projection of the incoming and outgoing $\PW$ bosons.
+We now turn to discuss the various approximations which are implemented in computer programs for the EW contribution at
+$\mathcal{O}{\left(\alpha^{6}\right)}$. Since we are mostly interested in 
+the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 
+full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a subpart.
+However, this set of contributions is not automatically gauge invariant. In order ensure gauge invariance, one 
+an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
 Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
-Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
+Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected 
+to the final-state leptons, which are already time-like, are put on-shell. {\bf MZ is this still gauge invariant? if so, one should change 
+the sentence above ``In order to ensure..''}
 Then the polarisation of the gauge boson is accommodated for following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
@@
 
-A less crude approximation consists in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two.
+An improvement of such an approximation consists 
+in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two classes.
 These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
-The $s$-channel squared diagrams and any interferences with $s$-channels are also discarded.
+The $s$-channel squared diagrams and any interferences between them and the  $t/u$-channels are also discarded.
 This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
 We will adopt the latter denomination in the following of the article.
-Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
-This approximation is gauge-invariant, which can be seen by considering that the two protons and therefore the two incoming quarks belong to two different, but otherwise identical, copies of the SU(3) gauge group.
+%Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
+This approximation is gauge-invariant, a fact that can be appreciated by considering the two incoming quarks as belonging to two different copies of the 
+$\rm{SU}(3)$ gauge group.
 
-A further refinement is to add the squared matrix element of the $s$-channel contributions, still neglecting 
-all interferences between different kinematic channels, as it is implemented in in {\sc VBFNLO}\AK{CITATIONS}.
+A further refinement is to add to the VBS approximation the squared matrix element of the $s$-channel contributions.
 
-All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard})\AK{CITATIONS} \MP{No ref.
-for MoCaNLO+Recola} consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
-Note that the final $\PW$ boson can always be considered either on-shell or off-shell without affecting the previous discussion.
-All the codes mentioned here are described in details in the following sub-section.
-
-Moving on to NLO accuracy, one can extend the approximations presented at LO.
-The VBS approximation at NLO is straightforward for the virtual contributions, for the real-contributions one must be careful about gluon-initiated processes\footnote{The initial gluon must not couple to the other initial quark, otherwise there are infrared divergences proportional to $s$-channels which do not match with the ones found in the virtual contributions.
-The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument as presented above.
-This approach is also fully consistent with the picture of two separate SU(3) copies.
-}.
+The approximations performed at LO can be extended when NLO QCD corrections to the $\mathcal{O}{\left(\alpha^{6}\right)}$ are computed.
+The VBS approximation can be extended at NLO in a straightforward manner for what concerns the virtual contributions; 
+for the real-emission contributions special care must be taken for the gluon-initiated processes\footnote{The initial-state gluon and quark 
+    must not couple together, otherwise infrared divergences proportional to $s$-channels will appear, 
+     which do not match with the ones found in the virtual contributions.
+     The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument presented above.}.
+     \iffalse
 This is implemented in the {\sc Powheg-Box}.
@@
 virtual contributions is included as a $K$-factor. 
+\fi
 
-A further refinement is to consider the full real contributions as well as part of the virtual.
+A further refinement is to consider the full real contributions, which include all interferences, and part of the virtual.
 In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and 
 assuming a cancellation of the infrared (IR) poles.
-Such an approximation is implemented by {\sc MG5\_aMC}.
-\MP{I think this is not a gauge invariant approximation. If not, this should be commented on.}
+%Such an approximation is implemented by {\sc MG5\_aMC}.
+%\MP{I think this is not a gauge invariant approximation. If not, this should be commented on (if yes also as this is not transparent to me).}
 
-Finally, when considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ and its corresponding real QCD radiation, other contributions have to be added.
+{\bf MZ: why are we changing here the notation from $\alpha$ to $g$????}
+In fact, when considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ and its corresponding real QCD radiation, 
+other contributions of EW origin have to be added.
 Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
 The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones. 
-Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
-
-In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
-\begin{itemize}
-    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
-    \item interferences between diagrams are included at LO;
-    \item diagrams which do not feature two resonant vector bosons are included;
-    \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
-        are included;
-    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
-        the  $\mathcal O (\alpha^6$) term.
-\end{itemize}
-
-\begin{table*}[ht!]
-    \footnotesize
-    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
-        \hline
-        \hline
-        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
-        {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
-        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
-        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
-        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
-        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
-        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
-    \end{tabularx}
-    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
-\end{table*}
+%Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

### 2018-02-20 Draft/crosssectionLO.tex
updated fixed-LO results from MG5_aMC

--- 2018-02-16 Draft/crosssectionLO.tex
@@
         \hline
-        {\sc Bonsay}  &  $X$ & $0.0002$ \\
-        {\sc MG5\_aMC}&  $1.435$ & $0.004$ TO BE UPDATED  \\
+        {\sc Bonsay}  &  $1.43636 \pm 0.00002$ \\
+        {\sc MG5\_aMC}&  $1.430$ & $0.001$ \\
         {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\

### 2018-02-20 Draft/shower.tex
minor changes and comments in shower.tex

@@
 the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
-can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO}, we
+can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} \BJ{ and the {\sc Powheg-Box}}, we
 restrict ourselves to showing results only in the VBS approximation,
 {\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
-also {\sc PHANTOM} is employed for LO+PS results.\\
+also {\sc PHANTOM} is used for LO+PS results.\\
 {\sc MG5\_aMC}, which
@@
     are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
-    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties is shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
 are respectively the nine-point scale uncertainty and the PDF one.}
@@
 theoretical uncertainties: for the former, we show both PDF and scale uncertainties, obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
-scale by a factor 2 around its central value, Eq.~\ref{eq:defscale} (nine-point variations); for the latter, we show the 
+scale by a factor of two around its central value, Eq.~(\ref{eq:defscale}) (nine-point variations); for the latter, we show the 
 three-point scale uncertainties, obtained by considering correlated variations of the renormalization and factorization scales. 
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within few per cent, both at LO and NLO. Larger discrepancies however will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within a few per cent, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
 the following. Before turning to the differential observables, we point out the smallness of the theory uncertainties due to the scale variations, both when
@@
 with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
-{\sc VBFNLO} \emph{i.e.}\ the VBS approximation with $s$-channel contributions).
-For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
+{\sc VBFNLO} \emph{i.e.}\ the VBS approximation with $s$-channel \BJ{Note that first paragraph of the Sec.
+says that s-channel contributions are neglected in VBFNLO.} For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
 As for the table, we show theoretical uncertainties for the NLO+PS samples
@@
 The first observable we investigate is the exclusive jet multiplicity, shown in Fig.~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
-main effects are driven by the parton shower that is employed {\sc Herwig++/7} or {\sc Pythia8}, with the clear tendency of producing more radiation for the latter,
+main effects are driven by the parton shower that is employed ({\sc Herwig++/7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
 leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
@@
 \caption{Exclusive jet multiplicity from predictions matched to parton shower, at LO (left) or NLO (right) accuracy, compared with the fixed-NLO result
-    computed with \sc{VBFNLO}. \MP{The plots themselves should probably have the label LO and NLO for the FO+PS predictions. One should also describe how the bands are obtaineds.}}
+    computed with \sc{VBFNLO}. \MP{The plots themselves should probably have the label LO and NLO for the FO+PS predictions. One should also describe how the bands are obtained.}}
 \label{fig:PSnjet}
@@
 
-The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj} has some similarities to the invariant-mass distribution: at LO+PS all predictions,
+The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities to the invariant-mass distribution: at LO+PS all predictions,
 except for {\sc VBFNLO3+Herwig7} where the effect is mitigated, show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
 quantitatively similar way. At NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
-exception is the the {\sc Powheg-Box} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
+exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
 it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
@@
 
-The transverse momentum of the hardest and second-hardest jets are shown in Figures~\ref{fig:PSpt1} and~\ref{fig:PSpt2} respectively. In general, for both observables,
+The transverse momentum of the hardest and second-hardest jets are shown in Figs.~\ref{fig:PSpt1} and~\ref{fig:PSpt2}, respectively. In general, for both observables,
 predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transverse-momentum spectra are softer than
@@
 
-Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}.
+Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Figs.~\ref{fig:PSy3} and~\ref{fig:PSz3}.
 {\bf MZ the rapidity can be dropped (check also the following discussion in case)}

### 2018-02-20 Draft/acknowledgements.tex
Many changes from Ansgar and Mathieu

@@
-We would like to thank \ldots \\
+The authors thank \ldots \\
 the {\sc Pythia8} authors, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
@@
 The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
-Moreover, this work was supported by several STSM Grant from the COST Action CA16108. Many authors acknowledge
-hospitality from Nikhef, where part of this work was performed.
+Moreover, this work was supported by several STSM Grants from the COST Action CA16108.
+Many authors acknowledge hospitality from Nikhef, where part of this work has been performed.
 
@@
 reference number DE 623/6-1.
-
-AK acknowledge financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
+%
+AK acknowledges financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
 MR acknowledges funding from the European Union's Horizon 2020 research and innovation programme as part of the Marie Sklodowska-Curie Innovative Training Network MCnetITN3 (grant agreement no.
 722104).
-MZ is supported
- by the Netherlands National Organisation for Scientific
- Research (NWO),
+MZ is supported by the Netherlands National Organisation for Scientific Research (NWO),

### 2018-02-20 Draft/conclusion.tex
Many changes from Ansgar and Mathieu

@@
 In the present article, a detailed study of the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC has been presented.
-The main focus is the electroweak (EW) production of such a final state where vector-boson (VBS) occurs.
+The main focus is the electroweak (EW) production of such a final state where vector-boson scattering (VBS) occurs.
 So far, all NLO computations have been performed in the so-called VBS approximation.
 Only recently a full computation became available \cite{Biedermann:2017bss}.
-Therefore, various theoretical predictions have been compared to the full computation.
+Various theoretical predictions have been compared to the full computation.
 This has not only been performed in a typical VBS fiducial region but also in more inclusive volumes.
 We quantify precisely the differences that arise for several physical observables and in particular for the di-jet invariant mass and the rapidity-separation of the leading two jets.
-This is the first time that such a in-depth study is performed and should be representative of the quality of the approximations for other VBS signatures.
+This is the first time that such an in-depth study is performed and should be representative of the quality of the approximations for other VBS signatures.
 In addition to fixed order predictions we have also investigated the impact of parton-shower.
 To that end, several fixed-order computations matched to parton shower have been used.
-It turns out that very large differences can appear for certain observables in the central region.
+It turns out that very large differences can appear for certain observables.
 These differences appear in the central region where for VBS, colour-recombination plays a significant role.
-These finding are new and should trigger further investigations in the theoretical community as well as by experimental collaborations.
+These findings are new and should trigger further investigations in the theoretical community as well as by experimental collaborations.
 Indeed, measurements of such observables should allow for a better understanding of colour-recombination in parton shower.
-\MP{It might be too strong a statement.}
+\MP{It might be too strong a statement. At least Simon will rephrase it.}
 The results presented here are exclusively theoretical.

### 2018-02-20 Draft/contributions.tex
Many changes from Ansgar and Mathieu

@@
-At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$ \AK{We have mentioned this many times at this point.
-Perhaps not worth repeating again?}.
+% At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$
+% \AK{We have mentioned this many times at this point. Perhaps not worth repeating again?}.
 In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
@@
 Note that these contributions are not present in calculations relying on the VBS approximation.
-Also, the EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
+The EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
 The same holds true for jet rapidity difference larger than $2.5$ (right).
@@
 The sum of all the contributions is in blue.
-The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.}
+The cuts applied are the ones of of Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.}
 \label{fig:mjjdyjj_1d}
@@
 % This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
-This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and for our LO inclusive study (see below).
+This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study (see below).
 Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
@@
 \caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top), $\mathcal{O}(\alphas\alpha^5)$ (middle), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
-The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
+The cuts applied are the ones of of Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
 }

### 2018-02-20 Draft/crosssectionLO.tex
Many changes from Ansgar and Mathieu

@@
 This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
-the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations. This is in agreement with the findings of Ref.~\cite{Oleari:2003tc}.
+the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations. This is in agreement with the findings of Ref.~\cite{Denner:2012dz,Oleari:2003tc}.
 
@@
     \caption{\label{tab:wg1_LOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
-    The uncertainties shown refers to the estimated statistical error of the Monte Carlo programs.
+    The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.
     The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.

### 2018-02-20 Draft/crosssectionNLO.tex
Many changes from Ansgar and Mathieu

--- 2018-02-16 Draft/crosssectionNLO.tex
@@
         \hline
-        {\sc Bonsay}  &  $X$ & $0.0009$  \\
+        {\sc Bonsay}  &  $1.35039$ & $0.00006$  \\
         {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
         {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
-        {\sc Powheg-Box}  &  $1.362$   $0.003$   \\
+        {\sc Powheg-Box}  &  $1.362$  & $0.003$   \\
         {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
@@
 
-The first observation is that the predictions featuring two versions of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are close.
+The first observation is that the predictions featuring two versions of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are relatively close (\MP{Final number to be added})
+\footnote{The {\sc VBFNLO}-predictions omitting $s$-channel contributions amounts to $1.3703(1)$ fb.}.
 This means that the double-pole approximation on the two W bosons used in {\sc Bonsay} constitutes a good approximation of the VBS-approximated virtual corrections implemented in the {\sc Powheg-Box}.

### 2018-02-20 Draft/definition.tex
Many changes from Ansgar and Mathieu

@@
 At LO, this process can proceed via three different coupling-order combinations:
-$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$ and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
+$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
 The first, commonly referred to as EW contribution or VBS~\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
@@
 triple-boson production (right diagram).
-Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines. $s$-channel 
-denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, 
-and $u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
+Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines.
+$s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
+$u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
 The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
@@
 
-Finally, the third contribution is the interference of diagrams belonging to the first with those belonging to the second. It is non-zero only for
-those partonic subprocesses which involve only one quark family. Such a contribution is typically small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
+Finally, the third contribution is the interference of the two type of amplitudes described above.
+It is non-zero only for those partonic subprocesses which involve only one quark family.
+Such a contribution is typically small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
 

### 2018-02-20 Draft/description.tex
Many changes from Ansgar and Mathieu

@@
 The {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.
-The renormalisation and factorisation scale used differ slightly from one defined in Eq.~\eqref{eq:defscale}, as rather than constructing the jets the {\sc Powheg-Box} uses the transverse momentum of the two final-state quarks in the underlying Born event.
+The renormalisation and factorisation scale used differ slightly from the one defined in Eq.~\eqref{eq:defscale}, as rather than constructing the jets the {\sc Powheg-Box} uses the transverse momentum of the two final-state quarks in the underlying Born event.
 

### 2018-02-20 Draft/distributionsLO.tex
Many changes from Ansgar and Mathieu

@@
 This means that at LO, in the fiducial volume and for energies relevant to the LHC, the VBS approximation is good to a per cent.
-This is in agreement with the findings of section \ref{subsec:LOinclusive} as the present comparison completely exclude the region where tri-boson contributions could have a noticeable impact.
+This is in agreement with the findings of section \ref{subsec:LOinclusive} as the present comparison completely excludes the region where tri-boson contributions could have a noticeable impact.
 
@@
    \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
-\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (top) and rapidity difference of the two tagging jets (bottom).
+\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
 The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.

### 2018-02-20 Draft/distributionsNLO.tex
Many changes from Ansgar and Mathieu

@@
 
-We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (top) and the rapidity separation (bottom) of the two tagging jets.
+We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (left) and the rapidity separation (right) of the two tagging jets.
 For high invariant mass, all predictions agree rather well.
@@
    \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
-\caption{\label{fig:distNLO1} Differential distributions in the invariant mass (top) and rapidity difference of the two tagging jets (bottom).
+\caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
 The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
-The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
@@
 
-Concerning the transverse momentum (top) and rapidity (bottom) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
+Concerning the transverse momentum (left) and rapidity (right) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
 While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
@@
    \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
-\caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (top) and rapidity of the hardest jet (bottom).
+\caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
 The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
-The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
@@
 
-The last set of differential distributions is the invariant mass of the two charged lepton (top) and the Zeppenfeld variable for the anti-muon (bottom).
+The last set of differential distributions is the invariant mass of the two charged lepton (left) and the Zeppenfeld variable for the anti-muon (right).
 Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
@@
    \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
-\caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (top) and Zeppenfeld variable for the muon (bottom).
+\caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
 The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
-The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.

### 2018-02-20 Draft/input.tex
Many changes from Ansgar and Mathieu

@@
-The VBS production mechanism is simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
+The partonic processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
 The NNPDF~3.0 parton density~\cite{Ball:2014uwa} with five flavour scheme, NLO QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ is employed.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
@@
         These are an in\-vari\-ant mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
-        The nominal value of these cuts if not stated explicitly read:
+        The nominal values of these cuts if not stated explicitly read:
         \begin{align}
@@
         \end{align}
-    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
+    \item When EW corrections are computed, real photons and charged fermions are clustered together using the anti-$k_T$ algorithm with
         radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.

### 2018-02-20 Draft/introduction.tex
Many changes from Ansgar and Mathieu

@@
 the scattering process can be mediated by a Higgs boson
-and involve in particular their longitudinal component.
+and involves in particular their longitudinal component.
 The interaction of longitudinally polarised bosons is of particular interest, 
@@
 it is thus of prime importance to provide predictions with systematic uncertainties
-at least comparable to the current and envisaged experimental precisions~\cite{CMS:2016rcn}.
+at least comparable to the current and envisaged experimental precision~\cite{CMS:2016rcn}.
 
@@
 limits the number of partonic processes and total number of Feynman diagrams for each process.
-Nonetheless, it posseses all features of VBS at the LHC and is thus representative of other VBS signatures.
+Nonetheless, it possesses all features of VBS at the LHC and is thus representative of other VBS signatures.
 Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.
@@
 In the last few years, several next-to-leading order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
-All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Oleari:2003tc,Denner:2012dz}.
-Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations used in most tools.
+All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Denner:2012dz,Oleari:2003tc}.
+Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations at NLO QCD.
 
-{\bf MZ: we can remove the following sentence, up to the citation of Oleari}
-Apart from Ref.~\cite{Biedermann:2017bss}, no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}.
+% {\bf MZ: we can remove the following sentence, up to the citation of Oleari}
+% Apart from Ref.~\cite{Biedermann:2017bss}, no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}.
 

### 2018-02-20 Draft/process.tex
Many changes from Ansgar and Mathieu

@@
 full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a subpart.
-However, this set of contributions is not automatically gauge invariant. In order ensure gauge invariance, one 
-an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
+However, this set of contributions is not gauge invariant.
+In order ensure gauge invariance, an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
 Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
 Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected 
-to the final-state leptons, which are already time-like, are put on-shell. {\bf MZ is this still gauge invariant? if so, one should change 
+to the final-state leptons, which are already time-like, are put on-shell. \ZM{is this still gauge invariant? if so, one should change 
 the sentence above ``In order to ensure..''}
-Then the polarisation of the gauge boson is accommodated for following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
+Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
 Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
@@
 An improvement of such an approximation consists 
-in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two classes.
+in considering all $t$- and $u$-channel diagrams and squaring them separately, neglecting interference contributions between the two classes.
 These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
@@
 %Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
-This approximation is gauge-invariant, a fact that can be appreciated by considering the two incoming quarks as belonging to two different copies of the 
-$\rm{SU}(3)$ gauge group.
+This approximation is gauge-invariant, a fact that can be appreciated by considering the two incoming quarks as belonging to two different copies of the $\rm{SU}(3)$ gauge group.
 
@@
 
-{\bf MZ: why are we changing here the notation from $\alpha$ to $g$????}
-In fact, when considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ and its corresponding real QCD radiation, 
-other contributions of EW origin have to be added.
-Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
-The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones. 
+When considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ squared with the tree amplitude of order $\mathcal{O}(g^6)$, not only real QCD radiation but also QED ones have to be included in order cancel IR singularities.
+But all IR singularities related to photon emissions are not cancelled by the above mentioned virtual corrections.
+Another type of virtual corrections have to incorporated, namely the one-loop amplitudes of order $\mathcal{O}(g^8)$ interfered with the tree-level ones of order $\mathcal{O}(g_{\rm s}^2 g^4)$.
+Hence the full NLO corrections of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consist not only of QCD-type corrections but also of EW ones \cite{Biedermann:2017bss}.
+\MP{@MZ g. gs are for amplitude and alpha, alphas for matrix element squared.}
 %Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

### 2018-02-20 Draft/scanLO.tex
Many changes from Ansgar and Mathieu

@@
-In Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
-Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
+In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
+Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
 In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
-The low rapidity difference region possesses remnants of the tri-bosons contributions that peek at the an di-jet invariant mass around the W-boson mass.
+The low rapidity difference region possesses remnants of the tri-bosons contributions that peak at di-jet invariant mass around the W-boson mass.
 It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
@@
 
-\begin{figure}[hbt]
+\begin{figure*}[hbt]
 \centering
@@
 \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
+\caption{Ratio of cross sections per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
 Ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (top) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (bottom).
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
 The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
 \label{fig:ratio2d_LO}
-\end{figure}
+\end{figure*}
 % As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.

### 2018-02-20 Draft/scanNLO.tex
Many changes from Ansgar and Mathieu

@@
 The inclusion of $s$-channels cures partly the discrepancy in this region.
-Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains.
-This might indicate that also interferences (GP: and non--factorizable QCD corrections ? \MP{I don't know, we have to think about it}) are needed in this phase-space region.
+Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains \MP{To be checked the exact numerical value in data}.
+This might indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
 
@@
 \caption{
-Differential distributions in $m_{\Pj\Pj}$ (left) and $|\Delta y_{\Pj\Pj}|$ (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+Differential distributions in the di-jet invariant mass (left) and the rapidity-separation of the two tagging jets (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
 \label{fig:mjjdyjj_1d_1}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[hbt]
+\begin{figure*}[hbt]
 \centering
-{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}}
-\caption{Ratio of cross sections (fb) per bin of $(m_{\Pj\Pj},\,|\Delta y_{\Pj\Pj}|)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
+{\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}}
+{\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
+\caption{Ratio of cross sections per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
+Ratio of approximated squared amplitudes over the full matrix element.
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right)
 In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
 \label{fig:ratio2d_NLO}
-\end{figure}
+\end{figure*}
 %
-\begin{figure}[hbt]
-\centering
-{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-\caption{Ratio of cross sections (fb) per bin of $(m_{\Pj\Pj},\,|\Delta y_{\Pj\Pj}|)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation with $s$-channel contributions over the full computation.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
-\label{fig:mjjdyjj_2d_NLO}
-\end{figure}
+% \begin{figure}[hbt]
+% \centering
+% {\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
+% \caption{Ratio of cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation with $s$-channel contributions over the full computation.
+% In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
+% \label{fig:mjjdyjj_2d_NLO}
+% \end{figure}
 
 As expected, in the low invariant mass--low rapidity separation region of the jet pair the VBS approximation fails significantly (up to $40\%$ discrepancies).
-The inclusion of the $s$-channel brings the difference down to at most $5\%$.
+The inclusion of the $s$-channel brings the difference down to at most $5\%$ \MP{To be checked the exact numerical value in data}.
 However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}.
-In this region, the two leading jets have soft transverse momenta, according to the following low-angle approximation
-
-\begin{equation}
-\begin{split}
-m_{\Pj_i\Pj_j}^2 &= 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,(\cosh \Delta y_{\Pj_i\Pj_j} - \cos \Delta\phi_{\Pj_i\Pj_j}) \\
-&\approx 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,\cosh \Delta y_{\Pj_i\Pj_j} \,\,.
-\end{split}
-\end{equation}
+% In this region, the two leading jets have soft transverse momenta, according to the following low-angle approximation
+% 
+% \begin{equation}
+% \begin{split}
+% m_{\Pj_i\Pj_j}^2 &= 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,(\cosh \Delta y_{\Pj_i\Pj_j} - \cos \Delta\phi_{\Pj_i\Pj_j}) \\
+% &\approx 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,\cosh \Delta y_{\Pj_i\Pj_j} \,\,.
+% \end{split}
+% \end{equation}
 
@@
 This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
-For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is of about $5-10\%$.
+For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.
 In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.
 
-\begin{figure}[hbt]
+\begin{figure*}[hbt]
 \centering
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
-\caption{Differential distributions in the transverse momentum and rapidity of the hardest tagging jet at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+\caption{Differential distributions in the transverse momentum (left) and rapidity of the hardest tagging jet (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
 \label{fig:mjjdyjj_1d_2}
-\end{figure}
+\end{figure*}
 
-Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron. 
-It is defined as
+Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron, defined as
 %
@@
 %
-\begin{figure}[hbt]
+\begin{figure*}[hbt]
 \centering
@@
 {\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
-\caption{Differential distributions in the lepton-lepton invariant mass and the electron Zeppenfeld variable at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+\caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
 \label{fig:mjjdyjj_1d_3}
-\end{figure}
+\end{figure*}
 %

### 2018-02-20 Draft/shower.tex
Many changes from Ansgar and Mathieu

--- 2018-02-19 Draft/shower.tex
@@
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For the {\sc Powheg-Box}, the eponymous 
-\MP{Is it the correct word? Because it would mean that the word ``Powheg'' has different meaning. Isn't it?} 
-\AK{Changed to epononymous. Although still not correct as the powheg-box takes its name from the powheg matching and not the other way around... :)}
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
 are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
-must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?} \AK{In powheg the separation is done after shower. So it's really the jet.}.
+must be employed in order not to bias the results. \ZM{lepton-jet separation at the hard-event level?} \AK{In powheg the separation is done after shower. So it's really the jet.}.
 
@@
 a small effect (6\%) on the normalisation of distribution is induced. Finally, when the renormalisation
-and factorisation scales are set, the $\Delta R_{\Pj\Pl}$ cut is not imposed during the jet-clustering procedure, but this has no visible effect
-on the results \MP{Is it true? Because I remember some numbers from Christopher with $1\%$ or so}.
+and factorisation scales are set, the $\Delta R_{\Pj\Pl}$ cut is not imposed during the jet-clustering procedure.
+But this effect is below a per cent at the level of the fiducial cross sections.
 

### 2018-02-20 Draft/contributions.tex
contributions.tex: modified caption of table

@@
     \end{tabular}
-    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
+    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$, obtained with full matrix elements.
     These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}

### 2018-02-20 Draft/article.tex
First corrections
processes and definiton
editing command added in article.tex
Many changes from Ansgar and Mathieu
Few typos fixed in draft+new numbers from MoCaNLO+Recola

--- 2018-02-16 Draft/article.tex
@@
  \usepackage{morefloats}
+ \usepackage[utf8]{inputenc}
 %  \usepackage{siunitx}
@@
 \newcommand{\MR}[1]{{ {\color{red}{ [MR: #1]}} }}
-\newcommand{\AK}[1]{{ {\color{pink}{ [AK: #1]}} }}
+\newcommand{\AK}[1]{{ {\color{magenta}{ [AK: #1]}} }}
+\newcommand{\ZM}[1]{{ {\color{green}{ [MZ: #1]}} }}
+
+\newcommand{\BJ}[1]{{ {\color{cyan}{ [BJ: #1]}} }}
 
@@
 
-\institute{Universit\"at W\"urzburg, %
+\institute{
+INFN, Sezione di Torino, %
+Via P. Giuria 1, %
+10125 Torino, %
+Italy\label{infnto}
+\and
+Universit\"at W\"urzburg, %
 Institut f\"ur Theoretische Physik und Astrophysik,  %
@@
 \and
+Institute for Theoretical Physics,
+University of T\"ubingen,
+Auf der Morgenstelle 14,
+72076 T\"ubingen,
+Germany\label{tub}
+\and
 Physik-Institut,
@@
 Switzerland\label{uzh}
-\and
-INFN, Sezione di Torino, %
-Via P. Giuria 1, %
-10125 Torino, %
-Italy\label{infnto}
 \and
@@
 \and
-Nikhef,
-Science Park 105,
-1098XG Amsterdam,
-The Netherlands\label{nikh}
-\and
 CERN,
@@
 \and
-Institute for Theoretical Physics,
-University of T\"ubingen,
-Auf der Morgenstelle 14,
-72076 T\"bingen,
-Germany\label{tub}
+Nikhef,
+Science Park 105,
+1098XG Amsterdam,
+The Netherlands\label{nikh}
 }
@@
 \maketitle
-
+% \AK{Some general comments: We don't write the names of programs consistently everywhere. I think the nicest is to use}
+% \begin{verbatim} 
+% {\sc Generator}
+% \end{verbatim}
+% \AK{Ie captial first letter and lower-case everywhere else for generator names instead of all capital. But this is a matter of taste of course...}
+% \AK{We may want to make it more clear in the abstract/introduction why this study is worth publishing.
+So focus on the large contributions from non-VBS approxiamtion at NLO which until now has been reproted as small, and the large discrepancies in the NLO+PS predictions.
+That plus the recommendations we give should be the main selling point, I think.}
 \input{abstract}
@@
 
-\appendix
-
-\section{Appendix one}
+% \appendix
+% 
+% \section{Appendix one}
 

### 2018-02-20 Draft/crosssectionLO.tex
Few typos fixed in draft+new numbers from MoCaNLO+Recola

@@
         \hline
-        {\sc Bonsay}  &  $1.43636 \pm 0.00002$ \\
-        {\sc MG5\_aMC}&  $1.430$ & $0.001$ \\
-        {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\
+        {\sc Bonsay}  &  $1.43636$ & $0.00002$ \\
+        {\sc MG5\_aMC}&  $1.430\phantom{0}\phantom{0}$ & $0.001$ \\
+        {\sc MoCaNLO+Recola}  &  $1.43476$ & $0.00009$ \\
         {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\

### 2018-02-20 Draft/crosssectionNLO.tex
Few typos fixed in draft+new numbers from MoCaNLO+Recola

@@
         {\sc Bonsay}  &  $1.35039$ & $0.00006$  \\
-        {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
-        {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
-        {\sc Powheg-Box}  &  $1.362$  & $0.003$   \\
-        {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
+        {\sc MG5\_aMC}&  $1.363\phantom{0}\phantom{0}$ & $0.004$  \\
+        {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ \\
+        {\sc Powheg-Box}  &  $1.362\phantom{0}\phantom{0}$  & $0.003$   \\
+        {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\
     \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha^6)$.
+    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alphas\alpha^6)$.
     The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.

### 2018-02-20 Draft/crosssectionLO.tex
LO numbers from MG5_aMC updated again

--- 2018-02-20 Draft/crosssectionLO.tex
@@
         \hline
-        {\sc Bonsay}  &  $1.43636 \pm 0.00002$ \\
-        {\sc MG5\_aMC}&  $1.430$ & $0.001$ \\
-        {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\
+        {\sc Bonsay}  &  $1.43636$ & $0.00002$ \\
+        {\sc MG5\_aMC}&  $1.4304\phantom{0}$ & $0.0007$ \\
+        {\sc MoCaNLO+Recola}  &  $1.43476$ & $0.00009$ \\
         {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\

### 2018-02-20 Results/comparison_plots/myreplace.py

@@ -1,0 +1,23 @@
+#!/usr/bin/python
+
+import sys
+import os
+
+infile = sys.argv[1]
+outfile = infile
+
+content = open(infile).read()
+
+
+#content = content.replace('set terminal pdf font "Helvetica,14" enhanced dashed size 12 cm, 18 cm', \
+#                          'set terminal pdf font "Helvetica,12" enhanced dashed size 8 cm, 12 cm')
+#content = content.replace('set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",14" at graph 0.1, graph 0.9', \
+#                          'set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",12" at graph 0.03, graph 0.9')
+content = content.replace('set label "MonteCarlo comparison, NLO fixed order" font ",12" at graph 0.1, graph 0.88', \
+                          'set label "MonteCarlo comparison, NLO fixed order" font ",10" at graph 0.03, graph 0.88')
+#content = content.replace('set key at graph 1, graph 0.9 noautotitles spacing 2.4', \
+#                          'set key at graph 1, graph 0.8 noautotitles spacing 2.4')
+#content = content.replace('set ylabel \'Ratio /VBFNLO\'', \
+#                          'set ylabel \'Ratio /VBFNLO\' offset 1')
+
+open(outfile, 'w').write(content)

### 2018-02-20 Results/comparison_plots/replace_all.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+GPL=`ls *.gnuplot`
+
+for GP in $GPL ; do
+    echo $GP
+    ./myreplace.py $GP
+done

### 2018-02-20 Results/comparison_plots/run_all_macros.sh

@@ -1,5 +1,5 @@
 #!/bin/bash
-GPL=`ls plot_*LO.gnuplot`
+GPL=`ls plot_*_LO.gnuplot`
 
 
 for GP in $GPL ; do

### 2018-02-20 Draft/description.tex
reference to CMS

@@
   at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alphas^2\alpha^4$ including interferences between the two sets of diagrams.
-It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
+It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
 The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.

### 2018-02-20 Draft/input.tex
reference to CMS

@@
 The CKM-Matrix is assumed to be diagonal, meaning that the mixing between different quark families is neglected.
-The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.
+The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.
 

### 2018-02-20 Draft/acknowledgements.tex
Add ackn. for CS, change BONSAY description
- shame on you Marco for modifying my description ;-)

@@
 MZ is supported by the Netherlands National Organisation for Scientific Research (NWO),
+CS acknowledges support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.

### 2018-02-20 Draft/description.tex
Add ackn. for CS, change BONSAY description
- shame on you Marco for modifying my description ;-)

@@
 
-    \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator. It implements the VBS approximation at LO and NLO, with
-        the exception of the virtual matrix elements, which are computed in the EVBA. Matrix elements are taken from several sources.
- Born matrix elements are adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic processes, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
+\item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator written by Christopher Schwan and matrix elements taken from different sources:
+Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
 One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
+For the fiducial cross sections it uses the VBS approximation at LO and NLO.
+The virtuals are additionally approximated using a double pole approximation.
+For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) are used.
 

### 2018-02-20 Draft/scanNLO.tex
some fixes

@@
 In particular, we compute in each bin the ratio of the approximated cross sections over the full one.
-In Fig.~\ref{fig:ratio2d_NLO} and Fig.~\ref{fig:mjjdyjj_2d_NLO} we show the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$, respectively.
+In Fig.~\ref{fig:ratio2d_NLO} we show the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$, in the left and right plot respectively.
 
@@
 The inclusion of the $s$-channel brings the difference down to at most $5\%$ \MP{To be checked the exact numerical value in data}.
-However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}.
+However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:ratio2d_NLO}.
 % In this region, the two leading jets have soft transverse momenta, according to the following low-angle approximation
@@
 The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low $\pt$ region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
-In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the level of $15\%$ are present.
+In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.
 This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.

### 2018-02-20 Draft/shower.tex
some fixes

@@
 the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
-can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} \BJ{ and the {\sc Powheg-Box}}, we
+can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} and the {\sc Powheg-Box}, we
 restrict ourselves to showing results only in the VBS approximation,
@@
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For the {\sc Powheg-Box}, the namesake
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). The same parton showers will be employed for the LO results of {\sc PHANTOM}. For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
 well as the dipole shower can be employed.
-Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.\AK{versions??}
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.
@@
 are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
-must be employed in order not to bias the results. \ZM{lepton-jet separation at the hard-event level?} \AK{In powheg the separation is done after shower. So it's really the jet.}.
+must be employed in order not to bias the results.
 
@@
 three-point scale uncertainties, obtained by considering correlated variations of the renormalization and factorization scales.
+Theory uncertainties should have very little dependence on the tool employed.
 We observe that, once the width effect is taken into
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
-\caption{Exclusive jet multiplicity from predictions matched to parton shower, at LO (left) or NLO (right) accuracy, compared with the fixed-NLO result
-    computed with \sc{VBFNLO}. \MP{The plots themselves should probably have the label LO and NLO for the FO+PS predictions. One should also describe how the bands are obtained.}}
+\caption{Exclusive jet multiplicity from predictions matched to parton shower, at LO (left) or NLO (right) accuracy, compared with the fixed-NLO result computed with {\sc VBFNLO}.
+At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. \MP{The plots themselves should probably have the label LO and NLO for these predictions}}
 \label{fig:PSnjet}
@@
 
-Finally, focusing on the third jet, we conclude the list of differential observables with the rapidity and the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Figs.~\ref{fig:PSy3} and~\ref{fig:PSz3}.
-{\bf MZ the rapidity can be dropped (check also the following discussion in case)}
-In general, for observables which involve the third jet, one
-can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The rapidity and Zeppenfeld variable $z$
-are a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation (corresponding to low values of $z$)
-is clearly visible\footnote{The effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF/S-type processes,
-can be mitigated by setting {\tt SpaceShower:dipoleRecoil = on} in the {\sc Pythia8} input file (this requires version $\ge8.230$). 
-However, such a setting is not compatible with the matching
-in {\sc MG5\_aMC}, and has other effects, though smaller, on the rapidity spectrum of the two hardest jets.}; it is interesting to notice that
-this effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+Pythia8}. A similar
+Finally, focusing on the third jet, we conclude the list of differential observables with showing the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Fig.~\ref{fig:PSz3}. This 
+variable is closed related to the third jet rapidity, and small (large) value of $z$ correpsond to central (peripheral) rapidities. In general, for observables which involve the third jet, one
+can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The Zeppenfeld variable is 
+a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation, corresponding to low values of $z$,
+is clearly visible. Such an effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF(VBS)-type processes,
+can be mitigated by setting {\tt SpaceShower:dipole\-Recoil = on} in the {\sc Pythia8} input file;\footnote{this requires version $\ge8.230$. 
+Note that such a setting is not compatible with the NLO matching
+in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching).
+Also, this setting has other effects, though smaller, on the rapidity spectra of the two hardest jets.} it is interesting to notice that
+it survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+ Pythia8}. A similar
 behaviour of {\sc Pythia8}
-has also been observed in the study of EW production of a Z boson in association with two jets (see the recent CMS measurement, 
+has also been observed in the study of EW production of a $\PZ$ boson in association with two jets (see the recent CMS measurement, 
 Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}. 
-It is true that the central enhancement
+The central enhancement
 is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
@@
 on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is
-generated {\bf MZ cite here H VBF at NNLO?} \AK{I agree! :)}. It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty estimated via scale variations systematically underestimates the spread of predictions. Again, this stresses the need
+generated, e.g.
+when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}.
+It is a remarkable fact that, even for those observables that display small discrepancies,
+the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. Again, this stresses the need
  to employ at least two different tools in order to have a conservative estimate of theoretical uncertainties.
@@
 \centering
-\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j3.pdf}
-\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j3.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the rapidity of the third-hardest jet.}
-\label{fig:PSy3}
-\end{figure*}
-
-\begin{figure*}[hbt]
-\centering
 \includegraphics[width=0.47\textwidth]{figures/LOPS/z_j3.pdf}

### 2018-02-21 Draft/acknowledgements.tex
Small corrections and Conclusion drafted

--- 2018-02-20 Draft/acknowledgements.tex
@@
 reference number DE 623/6-1.
-%
 AK acknowledges financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
@@
 722104).
-MZ is supported by the Netherlands National Organisation for Scientific Research (NWO),
+CS acknowledges support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.
+MZ is supported by the Netherlands National Organisation for Scientific Research (NWO).

### 2018-02-21 Draft/conclusion.tex
Small corrections and Conclusion drafted

@@
 \MP{It might be too strong a statement. At least Simon will rephrase it.}
+
 The results presented here are exclusively theoretical.
 Nonetheless, they should raise significant interests in the experimental collaborations.
-Therefore, to supplement this summary, we provide several recommendations for the use of theoretical predictions for the quest of measuring VBS processes precisely.
+Therefore, to supplement this summary, we provide several concluding remarks concerning the use of theoretical predictions.
 
-\MP{This might deserve a section on its own.} \\
-Recommendations to experimental collaborations: \\
-- Stress that this is only for W+W+ but that qualitative results should apply to other VBS signatures with massive gauge bosons.
-- Combinations with EW NLO corrections. \\
-- Missing higher EW order: $\pm \delta^2_{\rm NLO EW}$ \\
-- Systematics when using NLO QCD approximation \\
-- Systematics of different parton shower \\
-- Combined measurement including  EW, QCD, and interference \\
-- Move to NLO predictions / generators \\
-- Comment on the irreducible QCD background \\
-- Uncertainties related to PDF.
-Some of us have already presented preliminary results on this subjetc \cite{}. % Radcor proceedings from Christopher.
-A forthcoming article will addresses related questions.
+As found in Ref.~\cite{Biedermann:2017bss}, the NLO EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ are the dominant NLO contributions to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
+It is thus highly desirable that they are combined with NLO-QCD predictions matched with parton shower.
+In Ref.~\cite{Biedermann:2016yds}, it has been demonstrated that these large EW corrections originate from the Sudakov logarithms which factorise.
+Therefore we recommend to combined them in a multiplicative way.
+Concerning the estimation of missing higher-order corrections of EW type they can be obtained, in a first approximation, from $\pm \delta^2_{\rm NLO EW}$.
+The missing higher-order mixed QCD-EW corrections can be estimate by taking the difference between the multiplicative and additive prescription.
+A detailed study of the combination of higher-order corrections has been carried out in the context of SM background for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.
+
+We have shown how good the VBS approximation is performing in both inclusive and exclusive set-ups at both LO and NLO-QCD accuracy.
+It turns out that for typical fiducial region used by experimental collaborations for their measurements, the agreement between the approximations and full calculation is certainly satisfactory given the current experimental precision.
+Nonetheless, in the future when experimental measurements will improve, care has to be taken when using such approximations, in particular, if more inclusive phase-space are used.
+
+Concerning the fixed-order predictions supplemented with parton shower, we have shown that for observables defined at LO, the differences are reasonable.
+On the other hand, for observables only defined at NLO-QCD, such as the ones related to the third hardest jet, large differences can arise between different parton-shower algorithms.
+Therefore, jet-veto procedures or selections based on extra radiation should be avoided as they carry rather large uncertainties.
+
+In addition to the standard interpretation of EW signal versus QCD background, combined measurements should also be presented as they are well defined theoretically.
+At LO, the interferences can be included in the background component.
+Nonetheless, at NLO the concept of EW and QCD component become meaningless as at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes mix.
+Therefore, a combined measurement including the EW, QCD, and interference contributions is desirable.
+Note that with such a measurement, an interpretation in terms of EW component is still possible.
+This would amount to replace the subtraction of the QCD component based on Monte Carlo predictions by an actual measurement.
+\MP{I am aware that this might be the most touchy point.
+Therefore we should probably discuss it all together to ensure that we all agree on a definite statement.}
+
+As demonstrated above, numerous programs exist to simulate the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC.
+So far there is no public code that perform the full NLO computation matched with parton shower.
+Nonetheless, full computations at NLO and publicly available tools at NLO-QCD accuracy in the VBS approximation matched to parton shower are available.
+Therefore, we encourage experimental collaborations to move to NLO accuracy supplemented with parton shower as much as possible.
+In particular, we are willing to support this effort. \MP{Are we?}
+
+The present study has focused on the orders $\mathcal{O}{\left(\alpha^{6}\right)}$ at LO and $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ at NLO.
+Nonetheless NLO computations and publicly available tools also exist for the QCD-induced process \cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss}.
+They should therefore be also used as much as possible.
+
+Uncertainties related to PDF has been hardly addressed in the present article.
+It has only be discussed briefly in Sec.~\ref{sec:matching} where scale variation in combination with PDF variation has been shown.
+Some of us have already presented preliminary results on this subject \cite{Schwan:2017yy}. % Radcor proceedings from Christopher.
+Forthcoming publications will thus address related questions.
+
+Finally, the study presented here concentrates on the ${\rm W}^+{\rm W}^+$ signature.
+The features observed here (validity of the VBS approximation or comparison of theoretical predictions matched to parton shower for example) should be qualitatively similar for other VBS signatures with massive gauge bosons.
+But the quantitative conclusions are strictly restricted to ${\rm W}^+{\rm W}^+$ signature.
+For other signatures, similar quantitative study should be performed.
+Beyond the theoretical findings of this work, we also hope that it can serve as a guideline for experimental collaborations in their quest for the measurements of VBS processes at the LHC.

### 2018-02-21 Draft/scanNLO.tex
Small corrections and Conclusion drafted

@@
 
-The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low $\pt$ region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
+The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low transverse-momentum region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
 In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.

### 2018-02-21 Draft/shower.tex
Small corrections and Conclusion drafted

@@
 generated, e.g.
-when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}.
+when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
 It is a remarkable fact that, even for those observables that display small discrepancies,

### 2018-02-21 Draft/introduction.tex
Small corrections and Conclusion drafted
minor typos fixed in introduction.tex

@@
 the scattering process can be mediated by a Higgs boson
-and involves in particular their longitudinal component.
+and involves in particular its longitudinal component.
 The interaction of longitudinally polarised bosons is of particular interest, 
@@
 of the different contributions which lead to the production of two same-sign $\PW$ bosons and 
-two jets is performed, as a function of typical VBS cuts. In the same section predictions for VBS from different tools are compared
+two jets is performed, as a function of typical VBS cuts. In the same section predictions for VBS from different tools are compared at 
 the level of the cross section and differential distributions. The article continues in Sec.~\ref{sec:NLO} where the comparison is extended to the
@@
 discussed in Sec.~\ref{sec:matching}. Finally,
-Sec.~\ref{sec:conclusion} contains concluding remarks and recommendations for experimental collaborations.
+Sec.~\ref{sec:conclusion} contains a summary of the article and concluding remarks.
 

### 2018-02-21 Draft/definition.tex
minor changes on definition.tex

@@
         \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
-        In addition to typical VBS contribution (left), this order also possesses $s$-channel contributions such as decay chain (middle) and tri-boson contributions (right).}
+        In addition to typical VBS contributions (left), this order also possesses $s$-channel contributions such as decay chain (middle) and tri-boson contributions (right).}
 \label{diag:LO}
@@
 The first, commonly referred to as EW contribution or VBS~\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
-of vector bosons}, receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
+of vector bosons.}, receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
 in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
@@
 The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
-radiated off the quark lines. Because of the different colour structure, this contribution features
-different kinematical behaviours than VBS. Nonetheless they share the same final state and therefore constitute an irreducible background.
+radiated off the quark lines. Because of the different colour structure, this contribution features a 
+different kinematical behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.
 
-Finally, the third contribution is the interference of the two type of amplitudes described above.
+Finally, the third contribution is the interference of the two types of amplitudes described above.
 It is non-zero only for those partonic subprocesses which involve only one quark family.

### 2018-02-21 Draft/input.tex
some definitions added in input.tex

@@
-The partonic processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-The NNPDF~3.0 parton density~\cite{Ball:2014uwa} with five flavour scheme, NLO QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ is employed.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
-Since the employed PDF set has no photonic density, photon-induced processes are not considered.
-Initial-state collinear singularities are factorised with the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
+The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
+The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five flavour scheme, NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
+Since this PDF set has no photonic density, photon-induced processes are not considered.
+\BJ{I would change that sentence to simply {\em Photon-induced processes are not considered.}, as there are more reasons for disregarding the photon-induced contributions.
+}
+Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
+\BJ{Should we say something about singularities due to soft photon exchange in the $t$-channel that are removed in VBFNLO and POWHEG by a technical cutoff?}
 
-For the mass and width of the massive particles, the following values are used:
+For the massive particles, the following masses and decay widths are used:
 %
@@
 %
-The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
+The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj}, where
 %
@@
 \label{eq:defscale}
- \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}.
+ \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}, 
 \end{equation}
 %
+\BJ{defined via the transverse momenta of the two hardest identified jets. } 
 This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.
@@
 \begin{itemize}
-    \item The two same-sign charged leptons are required to have
+    \item The two same-sign charged leptons are required to \BJ{fulfill cuts on transverse momentum, rapidity, and separation in the rapidity-azimuthal angle separation, }
         \begin{align}
@@
         \end{align}
+        %
     \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
@@
         \end{align}
-    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
-        to have
+        %
+    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. %Jets are required to have
+    \BJ{We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons, } 
         \begin{align}
@@
         \end{align}
-        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated.
-        These are an in\-vari\-ant mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
-        The nominal values of these cuts if not stated explicitly read:
-        \begin{align}
+        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated. In particular, we impose a cut on the 
+         in\-vari\-ant mass of the di-jet system,  as well as on the rapidity-separation of the two jets,          \begin{align}
         \label{cut:4}
-         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
+         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5, 
         \end{align}
+        if not explicitly stated otherwise. 
+        %
     \item When EW corrections are computed, real photons and charged fermions are clustered together using the anti-$k_T$ algorithm with

### 2018-02-21 parton-shower/rivetplot.sh
Improve PS figures

@@ -1,8 +1,9 @@
 #! /bin/sh
 
+cp ../Setup/RivetAnalysis/MC_VBSCAN_MCComparison_NLO.plot ../Setup/RivetAnalysis/MC_VBSCAN_MCComparison.plot
 rivet-mkhtml -o rivet-NLOPS \
   VBFNLO/VBFNLO-NLO.yoda\
-:"Title=NLO"\
+:"Title=NLO (fixed order)"\
 :"LineColor={[rgb]{0.40,0.40,0.40}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\
@@ -63,9 +64,10 @@ rivet-mkhtml -o rivet-NLOPS \
 :"ErrorBandOpacity=0.3"\
 
 
+cp ../Setup/RivetAnalysis/MC_VBSCAN_MCComparison_LO.plot ../Setup/RivetAnalysis/MC_VBSCAN_MCComparison.plot
 rivet-mkhtml -o rivet-LOPS \
   VBFNLO/VBFNLO-NLO.yoda\
-:"Title=NLO"\
+:"Title=NLO (fixed order)"\
 :"LineColor={[rgb]{0.40,0.40,0.40}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\

### 2018-02-21 Draft/description.tex
some minor changes, some comments by BJ incorporated in input.tex

@@
 \begin{verbatim}
-> set complex_mass_scheme #1
-> import model loop_qcd_qed_sm_Gmu #2
-> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
-> output #4
+> set complex_mass_scheme
+> import model loop_qcd_qed_sm_Gmu
+> generate p p > e+ ve mu+ vm j j QCD=0 [QCD]
+> output
 \end{verbatim}
-  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
+  With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded,\footnote{Despite
             the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
-        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
-        and written to disk {\tt \#4}. No approximation is performed for the Born and real-emission matrix elements. 
+        with the current version of the code.} finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
+        and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
         For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
@@
         pole-cancelation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
-        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards/FKS\_params.dat} file to -1.
+        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards\-/FKS\_\-params.dat} file to -1.
         {\bf MZ what exactly needs to be clarified here? perhaps I am just too used to this that I do not see problems here}

### 2018-02-21 Draft/input.tex
some minor changes, some comments by BJ incorporated in input.tex

@@
 %
-\BJ{defined via the transverse momenta of the two hardest identified jets. } 
+defined via the transverse momenta of the two hardest identified jets.  
 This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.
@@
 \begin{itemize}
-    \item The two same-sign charged leptons are required to \BJ{fulfill cuts on transverse momentum, rapidity, and separation in the rapidity-azimuthal angle separation, }
+    \item The two same-sign charged leptons are required to fulfill cuts on transverse momentum, rapidity, and separation in the rapidity-azimuthal angle separation, 
         \begin{align}
@@
     \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. %Jets are required to have
-    \BJ{We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons, } 
+    We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons,  
         \begin{align}

### 2018-02-21 Draft/conclusion.tex
updated figures, added comments in the conclusion

@@
 In addition to fixed order predictions we have also investigated the impact of parton-shower.
-To that end, several fixed-order computations matched to parton shower have been used.
-It turns out that very large differences can appear for certain observables.
-These differences appear in the central region where for VBS, colour-recombination plays a significant role.
+To that end, several generators which include matching to parton shower have been employed, and various observables have been thoroughly compared.
+While in general observables which are described at NLO accuracy show reasonable agreement among the tools, larger differences can 
+appear for those observables described at a lower accuracy, such as those that involve the third jet.
+These differences appear in the central region where for VBS, colour-recombination plays a significant role \ZM{it is not color recombination, it 
+is the recoil scheme of the shower}.
 These findings are new and should trigger further investigations in the theoretical community as well as by experimental collaborations.
-Indeed, measurements of such observables should allow for a better understanding of colour-recombination in parton shower.
+Indeed, measurements of related observables for similar processes should allow for a better understanding of these  issues.
 \MP{It might be too strong a statement. At least Simon will rephrase it.}
@@
 The missing higher-order mixed QCD-EW corrections can be estimate by taking the difference between the multiplicative and additive prescription.
-A detailed study of the combination of higher-order corrections has been carried out in the context of SM background for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.
+A detailed study of the combination of higher-order corrections has been carried out e.g. in the context of top-pair production~\cite{Czakon:2017wor} or SM 
+background for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.
 
-We have shown how good the VBS approximation is performing in both inclusive and exclusive set-ups at both LO and NLO-QCD accuracy.
-It turns out that for typical fiducial region used by experimental collaborations for their measurements, the agreement between the approximations and full calculation is certainly satisfactory given the current experimental precision.
+For the typical fiducial region used by experimental collaborations for their measurements, the agreement between the approximations and full calculation is certainly satisfactory given the current {\bf MZ and future?} experimental precision.
 Nonetheless, in the future when experimental measurements will improve, care has to be taken when using such approximations, in particular, if more inclusive phase-space are used.
 
-Concerning the fixed-order predictions supplemented with parton shower, we have shown that for observables defined at LO, the differences are reasonable.
+{\bf MZ there are many repetitions here}
+Concerning predictions that include parton shower, we have shown that for observables defined at NLO, the differences are reasonable.
 On the other hand, for observables only defined at NLO-QCD, such as the ones related to the third hardest jet, large differences can arise between different parton-shower algorithms.
@@
 Therefore, we encourage experimental collaborations to move to NLO accuracy supplemented with parton shower as much as possible.
-In particular, we are willing to support this effort. \MP{Are we?}
+In particular, we are willing to support this effort. \MP{Are we? - MZ: remove this sentence}
 
@@
 Uncertainties related to PDF has been hardly addressed in the present article.
+{\bf MZ I would remove this and the following sentence: we computed PDF uncertainties,
+    it is true that we did not comment much on it, but I think sayng 'Hardly addressed' is too much. I would anyway cite CS's proceedings when we
+show the PDF uncertainties in the shower section}
 It has only be discussed briefly in Sec.~\ref{sec:matching} where scale variation in combination with PDF variation has been shown.

### 2018-02-22 Draft/input.tex
Small comment on b-quark initiated processes

@@
 Since this PDF set has no photonic density, photon-induced processes are not considered.
-\BJ{I would change that sentence to simply {\em Photon-induced processes are not considered.}, as there are more reasons for disregarding the photon-induced contributions.
-}
+\BJ{I would change that sentence to simply {\em Photon-induced processes are not considered.}, as there are more reasons for disregarding the photon-induced contributions. } 
 Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
 \BJ{Should we say something about singularities due to soft photon exchange in the $t$-channel that are removed in VBFNLO and POWHEG by a technical cutoff?}
+Note that no bottom-quark induced processes are included.
+They would lead to top quarks in the final state which have a different experimental signature than two light jets, missing transverse energy, and two positively charged leptons.
 
@@
         %
-    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. %Jets are required to have
+    \item QCD partons (light quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. %Jets are required to have
     We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons,  

### 2018-02-22 Draft/article.tex
Add ackn. for CS, change BONSAY description
- shame on you Marco for modifying my description ;-)
some fixes
Correct the title
Adding DESY preprint number.
Add Dieter Zeppenfeld as author
Add Karlsruhe preprint number
Tentative of uniformisation of all affiliations

@@
 % {subcaption}
-\hyphenation{quan-ti-ta-tive-ly}
+\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons}
 
@@
 %
-\journalname{ZU-TH-08/18} % Preprint numbers here
+\journalname{DESY 18-025, FR-PHENO-2018-003, KA-TP-05-2018, ZU-TH-08/18} % Preprint numbers here
 %
@@
 
-\title{Precise predictions for same-sign W-bosons scattering at the LHC}
+\title{Precise predictions for same-sign W-boson scattering at the LHC}
 
@@
 Marco Zaro\thanksref{nikh}
+\and
+Dieter Zeppenfeld\thanksref{kit}
 }
@@
 Via P. Giuria 1, %
-10125 Torino, %
+10125 Turin, %
 Italy\label{infnto}
@@
 \and
-Milan, Italy\label{mila}
+University and INFN, Milano-Bicocca, %
+piazza della Scienza, 3, 2016 Milan, %
+Italy\label{mila}
 \and
@@
 IBM Italia s.p.a. %
-Circonvallazione Idroscalo , %
+Circonvallazione Idroscalo, %
 20090 Segrate (MI), %
@@
 \and
+University of T\"ubingen,
 Institute for Theoretical Physics,
-University of T\"ubingen,
 Auf der Morgenstelle 14,
@@
 \and
+Universit\"at Z\"urich,
 Physik-Institut,
-Universit\"at Z\"urich,
 Winterthurerstrasse 190,
-CH-8057 Z\"urich,
+8057 Z\"urich,
 Switzerland\label{uzh}
 \and
-Universit\`a di Torino, Dipartimento di Fisica, %
+Universit\`a di Torino, %
+Dipartimento di Fisica, %
 Via P. Giuria 1, %
-10125 Torino, %
+10125 Turin, %
 Italy\label{unito}
 \and
-Particle Physics, Faculty of Physics, University of Vienna, %
+University of Vienna,
+Particle Physics, Faculty of Physics, %
 Vienna, %
@@
 \and
-Institute for Theoretical Physics, Karlsruhe Institute of
-Technology (KIT), %
+Karlsruhe Institute of Technology (KIT), %
+Institute for Theoretical Physics, %
 76131 Karlsruhe,
@@
 Theoretical Physics Department,
-CH-1211, Geneva 23,
+1211, Geneva 23,
 Switzerland\label{cern}

### 2018-02-23 Draft/input.tex
removed some notes by BJ in the input section (discussed in the email thread), added HSS and RF as authors

@@
 The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five flavour scheme, NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
-Since this PDF set has no photonic density, photon-induced processes are not considered.
-\BJ{I would change that sentence to simply {\em Photon-induced processes are not considered.}, as there are more reasons for disregarding the photon-induced contributions. } 
+The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{
+For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.} 
+NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
+%Since this PDF set has no photonic density, photon-induced processes are not considered.
 Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
-\BJ{Should we say something about singularities due to soft photon exchange in the $t$-channel that are removed in VBFNLO and POWHEG by a technical cutoff?}
-Note that no bottom-quark induced processes are included.
-They would lead to top quarks in the final state which have a different experimental signature than two light jets, missing transverse energy, and two positively charged leptons.
 

### 2018-02-23 Draft/description.tex
Some small corrections

@@
 \end{verbatim}
-  With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded,\footnote{Despite
+  With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded\footnote{Despite
             the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
-        with the current version of the code.} finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
+        with the current version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
         and written to disk. No approximation is performed for the Born and real-emission matrix elements. 

### 2018-02-23 Draft/process.tex
some fixes
Some small corrections

@@
 the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 
-full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a subpart.
+full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
 However, this set of contributions is not gauge invariant.
@@
 in considering all $t$- and $u$-channel diagrams and squaring them separately, neglecting interference contributions between the two classes.
-These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
+These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc,Denner:2012dz}.
 The $s$-channel squared diagrams and any interferences between them and the  $t/u$-channels are also discarded.
@@
 
-The approximations performed at LO can be extended when NLO QCD corrections to the $\mathcal{O}{\left(\alpha^{6}\right)}$ are computed.
-The VBS approximation can be extended at NLO in a straightforward manner for what concerns the virtual contributions; 
-for the real-emission contributions special care must be taken for the gluon-initiated processes\footnote{The initial-state gluon and quark 
+The approximations performed at LO can be extended when NLO QCD corrections to the order $\mathcal{O}{\left(\alpha^{6}\right)}$ are computed.
+The VBS approximation can be extended at NLO in a straightforward manner for what concerns the virtual contributions.
+For the real-emission contributions special care must be taken for the gluon-initiated processes\footnote{The initial-state gluon and quark 
     must not couple together, otherwise infrared divergences proportional to $s$-channels will appear, 
@@
 A further refinement is to consider the full real contributions, which include all interferences, and part of the virtual.
-In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and 
+In particular one can consider only one-loop amplitudes where there is no gluon exchange between the two quark lines and 
 assuming a cancellation of the infrared (IR) poles.
@@
 But all IR singularities related to photon emissions are not cancelled by the above mentioned virtual corrections.
-Another type of virtual corrections have to incorporated, namely the one-loop amplitudes of order $\mathcal{O}(g^8)$ interfered with the tree-level ones of order $\mathcal{O}(g_{\rm s}^2 g^4)$.
+Another type of virtual corrections has to be incorporated, namely the one-loop amplitude of order $\mathcal{O}(g^8)$ interfered with the tree-level one of order $\mathcal{O}(g_{\rm s}^2 g^4)$.
 Hence the full NLO corrections of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consist not only of QCD-type corrections but also of EW ones \cite{Biedermann:2017bss}.
-\MP{@MZ g. gs are for amplitude and alpha, alphas for matrix element squared.}
 %Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

### 2018-02-24 Results/comparison_plots/myreplace.py
Gnuplot-plots: 	Remove "MonteCarlo comparison" and "fixed order" from subcaption

@@ -13,8 +13,10 @@ content = open(infile).read()
 #                          'set terminal pdf font "Helvetica,12" enhanced dashed size 8 cm, 12 cm')
 #content = content.replace('set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",14" at graph 0.1, graph 0.9', \
 #                          'set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",12" at graph 0.03, graph 0.9')
-content = content.replace('set label "MonteCarlo comparison, NLO fixed order" font ",12" at graph 0.1, graph 0.88', \
-                          'set label "MonteCarlo comparison, NLO fixed order" font ",10" at graph 0.03, graph 0.88')
+#content = content.replace('set label "MonteCarlo comparison, NLO fixed order" font ",12" at graph 0.1, graph 0.88', \
+#                          'set label "MonteCarlo comparison, NLO fixed order" font ",10" at graph 0.03, graph 0.88')
+content = content.replace('set label "MonteCarlo comparison, NLO fixed order" font ",10" at graph 0.03, graph 0.88', \
+                          'set label "NLO" font ",10" at graph 0.03, graph 0.88')
 #content = content.replace('set key at graph 1, graph 0.9 noautotitles spacing 2.4', \
 #                          'set key at graph 1, graph 0.8 noautotitles spacing 2.4')
 #content = content.replace('set ylabel \'Ratio /VBFNLO\'', \

### 2018-02-24 Results/comparison_plots/myreplace.py
Gnuplot-plots:         Remove "MonteCarlo comparison" and "fixed order" from subcaption 	... also for the LO plots

@@ -15,8 +15,8 @@ content = open(infile).read()
 #                          'set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",12" at graph 0.03, graph 0.9')
 #content = content.replace('set label "MonteCarlo comparison, NLO fixed order" font ",12" at graph 0.1, graph 0.88', \
 #                          'set label "MonteCarlo comparison, NLO fixed order" font ",10" at graph 0.03, graph 0.88')
-content = content.replace('set label "MonteCarlo comparison, NLO fixed order" font ",10" at graph 0.03, graph 0.88', \
-                          'set label "NLO" font ",10" at graph 0.03, graph 0.88')
+content = content.replace('set label "MonteCarlo comparison, LO fixed order" font ",10" at graph 0.03, graph 0.88', \
+                          'set label "LO" font ",10" at graph 0.03, graph 0.88')
 #content = content.replace('set key at graph 1, graph 0.9 noautotitles spacing 2.4', \
 #                          'set key at graph 1, graph 0.8 noautotitles spacing 2.4')
 #content = content.replace('set ylabel \'Ratio /VBFNLO\'', \

### 2018-02-26 Draft/conclusion.tex
minor typos fixed and small comments added in file conclusion.tex

@@
 In Ref.~\cite{Biedermann:2016yds}, it has been demonstrated that these large EW corrections originate from the Sudakov logarithms which factorise.
-Therefore we recommend to combined them in a multiplicative way.
+Therefore we recommend to combine them in a multiplicative way.
 Concerning the estimation of missing higher-order corrections of EW type they can be obtained, in a first approximation, from $\pm \delta^2_{\rm NLO EW}$.
-The missing higher-order mixed QCD-EW corrections can be estimate by taking the difference between the multiplicative and additive prescription.
-A detailed study of the combination of higher-order corrections has been carried out e.g. in the context of top-pair production~\cite{Czakon:2017wor} or SM 
-background for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.
+The missing higher-order mixed QCD-EW corrections can be estimated by taking the difference between the multiplicative and additive prescription.
+A detailed study of the combination of higher-order corrections has been carried out, e.g., in the context of top-pair production~\cite{Czakon:2017wor} or SM 
+backgrounds for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.
 
@@
 
-{\bf MZ there are many repetitions here}
+{\bf MZ there are many repetitions here} \BJ{I would suggest to remove the following paragraph as it repeats what was already said before.}
 Concerning predictions that include parton shower, we have shown that for observables defined at NLO, the differences are reasonable.
@@
 As demonstrated above, numerous programs exist to simulate the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC.
-So far there is no public code that perform the full NLO computation matched with parton shower.
+So far there is no public code that performs the full NLO computation matched with parton shower.
 Nonetheless, full computations at NLO and publicly available tools at NLO-QCD accuracy in the VBS approximation matched to parton shower are available.
@@
 The present study has focused on the orders $\mathcal{O}{\left(\alpha^{6}\right)}$ at LO and $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ at NLO.
-Nonetheless NLO computations and publicly available tools also exist for the QCD-induced process \cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss}.
+Nonetheless, NLO computations and publicly available tools also exist for the QCD-induced process \cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss}.
 They should therefore be also used as much as possible.
 
-Uncertainties related to PDF has been hardly addressed in the present article.
+Uncertainties related to PDFs have been hardly addressed in the present article.
 {\bf MZ I would remove this and the following sentence: we computed PDF uncertainties,
@@
 show the PDF uncertainties in the shower section}
-It has only be discussed briefly in Sec.~\ref{sec:matching} where scale variation in combination with PDF variation has been shown.
+These have only been discussed briefly in Sec.~\ref{sec:matching} where scale variations in combination with PDF variations have been shown.
 Some of us have already presented preliminary results on this subject \cite{Schwan:2017yy}. % Radcor proceedings from Christopher.
@@
 Finally, the study presented here concentrates on the ${\rm W}^+{\rm W}^+$ signature.
-The features observed here (validity of the VBS approximation or comparison of theoretical predictions matched to parton shower for example) should be qualitatively similar for other VBS signatures with massive gauge bosons.
+The features observed here (validity of the VBS approximation or comparison of theoretical predictions matched to parton shower, for example) should be qualitatively similar for other VBS signatures with massive gauge bosons.
+\BJ{I am not sure this statement is generally true.
+For other VBS channels, backgrounds are much more troublesome.
+If we want to make a statement like ``qualitatively similar for other VBS signatures'' we need to say more explicitly in which respect, for instance concerning the validity of the VBS approximation.}
 But the quantitative conclusions are strictly restricted to ${\rm W}^+{\rm W}^+$ signature.
-For other signatures, similar quantitative study should be performed.
+For other signatures, similar quantitative studies should be performed.
 Beyond the theoretical findings of this work, we also hope that it can serve as a guideline for experimental collaborations in their quest for the measurements of VBS processes at the LHC.

### 2018-02-26 Draft/crosssectionNLO.tex
Updated NLO numbers from powheg

@@
         {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ \\
-        {\sc Powheg-Box}  &  $1.362\phantom{0}\phantom{0}$  & $0.003$   \\
+        {\sc Powheg-Box}  &  $1.362\phantom{0}\phantom{0}$  & $0.001$   \\
         {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\

### 2018-02-26 Draft/conclusion.tex
fixed the comments in sections 1-3 and 6-7

--- 2018-02-21 Draft/conclusion.tex
@@
-In the present article, a detailed study of the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC has been presented.
-The main focus is the electroweak (EW) production of such a final state where vector-boson scattering (VBS) occurs.
-So far, all NLO computations have been performed in the so-called VBS approximation.
-Only recently a full computation became available \cite{Biedermann:2017bss}.
-Various theoretical predictions have been compared to the full computation.
-This has not only been performed in a typical VBS fiducial region but also in more inclusive volumes.
-We quantify precisely the differences that arise for several physical observables and in particular for the di-jet invariant mass and the rapidity-separation of the leading two jets.
-This is the first time that such an in-depth study is performed and should be representative of the quality of the approximations for other VBS signatures.
-In addition to fixed order predictions we have also investigated the impact of parton-shower.
-To that end, several fixed-order computations matched to parton shower have been used.
-It turns out that very large differences can appear for certain observables.
-These differences appear in the central region where for VBS, colour-recombination plays a significant role.
-These findings are new and should trigger further investigations in the theoretical community as well as by experimental collaborations.
-Indeed, measurements of such observables should allow for a better understanding of colour-recombination in parton shower.
-\MP{It might be too strong a statement. At least Simon will rephrase it.}
+In the present article, a detailed study of the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC has been presented, 
+mainly focused on the electroweak production mechanism which involves the scattering fo massive vector bosons.
+Until very recently, when the complete calculation became available for the NLO QCD corrections ($\mathcal O (\alphas\alpha^6)$),
+the so-called VBS approximation was the standard for this kind of simulations. For this reason, various theoretical predictions 
+have been compared to the full computation, both in a typical VBS fiducial region and also in more inclusive phase-space.
+We have precisely quantified the differences that arise for several physical observables, 
+in particular for the di-jet invariant mass and the rapidity-separation of the leading two jets.
+This is the first time that such an in-depth study is performed.
+%%%%and should be representative of the quality of the approximations for other VBS signatures.
+Besides the study of fixed-order predictions, we have also investigated the impact of parton-shower.
+To that end, several LO and NLO event generators 
+which give the possibility to perform matching to parton showers have been employed, and various observables have been thoroughly compared.
+While in general observables which are described at NLO accuracy show reasonable agreement among the tools, larger differences can 
+appear for those observables described at a lower accuracy, such as those that involve the third jet.
+These differences appear in the central region where for VBS, and are the largest for those simulations which employ {\sc Pythia8}. The effect
+has been understood, and it can be somehow mitigated by changed the recoil scheme of the parton shower. These findings makes it worth 
+to further investigate these issues not only in the theoretical community, but also by experimental collaborations, for example by 
+measuring related observables for similar processes.
 
-The results presented here are exclusively theoretical.
-Nonetheless, they should raise significant interests in the experimental collaborations.
-Therefore, to supplement this summary, we provide several concluding remarks concerning the use of theoretical predictions.
+%The results presented here are exclusively theoretical.
+%Nonetheless, they should raise significant interests in the experimental collaborations.
+The last part of our work is devoted to 
+ remarks and recommendations concerning the usage of theoretical predictions by experimental collaborators.
+\begin{itemize}
+    \item As found in Ref.~\cite{Biedermann:2017bss}, the NLO EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ are 
+        the dominant NLO contribution to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
+        It is thus highly desirable that they are combined with NLO-QCD predictions matched with parton shower, or at least that they accounted for
+        by experimental analyses. Since, as shown in~\cite{Biedermann:2017bss}, 
+        these large EW corrections originate from the Sudakov logarithms which factorise, we recommend to combine them with QCD 
+        corrections in a multiplicative way. The estimate of missing higher-order EW corrections can be done, 
+        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$, while the missing higher-order mixed QCD-EW corrections 
+        can be estimated by taking the difference between the multiplicative and additive prescription.
+        For more detailed studies of the combination of QCD and EW higher-order corrections, see
+        e.g., Ref.~\cite{Czakon:2017wor} in the context of top-pair production, or Ref.~\cite{Lindert:2017olm} for SM 
+        backgrounds for dark matter searches at the LHC.
+    \item For the typical fiducial region used by experimental collaborations for their measurements, 
+        the agreement between the approximations and the full calculation is certainly satisfactory given 
+        the current experimental precision, as well as the one foreseen for the near future \ZM{references, etc}.
+        Nonetheless, care has to be taken when using such approximations, in particular if more inclusive phase-space cuts are used.
 
-As found in Ref.~\cite{Biedermann:2017bss}, the NLO EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ are the dominant NLO contributions to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
-It is thus highly desirable that they are combined with NLO-QCD predictions matched with parton shower.
-In Ref.~\cite{Biedermann:2016yds}, it has been demonstrated that these large EW corrections originate from the Sudakov logarithms which factorise.
-Therefore we recommend to combined them in a multiplicative way.
-Concerning the estimation of missing higher-order corrections of EW type they can be obtained, in a first approximation, from $\pm \delta^2_{\rm NLO EW}$.
-The missing higher-order mixed QCD-EW corrections can be estimate by taking the difference between the multiplicative and additive prescription.
-A detailed study of the combination of higher-order corrections has been carried out in the context of SM background for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.
+%{\bf MZ there are many repetitions here} \BJ{I would suggest to remove the following paragraph as it repeats what was already said before.}
+%Concerning predictions that include parton shower, we have shown that for observables defined at NLO, the differences are reasonable.
+%On the other hand, for observables only defined at NLO-QCD, such as the ones related to the third hardest jet, large differences can arise between different parton-shower algorithms.
+%Therefore, jet-veto procedures or selections based on extra radiation should be avoided as they carry rather large uncertainties.
 
-We have shown how good the VBS approximation is performing in both inclusive and exclusive set-ups at both LO and NLO-QCD accuracy.
-It turns out that for typical fiducial region used by experimental collaborations for their measurements, the agreement between the approximations and full calculation is certainly satisfactory given the current experimental precision.
-Nonetheless, in the future when experimental measurements will improve, care has to be taken when using such approximations, in particular, if more inclusive phase-space are used.
-
-Concerning the fixed-order predictions supplemented with parton shower, we have shown that for observables defined at LO, the differences are reasonable.
-On the other hand, for observables only defined at NLO-QCD, such as the ones related to the third hardest jet, large differences can arise between different parton-shower algorithms.
-Therefore, jet-veto procedures or selections based on extra radiation should be avoided as they carry rather large uncertainties.
-
-In addition to the standard interpretation of EW signal versus QCD background, combined measurements should also be presented as they are well defined theoretically.
-At LO, the interferences can be included in the background component.
-Nonetheless, at NLO the concept of EW and QCD component become meaningless as at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes mix.
+    \item In addition to the standard interpretation of EW signal versus QCD background, 
+        combined measurements should also be presented as they are better defined theoretically. In fact, while at at LO 
+        the interference term can be included in the background component, at NLO the separation of EW and QCD component become more blurred, as, e.g.,
+        as at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes mix.
         Therefore, a combined measurement including the EW, QCD, and interference contributions is desirable.
+        \ZM{the following has to be clarified. one way would be to suggest to use  phase-space  cuts to enhance/suppress configurations 
+            where EW/QCD are the dominant contributions}
 Note that with such a measurement, an interpretation in terms of EW component is still possible.
@@
 
-As demonstrated above, numerous programs exist to simulate the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC.
-So far there is no public code that perform the full NLO computation matched with parton shower.
-Nonetheless, full computations at NLO and publicly available tools at NLO-QCD accuracy in the VBS approximation matched to parton shower are available.
-Therefore, we encourage experimental collaborations to move to NLO accuracy supplemented with parton shower as much as possible.
-In particular, we are willing to support this effort. \MP{Are we?}
+    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguites related to the 
+        matching details and/or the parton-shower employed, we encourage the use of NLO-accurate event generators in experimental analyses.
 
-The present study has focused on the orders $\mathcal{O}{\left(\alpha^{6}\right)}$ at LO and $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ at NLO.
-Nonetheless NLO computations and publicly available tools also exist for the QCD-induced process \cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss}.
-They should therefore be also used as much as possible.
+    \item The present study has focused on the orders $\mathcal{O}{\left(\alpha^{6}\right)}$ at 
+    LO and $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ at NLO.
+NLO computations and publicly-available tools also exist for the QCD-induced process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss,Alwall:2014hca}.
 
-Uncertainties related to PDF has been hardly addressed in the present article.
-It has only be discussed briefly in Sec.~\ref{sec:matching} where scale variation in combination with PDF variation has been shown.
-Some of us have already presented preliminary results on this subject \cite{Schwan:2017yy}. % Radcor proceedings from Christopher.
-Forthcoming publications will thus address related questions.
-
-Finally, the study presented here concentrates on the ${\rm W}^+{\rm W}^+$ signature.
-The features observed here (validity of the VBS approximation or comparison of theoretical predictions matched to parton shower for example) should be qualitatively similar for other VBS signatures with massive gauge bosons.
-But the quantitative conclusions are strictly restricted to ${\rm W}^+{\rm W}^+$ signature.
-For other signatures, similar quantitative study should be performed.
-Beyond the theoretical findings of this work, we also hope that it can serve as a guideline for experimental collaborations in their quest for the measurements of VBS processes at the LHC.
+    \item For practical reasons, we have focused on the ${\rm W}^+{\rm W}^+$ signature. Nonetheless, 
+    the observed features 
+    (e.g. validity of the VBS approximation or comparison of theoretical predictions matched to parton shower) should 
+    be qualitatively similar for other VBS signatures with massive gauge bosons. For these other signatures, similar quantitative studies should be performed.
+\end{itemize}

### 2018-02-26 Draft/description.tex
fixed the comments in sections 1-3 and 6-7

@@
         {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards\-/FKS\_\-params.dat} file to -1.
-        {\bf MZ what exactly needs to be clarified here? perhaps I am just too used to this that I do not see problems here}
 
@@
 For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
-{\bf MZ : I would move these sentences in the setup part, possibly as footnotes}
-The {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.
-The renormalisation and factorisation scale used differ slightly from the one defined in Eq.~\eqref{eq:defscale}, as rather than constructing the jets the {\sc Powheg-Box} uses the transverse momentum of the two final-state quarks in the underlying Born event.
 
@@
   \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
-      event generator with the LO matrix element generator {\sc O'Mega}.
-{\bf MZ: if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
+      event generator with the LO matrix element generator {\sc O'Mega}. \ZM{ if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
 provides FKS subtraction terms for any NLO process, while virtual matrix

### 2018-02-26 Draft/input.tex
fixed the comments in sections 1-3 and 6-7

@@
 For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.} 
-NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
+NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
 %Since this PDF set has no photonic density, photon-induced processes are not considered.
@@
 \begin{equation}
- \alpha = 7.555310522369 \times 10^{-3}.
+ 1/\alpha = 132.3572\ldots\,.
 \end{equation}
@@
 %
-defined via the transverse momenta of the two hardest identified jets.  
+defined via the transverse momenta of the two hardest identified jets.\footnote{
+    The renormalisation and factorisation scale employed in the {\sc Powheg-Box} slightly differ from the 
+    one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are i
+    employed instead of those of the two hardest jets.} 
 This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

### 2018-02-26 Draft/shower.tex
fixed the comments in sections 1-3 and 6-7

@@
 take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
-theoretical uncertainties: for the former, we show both PDF and scale uncertainties, obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
+theoretical uncertainties: for the former, we show both PDF and scale uncertainties (a preliminar study on PDF uncertainties in VBS has appeared 
+in Ref.~\cite{Schwan:2017yy}), obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
 scale by a factor of two around its central value, Eq.~(\ref{eq:defscale}) (nine-point variations); for the latter, we show the 
@@
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
-    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. \MP{The plots themselves should probably have the label LO and NLO for these predictions}}
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. }
 \label{fig:PSnjet}
@@
 effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of the {\sc Powheg-Box} to suppress the
-hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).\AK{This effect seems to be cured by the dipole shower.}\\
+hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).\\
 If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
@@
 peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
-at most $10\%$ \AK{This effect again seems to be evened out by the dipole shower}.
+at most $10\%$.\footnote{If the setting {\tt SpaceShower:dipole\-Recoil = on} (discussed in the following of the article) 
+is used when {\sc Pythia8}\ is employed together with the {\sc Powheg-Box}, the enhancement at central rapidities and the depletion 
+at small value of transverse momentum are partially compensated.}
 
@@
 Note that such a setting is not compatible with the NLO matching
-in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching).
-Also, this setting has other effects, though smaller, on the rapidity spectra of the two hardest jets.} it is interesting to notice that
-it survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+ Pythia8}. A similar
+in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching). Also, this setting has other 
+effects, though smaller, on the rapidity spectra of the two hardest jets.} it is interesting to notice that
+the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+ Pythia8}. A similar
 behaviour of {\sc Pythia8}
@@
 experimental analyses should rely as little as possible on those observables and, in any case, use conservative estimate of the theory 
-uncertainties.\AK{Are there any current analyses with a central jet veto in VBS? The experimentalists might take this statement a little too literal.} On the one hand, in order to improve the
+uncertainties. On the one hand, in order to improve the
 description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern 
@@
 color flow (EW production of a single vector boson plus jets,
- VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data. \AK{Include some references here?}
+VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data~\cite{Aaboud:2017emo,Sirunyan:2017jej}.
 

### 2018-02-26 Draft/distributionsLO.tex
fixed the comments in sections 4 and 5 and add some discussions in the comparison

@@
-In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (top) and the rapidity difference of the two tagging jets (bottom) which are key observables for VBS measurements.
-In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over {\sc VBFNLO} \MP{To be changed to Recola}.
+In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
+In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}.
 For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.
@@
 This means that at LO, in the fiducial volume and for energies relevant to the LHC, the VBS approximation is good to a per cent.
-This is in agreement with the findings of section \ref{subsec:LOinclusive} as the present comparison completely excludes the region where tri-boson contributions could have a noticeable impact.
+This is in agreement with the findings of Sec.~\ref{subsec:LOinclusive} as the present comparison completely excludes the phase-space region where tri-boson contributions could have a noticeable impact.
 
@@
 The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
-The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
-\MP{MG statistics should be improved and the baseline changed to Recola.}
-}
+The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \end{figure*}

### 2018-02-26 Draft/distributionsNLO.tex
fixed the comments in sections 4 and 5 and add some discussions in the comparison

@@
 In Figs.~(\ref{fig:distNLO1}-\ref{fig:distNLO3}), several differential distributions are shown.
-All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
-\MP{Physics and conclusion on interference/non-factorisable etc.\ effects are not addresses yet in the discussion.}
+All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alphas\alpha^6)$.
 
@@
 On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
-The VBS-approximated predictions ({\sc Bonsay} and the {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
+The VBS-approximated predictions ({\sc Bonsay} and {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
 The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
@@
 For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.
+Therefore, depending on the approximation used, it can vary by $\pm7\%$ and $\pm4\%$ with respect to the full computation at low invariant mass and low rapidity difference for the tagging jets, respectively
 
@@
 The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
-\MP{MG statistics should be improved and the baseline changed to Recola.}
 }
@@
 Concerning the transverse momentum (left) and rapidity (right) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
-While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
-This is in contrast with {\sc Bonsay} and {\sc Powheg} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
-Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.
+While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum by about $10\%$.
+This difference can be attributed to EW Sudakov logarithms that become large in this phase-space region.
+This is in contrast with the VBS-approximated predictions such as {\sc Bonsay}, {\sc Powheg}, and {\sc VBFNLO} which are lower than the full computation at low transverse momentum and higher for larger transverse momentum.
+While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different different at low transverse momentum where it is even higher than the full computation.
+% Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.
 Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
@@
 Indeed, the hierarchy mentioned previously is here respected and enhanced towards high invariant mass or high Zeppenfeld variable.
-{\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
+The predictions of {\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
 The other three VBS approximations are close to each other within few per cent.
@@
 The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
-\MP{MG statistics should be improved and the baseline changed to Recola.}
 }
 \end{figure*}
+
+In the end, the quality of the VBS-approximations amount to tenths of per cent depending on the observables and phase-space range.
+These differences are larger than at what is observed at LO.
+
+The contributions from $s$-channel amplitude can be sizeable especially at low invariant mass for the two tagging jet (comparing the predictions of {\sc VBFNLO} against the ones of {\sc Bonsay} and {\sc Powheg}).
+This can be explained by the fact that $s$-channel contributions are less suppressed at NLO.
+In the real, an extra gluon-jet can be radiated from any of the charged particles while the two quarks originating from the W-boson decay can be recombined in a single jet.
+Therefore, the jet requirements ($ m_{\Pj \Pj} >  500\GeV$ and $|\Delta y_{\Pj \Pj}| > 2.5$) that were suppressing $s$-channel contributions at LO are partially lifted with the inclusion of a third jet at NLO.
+Such an effect has also been observed for top--antitop production in the lepton+jet channel at NLO QCD \cite{Denner:2017kzu}.
+
+At the $s$-channel contributions are sizeable, their interferences with the $t$/$u$-channel can be of similar size in the phase-space region where the former are large.
+This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MadGraph5\_aMC\-@NLO}.
+
+Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
+But they can be particularly large (about $10\%$) for large transverse momentum of the hardest jet.
+These high-energy region of the phase space are where EW Sudakov logarithms become large.
+Nonetheless these regions are rather suppressed and thus these effects are hardly visible at the level of the cross section.

### 2018-02-26 Results/comparison_plots/myreplace.py
Gnuplot-plots: Remove general label

@@ -11,12 +11,12 @@ content = open(infile).read()
 
 #content = content.replace('set terminal pdf font "Helvetica,14" enhanced dashed size 12 cm, 18 cm', \
 #                          'set terminal pdf font "Helvetica,12" enhanced dashed size 8 cm, 12 cm')
-#content = content.replace('set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",14" at graph 0.1, graph 0.9', \
-#                          'set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",12" at graph 0.03, graph 0.9')
+#content = content.replace('set label "e^+mu^+{/Symbol nn}jj production at the LHC, 13 TeV" font ",12" at graph 0.03, graph 0.94', \
+#                          '')
 #content = content.replace('set label "MonteCarlo comparison, NLO fixed order" font ",12" at graph 0.1, graph 0.88', \
 #                          'set label "MonteCarlo comparison, NLO fixed order" font ",10" at graph 0.03, graph 0.88')
-content = content.replace('set label "MonteCarlo comparison, LO fixed order" font ",10" at graph 0.03, graph 0.88', \
-                          'set label "LO" font ",10" at graph 0.03, graph 0.88')
+content = content.replace('set label "NLO" font ",10" at graph 0.03, graph 0.88', \
+                          'set label "NLO" font ",10" at graph 0.03, graph 0.94')
 #content = content.replace('set key at graph 1, graph 0.9 noautotitles spacing 2.4', \
 #                          'set key at graph 1, graph 0.8 noautotitles spacing 2.4')
 #content = content.replace('set ylabel \'Ratio /VBFNLO\'', \

### 2018-02-27 Draft/scanNLO.tex

@@
 The inclusion of $s$-channels cures partly the discrepancy in this region.
-Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains \MP{To be checked the exact numerical value in data}.
+Still, for the very low $m_{\Pj\Pj}$ a difference of about $8\%$ remains \MP{To be checked the exact numerical value in data}.
 This might indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
@@
 In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.
-This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
+This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.{\bf GP: should think again about it, in the lights of the new high stat Recola results.
+The discrepancy is no more negative in the large pt region.}
 For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.
@@
 The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
-The prediction from {\sc Bonsay} is about $10\%$ lower.
-The discrepancies are roughly constant over the whole spectrum.
-Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$-channels, with increasing discrepancy with respect to the full result at large values.
+The prediction from {\sc Bonsay} is about $10\%$ lower for $m_{e^+\mu^+}<1200 \GeV$; this discrepancy reaches about $20\%$ in the very high mass region. 
+%The discrepancies are roughly constant over the whole spectrum.
+Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$-channels, with increasing negative discrepancy with respect to the full result at large values (up to $30\%$ for $z_{e^+}>1.2$).
+Including $s$-channels makes this discrepancy become positive, but smaller than $10\%$ over the whole spectrum.
 The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.

### 2018-02-28 Draft/crosssectionNLO.tex
Updated with final powheg statistics

@@
         {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ \\
-        {\sc Powheg-Box}  &  $1.362\phantom{0}\phantom{0}$  & $0.001$   \\
+        {\sc Powheg-Box}  &  $1.3605\phantom{0}\phantom{0}$  & $0.0007$   \\
         {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\

### 2018-02-28 Draft/description.tex
Small typos/additions

@@
 For the fiducial cross sections it uses the VBS approximation at LO and NLO.
-The virtuals are additionally approximated using a double pole approximation.
+The virtual corrections are additionally approximated using a double pole approximation.
 For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) are used.
@@
         Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
-        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweigthing
+        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweighting
         at zero additional CPU cost~\cite{Frederix:2011ss}.\\
@@
         those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
-        pole-cancelation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
+        pole-cancellation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
         {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards\-/FKS\_\-params.dat} file to -1.
@@
     approximation, with process IDs between 200 and 290. The corresponding
-    s-channel contributions are available separately as triboson processes with
+    s-channel contributions are available separately as tri-boson processes with
     semi-leptonic decays, with process IDs in the 400 range. These can simply
@@
 
-We conclude this section by summarizing the details of the various codes in Tab.~\ref{tab:wg1_codes}. In particular, it is specified whether
+We conclude this section by summarising the details of the various codes in Tab.~\ref{tab:wg1_codes}. In particular, it is specified whether
 \begin{itemize}

### 2018-02-28 Draft/introduction.tex
Small typos/additions

@@
 All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Denner:2012dz,Oleari:2003tc}.
-Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations at NLO QCD.
+Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, 
+making it possible for the first time to study in detail the quality of the VBS approximations at NLO QCD.\footnote{Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
+A similar study has also been made public very recently for the EW production of a Higgs boson in association with 3 jets \cite{Campanario:2018ppz}.}
 
@@
 Sec.~\ref{sec:conclusion} contains a summary of the article and concluding remarks.
-
-Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
 

### 2018-02-28 Results/VBFNLO/internal2flat.py
Update parton-shower plots
consistent naming of H7-Default in plots and text
use correct VBFNLO NLO data as basis

@@ -35,10 +35,10 @@ YLabel=
   fin = open(dataconversion[key],'r')
   for l in fin:
     entries = l.split()
-    fout.write("{0}   {1}   {2}   {3}   {3}\n".format(entries[0],entries[1],entries[2],entries[3]))
+    fout.write("{0}   {1}   {2}   {3}   {3}\n".format(entries[0],entries[1],entries[6],entries[7]))
     if key == "jetsinclusive" and float(entries[0]) == 1.5:
-      cs = float(entries[2])
-      cserr = float(entries[3])
+      cs = float(entries[6])
+      cserr = float(entries[7])
   fout.write("# END HISTO1D\n")
   fin.close()
 

### 2018-02-28 parton-shower/rivetplot.sh

@@ -46,6 +46,14 @@ rivet-mkhtml -o rivet-NLOPS \
 :"LineColor={[rgb]{0.85,0.37,0.01}}"\
 :"LineStyle=dashed"\
 :"ErrorBands=0"\
+  VBFNLO/Herwig-MCatNLO-DefaultShower.yoda\
+:"Title=VBFNLO 3+H7-Default"\
+:"LineColor={[rgb]{0.40,0.65,0.12}}"\
+:"LineStyle=solid"\
+:"ErrorBands=0"\
+:"ErrorBandColor={[rgb]{0.40,0.65,0.12}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.40,0.65,0.12}}"\
+:"ErrorBandOpacity=0.3"\
   VBFNLO/Herwig-MCatNLO-DipoleShower_scale.yoda\
 :"Title=VBFNLO 3+H7-Dipole"\
 :"LineColor={[rgb]{0.11,0.62,0.47}}"\
@@ -53,14 +61,6 @@ rivet-mkhtml -o rivet-NLOPS \
 :"ErrorBands=1"\
 :"ErrorBandColor={[rgb]{0.11,0.62,0.47}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.11,0.62,0.47}}"\
-:"ErrorBandOpacity=0.3"\
-  VBFNLO/Herwig-MCatNLO-DefaultShower.yoda\
-:"Title=VBFNLO 3+H7-QTilde"\
-:"LineColor={[rgb]{0.40,0.65,0.12}}"\
-:"LineStyle=solid"\
-:"ErrorBands=0"\
-:"ErrorBandColor={[rgb]{0.40,0.65,0.12}}"\
-:"RatioPlotErrorBandColor={[rgb]{0.40,0.65,0.12}}"\
 :"ErrorBandOpacity=0.3"\
 
 

### 2018-02-28 Draft/scanNLO.tex
scanNLO.tex: updated total inclusive cross-section for Recola
Updated exact number for NLO scan
Address comment and some formatting

@@
 \hline
-full &  $1.8120 \pm 0.0144$ & - \\
+full &  $1.733\phantom{0} \pm 0.002\phantom{0}$ & - \\
 \hline
-$|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-10$ \\
+$|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-6$ \\
 \hline
-$|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $-2$
+$|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $+2$
 \end{tabular}
@@
 
-The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) is lower by about $10\%$ with respect to the full calculation.
-The inclusion of $s$-channel diagrams improves the approximate prediction down to a $2\%$-level.
+The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) is lower by about $6\%$ with respect to the full calculation.
+The inclusion of $s$-channel diagrams improves the approximate prediction down to a slight excess at the $2\%$-level.
 

### 2018-02-28 Draft/shower.tex
Address comment and some formatting

@@
 the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
-can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} and the {\sc Powheg-Box}, we
+can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
 restrict ourselves to showing results only in the VBS approximation,
@@
     \centering
-    \begin{tabular}{c|r@{ $\pm$ }l}
+    \begin{tabular}{c|l@{ $\pm$ }l}
       Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
@@
         {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.267$ & $ 0.003$  \\
-        {\sc PHANTOM}+{\sc Pythia8} &  $1.235\phantom{0} $ & $0.001$  \\
-        {\sc PHANTOM}+{\sc Herwig++} &  $1.260\phantom{0} $ & $0.001$  \\
-        {\sc VBFNLO}+{\sc Herwig7} &  $1.3001$ & $0.0002$  \\
+        {\sc PHANTOM}+{\sc Pythia8} &  $1.235 $ & $0.001$  \\
+        {\sc PHANTOM}+{\sc Herwig++} &  $1.260 $ & $0.001$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3001$ & $0.0002$  \\
     \end{tabular}
@@
 with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
-{\sc VBFNLO} \emph{i.e.}\ the VBS approximation with $s$-channel \BJ{Note that first paragraph of the Sec.
-says that s-channel contributions are neglected in VBFNLO.} For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
+{\sc VBFNLO}, \emph{i.e.}\ the VBS approximation with $s$-channel).
+For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
 As for the table, we show theoretical uncertainties for the NLO+PS samples

### 2018-02-28 Draft/crosssectionNLO.tex
Updated discussion on powheg t/u

--- 2018-02-26 Draft/crosssectionNLO.tex
@@
         {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ \\
-        {\sc Powheg-Box}  &  $1.362\phantom{0}\phantom{0}$  & $0.001$   \\
+        {\sc Powheg-Box}  &  $1.3605\phantom{0}$  & $0.0007$   \\
         {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\
@@
     The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.
-    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
-    \MP{Please add or check your respective numbers.}}
-    \MR{My $t$-/$u$-channel-only number is $1.3703(1)$, so something additionally must be going on with Powheg, which we should comment on.}
-    \AK{The number here was wrong. I have updated the table and plots. I am also running some more statistics... }
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \end{table}
@@
 The first observation is that the predictions featuring two versions of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are relatively close (\MP{Final number to be added})
-\footnote{The {\sc VBFNLO}-predictions omitting $s$-channel contributions amounts to $1.3703(1)$ fb.}.
+\footnote{The {\sc VBFNLO}-predictions omitting $s$-channel contributions amounts to $1.3703(1)$ fb.
+This differs from the {\sc Powheg-Box} prediction mainly due to the different choice of scales used in the {\sc Powheg-Box} (\emph{cf.} footnote \ref{foot:powheg})}.
 This means that the double-pole approximation on the two W bosons used in {\sc Bonsay} constitutes a good approximation of the VBS-approximated virtual corrections implemented in the {\sc Powheg-Box}.

### 2018-02-28 Draft/input.tex
Updated discussion on powheg t/u

@@
     one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are i
-    employed instead of those of the two hardest jets.} 
+    employed instead of those of the two hardest jets.\label{foot:powheg}} 
 This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

### 2018-02-28 Draft/scanLO.tex
fixed the comments in sections 4 and 5 and add some discussions in the comparison
Commented about the MC errors of fig.4,7

@@
 The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
-\AK{What are the MC error on these plots?}
-\MP{@AK: I changed some stuffs in the text to justify the plot range}
+\AK{What are the MC error on these plots?} \GP{It would be hard to show them on the plot: I have uploaded the MC errors of each bin in th edirectory SCAN, both for fig.4 (LO) and fig.7 (NLO).}
 

### 2018-02-28 Draft/scanNLO.tex
scanNLO.tex: checked the exact discrepancy numbers in the low mjj low dyjj region

@@
 The inclusion of $s$-channels cures partly the discrepancy in this region.
-Still, for the very low $m_{\Pj\Pj}$ a difference of about $8\%$ remains \MP{To be checked the exact numerical value in data}.
+Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains \MP{To be checked the exact numerical value in data}\GP{Checked in the data}.
 This might indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
@@
 
-As expected, in the low invariant mass--low rapidity separation region of the jet pair the VBS approximation fails significantly (up to $40\%$ discrepancies).
-The inclusion of the $s$-channel brings the difference down to at most $5\%$ \MP{To be checked the exact numerical value in data}.
+As expected, in the low invariant mass--low rapidity separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly ($30\%$ discrepancy).
+The inclusion of the $s$-channel brings the difference down to $5\%$ \MP{To be checked the exact numerical value in data}\GP{Checked in the data: respectively the two numbers are 29.4\% and 5.4\% in terms of integrated cross-section in this region}.
 However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:ratio2d_NLO}.

### 2018-03-01 Draft/crosssectionNLO.tex
Added a short discussion regarding the NLO fiducial numbers

@@
         {\sc Bonsay}  &  $1.35039$ & $0.00006$  \\
+        {\sc Powheg-Box}  &  $1.3605\phantom{0}$  & $0.0007$   \\
         {\sc MG5\_aMC}&  $1.363\phantom{0}\phantom{0}$ & $0.004$  \\
         {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ \\
-        {\sc Powheg-Box}  &  $1.3605\phantom{0}$  & $0.0007$   \\
         {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\
@@
 
-The first observation is that the predictions featuring two versions of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are relatively close (\MP{Final number to be added})
-\footnote{The {\sc VBFNLO}-predictions omitting $s$-channel contributions amounts to $1.3703(1)$ fb.
-This differs from the {\sc Powheg-Box} prediction mainly due to the different choice of scales used in the {\sc Powheg-Box} (\emph{cf.} footnote \ref{foot:powheg})}.
-This means that the double-pole approximation on the two W bosons used in {\sc Bonsay} constitutes a good approximation of the VBS-approximated virtual corrections implemented in the {\sc Powheg-Box}.
-Both predictions differ by about $2\%$ with respect to the full computation ({\sc MoCaNLO+Recola}).
-The second observation is that the inclusion of $s$-channel contributions seems to have a significant impact.
-Indeed, its inclusion (as done in {\sc VBFNLO}) approximates the full computation by less than a per-cent ($0.7\%$).
-The main source of the $s$-channel diagrams thereby consists of
-real-emission contributions, where one of the two leading jets is formed
-by one quark, or possibly also both quarks, originating from the $W$
-decay, and the second one by the extra radiation emitted from the
-initial state. In such configurations, the hadronically decaying W boson
-can become on-shell and hence yield larger contributions than at LO, where the
-invariant mass cut on the two jets forces the boson into the far
+The first observation is that the predictions featuring two versions
+of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are
+relatively close\footnote{The {\sc VBFNLO}-predictions omitting
+$s$-channel contributions amounts to $1.3703(1)$ fb. This differs from
+the {\sc Powheg-Box} prediction mainly due to the different choice of
+scales used in the {\sc Powheg-Box} (\emph{cf.}
+footnote \ref{foot:powheg})}. {\sc Bonsay} uses the double pole
+approximation for the virtual matrix element, and it is worth noticing
+that this approximation seems to be accurate at $1\%$ level as
+compared to the {\sc Powheg-Box}. This means that the double-pole
+approximation on the two W bosons used in {\sc Bonsay} constitutes a
+good approximation of the VBS-approxi\-mated virtual corrections
+implemented in the {\sc Powheg-Box}.  Both predictions differ by about
+$2\%$ with respect to the full computation ({\sc MoCaNLO+Recola}).
+The second observation is that the inclusion of $s$-channel
+contributions seems to have a significant impact.  Indeed, its
+inclusion (as done in {\sc VBFNLO}) approximates the full computation
+by less than a per-cent ($0.7\%$). The main source of
+the $s$-channel diagrams thereby consists of real-emission
+contributions, where one of the two leading jets is formed by one
+quark, or possibly also both quarks, originating from the $W$ decay,
+and the second one by the extra radiation emitted from the initial
+state. In such configurations, the hadronically decaying W boson can
+become on-shell and hence yield larger contributions than at LO, where
+the invariant mass cut on the two jets forces the boson into the far
 off-shell region.
+However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effect and non-factorisable corrections in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
+Not unexpectedly none of the approximations used here agree perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.
+Nevertheless, the disagreement seems to never exceed $2\%$ at the fiducial cross section level.

### 2018-03-01 Draft/crosssectionNLO.tex
some small corrections in the text

@@
 of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are
-relatively close\footnote{The {\sc VBFNLO}-predictions omitting
+relatively close.\footnote{The {\sc VBFNLO}-predictions omitting
 $s$-channel contributions amounts to $1.3703(1)$ fb. This differs from
@@
 scales used in the {\sc Powheg-Box} (\emph{cf.}
-footnote \ref{foot:powheg})}. {\sc Bonsay} uses the double pole
+footnote \ref{foot:powheg}).} {\sc Bonsay} uses the double-pole
 approximation for the virtual matrix element, and it is worth noticing
@@
 contributions, where one of the two leading jets is formed by one
-quark, or possibly also both quarks, originating from the $W$ decay,
+quark, or possibly also both quarks, originating from the W-boson decay,
 and the second one by the extra radiation emitted from the initial
@@
 off-shell region.
-However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effect and non-factorisable corrections in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
+However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effect and some non-factorisable corrections (in the real corrections) in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
 Not unexpectedly none of the approximations used here agree perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.

### 2018-03-01 Draft/scanLO.tex
some small corrections in the text

--- 2018-02-20 Draft/scanLO.tex
@@
-In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
+In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
 Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
@@
 The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
-\AK{What are the MC error on these plots?}
-\MP{@AK: I changed some stuffs in the text to justify the plot range}
 

### 2018-03-01 Draft/scanNLO.tex
some small corrections in the text

--- 2018-02-28 Draft/scanNLO.tex
@@
 The inclusion of $s$-channels cures partly the discrepancy in this region.
-Still, for the very low $m_{\Pj\Pj}$ a difference of about $8\%$ remains \MP{To be checked the exact numerical value in data}.
+Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains.
 This might indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
@@
 
-As expected, in the low invariant mass--low rapidity separation region of the jet pair the VBS approximation fails significantly (up to $40\%$ discrepancies).
-The inclusion of the $s$-channel brings the difference down to at most $5\%$ \MP{To be checked the exact numerical value in data}.
+As expected, in the low invariant mass--low rapidity separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly ($29.4\%\%$ discrepancy).
+The inclusion of the $s$-channel brings the difference down to $5.4\%$.
 However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:ratio2d_NLO}.
@@
 In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.
-This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.{\bf GP: should think again about it, in the lights of the new high stat Recola results.
-The discrepancy is no more negative in the large pt region.}
+This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
 For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.

### 2018-03-01 Draft/contributions.tex
added comments to sects 4 and 5

@@
 % \AK{We have mentioned this many times at this point. Perhaps not worth repeating again?}.
-In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
+In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$, 
+Eq.~(\ref{cut:4}).
 In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are reported.
@@
 This results in a small contribution although the VBS cuts have not been imposed.
-The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).
+The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ \ZM{and t/s }interference with identical fermions).
 
@@
 The same holds true for jet rapidity difference larger than $2.5$ (right).
-This clearly explains why these two observables are used to enhanced the EW contribution over the QCD one.
+This clearly explains why cuts on these two observables are used in order to enhance the EW contribution over the QCD one.
 In particular, in order to have a large EW contribution, rather exclusive cuts are required.
@@
 
-This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a function of the di-jet invariant mass and jet rapidity difference.
-Again, it is obvious that the region with low di-jet invariant mass should be avoided as it is dominated by tri-boson contributions.
+This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a (double-differential) function of the di-jet invariant mass and jet rapidity difference.
+Again, it is obvious that the region with low di-jet invariant mass should be avoided in VBS studies as it is dominated by tri-boson contributions.
 % This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
-This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study (see below).
-Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
-These are the cuts used in Sec.~\ref{subsec:LOfiducial}.
+%Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
+This motivates in particular the choice of employing the cut $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study in Sec.~\ref{subsec:LOinclusive}.
 

### 2018-03-01 Draft/crosssectionNLO.tex
added comments to sects 4 and 5

@@
 and the second one by the extra radiation emitted from the initial
-state. In such configurations, the hadronically decaying W boson can
+state. In such configurations, the hadronically-decaying W boson can
 become on-shell and hence yield larger contributions than at LO, where

### 2018-03-01 Draft/distributionsLO.tex
added comments to sects 4 and 5

@@
 In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
-In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}.
+In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
+for which we also display the scale-uncertainty band (\ZM{3-points/9points?}).
 For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.

### 2018-03-01 Draft/distributionsNLO.tex
added comments to sects 4 and 5

@@
 Concerning the transverse momentum (left) and rapidity (right) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
-While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum by about $10\%$.
-This difference can be attributed to EW Sudakov logarithms that become large in this phase-space region.
+While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it departs from it 
+at larger transverse momentum by about $10\%$.
+This difference can be attributed to EW Sudakov logarithms that become large in this phase-space region \ZM{I do not understand: MG5aMC is below
+the full computation and in MG5aMC there are no EW corrections\ldots which Sudakov logs are we speaking about?}.
 This is in contrast with the VBS-approximated predictions such as {\sc Bonsay}, {\sc Powheg}, and {\sc VBFNLO} which are lower than the full computation at low transverse momentum and higher for larger transverse momentum.
@@
 
-In the end, the quality of the VBS-approximations amount to tenths of per cent depending on the observables and phase-space range.
+In the end, the quality of the VBS-approximations amount to tenths of per cent \ZM{tenths is too much\ldots I would say can reach/be as large as 10\%} depending on the observables and phase-space range.
 These differences are larger than at what is observed at LO.

### 2018-03-01 Draft/scanLO.tex
added comments to sects 4 and 5

@@
 In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
-The low rapidity difference region possesses remnants of the tri-bosons contributions that peak at di-jet invariant mass around the W-boson mass.
+The low rapidity-difference region possesses remnants of the tri-bosons contributions that have a di-jet invariant mass around the $\PW$-boson mass.
 It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
@@
 
+\ZM {the following is rather confusing, I will drop it from here and discuss it in the NLO-fiducial section}
 Therefore, the \emph{inclusive} study at NLO is only performed in the region 

### 2018-03-01 Draft/scanNLO.tex
added comments to sects 4 and 5

@@
 % In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
-This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation goes up to $30\%$.
+This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
+the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation reaches $30\%$.
 The inclusion of $s$-channels cures partly the discrepancy in this region.
@@
 
-As expected, in the low invariant mass--low rapidity separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly ($29.4\%\%$ discrepancy).
-The inclusion of the $s$-channel brings the difference down to $5.4\%$.
+As expected, in the low invariant-mass and low rapidity-separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly ($30\%$ discrepancy).
+The inclusion of the $s$-channel brings the difference down to $5\%$.
 However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:ratio2d_NLO}.

### 2018-03-01 Draft/contributions.tex
Few comments discussed with Marco addressed

@@
 This results in a small contribution although the VBS cuts have not been imposed.
-The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ \ZM{and t/s }interference with identical fermions).
+The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ and $t/s$ interferences with identical fermions).
 

### 2018-03-01 Draft/distributionsLO.tex
Few comments discussed with Marco addressed

--- 2018-02-26 Draft/distributionsLO.tex
@@
 In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
-In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}.
+In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
+for which we also display the scale-uncertainty band (7-points variation).
 For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.

### 2018-03-01 Draft/distributionsNLO.tex
Few comments discussed with Marco addressed

@@
 at larger transverse momentum by about $10\%$.
-This difference can be attributed to EW Sudakov logarithms that become large in this phase-space region \ZM{I do not understand: MG5aMC is below
-the full computation and in MG5aMC there are no EW corrections\ldots which Sudakov logs are we speaking about?}.
 This is in contrast with the VBS-approximated predictions such as {\sc Bonsay}, {\sc Powheg}, and {\sc VBFNLO} which are lower than the full computation at low transverse momentum and higher for larger transverse momentum.
+The difference at high transverse momentum between the latter predictions and the full computation can be attributed to EW Sudakov logarithms that become large in this phase-space region.
 While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different different at low transverse momentum where it is even higher than the full computation.
+We note that for the transverse momentum of the second hardest jet, the predictions from {\sc MadGraph5\_aMC\-@NLO} are in good agreement with the other VBS-approximated predictions.
 % Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.
@@
 
-In the end, the quality of the VBS-approximations amount to tenths of per cent \ZM{tenths is too much\ldots I would say can reach/be as large as 10\%} depending on the observables and phase-space range.
+In the end, the quality of the VBS-approximations is good up to $10\%$ in the fiducial region.
 These differences are larger than at what is observed at LO.

### 2018-03-02 Draft/article.tex
removed some notes by BJ in the input section (discussed in the email thread), added HSS and RF as authors
Some small corrections
Commented about the MC errors of fig.4,7
fixed post-code for bicocca

@@
 \newcommand{\ZM}[1]{{ {\color{green}{ [MZ: #1]}} }}
-
 \newcommand{\BJ}[1]{{ {\color{cyan}{ [BJ: #1]}} }}
+\newcommand{\GP}[1]{{ {\color{orange}{ [GP: #1]}} }}
 
@@
 \and
+Rikkert Frederix\thanksref{tum}
+\and
 Pietro Govoni\thanksref{mila}
@@
 Christopher Schwan\thanksref{frei}
+\and
+Hua-Sheng Shao\thanksref{lpthe}
 \and
@@
 \and
+Technische Universit\"{a}t M\"{u}nchen, %
+James-Franck-Str.~1, %
+85748 Garching, %
+Germany\label{tum}
+\and
 University and INFN, Milano-Bicocca, %
-piazza della Scienza, 3, 2016 Milan, %
+piazza della Scienza, 3, 20126 Milan, %
 Italy\label{mila}
@@
 Germany\label{desy}
+\and
+Sorbonne Universit\'e et CNRS, %
+Laboratoire de Physique Th\'eorique et Hautes \'Energies (LPTHE), % 
+UMR 7589, 
+4 place Jussieu, %
+75252 Paris Cedex 05, %
+France\label{lpthe}
 \and

### 2018-03-04 Draft/acknowledgements.tex
removed some notes by BJ in the input section (discussed in the email thread), added HSS and RF as authors
added funding info for BJ in acknowledgements.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
-The authors thank \ldots \\
-the {\sc Pythia8} authors, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
+The authors thank the {\sc Pythia8} authors, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
 discussions and clarifications about the third-jet rapidity spectrum.
@@
 CS acknowledges support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.
+HSS is supported by the ILP Labex (ANR-11-IDEX-0004-02, ANR-10-LABX-63).
 MZ is supported by the Netherlands National Organisation for Scientific Research (NWO).
+The work of BJ was supported in part by the Institutional Strategy of the University of T\"ubingen (DFG, ZUK 63) and in part by
+the BMBF under contract number 05H2015.

### 2018-03-04 Draft/conclusion.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
 mainly focused on the electroweak production mechanism which involves the scattering fo massive vector bosons.
-Until very recently, when the complete calculation became available for the NLO QCD corrections ($\mathcal O (\alphas\alpha^6)$),
+Until very recently, when the complete calculation became available for the NLO QCD corrections (order $\mathcal O (\alphas\alpha^6)$),
 the so-called VBS approximation was the standard for this kind of simulations. For this reason, various theoretical predictions 
@@
 To that end, several LO and NLO event generators 
-which give the possibility to perform matching to parton showers have been employed, and various observables have been thoroughly compared.
+which are able to perform matching to parton showers have been employed, and various observables have been thoroughly compared.
 While in general observables which are described at NLO accuracy show reasonable agreement among the tools, larger differences can 
@@
 These differences appear in the central region where for VBS, and are the largest for those simulations which employ {\sc Pythia8}. The effect
-has been understood, and it can be somehow mitigated by changed the recoil scheme of the parton shower. These findings makes it worth 
+has been understood, and it can be partially mitigated by changing the recoil scheme of the parton shower. These findings makes it worth 
 to further investigate these issues not only in the theoretical community, but also by experimental collaborations, for example by 
@@
         the dominant NLO contribution to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
-        It is thus highly desirable that they are combined with NLO-QCD predictions matched with parton shower, or at least that they accounted for
-        by experimental analyses. Since, as shown in~\cite{Biedermann:2017bss}, 
+        It is thus highly desirable to combine them with NLO-QCD predictions matched with parton shower, or at least that they are accounted for
+        by experimental analyses. Since, as shown in Ref.~\cite{Biedermann:2016yds}, 
         these large EW corrections originate from the Sudakov logarithms which factorise, we recommend to combine them with QCD 
@@
         For more detailed studies of the combination of QCD and EW higher-order corrections, see
-        e.g., Ref.~\cite{Czakon:2017wor} in the context of top-pair production, or Ref.~\cite{Lindert:2017olm} for SM 
+        \emph{e.g.}\, Ref.~\cite{Czakon:2017wor} in the context of top-pair production, or Ref.~\cite{Lindert:2017olm} for SM 
         backgrounds for dark matter searches at the LHC.
@@
         combined measurements should also be presented as they are better defined theoretically. In fact, while at at LO 
-        the interference term can be included in the background component, at NLO the separation of EW and QCD component become more blurred, as, e.g.,
+        the interference term can be included in the background component, at NLO the separation of EW and QCD component become more blurred, as, \emph{e.g.}\,
         as at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes mix.
@@
 
-    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguites related to the 
+    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguities related to the 
         matching details and/or the parton-shower employed, we encourage the use of NLO-accurate event generators in experimental analyses.
@@
     the observed features 
-    (e.g. validity of the VBS approximation or comparison of theoretical predictions matched to parton shower) should 
+    (\emph{e.g.}\ validity of the VBS approximation or comparison of theoretical predictions matched to parton shower) should 
     be qualitatively similar for other VBS signatures with massive gauge bosons. For these other signatures, similar quantitative studies should be performed.

### 2018-03-04 Draft/contributions.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
 The QCD contribution does not posses external gluons due to charge conservation.
-Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchange in the $t/u$-channel between the quark lines.
+Thus the diagrams of order $\mathcal{O}(\alphas^2\alpha^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
 This results in a small contribution although the VBS cuts have not been imposed.
-The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ and $t/s$ interferences with identical fermions).
+The interference between EW and QCD contributions is small, due to color suppression, but not negligible.
+% ($t/u$ and $t/s$ interferences with identical fermions).
 
@@
     \end{tabular}
-    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$, obtained with full matrix elements.
-    These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}
+    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$, obtained with exact matrix elements.
+    These results are for the set-up described in Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
+    The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.}
 \end{table}
@@
 In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
-In the distributions in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
+For the distribution in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
 These are due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
@@
 The same holds true for jet rapidity difference larger than $2.5$ (right).
-This clearly explains why cuts on these two observables are used in order to enhance the EW contribution over the QCD one.
+This justifies why cuts on these two observables are used in order to enhance the EW contribution over the QCD one.
 In particular, in order to have a large EW contribution, rather exclusive cuts are required.
@@
 \includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
-\caption{Differential distribution in the di-jet invariant mass $m_{\Pj\Pj}$ (left) and the difference of the jet rapidities $|\Delta y_{\Pj\Pj}|$ (right) at LO.
-The EW contribution is in red, the QCD one in green, and the interference in grey.
+\caption{Differential distribution in the di-jet invariant mass $m_{\Pj\Pj}$ (left) and the difference of the jet rapidities $|\Delta y_{\Pj\Pj}|$ (right) for the three LO contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
+The EW contribution is in red, the QCD one in green, and the interference one in grey.
 The sum of all the contributions is in blue.
@@
 \includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
-\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top), $\mathcal{O}(\alphas\alpha^5)$ (middle), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
+\caption{Double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alphas\alpha^5)$ (top right), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
 The cuts applied are the ones of of Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.

### 2018-03-04 Draft/crosssectionLO.tex
fixed the comments in sections 4 and 5 and add some discussions in the comparison
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
-In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
-The order considered here is the order $\mathcal{O}(\alpha^6)$.
+In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy at order $\mathcal{O}(\alpha^6)$ obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
 We note that several full predictions are not in statistical agreement. These are possibly due to Monte-Carlo 
@@
 This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
-the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations. This is in agreement with the findings of Ref.~\cite{Denner:2012dz,Oleari:2003tc}.
+the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
+This is in agreement with the findings of Ref.~\cite{Denner:2012dz,Oleari:2003tc}.
 
@@
     \end{tabular}
-    \caption{\label{tab:wg1_LOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
-    The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.
+    \caption{\label{tab:wg1_LOrates} Cross sections at LO accuracy and order $\mathcal{O}(\alpha^6)$.
     The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
-    \MP{Please add or check your respective numbers}}
+    The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.}
 \end{table}

### 2018-03-04 Draft/crosssectionNLO.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
     \end{tabular}
-    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alphas\alpha^6)$.
-    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.
-    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+    \caption{\label{tab:wg1_NLOrates} Cross sections at NLO accuracy and order $\mathcal{O}(\alphas\alpha^6)$.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
+    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.}
 \end{table}
@@
 scales used in the {\sc Powheg-Box} (\emph{cf.}
-footnote \ref{foot:powheg}).} {\sc Bonsay} uses the double-pole
+footnote \ref{foot:powheg}).} {\sc Bonsay} uses a double-pole
 approximation for the virtual matrix element, and it is worth noticing
@@
 inclusion (as done in {\sc VBFNLO}) approximates the full computation
-by less than a per-cent ($0.7\%$). The main source of
+by less than a per cent ($0.7\%$). The main contribution due to 
 the $s$-channel diagrams thereby consists of real-emission

### 2018-03-04 Draft/definition.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
 $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
-The first, commonly referred to as EW contribution or VBS~\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
-of vector bosons.}, receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
+The first, commonly referred to as EW contribution or VBS,\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
+of vector bosons.} receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
 in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
@@
 radiated off the quark lines. Because of the different colour structure, this contribution features a 
-different kinematical behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.
+different kinematic behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.
 
@@
 In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
-These cuts are based on the different kinematical behaviour of the two contributions.
+These cuts are based on the different kinematical behaviour of the contributions.
 The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.

### 2018-03-04 Draft/description.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
-\begin{table*}[ht!]
-    \footnotesize
-    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
-        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
-        \hline
-        \hline
-        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
-        {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
-        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
-        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
-        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
-        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
-        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
-    \end{tabularx}
-    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
-\end{table*}
-
 In the following, the codes employed throughout this paper and the approximations implemented in each of them will be discussed:
@@
 For the fiducial cross sections it uses the VBS approximation at LO and NLO.
-The virtual corrections are additionally approximated using a double pole approximation.
+The virtual corrections are additionally approximated using a double-pole approximation.
 For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) are used.
@@
   With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded\footnote{Despite
-            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
+            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electroweak corrections, it is not yet possible to compute such corrections
         with the current version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
@@
 The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
-In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained from this tool.
+In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained thanks to this tool.
 One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
-In {\sc MoCaNLO+Recola} no approximation is performed at LO as well as at NLO, and, in particular, also contributions stemming from EW corrections to the interference are computed.
+In {\sc MoCaNLO+Recola} no approximation is performed neither at LO nor at NLO.
+It implies that, also contributions stemming from EW corrections to the interference are computed.
 
@@
   \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw,Nason:2006hfa} is a framework for matching NLO-QCD calculations with parton showers.
-It relies on the user providing the matrix elements and Born phase space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
-For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
+It relies on the user providing the matrix elements and Born phase-space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
+For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.
 
@@
     approximation, with process IDs between 200 and 290. The corresponding
-    s-channel contributions are available separately as tri-boson processes with
+    $s$-channel contributions are available separately as tri-boson processes with
     semi-leptonic decays, with process IDs in the 400 range. These can simply
-    be added on top of the VBS contribution, as interferences between the two are neglected.
+    be added on top of the VBS contribution. Interferences between the two are therefore neglected.
     The usage of leptonic tensors in the calculation, pioneered in
@@
 OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
-(cf. above) can be used as well). {\sc Whizard} allows to simulate a
-huge number of BSM models as well, in particular for new physics in
+(\emph{cf.}\ above) can be used as well). {\sc Whizard} allows to simulate a
+huge number of BSM models as well, in particular in
 the VBS channel in terms of both higher-dimensional operators as well as explicit
@@
 
-We conclude this section by summarising the details of the various codes in Tab.~\ref{tab:wg1_codes}. In particular, it is specified whether
+We conclude this section by summarising the characteristics of the various codes in Tab.~\ref{tab:wg1_codes}.
+In particular, it is specified whether
 \begin{itemize}
-    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
-    \item interferences between diagrams are included at LO;
-    \item diagrams which do not feature two resonant vector bosons are included;
+    \item all $s$- and $t/u$-channel diagrams are included;
+    \item interferences between different diagrams of diagrams ($s/t/u$-channel) are included at LO;
+    \item diagrams which do not feature two resonant vector-bosons are included;
     \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
         are included;
-    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
-        the  $\mathcal O (\alpha^6$) term.
+    \item EW corrections to the interference of order $\mathcal O (\alpha^5\alphas)$ are included.
+    These corrections are of the same order as the NLO QCD corrections to the contribution of order $\mathcal O (\alpha^6$) term.
 \end{itemize}
+
+\begin{table*}[ht!]
+    \footnotesize
+    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
+        Code  &  $\mathcal O(\alpha^6)$ $s, t, u$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to order $\mathcal O(\alphas \alpha^5)$  \\
+        \hline
+        \hline
+        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
+        {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & virt. No &  No \\
+        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
+        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
+        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
+        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
+    \end{tabularx}
+    \caption{\label{tab:wg1_codes} Summary of the different properties of the computer programs employed in the comparison.}
+\end{table*}

### 2018-03-04 Draft/distributionsLO.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

--- 2018-02-26 Draft/distributionsLO.tex
@@
 In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
-In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}.
-For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.
-In general, the agreement is at the level of $1\%$ or below for each bin.
+In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
+for which we also display the scale-uncertainty band (seven-points variation).
+For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as interferences are suppressed in the fiducial region.
+In general, the agreement is at the level of $1\%$ or below in each bin.
 We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
@@
    \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
-\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
-The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
+\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right) at LO accuracy and order $\mathcal{O}(\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
 The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
 The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}

### 2018-03-04 Draft/distributionsNLO.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
 All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alphas\alpha^6)$.
+In the upper panel, the absolute predictions are shown while in the lower panel, the ratio with respect to the full predictions are displayed.
+The band corresponds to a seven-points variation of the factorisation and renormalisation scales.
 
@@
 The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
-Finally, {\sc VBFNLO} which includes as well $s$-channel contributions provides larger predictions at low invariant mass.
+Finally, {\sc VBFNLO} which includes also $s$-channel contributions provides larger predictions at low invariant mass.
 For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.
@@
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
-The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
+The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
 The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
@@
 In the end, the quality of the VBS-approximations is good up to $10\%$ in the fiducial region.
-These differences are larger than at what is observed at LO.
+These differences are larger than at LO.
 
@@
 
-At the $s$-channel contributions are sizeable, their interferences with the $t$/$u$-channel can be of similar size in the phase-space region where the former are large.
+As the $s$-channel contributions are sizeable, their interferences with the $t$/$u$-channel can be of similar size in the phase-space region where the former are large.
 This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MadGraph5\_aMC\-@NLO}.
@@
 Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
-But they can be particularly large (about $10\%$) for large transverse momentum of the hardest jet.
+But they can be relatively large (about $10\%$) for large transverse momentum of the hardest jet.
 These high-energy region of the phase space are where EW Sudakov logarithms become large.

### 2018-03-04 Draft/input.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

--- 2018-02-23 Draft/input.tex
@@
 The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{
-For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.} 
-NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
+The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.}
+NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
 %Since this PDF set has no photonic density, photon-induced processes are not considered.
@@
 %
-defined via the transverse momenta of the two hardest identified jets.  
+defined via the transverse momenta of the two hardest identified jets.\footnote{The renormalisation and factorisation scale employed in the {\sc Powheg-Box} slightly differ from the 
+    one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are
+    employed instead of those of the two hardest jets.\label{foot:powheg}} 
 This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

### 2018-03-04 Draft/introduction.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
 because the corresponding matrix elements feature unitarity cancellations 
-that strongly depend on the actual structure of the Higgs sector.
+that strongly depend on the actual structure of the Higgs sector of the Standard Model (SM).
 A detailed study of this class of processes will therefore further constrain the Higgs couplings 
@@
 
-The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio at the LHC of all the VBS processes:
+The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio of all the VBS processes at the Large Hadron Collider (LHC):
 evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
@@
 Nonetheless, it possesses all features of VBS at the LHC and is thus representative of other VBS signatures.
-Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.
+Therefore, it is the ideal candidate for a comparative study of the different simulation tools.
 
@@
 \fi
-After having defined the VBS process in Sec.~\ref{sec:definition} and having described the approximations of the various computer 
+This article starts with the definition of the VBS process in Sec.~\ref{sec:definition}.
+After having described the approximations of the various computer 
 codes in Sec.~\ref{sec:details}, in Sec.~\ref{sec:LO} a leading-order (LO) study 

### 2018-03-04 Draft/process.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
-We now turn to discuss the various approximations which are implemented in computer programs for the EW contribution at
-$\mathcal{O}{\left(\alpha^{6}\right)}$. Since we are mostly interested in 
+We now discuss the various approximations which are implemented in computer programs for the EW contribution at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
+Since we are mostly interested in 
 the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 

### 2018-03-04 Draft/scanLO.tex
Few comments discussed with Marco addressed
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
-In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
+In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ are shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
 Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
@@
 \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Ratio of cross sections per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
+\caption{Ratios of double-differential distributions in the variables the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
 Ratio of approximated squared amplitudes over the full matrix element.
@@
 
-\ZM {the following is rather confusing, I will drop it from here and discuss it in the NLO-fiducial section}
-Therefore, the \emph{inclusive} study at NLO is only performed in the region 
-%
-\begin{equation}
-\label{eq:inclusive}
-	m_{jj} > 200\GeV\, \qquad {\rm and} \qquad |\Delta y_{jj}| > 2 .
-\end{equation}
-%
-Hence, the differences arising at NLO in this fiducial region originate solely from NLO effects.
+% Therefore, the \emph{inclusive} study at NLO is only performed in the region 
+% %
+% \begin{equation}
+% \label{eq:inclusive}
+% 	m_{jj} > 200\GeV\, \qquad {\rm and} \qquad |\Delta y_{jj}| > 2 .
+% \end{equation}
+% %
+% Hence, the differences arising at NLO in this fiducial region originate solely from NLO effects.
 

### 2018-03-04 Draft/scanNLO.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
-We now present an inclusive study performed at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$.
+According to the results shown in Sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails drastically in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
+Therefore, we present an inclusive study at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$ for the set-up described in Sec.~\ref{subsec:inputpar} but imposing $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
 
-According to the results shown in Sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
-For the inclusive region (see Eq.~\eqref{eq:inclusive}), this approximation is good up to $\pm10\%$ apart for large di-jet differences and low di-jet invariant mass.
-It is therefore interesting to check how good this approximation performs at NLO.
-Thus, we impose the same kinematic cuts shown in Sec.~\ref{subsec:inputpar} and apply the VBS cuts of Eq.~\eqref{eq:inclusive}.
+% For the inclusive region (see Eq.~\eqref{eq:inclusive}), this approximation is good up to $\pm10\%$ apart for large di-jet differences and low di-jet invariant mass.
+% It is therefore interesting to check how good this approximation performs at NLO.
+% Thus, we impose the same kinematic cuts shown in Sec.~\ref{subsec:inputpar} and apply the VBS cuts of Eq.~\eqref{eq:inclusive}.
 
 We compare three different predictions at NLO QCD: 
-the VBS approximation ($|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions ($|s|^2+|t|^2+|u|^2$) from {\sc VBFNLO}, and the full computation.
-The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable, and non-factorisable QCD corrections as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^6)$ are included.
+the VBS approximation (dubbed $|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
+The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable, and non-factorisable QCD corrections as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
 % This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.
+
 The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
+The $|t|^2+|u|^2$ approximation for NLO QCD predictions is lower by about $6\%$ with respect to the full calculation.
+The inclusion of $s$-channel diagrams improves the approximate prediction, leading to a slight excess at the $2\%$-level.
 
@@
 \end{tabular}
-\caption{
-Total cross sections at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
+\caption{Cross sections at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
+The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.}
 \label{tab:crosssecINCLUSIVE}
 \end{table}
-
-The VBS approximation for NLO QCD predictions (labelled by $|t|^2 + |u|^2$) is lower by about $6\%$ with respect to the full calculation.
-The inclusion of $s$-channel diagrams improves the approximate prediction down to a slight excess at the $2\%$-level.
 
@@
 This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
-the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation reaches $30\%$.
-The inclusion of $s$-channels cures partly the discrepancy in this region.
+the difference between the $|t|^2+|u|^2$ approximation and the full computation reaches $30\%$.
+The inclusion of $s$-channels cures partly this behaviour in this region.
 Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains.
-This might indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
+This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
 
@@
 In particular, we compute in each bin the ratio of the approximated cross sections over the full one.
-In Fig.~\ref{fig:ratio2d_NLO} we show the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$, in the left and right plot respectively.
+In Fig.~\ref{fig:ratio2d_NLO} we show the ratio $\sigma(|t|^2+|u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2+|u|^2)/\sigma(\textrm{full})$.
 
@@
 The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
 \label{fig:mjjdyjj_1d_1}
@@
 {\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-\caption{Ratio of cross sections per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
+\caption{Ratios of double-differential distributions in the variables the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
 Ratio of approximated squared amplitudes over the full matrix element.
-The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right)
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
+The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2+|u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2+|t|^2+|u|^2$ (right)
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
 \label{fig:ratio2d_NLO}
@@
 
-As expected, in the low invariant-mass and low rapidity-separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly ($30\%$ discrepancy).
-The inclusion of the $s$-channel brings the difference down to $5\%$.
-However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:ratio2d_NLO}.
+As expected, in the low invariant-mass and low rapidity-separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly (up to $30\%$ discrepancy).
+Including the $s$-channel contributions leads to a difference of $5\%$.
+However, in the region of large di-jet invariant mass and low rapidity separation of the jets, the $|s|^2+|t|^2+|u|^2$ approximation overshoot the full computation by $40\%$.
+On the other hand, in the typical VBS region, the VBS approximation shows a good agreement with the full computation as documented in details in Sec.~\ref{sec:fidNLO}
+
+% However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:ratio2d_NLO}.
 % In this region, the two leading jets have soft transverse momenta, according to the following low-angle approximation
@@
 
-The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low transverse-momentum region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
-In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.
-This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
-For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.
-In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.
+% The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low transverse-momentum region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
+% In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.
+% This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
+% For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.
+% In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.
+
+In Fig.~\ref{fig:mjjdyjj_1d_2}, the distributions in the transverse momentum of the hardest jet and its rapidity are shown.
+At low transverse momentum, $|t|^2+|u|^2$ and $|s|^2+|t|^2+|u|^2$ approximations are lower and higher than the full computation by about $20\%$, respectively.
+At high transverse momentum, they have a similar behaviour.
+They both diverge from the full computation towards larger transverse momentum to reach about $10\%$ at $1000\GeV$.
+Regarding the rapidity of the hardest jet, the two approximations have opposite behaviours.
+In the central region, the $|t|^2+|u|^2$ approximation differs by $12\%$ with respect to the full computation while the $|s|^2+|t|^2+|u|^2$ one is good within $5\%$.
+In the peripheral region, the $|t|^2+|u|^2$ approximation is rather close to the full computation ($5\%$) while the $|s|^2+|t|^2+|u|^2$ one differs by $10\%$.
 
@@
 The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
 \label{fig:mjjdyjj_1d_2}
@@
 
-Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron, defined as
+Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions in the di-lepton invariant mass and in the Zeppenfeld variable of the electron, defined as
 %
@@
 The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
-In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
 \label{fig:mjjdyjj_1d_3}
@@
 %
-The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
-The prediction from {\sc Bonsay} is about $10\%$ lower for $m_{e^+\mu^+}<1200 \GeV$; this discrepancy reaches about $20\%$ in the very high mass region. 
+The $|s|^2+|t|^2+|u|^2$ predictions for $m-{\rm e^+\mu^+}$ agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
+The prediction from {\sc Bonsay} is about $10\%$ lower around $1000 \GeV$.
+% ; this discrepancy reaches about $20\%$ in the very high mass region. 
 %The discrepancies are roughly constant over the whole spectrum.
-Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$-channels, with increasing negative discrepancy with respect to the full result at large values (up to $30\%$ for $z_{e^+}>1.2$).
-Including $s$-channels makes this discrepancy become positive, but smaller than $10\%$ over the whole spectrum.
-The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.
+% Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that
+The Zeppenfeld variable of the positron $z_e$ is more strongly affected by the exclusion of $s$-channels.
+% with increasing negative discrepancy with respect to the full result at large values (up to $30\%$ for $z_{e^+}>1.2$).
+% Including $s$-channels makes this discrepancy become positive, but smaller than $10\%$ over the whole spectrum.
+% The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.
+For increasing $z_{\rm e}$, the $|t|^2+|u|^2$ approximation diverges from the full computation to reach about a $25\%$ difference  at $1.5$.
+On the other hand, including $s$-channel contributions leads to a better approximation, staying within $10\%$ difference over the whole range.
 
 In conclusion, both the loose minimum di-jet invariant mass cut and the inclusion of QCD radiative correction make the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
-Nevertheless, interferences and non-factorizable QCD corrections should be included to reduce the discrepancies down to about $1\%$, mainly in inclusive analyses.
-Instead, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($M_{\Pj\Pj} \gtrsim 600 \GeV$, $|\Delta y_{\Pj\Pj}| \gtrsim 3$), for both total cross section and differential distributions.
+% Nevertheless, interferences and non-factorizable QCD corrections should be included to reduce the discrepancies down to about $1\%$, mainly in inclusive analyses.
+In the inclusive region studied here, neglecting $s$-channel, non-factorisable corrections, and electroweak corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.
+Nevertheless, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($m_{\Pj\Pj} \gtrsim 500 \GeV$, $|\Delta y_{\Pj\Pj}| \gtrsim 2.5$), for both total cross section and differential distributions.
+This more exclusive region is studied in more details in the next section.

### 2018-03-04 Draft/shower.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

@@
-We now discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
+We now discuss how different predictions compare when the matching to parton-shower is included. For such
 a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
-matching schemes, parton shower employed and of other details of the matching (such as the choice of the parton shower initial scale). Among
+matching schemes, parton shower employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
 the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
@@
 Compared to the fixed order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
-${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is anyway dominated by doubly-resonant contribution, the
-events are produced for the process with two stable W$^+$ bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and these W$^+$ bosons
-are decayed with {\sc MadSpin}~\cite{Artoisenet:2012st} (keeping spin correlations) before the PS. Since {\sc MadSpin}\ computes
+${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is dominated by doubly-resonant contribution, the
+events are produced for the process with two stable ${\rm W}^+$-bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and the decay of these ${\rm W}^+$-bosons
+is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the PS. Since {\sc MadSpin}\ computes
 the partial and total decay width of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
-a small effect (6\%) on the normalisation of distribution is induced. Finally, when the renormalisation
+an effect ($6\%$) on the normalisation is induced. Finally, when the renormalisation
 and factorisation scales are set, the $\Delta R_{\Pj\Pl}$ cut is not imposed during the jet-clustering procedure.
-But this effect is below a per cent at the level of the fiducial cross sections.
+This effect is below a per cent at the level of the fiducial cross sections.
 
@@
     \end{tabular}
-    \caption{\label{tab:PSratesLO} Rates at LO-QCD accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
-    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).}
+    \caption{\label{tab:PSratesLO} Cross sections at LO+PS accuracy.
+    The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).
+    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.}
 \end{table}
@@
     \end{tabular}
-    \caption{\label{tab:PSratesNLO} Rates at NLO-QCD  accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
-    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
+    \caption{\label{tab:PSratesNLO} Cross sections at NLO+PS accuracy.
+    The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
     are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
-are respectively the nine-point scale uncertainty and the PDF one.}
+are respectively the nine-point scale uncertainty and the PDF one.
+The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.}
 \end{table}
 
-We now present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
+We now present the results of predictions matched to parton shower.
+The total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
 \ref{tab:PSratesNLO}, at LO and NLO
@@
 take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
-theoretical uncertainties: for the former, we show both PDF and scale uncertainties (a preliminar study on PDF uncertainties in VBS has appeared 
-in Ref.~\cite{Schwan:2017yy}), obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
-scale by a factor of two around its central value, Eq.~(\ref{eq:defscale}) (nine-point variations); for the latter, we show the 
-three-point scale uncertainties, obtained by considering correlated variations of the renormalization and factorization scales.
+theoretical uncertainties.
+For the former, we show both PDF and scale uncertainties,\footnote{A preliminary study on PDF uncertainties in VBS has appeared 
+in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorization
+scale by a factor of two around its central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
+For the latter, we show the 
+three-point scale uncertainties, obtained by considering correlated variations of the renormalisation and factorisation scales.
 Theory uncertainties should have very little dependence on the tool employed.
@@
 scales are varied independently and when they are varied in a correlated manner, as well as those due to PDF.  
-Concerning differential kinematic distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
+Concerning differential distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
 with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
@@
 leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
-initial scale of the parton shower. The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
+initial scale of the parton shower.\MP{More details/comments there?}
+The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
 among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
-\caption{Exclusive jet multiplicity from predictions matched to parton shower, at LO (left) or NLO (right) accuracy, compared with the fixed-NLO result computed with {\sc VBFNLO}.
-At NLO+PS accuracy, for
+\caption{Differential distribution in the 
+exclusive jet multiplicity
+from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
-    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. }
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. 
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \label{fig:PSnjet}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/m_jj.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
+\caption{Differential distribution in the 
+invariant mass of the two tagging jets
+from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. 
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \label{fig:PSmjj}
@@
 the spread of predictions matched with parton shower is rather small
-($\lesssim 10\%$, if one compensates for the 6\% width effect for {\sc MG5\_aMC}); LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
+($\lesssim 10\%$, if one compensates for the $6\%$ width effect for {\sc MG5\_aMC}).
+The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
 about -30\% at the end of the displayed range.
@@
 
-The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities to the invariant-mass distribution: at LO+PS all predictions,
-except for {\sc VBFNLO3+Herwig7} where the effect is mitigated, show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
+The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities to the invariant-mass distribution.
+At LO+PS all predictions,
+except for {\sc VBFNLO+Herwig7} where the effect is mitigated, show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
 quantitatively similar way. At NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
-exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations: since such a suppression is already there for the {\sc Powheg-no shower} sample,
+exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations.
+Since such a suppression is already there for the {\sc Powheg-no shower} sample,
 it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
@@
 peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
-at most $10\%$.\footnote{If the setting {\tt SpaceShower:dipole\-Recoil = on} (discussed in the following of the article) 
+at most $10\%$.\footnote{If the setting {\tt SpaceShower:dipole\-Recoil = on} (discussed in the following) 
 is used when {\sc Pythia8}\ is employed together with the {\sc Powheg-Box}, the enhancement at central rapidities and the depletion 
@@
 
-Finally, focusing on the third jet, we conclude the list of differential observables with showing the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Fig.~\ref{fig:PSz3}. This 
-variable is closed related to the third jet rapidity, and small (large) value of $z$ correpsond to central (peripheral) rapidities. In general, for observables which involve the third jet, one
+Finally, focusing on the third jet, we conclude the list of differential observables by showing the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Fig.~\ref{fig:PSz3}. This 
+variable is closely related to the third jet rapidity, and small (large) values of $z$ correspond to central (peripheral) rapidities. In general, for observables which involve the third jet, one
 can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The Zeppenfeld variable is 
@@
 is clearly visible. Such an effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF(VBS)-type processes,
-can be mitigated by setting {\tt SpaceShower:dipole\-Recoil = on} in the {\sc Pythia8} input file;\footnote{this requires version $\ge8.230$. 
+can be mitigated by setting {\tt SpaceShower:dipole\-Recoil = on} in the {\sc Pythia8} input file.\footnote{This requires version $\ge8.230$. 
 Note that such a setting is not compatible with the NLO matching
 in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching). Also, this setting has other 
-effects, though smaller, on the rapidity spectra of the two hardest jets.} it is interesting to notice that
+effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
 the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+ Pythia8}. A similar
@@
 on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is
-generated, e.g.
-when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
+generated, \emph{e.g.}\ when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
 It is a remarkable fact that, even for those observables that display small discrepancies,
 the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. Again, this stresses the need
- to employ at least two different tools in order to have a conservative estimate of theoretical uncertainties.
+ to employ at least two different tools in order to obtain a conservative estimate of theoretical uncertainties.
 Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
@@
 description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern 
-automated tools, is certainly desirable; on the other hand, measurements of processes with similar 
+automated tools, is certainly desirable.
+On the other hand, measurements of processes with similar 
 color flow (EW production of a single vector boson plus jets,
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/Deltay_jj.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the rapidity separation of the two tagging jets.}
+\caption{Differential distribution in the 
+rapidity separation of the two tagging jets
+from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. 
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \label{fig:PSdyjj}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the transverse momentum of the hardest jet.}
+\caption{Differential distribution in the 
+transverse momentum of the hardest jet
+from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. 
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \label{fig:PSpt1}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the transverse momentum of the second-hardest jet.}
+\caption{Differential distribution in the 
+transverse momentum of the second-hardest jet
+from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. 
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \label{fig:PSpt2}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j2.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the rapidity of the second-hardest jet.}
+\caption{Differential distribution in the 
+rapidity of the second-hardest jet
+from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. 
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \label{fig:PSy2}
@@
 \includegraphics[width=0.47\textwidth]{figures/NLOPS/z_j3.pdf}
-\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the $z$ variable of the third-hardest jet.}
+\caption{Differential distribution in the 
+Zeppenfeld variable of the third-hardest jet
+from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond  
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly. 
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
 \label{fig:PSz3}

### 2018-03-04 Draft/contributions.tex
Start of implementing Ansgar's comments

@@
 Eq.~(\ref{cut:4}).
-In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are reported.
+In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three LO contributions are reported.
 The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
@@
 Thus the diagrams of order $\mathcal{O}(\alphas^2\alpha^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
-This results in a small contribution although the VBS cuts have not been imposed.
+This results in a small contribution even if the VBS cuts have not been imposed.
 The interference between EW and QCD contributions is small, due to color suppression, but not negligible.
@@
 For the distribution in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
-These are due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
+This is due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
 Note that these contributions are not present in calculations relying on the VBS approximation.

### 2018-03-04 Draft/definition.tex
Start of implementing Ansgar's comments

@@
 At LO, this process can proceed via three different coupling-order combinations:
-$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
+$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
 The first, commonly referred to as EW contribution or VBS,\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
@@
 $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
-$u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
+$u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical quarks or anti-quarks in the final state
 The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
@@
 Finally, the third contribution is the interference of the two types of amplitudes described above.
-It is non-zero only for those partonic subprocesses which involve only one quark family.
+It is non-zero only for those partonic subprocesses which involve identical quarks or antiquarks.
 Such a contribution is typically small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.

### 2018-03-04 Draft/input.tex
Start of implementing Ansgar's comments

@@
 The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.}
+The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.}
 NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}

### 2018-03-04 Draft/process.tex
Start of implementing Ansgar's comments

@@
 Since we are mostly interested in 
-the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 
+the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, it may appear justified to approximate the 
 full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
 However, this set of contributions is not gauge invariant.
-In order ensure gauge invariance, an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
-Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
-Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected 
-to the final-state leptons, which are already time-like, are put on-shell. \ZM{is this still gauge invariant? if so, one should change 
-the sentence above ``In order to ensure..''}
-Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
-Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
+In order ensure gauge invariance, an on-shell projection of
+the incoming and outgoing W bosons should be performed.
+While this can be done in the usual way for the time-like
+outgoing W bosons, the treatment of the space-like W bosons
+emitted from the incoming quarks requires some care.
+Following Refs.~\cite{Kuss:1995yv,Accomando:2006hq} these W-boson lines can be split,
+the W bosons entering the scattering process can be projected
+on-shell, and the emission of the W bosons from the quarks can be
+described by vector-boson luminosities.
+Such an approximation is usually called effective vector-boson
+approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
 
@@
 
-When considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ squared with the tree amplitude of order $\mathcal{O}(g^6)$, not only real QCD radiation but also QED ones have to be included in order cancel IR singularities.
-But all IR singularities related to photon emissions are not cancelled by the above mentioned virtual corrections.
-Another type of virtual corrections has to be incorporated, namely the one-loop amplitude of order $\mathcal{O}(g^8)$ interfered with the tree-level one of order $\mathcal{O}(g_{\rm s}^2 g^4)$.
-Hence the full NLO corrections of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consist not only of QCD-type corrections but also of EW ones \cite{Biedermann:2017bss}.
-%Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
+When considering the NLO corrections of order
+$\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$
+to the full process, besides real and virtual QCD corrections
+to the EW tree-level contribution of order
+$\mathcal{O}{\left(\alpha^{6}\right)}$
+also real and virtual EW corrections to the LO interference
+of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$
+have to be taken into account. Since some loop diagrams contribute
+to both types of corrections, QCD and EW corrections cannot be
+separated any more on the basis of Feynman diagrams, and the
+cancellation of IR singularities requires to include all of them \cite{Biedermann:2017bss}.

### 2018-03-04 Draft/scanLO.tex
Start of implementing Ansgar's comments

@@
-In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ are shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
+In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the variables  $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
 Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
@@
 The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
-The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
+The full calculation is approximated at the level of $\pm5\%$ apart in the region where $|\Delta y_{\Pj\Pj}| < 2$.
 

### 2018-03-04 Draft/scanNLO.tex
Start of implementing Ansgar's comments

@@
 In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
-For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agree with the full calculation within $10\%$ per cent.
+For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$ per cent.
 % On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.

### 2018-03-05 Draft/conclusion.tex
End of implementation of Ansgar's comment

@@
 In the present article, a detailed study of the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC has been presented, 
-mainly focused on the electroweak production mechanism which involves the scattering fo massive vector bosons.
+mainly focused on the electroweak production mechanism which involves the scattering of massive vector-bosons.
 Until very recently, when the complete calculation became available for the NLO QCD corrections (order $\mathcal O (\alphas\alpha^6)$),
@@
 These differences appear in the central region where for VBS, and are the largest for those simulations which employ {\sc Pythia8}. The effect
-has been understood, and it can be partially mitigated by changing the recoil scheme of the parton shower. These findings makes it worth 
+has been understood, and it can be partially mitigated by changing the recoil scheme of the parton shower. These findings make it worth 
 to further investigate these issues not only in the theoretical community, but also by experimental collaborations, for example by 
@@
     \item In addition to the standard interpretation of EW signal versus QCD background, 
-        combined measurements should also be presented as they are better defined theoretically. In fact, while at at LO 
+        combined measurements should also be presented as they are better defined theoretically. In fact, while at LO 
         the interference term can be included in the background component, at NLO the separation of EW and QCD component become more blurred, as, \emph{e.g.}\,
-        as at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes mix.
+        at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes contribute.
         Therefore, a combined measurement including the EW, QCD, and interference contributions is desirable.
@@
             where EW/QCD are the dominant contributions}
-Note that with such a measurement, an interpretation in terms of EW component is still possible.
-This would amount to replace the subtraction of the QCD component based on Monte Carlo predictions by an actual measurement.
+Note that with such a measurement a comparison to the SM would
+  be straigtforward and still be sensitive to the EW component.
+  In addition the QCD component could be subtracted based on a
+  well-defined Monte-Carlo prediction.
 \MP{I am aware that this might be the most touchy point.

### 2018-03-05 Draft/contributions.tex
End of implementation of Ansgar's comment

@@
 The sum of all the contributions is in blue.
-The cuts applied are the ones of of Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.}
+The cuts applied are the ones of Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.}
 \label{fig:mjjdyjj_1d}
@@
 \caption{Double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alphas\alpha^5)$ (top right), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
-The cuts applied are the ones of of Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
+The cuts applied are the ones of Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
 }

### 2018-03-05 Draft/distributionsNLO.tex
End of implementation of Ansgar's comment

@@
-In Figs.~(\ref{fig:distNLO1}-\ref{fig:distNLO3}), several differential distributions are shown.
+In Figs.~\ref{fig:distNLO1}--\ref{fig:distNLO3}, several differential distributions are shown.
 All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alphas\alpha^6)$.
@@
 The difference at high transverse momentum between the latter predictions and the full computation can be attributed to EW Sudakov logarithms that become large in this phase-space region.
-While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different different at low transverse momentum where it is even higher than the full computation.
+While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different at low transverse momentum where it is even higher than the full computation.
 We note that for the transverse momentum of the second hardest jet, the predictions from {\sc MadGraph5\_aMC\-@NLO} are in good agreement with the other VBS-approximated predictions.
@@
 
-In the end, the quality of the VBS-approximations is good up to $10\%$ in the fiducial region.
-These differences are larger than at LO.
+In the end, the quality of the VBS approximations is good up to $10\%$ in the fiducial region.
+These differences are larger than those at LO.
 
-The contributions from $s$-channel amplitude can be sizeable especially at low invariant mass for the two tagging jet (comparing the predictions of {\sc VBFNLO} against the ones of {\sc Bonsay} and {\sc Powheg}).
+The contributions from the $s$-channel amplitude can be sizeable especially at low invariant mass for the two tagging jets (comparing the predictions of {\sc VBFNLO} against the ones of {\sc Bonsay} and {\sc Powheg}).
 This can be explained by the fact that $s$-channel contributions are less suppressed at NLO.
@@
 
-As the $s$-channel contributions are sizeable, their interferences with the $t$/$u$-channel can be of similar size in the phase-space region where the former are large.
+% As the $s$-channel contributions are sizeable, their interferences with the $t$/$u$-channel can be of similar size in the phase-space region where the former are large.
+In phase-space regions where the $s$-channel contributions are sizeable their interference with the $t/u$-channel can be of similar size.
 This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MadGraph5\_aMC\-@NLO}.

### 2018-03-05 Draft/scanNLO.tex
small fix

@@
 This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
-the difference between the $|t|^2+|u|^2$ approximation and the full computation reaches $30\%$.
+the difference between the $|t|^2+|u|^2$ approximation and the full computation can reach $30\%$.
 The inclusion of $s$-channels cures partly this behaviour in this region.
-Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains.
+Still, for the very low $m_{\Pj\Pj}$ a difference of more than $10\%$ remains.
 This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.

### 2018-03-05 Draft/conclusion.tex
Parton shower/parton-shower should eb consistent everywhere now+comments removed in conclusion

@@
 %%%%and should be representative of the quality of the approximations for other VBS signatures.
-Besides the study of fixed-order predictions, we have also investigated the impact of parton-shower.
+Besides the study of fixed-order predictions, we have also investigated the impact of parton shower.
 To that end, several LO and NLO event generators 
@@
         Therefore, a combined measurement including the EW, QCD, and interference contributions is desirable.
-        \ZM{the following has to be clarified. one way would be to suggest to use  phase-space  cuts to enhance/suppress configurations 
-            where EW/QCD are the dominant contributions}
         Note that with such a measurement a comparison to the SM would
@@
         well-defined Monte-Carlo prediction.
-\MP{I am aware that this might be the most touchy point.
-Therefore we should probably discuss it all together to ensure that we all agree on a definite statement.}
 
     \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguities related to the 
-        matching details and/or the parton-shower employed, we encourage the use of NLO-accurate event generators in experimental analyses.
+        matching details and/or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses.
 

### 2018-03-05 Draft/shower.tex
Parton shower/parton-shower should eb consistent everywhere now+comments removed in conclusion

@@
-We now discuss how different predictions compare when the matching to parton-shower is included. For such
+We now discuss how different predictions compare when the matching to parton shower is included. For such
 a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
@@
 
-In conclusion, the comparison of tools including matching with parton-shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
+In conclusion, the comparison of tools including matching to parton shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
 effectively at NLO accuracy differences between tools are at (or below) the $10\%$ level. 

### 2018-03-05 parton-shower/rivetplot.sh
Add Whizard LOPS data

@@ -114,3 +114,12 @@ rivet-mkhtml -o rivet-LOPS \
 :"ErrorBandColor={[rgb]{0.11,0.62,0.47}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.11,0.62,0.47}}"\
 :"ErrorBandOpacity=0.3"\
+  WHIZARD/WHIZARD_EW_Pyth8223_4M.yoda\
+:"Title=WHIZARD+Pythia 8"\
+:"LineColor={[rgb]{0.01,0.58,0.6}}"\
+:"LineStyle=solid"\
+:"ErrorBands=0"\
+:"ErrorBandColor={[rgb]{0.01,0.58,0.6}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.01,0.58,0.6}}"\
+:"ErrorBandOpacity=0.3"\
+

### 2018-03-05 Draft/shower.tex
aded shower_scale discussion

@@
 leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
-initial scale of the parton shower.\MP{More details/comments there?}
+initial scale of the parton shower (the {\tt scalup} entry of the LHE file). This event-by-event number corresponds 
+to the maximum hardness (translated into the shower evolution variable) of the radiation that 
+can be generated by the shower. \footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense, 
+as it is the case for the factorization and renormalization scales.
+    At NLO, one has the freedom to change the shower scale without losing formal NLO accuracy within the {\sc MC@NLO} matching, 
+    provided the Monte Carlo counterterms are also consistently
+updated. In the {\sc Powheg} matching, the shower scale of the so-called $\tilde B$ events is fixed to the transverse momentum of the radiation 
+generated by the {\sc Powheg} Sudakov, while it can be changed in the remnants events.}
 The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies

### 2018-03-05 Draft/shower.tex
small typos fixed

@@
 can be generated by the shower. \footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense, 
-as it is the case for the factorization and renormalization scales.
+as it is the case for the factorisation and renormalisation scales.
     At NLO, one has the freedom to change the shower scale without losing formal NLO accuracy within the {\sc MC@NLO} matching, 
@@
 updated. In the {\sc Powheg} matching, the shower scale of the so-called $\tilde B$ events is fixed to the transverse momentum of the radiation 
-generated by the {\sc Powheg} Sudakov, while it can be changed in the remnants events.}
+generated according the {\sc Powheg} Sudakov factor, while it can be changed in the remnants events.}
 The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies

### 2018-03-05 Draft/shower.tex
Add WHIZARD LOPS results to shower.tex

--- 2018-03-05 Draft/shower.tex
@@
 {\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
-also {\sc PHANTOM} is used for LO+PS results.\\
+also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
 {\sc MG5\_aMC}, which
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). The same parton showers will be employed for the LO results of {\sc PHANTOM}. For the {\sc Powheg-Box}, the namesake
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
+The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc WHIZARD}.
+For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
         {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3001$ & $0.0002$  \\
+        {\sc WHIZARD}+{\sc Pythia8} &  $1.229$ & $0.001$  \\
     \end{tabular}

### 2018-03-05 parton-shower/rivetplot.sh
Add Whizard LO+PS plots

@@ -1,5 +1,7 @@
 #! /bin/sh
 
+export RIVET_ANALYSIS_PATH=`realpath ../Setup/RivetAnalysis`
+
 cp ../Setup/RivetAnalysis/MC_VBSCAN_MCComparison_NLO.plot ../Setup/RivetAnalysis/MC_VBSCAN_MCComparison.plot
 rivet-mkhtml -o rivet-NLOPS \
   VBFNLO/VBFNLO-NLO.yoda\
@@ -116,10 +118,10 @@ rivet-mkhtml -o rivet-LOPS \
 :"ErrorBandOpacity=0.3"\
   WHIZARD/WHIZARD_EW_Pyth8223_4M.yoda\
 :"Title=WHIZARD+Pythia 8"\
-:"LineColor={[rgb]{0.01,0.58,0.6}}"\
+:"LineColor={[rgb]{0.96,0.50,0.75}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\
-:"ErrorBandColor={[rgb]{0.01,0.58,0.6}}"\
-:"RatioPlotErrorBandColor={[rgb]{0.01,0.58,0.6}}"\
+:"ErrorBandColor={[rgb]{0.96,0.50,0.75}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.96,0.50,0.75}}"\
 :"ErrorBandOpacity=0.3"\
 

### 2018-03-06 Draft/scanLO.tex
End of implementation of Ansgar's comment

@@
 \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-\caption{Ratios of double-differential distributions in the variables the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
+\caption{Ratios of double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
 Ratio of approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
-The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
+The cuts applied are the ones of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
 \label{fig:ratio2d_LO}

### 2018-03-06 Draft/scanNLO.tex

@@
 
-In order to investigate further the jet-pair kinematics, we look at the double-differential distribution in the variables $m_{\Pj\Pj}$ and $\Delta y_{\Pj\Pj}$.
+In order to investigate further the jet-pair kinematics, we look at the double-differential distribution in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
 In particular, we compute in each bin the ratio of the approximated cross sections over the full one.
@@
 {\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-\caption{Ratios of double-differential distributions in the variables the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
+\caption{Ratios of double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
 Ratio of approximated squared amplitudes over the full matrix element.

### 2018-03-06 Draft/shower.tex

@@
 leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
-initial scale of the parton shower.\MP{More details/comments there?}
+initial scale of the parton shower (the {\tt scalup} entry of the LHE file). This event-by-event number corresponds 
+to the maximum hardness (translated into the shower evolution variable) of the radiation that 
+can be generated by the shower. \footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense, 
+as it is the case for the factorisation and renormalisation scales.
+    At NLO, one has the freedom to change the shower scale without losing formal NLO accuracy within the {\sc MC@NLO} matching, 
+    provided the Monte Carlo counterterms are also consistently
+updated. In the {\sc Powheg} matching, the shower scale of the so-called $\tilde B$ events is fixed to the transverse momentum of the radiation 
+generated according the {\sc Powheg} Sudakov factor, while it can be changed in the remnants events.}
 The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies

### 2018-03-06 Draft/shower.tex
minor changes to shower.tex
small changes in shower.tex

@@
 and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
-The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc WHIZARD}.
+The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}.
 For the {\sc Powheg-Box}, the namesake
@@
 are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
-must be employed in order not to bias the results.
+must be employed in order not to bias the results. This also implies that the tagging jets, whose momenta enter in the 
+renormalisation and factorisation scales, Eq.~(\ref{eq:defscale}), are now defined without imposing
+the $\Delta R_{\Pj\Pl}$ cut. The effect of this change is below one per cent at the level of the fiducial cross sections.
 
@@
 the partial and total decay width of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
-an effect ($6\%$) on the normalisation is induced. Finally, when the renormalisation
-and factorisation scales are set, the $\Delta R_{\Pj\Pl}$ cut is not imposed during the jet-clustering procedure.
-This effect is below a per cent at the level of the fiducial cross sections.
+an effect ($6\%$) on the normalisation is induced.
 

### 2018-03-07 Draft/contributions.tex
cosmetic corrections in section 4

@@
 % \AK{We have mentioned this many times at this point. Perhaps not worth repeating again?}.
-In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$, 
+In the present section, the cross sections and distributions are obtained without applying the VBS cuts on the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$, 
 Eq.~(\ref{cut:4}).
@@
 The QCD contribution does not posses external gluons due to charge conservation.
-Thus the diagrams of order $\mathcal{O}(\alphas^2\alpha^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
+Thus the diagrams of order $\mathcal{O}(g_{\rm s}^2g^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
 This results in a small contribution even if the VBS cuts have not been imposed.
@@
 
-In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
+In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
 For the distribution in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
@@
 
-This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a (double-differential) function of the di-jet invariant mass and jet rapidity difference.
-Again, it is obvious that the region with low di-jet invariant mass should be avoided in VBS studies as it is dominated by tri-boson contributions.
+This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as double-differential distributions in the di-jet invariant mass and jet rapidity difference.
+Again, it is clear that the region with low di-jet invariant mass should be avoided in VBS studies as it is dominated by tri-boson contributions.
 % This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).

### 2018-03-07 Draft/shower.tex
included comments by rikkert in shower.tex

@@
 matching. As parton shower, both the default angular-ordered shower as
-well as the dipole shower can be employed.
-Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.
+well as the dipole shower can be employed.\ZM{Which matching scheme is used here in VBFNLO?}
+Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
 
@@
 account, total rates from different tools agree within a few per cent, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
-the following. Before turning to the differential observables, we point out the smallness of the theory uncertainties due to the scale variations, both when
-scales are varied independently and when they are varied in a correlated manner, as well as those due to PDF.
+the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
+independent or correlated variations of the renormalisation and factorisation scales.
 Concerning differential distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
@@
 main effects are driven by the parton shower that is employed ({\sc Herwig++/7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
-leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
+leading to higher jet multiplicities. Differences among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
 initial scale of the parton shower (the {\tt scalup} entry of the LHE file). This event-by-event number corresponds
@@
 The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
-about -30\% at the end of the displayed range.
-At NLO+PS, this effect is much more mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
+about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
 
 The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities to the invariant-mass distribution.
-At LO+PS all predictions,
-except for {\sc VBFNLO+Herwig7} where the effect is mitigated, show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
-quantitatively similar way. At NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
+At LO+PS all predictions show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
+quantitatively similar way,
+except for {\sc VBFNLO+Herwig7} where the effect is mitigated. At 
+NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
 exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations.

### 2018-03-07 Draft/scanNLO.tex

@@
-According to the results shown in Sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails drastically in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
+According to the results shown in Secs.~\ref{subsec:contributions} and \ref{subsec:LOinclusive}, the VBS approximation at LO fails drastically in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
 Therefore, we present an inclusive study at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$ for the set-up described in Sec.~\ref{subsec:inputpar} but imposing $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.

### 2018-03-08 Draft/scanNLO.tex
Typos corrected scanNLO.tex

@@
 the VBS approximation (dubbed $|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
-The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable, and non-factorisable QCD corrections as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
+The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable and non-factorisable QCD corrections, as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
 % This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.
@@
 %
-The $|s|^2+|t|^2+|u|^2$ predictions for $m-{\rm e^+\mu^+}$ agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
+The $|s|^2+|t|^2+|u|^2$ predictions for $m_{\rm e^+\mu^+}$ agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
 The prediction from {\sc Bonsay} is about $10\%$ lower around $1000 \GeV$.

### 2018-03-08 Draft/conclusion.tex
Further corrections of Ansgar
comments by hua-sheng incorporated

@@
 appear for those observables described at a lower accuracy, such as those that involve the third jet.
-These differences appear in the central region where for VBS, and are the largest for those simulations which employ {\sc Pythia8}. The effect
+These differences appear in the central region where for VBS, and are the largest for those simulations which employ {\sc Pythia8}.
+\MP{This sentence does not make sense (one part probably missing)}.
+The effect
 has been understood, and it can be partially mitigated by changing the recoil scheme of the parton shower. These findings make it worth 
@@
         corrections in a multiplicative way. The estimate of missing higher-order EW corrections can be done, 
-        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$, while the missing higher-order mixed QCD-EW corrections 
-        can be estimated by taking the difference between the multiplicative and additive prescription.
+        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$\ZM{$\delta$ is not defined}, while the missing higher-order mixed QCD-EW corrections 
+        can be estimated by taking the difference between the multiplicative and additive prescriptions.
         For more detailed studies of the combination of QCD and EW higher-order corrections, see
@@
         combined measurements should also be presented as they are better defined theoretically. In fact, while at LO 
-        the interference term can be included in the background component, at NLO the separation of EW and QCD component become more blurred, as, \emph{e.g.}\,
+        the interference term can be included in the background component, at NLO the separation of EW and QCD components become more blurred, as, \emph{e.g.}\,
         at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes contribute.

### 2018-03-08 Draft/description.tex
comments by hua-sheng incorporated

@@
 The virtual corrections are additionally approximated using a double-pole approximation.
-For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) are used.
+For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) can also be used.
 
-  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
-      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
+  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\_aMC}) is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
+      including NLO QCD corrections both at fixed order and including matching to parton showers, using the {\sc MC@NLO}\ method~\cite{Frixione:2002ik}.
+It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
         Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
@@
         two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
-        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
+        and tensor-integral reduction~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
         in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
@@
   With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded\footnote{Despite
-            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electroweak corrections, it is not yet possible to compute such corrections
-        with the current version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
+            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing EW corrections, it is not yet possible to compute such corrections
+        with the current public version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-EW process)
         and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
@@
   \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states 
-  at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alphas^2\alpha^4$ including interferences between the two sets of diagrams.
+  at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at  $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
 It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
 The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
-{\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of BSM theories.
+{\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of beyond the Standard Model (BSM) theories.
 
@@
   \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
-    parton-level Monte Carlo for processes with electroweak bosons. It
+    parton-level Monte Carlo for processes with EW bosons. It
     allows the calculation of VBS processes at NLO QCD in the VBS
@@
     $s$-channel contributions are available separately as tri-boson processes with
-    semi-leptonic decays, with process IDs in the 400 range. These can simply
+    semi-leptonic decays, with process IDs in the 400 range\ZM{which range is it?}. These can simply
     be added on top of the VBS contribution. Interferences between the two are therefore neglected.

### 2018-03-08 Draft/input.tex
comments by hua-sheng incorporated

--- 2018-02-28 Draft/input.tex
@@
 The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{
-For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.} 
-NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
+The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.}
+NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
 %Since this PDF set has no photonic density, photon-induced processes are not considered.
@@
 \end{equation}
-The CKM-Matrix is assumed to be diagonal, meaning that the mixing between different quark families is neglected.
+The Cabibbo-Kobayashi-Maskawa matrix is assumed to be diagonal, meaning that the mixing between different quark generations is neglected.
 The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.
 
-The renormalisation and factorisation scales are set to the dynamical scale
+The central value of the renormalisation and factorisation scales is set to 
 %
@@
 %
-defined via the transverse momenta of the two hardest identified jets.\footnote{
-    The renormalisation and factorisation scale employed in the {\sc Powheg-Box} slightly differ from the 
-    one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are i
+defined via the transverse momenta of the two hardest identified jets, event by event.\footnote{The renormalisation and factorisation scales employed in the {\sc Powheg-Box} slightly differ from the 
+    one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are
     employed instead of those of the two hardest jets.\label{foot:powheg}} 

### 2018-03-08 Draft/scanNLO.tex
comments by hua-sheng incorporated

@@
 the VBS approximation (dubbed $|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
-The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable and non-factorisable QCD corrections, as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
+The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable and NF QCD corrections, as well as EW corrections up to $\mathcal{O}(\alphas \alpha^5)$ are included.
 % This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.
@@
 In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
-For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$ per cent.
+For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$.
 % On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
@@
 Still, for the very low $m_{\Pj\Pj}$ a difference of more than $10\%$ remains.
-This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
+This tends to indicate that interference contributions and/or NF QCD corrections play a non-negligible role in this phase-space region.
 
@@
 Differential distributions in the di-jet invariant mass (left) and the rapidity-separation of the two tagging jets (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
@@
 \caption{Ratios of double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
-Ratio of approximated squared amplitudes over the full matrix element.
+Ratio of the approximated squared amplitudes over the full matrix element.
 The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2+|u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2+|t|^2+|u|^2$ (right)
@@
 \caption{Differential distributions in the transverse momentum (left) and rapidity of the hardest tagging jet (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
 In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 

### 2018-03-08 Draft/scanNLO.tex
Rephrasing in section 5.1

--- 2018-03-08 Draft/scanNLO.tex
@@
-According to the results shown in Secs.~\ref{subsec:contributions} and \ref{subsec:LOinclusive}, the VBS approximation at LO fails drastically in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
-Therefore, we present an inclusive study at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$ for the set-up described in Sec.~\ref{subsec:inputpar} but imposing $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
-
-% For the inclusive region (see Eq.~\eqref{eq:inclusive}), this approximation is good up to $\pm10\%$ apart for large di-jet differences and low di-jet invariant mass.
-% It is therefore interesting to check how good this approximation performs at NLO.
-% Thus, we impose the same kinematic cuts shown in Sec.~\ref{subsec:inputpar} and apply the VBS cuts of Eq.~\eqref{eq:inclusive}.
+According to the results of Secs.~\ref{subsec:contributions} and \ref{subsec:LOinclusive}, the VBS approximation at LO fails drastically in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
+Therefore, we present an inclusive study at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$ for the set-up described in Sec.~\ref{subsec:inputpar} but imposing the requirements $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
 
 We compare three different predictions at NLO QCD: 
-the VBS approximation (dubbed $|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
-The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable and non-factorisable QCD corrections, as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
-% This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.
+the VBS approximation implemented in {\sc Bonsay} (dubbed $|t|^2+|u|^2$), the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
+The full computation employs exact matrix elements meaning that $t/u/s$ interferences, factorisable and non-factorisable QCD corrections, as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
 
 The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
-The $|t|^2+|u|^2$ approximation for NLO QCD predictions is lower by about $6\%$ with respect to the full calculation.
-The inclusion of $s$-channel diagrams improves the approximate prediction, leading to a slight excess at the $2\%$-level.
+The $|t|^2+|u|^2$ approximation for NLO QCD predictions is lower by about $6\%$ than the full calculation.
+The inclusion of $s$-channel diagrams improves the approximate prediction, leading to an excess at the $3\%$-level.
 
@@
 \hline
-$|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-6$ \\
+$|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-6.0$ \\
 \hline
-$|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $+2$
+$|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $+2.6$
 \end{tabular}
@@
 
-These differences are much more evident in differential distributions.
-In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
+These differences are more evident in differential distributions.
+In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
 For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$ per cent.
-% On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
-% In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
 This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
-the difference between the $|t|^2+|u|^2$ approximation and the full computation can reach $30\%$.
-The inclusion of $s$-channels cures partly this behaviour in this region.
-Still, for the very low $m_{\Pj\Pj}$ a difference of more than $10\%$ remains.
+the difference between the $|t|^2+|u|^2$ approximation and the full computation can be above $30\%$.
+The inclusion of $s$-channels cures partly this behaviour by rendering the approximation good by about $10\%$.
 This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
-
-In order to investigate further the jet-pair kinematics, we look at the double-differential distribution in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
-In particular, we compute in each bin the ratio of the approximated cross sections over the full one.
-In Fig.~\ref{fig:ratio2d_NLO} we show the ratio $\sigma(|t|^2+|u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2+|u|^2)/\sigma(\textrm{full})$.
 
@@
 
+In order to investigate further the jet-pair kinematics, we study the double-differential distribution in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
+In particular, in Fig.~\ref{fig:ratio2d_NLO}, we compute in each bin the ratios of the approximated cross sections over the full one [$\sigma(|t|^2+|u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2+|u|^2)/\sigma(\textrm{full})$].
+As expected, in the low invariant-mass and low rapidity-separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly (by more than $40\%$).
+Including the $s$-channel contributions leads to a difference of less than $10\%$ in this very region.
+However, in the region of large di-jet invariant mass and low rapidity separation of the jets, the $|s|^2+|t|^2+|u|^2$ approximation overestimate the full computation by more than $40\%$.\footnote{The bin
+in the top-left corner of the right-hand side plot of Fig.~\ref{fig:ratio2d_NLO} suffers from large uncertainty ($30\%$) while the other errors are at the per-cent level.}
+Again, this seems to support the fact that interferences and non-factorisable corrections can be non-negligible in this region.
+On the other hand, in the typical VBS region, the VBS approximation shows a good agreement with the full computation as documented in details in Sec.~\ref{sec:fidNLO}.
+
 \begin{figure*}[hbt]
@@
 \end{figure*}
-%
-% \begin{figure}[hbt]
-% \centering
-% {\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-% \caption{Ratio of cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation with $s$-channel contributions over the full computation.
-% In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
-% \label{fig:mjjdyjj_2d_NLO}
-% \end{figure}
-
-As expected, in the low invariant-mass and low rapidity-separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly (up to $30\%$ discrepancy).
-Including the $s$-channel contributions leads to a difference of $5\%$.
-However, in the region of large di-jet invariant mass and low rapidity separation of the jets, the $|s|^2+|t|^2+|u|^2$ approximation overshoot the full computation by $40\%$.
-On the other hand, in the typical VBS region, the VBS approximation shows a good agreement with the full computation as documented in details in Sec.~\ref{sec:fidNLO}
-
-% However, the positive discrepancy shown in the low $m_{\Pj\Pj}$ region (black curve on the upper plots of Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{\Pj\Pj}$, large $\Delta y_{\Pj\Pj}$ region of Fig.~\ref{fig:ratio2d_NLO}.
-% In this region, the two leading jets have soft transverse momenta, according to the following low-angle approximation
-% 
-% \begin{equation}
-% \begin{split}
-% m_{\Pj_i\Pj_j}^2 &= 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,(\cosh \Delta y_{\Pj_i\Pj_j} - \cos \Delta\phi_{\Pj_i\Pj_j}) \\
-% &\approx 2\,\ptsub{\Pj_i}\ptsub{\Pj_j}\,\cosh \Delta y_{\Pj_i\Pj_j} \,\,.
-% \end{split}
-% \end{equation}
-
-% The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low transverse-momentum region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
-% In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.
-% This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
-% For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.
-% In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.
 
@@
 \begin{equation}
-%  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
   z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
@@
 The prediction from {\sc Bonsay} is about $10\%$ lower around $1000 \GeV$.
-% ; this discrepancy reaches about $20\%$ in the very high mass region. 
-%The discrepancies are roughly constant over the whole spectrum.
-% Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that
-The Zeppenfeld variable of the positron $z_e$ is more strongly affected by the exclusion of $s$-channels.
-% with increasing negative discrepancy with respect to the full result at large values (up to $30\%$ for $z_{e^+}>1.2$).
-% Including $s$-channels makes this discrepancy become positive, but smaller than $10\%$ over the whole spectrum.
-% The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.
-For increasing $z_{\rm e}$, the $|t|^2+|u|^2$ approximation diverges from the full computation to reach about a $25\%$ difference  at $1.5$.
+The Zeppenfeld variable of the positron $z_e$ is more strongly affected by the exclusion of $s$-channel contributions.
+For increasing $z_{\rm e}$, the $|t|^2+|u|^2$ approximation diverges from the full computation to reach a difference of about $25\%$ at $1.5$.
 On the other hand, including $s$-channel contributions leads to a better approximation, staying within $10\%$ difference over the whole range.
@@
 In conclusion, both the loose minimum di-jet invariant mass cut and the inclusion of QCD radiative correction make the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
-% Nevertheless, interferences and non-factorizable QCD corrections should be included to reduce the discrepancies down to about $1\%$, mainly in inclusive analyses.
 In the inclusive region studied here, neglecting $s$-channel, non-factorisable corrections, and electroweak corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.

### 2018-03-08 Draft/contributions.tex

@@
 In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
-For the distribution in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
+For the di-jet invariant-mass  distribution (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
 This is due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
@@
 The EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
-The same holds true for jet rapidity difference larger than $2.5$ (right).
+The same holds true for jet-rapidity difference larger than $2.5$ (right).
 This justifies why cuts on these two observables are used in order to enhance the EW contribution over the QCD one.

### 2018-03-08 Draft/description.tex

@@
       including NLO QCD corrections both at fixed order and including matching to parton showers, using the {\sc MC@NLO}\ method~\cite{Frixione:2002ik}.
-It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
+It makes use of the subtraction method by Frixione-Kunszt and Signer (FKS)~\cite{Frixione:1995ms,
         Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,

### 2018-03-08 Draft/distributionsNLO.tex

@@
 The VBS-approximated predictions ({\sc Bonsay} and {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
-The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
+The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MG5\_aMC}.
 Finally, {\sc VBFNLO} which includes also $s$-channel contributions provides larger predictions at low invariant mass.
@@
 \caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
-The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
-The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
 The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
@@
 Concerning the transverse momentum (left) and rapidity (right) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
-While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it departs from it 
+While {\sc MG5\_aMC} is very close to the full prediction for low transverse momentum, it departs from it 
 at larger transverse momentum by about $10\%$.
@@
 The difference at high transverse momentum between the latter predictions and the full computation can be attributed to EW Sudakov logarithms that become large in this phase-space region.
-While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different at low transverse momentum where it is even higher than the full computation.
-We note that for the transverse momentum of the second hardest jet, the predictions from {\sc MadGraph5\_aMC\-@NLO} are in good agreement with the other VBS-approximated predictions.
+While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very drifferent at low transverse momentum where it is even higher than the full computation.
+We note that for the transverse momentum of the second hardest jet, the predictions from {\sc MG5\_aMC} are in good agreement with the other VBS-approximated predictions.
 % Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.
@@
 \caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
-The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
-The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
 The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
@@
 The predictions of {\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
-The other three VBS approximations are close to each other within few per cent.
+The other three VBS approximations are close to each other within few per cents.
 
@@
 \caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
-The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
-The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
+The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
 The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
@@
 In phase-space regions where the $s$-channel contributions are sizeable their interference with the $t/u$-channel can be of similar size.
-This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MadGraph5\_aMC\-@NLO}.
+This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MG5\_aMC}.
 
-Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
+Finally, the effect of EW corrections and NF contributions in the virtual corrections are usually small.
 But they can be relatively large (about $10\%$) for large transverse momentum of the hardest jet.

### 2018-03-08 Draft/shower.tex

@@
 can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
-restrict ourselves to showing results only in the VBS approximation,
+restrict ourselves to show results only in the VBS approximation,
 {\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
@@
 for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
-Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the BLHA
+Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houcehs Accord
 interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
@@
 is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the PS. Since {\sc MadSpin}\ computes
-the partial and total decay width of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
+the partial and total decay widths of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
 an effect ($6\%$) on the normalisation is induced.
@@
 For the former, we show both PDF and scale uncertainties,\footnote{A preliminary study on PDF uncertainties in VBS has appeared
-in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorization
-scale by a factor of two around its central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
+in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorisation
+scales by a factor of two around the central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
 For the latter, we show the
@@
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within a few per cent, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within a few per cents, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
 the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
@@
 exclusive jet multiplicity
-from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
@@
 invariant mass of the two tagging jets
-from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
@@
 effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of the {\sc Powheg-Box} to suppress the
-hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).\\
+hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).
+
 If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
@@
 rapidity separation of the two tagging jets
-from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
@@
 transverse momentum of the hardest jet
-from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
@@
 transverse momentum of the second-hardest jet
-from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
@@
 rapidity of the second-hardest jet
-from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
@@
 Zeppenfeld variable of the third-hardest jet
-from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond

### 2018-03-08 Draft/description.tex
Undo/modify some corrections of Hua Sheng. I don't like NF, I think we should limit its use to the table.

@@
   \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states 
-  at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at  $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
+  at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
 It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.

### 2018-03-08 Draft/distributionsNLO.tex
Undo/modify some corrections of Hua Sheng. I don't like NF, I think we should limit its use to the table.

@@
 \caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
-The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
@@
 \caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
-The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
@@
 The predictions of {\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
-The other three VBS approximations are close to each other within few per cents.
+The other three VBS approximations are close to each other within few per cent.
 
@@
 \caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
-The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
 The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
@@
 
-Finally, the effect of EW corrections and NF contributions in the virtual corrections are usually small.
+Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
 But they can be relatively large (about $10\%$) for large transverse momentum of the hardest jet.

### 2018-03-09 Draft/description.tex
Fixed some typos and added/changed references

@@
       including NLO QCD corrections both at fixed order and including matching to parton showers, using the {\sc MC@NLO}\ method~\cite{Frixione:2002ik}.
-It makes use of the subtraction method by Frixione-Kunszt and Signer (FKS)~\cite{Frixione:1995ms,
+It makes use of the subtraction method by Frixione, Kunszt and Signer (FKS)~\cite{Frixione:1995ms,
         Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
@@
 
-  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw,Nason:2006hfa} is a framework for matching NLO-QCD calculations with parton showers.
+  \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
 It relies on the user providing the matrix elements and Born phase-space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.

### 2018-03-09 Draft/distributionsNLO.tex
Fixed some typos and added/changed references

@@
 The difference at high transverse momentum between the latter predictions and the full computation can be attributed to EW Sudakov logarithms that become large in this phase-space region.
-While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very drifferent at low transverse momentum where it is even higher than the full computation.
+While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different at low transverse momentum where it is even higher than the full computation.
 We note that for the transverse momentum of the second hardest jet, the predictions from {\sc MG5\_aMC} are in good agreement with the other VBS-approximated predictions.

### 2018-03-09 Draft/process.tex
Fixed some typos and added/changed references

@@
-We now discuss the various approximations which are implemented in computer programs for the EW contribution at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
+We now discuss the various approximations which are implemented in computer programs for the EW contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$.
 Since we are mostly interested in 
@@
 However, this set of contributions is not gauge invariant.
-In order ensure gauge invariance, an on-shell projection of
+In order to ensure gauge invariance, an on-shell projection of
 the incoming and outgoing W bosons should be performed.
@@
 
-A further refinement is to add to the VBS approximation the squared matrix element of the $s$-channel contributions.
+A further refinement is to add the squared matrix element of the $s$-channel contributions to the VBS approximation.
 
@@
 separated any more on the basis of Feynman diagrams, and the
-cancellation of IR singularities requires to include all of them \cite{Biedermann:2017bss}.
+cancellation of IR singularities requires the inclusion of all of them \cite{Biedermann:2017bss}.

### 2018-03-09 Draft/shower.tex
Fixed some typos and added/changed references

@@
         {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
-        {\sc Powheg-Box}  & $1.3642$ & $0.0004$  \\
+        {\sc Powheg-Box}+{\sc Pythia8}  & $1.3642$ & $0.0004$  \\
         {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0\%}_{-1\%}$ & $0.0006$  \\
@@
 is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
-($z_{j_3}<0.5$) is cursed by huge differences between tools. Large differences, reaching a factor 2, persist also away from the central region. \\
+($z_{j_3}<0.5$) is cursed by huge differences between tools.
+Large differences, reaching a factor 2, persist also away from the central region.
+These findings are consistent with behaviour displayed in Refs.~\cite{Jager:2011ms,Jager:2012xk,Jager:2013mu,Jager:2013iza,Schissler:2013nga} where the behaviour of NLO mathcing in VBS processes have been reported.\\
 

### 2018-03-09 Draft/process.tex
Validation of Alexander's changes

@@
-We now discuss the various approximations which are implemented in computer programs for the EW contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$.
+We now discuss the various approximations which are implemented in computer programs for the EW contribution at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
 Since we are mostly interested in 

### 2018-03-09 Draft/conclusion.tex
Further improvements following Alexander's email

@@
         corrections in a multiplicative way. The estimate of missing higher-order EW corrections can be done, 
-        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$\ZM{$\delta$ is not defined}, while the missing higher-order mixed QCD-EW corrections 
+        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$,\footnote{The quantity $\delta_{\rm NLO EW}$ through the relation $\sigma_{\rm NLO EW} = \sigma_{\rm LO} \left(1+ \delta_{\rm NLO EW}\right).$} while the missing higher-order mixed QCD-EW corrections
         can be estimated by taking the difference between the multiplicative and additive prescriptions.

### 2018-03-09 Draft/process.tex
Further improvements following Alexander's email

@@
 The VBS approximation can be extended at NLO in a straightforward manner for what concerns the virtual contributions.
-For the real-emission contributions special care must be taken for the gluon-initiated processes\footnote{The initial-state gluon and quark 
+For the real-emission contributions special care must be taken for the gluon-initiated processes.
+The initial-state gluon and quark 
     must not couple together, otherwise infrared divergences proportional to $s$-channels will appear, 
      which do not match with the ones found in the virtual contributions.
-     The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument presented above.}.
-     \iffalse
-This is implemented in the {\sc Powheg-Box}.
-This approximation can be used in combination with a double-pole approximation \cite{Dittmaier:2015bfe} for the virtual contribution.
-Such an approximation is implemented in {\sc Bonsay}.
-In {\sc VBFNLO}, the $s$-channel contributions are available as well and can be
-added on top of the VBS approximation. For the real emission diagrams, thereby
-as simplification the gluon emission is fully modelled only for initial-state
-radiation\AK{I don't understand this sentence. What does 'thereby' refer to?}. The effect of final-state radiation together with the corresponding
-virtual contributions is included as a $K$-factor. 
-\fi
+     The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument presented above.
+
+% For the real-emission contributions special care must be taken for the gluon-initiated processes\footnote{The initial-state gluon and quark 
+%     must not couple together, otherwise infrared divergences proportional to $s$-channels will appear, 
+%      which do not match with the ones found in the virtual contributions.
+%      The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument presented above.}.
 

### 2018-03-09 Draft/input.tex
Added reference to fastjet

@@
         %
-    \item QCD partons (light quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. %Jets are required to have
+    \item QCD partons (light quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp}, possibly using the {\sc FastJet} implementation~\cite{Cacciari:2011ma}, with distance parameter $R=0.4$.
+%Jets are required to have
     We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons,  

### 2018-03-09 Draft/conclusion.tex
incorporated comments by Giulia

@@
 appear for those observables described at a lower accuracy, such as those that involve the third jet.
-These differences appear in the central region where for VBS, and are the largest for those simulations which employ {\sc Pythia8}.
-\MP{This sentence does not make sense (one part probably missing)}.
+In particular such differences are quite prominent in the central-rapidity region, and are the largest for those simulations which employ {\sc Pythia8}.
 The effect
@@
     \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguities related to the 
-        matching details and/or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses.
+        matching details and/or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses. In doing
+        so, special care should be employed in order to estimate the theoretical uncertainties, as the standard prescription based on 
+        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different generators and/or parton showers should be employed.
 

### 2018-03-09 Draft/crosssectionNLO.tex
comments by hua-sheng incorporated
incorporated comments by Giulia

@@
     The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
-    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.}
+    The uncertainties shown refes to estimated statistical errors of the Monte Carlo integrations.}
 \end{table}
@@
 The second observation is that the inclusion of $s$-channel
-contributions seems to have a significant impact.  Indeed, its
+contributions seems to have a significant impact.  Indeed, their
 inclusion (as done in {\sc VBFNLO}) approximates the full computation

### 2018-03-09 Draft/description.tex
incorporated comments by Giulia

@@
         implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweighting
-        at zero additional CPU cost~\cite{Frederix:2011ss}.\\
+        at negligible additional CPU cost~\cite{Frederix:2011ss}.\\
         The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:

### 2018-03-09 Draft/input.tex
incorporated comments by Giulia

@@
 %
-defined via the transverse momenta of the two hardest identified jets, event by event.\footnote{The renormalisation and factorisation scales employed in the {\sc Powheg-Box} slightly differ from the 
+defined via the transverse momenta of the two hardest jets (identified with the procedure outlined in the following), 
+event by event.\footnote{By default, the renormalisation and factorisation scales employed in the {\sc Powheg-Box} slightly differ from the 
     one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are
@@
         %
-    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
+    \item The total missing transverse momentum, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
         \begin{align}
         \label{cut:2}
-          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
+          %\etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
+          p_{\rm T, miss} >  40\GeV\,.
         \end{align}

### 2018-03-09 Draft/shower.tex
incorporated comments by Giulia

@@
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within a few per cents, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within some or few per cents, respectively at LO and NLO.
+Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
 the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
@@
 exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations.
-Since such a suppression is already there for the {\sc Powheg-no shower} sample,
+Since such a suppression is already there for the {\sc Powheg-no shower} sample (at the LHE level),
 it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
@@
 Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
-on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is
+on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
 generated, \emph{e.g.}\ when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).

### 2018-03-09 Draft/conclusion.tex
minor edits to showers (shower section and conclusion)

@@
 %%%%and should be representative of the quality of the approximations for other VBS signatures.
-Besides the study of fixed-order predictions, we have also investigated the impact of parton shower.
+Besides the study of fixed-order predictions, we have also investigated the impact of parton showering.
 To that end, several LO and NLO event generators 
@@
 The effect
-has been understood, and it can be partially mitigated by changing the recoil scheme of the parton shower. These findings make it worth 
+has been understood, and it can be partially mitigated by changing the recoil scheme of {\sc Pythia8} to distribute momenta within initial-final colour connections. These findings make it worth 
 to further investigate these issues not only in the theoretical community, but also by experimental collaborations, for example by 

### 2018-03-09 Draft/shower.tex
minor edits to showers (shower section and conclusion)

@@
 for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
-Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houcehs Accord
+Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houches Accord
 interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
@@
 matching. As parton shower, both the default angular-ordered shower as
-well as the dipole shower can be employed.\ZM{Which matching scheme is used here in VBFNLO?}
+well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton shower algorithms.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
@@
 
-We now present the results of predictions matched to parton shower.
+We now present the results of predictions matched to parton showers.
 The total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and

### 2018-03-09 Draft/input.tex
second round of comments by giulia

@@
 The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.}
+The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO, as they will lead to top quarks, and not light jets, in the final state.}
 NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}

### 2018-03-09 Draft/shower.tex
second round of comments by giulia

@@
 is different among the two tools. In particular, for the {\sc Powheg-Box}, the first emission is generated with an internal Sudakov form factor (the
-prediction dubbed {\sc Powheg-no shower} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
+prediction dubbed {\sc Powheg-LHE} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
 interplay between the real-emission matrix element and the shower emission.
@@
 exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations.
-Since such a suppression is already there for the {\sc Powheg-no shower} sample (at the LHE level),
+Since such a suppression is already there for the {\sc Powheg-LHE} sample,
 it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
@@
 effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
-the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-no shower} with {\sc Powheg+ Pythia8}. A similar
+the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}. A similar
 behaviour of {\sc Pythia8}
@@
 It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. Again, this stresses the need
+the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. We note 
+that in the only VBF process where NNLO corrections are known, i.e. VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 
+the NLO scale-uncertainty band does not include the NNLO prediction. This suggest that the NLO scale variation 
+underestimates the size of the perturbative uncertainty. Again, this stresses the need
  to employ at least two different tools in order to obtain a conservative estimate of theoretical uncertainties.

### 2018-03-09 Draft/acknowledgements.tex
incorporated comments by Giulia
Add Stefan's acknowledgements

@@
 722104).
-CS acknowledges support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.
+SD and CS acknowledge support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.
 HSS is supported by the ILP Labex (ANR-11-IDEX-0004-02, ANR-10-LABX-63).
+GZ is supported by ERC Consolidator Grant HICCUP (No. 614577).
 MZ is supported by the Netherlands National Organisation for Scientific Research (NWO).

### 2018-03-11 Draft/contributions.tex
Undo/modify some corrections of Hua Sheng. I don't like NF, I think we should limit its use to the table.
incorporated comments by Giulia
Comments of Hua-Sheng (second round)

@@
 The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
-The QCD contribution does not posses external gluons due to charge conservation.
+The QCD contribution does not possess external gluons due to charge conservation.
 Thus the diagrams of order $\mathcal{O}(g_{\rm s}^2g^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
@@
     These results are for the set-up described in Sec.~\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
-    The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.}
+    The uncertainties shown refer to the estimated statistical error of the Monte Carlo integrations.}
 \end{table}
@@
 \caption{Differential distribution in the di-jet invariant mass $m_{\Pj\Pj}$ (left) and the difference of the jet rapidities $|\Delta y_{\Pj\Pj}|$ (right) for the three LO contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
-The EW contribution is in red, the QCD one in green, and the interference one in grey.
+The EW contribution is in red, the QCD one in orange, and the interference one in grey.
 The sum of all the contributions is in blue.

### 2018-03-11 Draft/description.tex
Comments of Hua-Sheng (second round)

@@
         and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
-        For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
-        only loops with QCD-interacting particles are generated. Such an approximation is equivalent to the assumption that the finite part of
+%         For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
+%         only loops with QCD-interacting particles are generated.
+	Only QCD-interacting particles circulating in the loops are generated for the virtual matrix element.
+	The version capable of computing both QCD and EW corrections will be released in the future.
+        Such an approximation is equivalent to the assumption that the finite part of
         those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
@@
 \item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
-It can compute arbitrary processes for the LHC at both NLO QCD and EW accuracy in the Standard Model.
-This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the Standard Model.
+It can compute arbitrary processes at the LHC with both NLO QCD and EW accuracy in the SM.
+This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the SM.
 To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
@@
     \item all $s$- and $t/u$-channel diagrams are included;
-    \item interferences between different diagrams of diagrams ($s/t/u$-channel) are included at LO;
+    \item interferences between diagrams of different types ($s/t/u$-channel) are included at LO;
     \item diagrams which do not feature two resonant vector-bosons are included;

### 2018-03-12 Draft/conclusion.tex
Some extra references added

@@
         the agreement between the approximations and the full calculation is certainly satisfactory given 
-        the current experimental precision, as well as the one foreseen for the near future \ZM{references, etc}.
+        the current experimental precision, as well as the one foreseen for the near future \cite{CMSCollaboration:2015zni,CMS:2016rcn}.
         Nonetheless, care has to be taken when using such approximations, in particular if more inclusive phase-space cuts are used.

### 2018-03-12 Draft/input.tex
Clean-up of the .tex files

--- 2018-03-09 Draft/input.tex
@@
 The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.}
+The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO, as they will lead to top quarks, and not light jets, in the final state.}
 NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
-%Since this PDF set has no photonic density, photon-induced processes are not considered.
 Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.

### 2018-03-12 Draft/acknowledgements.tex

@@
-The authors thank the {\sc Pythia8} authors, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
-discussions and clarifications about the third-jet rapidity spectrum.
+The authors are grateful to the members of the VBSCan collaboration for several discussions and comments to this work. The author also thank
+the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
+discussions and clarifications about the third-jet rapidity spectrum. RF, HSS and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
+they are particularly grateful to Valentin Hirschi for comments to this manuscript.
 
@@
 the BMBF under contract number 05H2015.
+\ZM{The funding bodies should be in alphabetical order following the author's surname}

### 2018-03-12 Draft/article.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent
Start of implementing Ansgar's comments
incorporated comments by Giulia
preprint number
Clean-up of the .tex files
Nikhef number added
VBSCAN preprint
Please enter the commit message for your changes. Lines starting

@@
  \usepackage{dcolumn}
-%  \usepackage{hyperref}
-  \usepackage[draft]{hyperref}
+ \usepackage{hyperref}
+% \usepackage[draft]{hyperref}
  \usepackage{caption}
@@
 
+% to prevent pdftex errors
+\let\oldhref\href
+\renewcommand{\href}[2]{\oldhref{#1}{\hbox{#2}}}
+
 \newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
@@
 
-\input{macros}
+%%%%MACROS
+\newcommand{\Pl}{\ell}
+\newcommand{\fb}{{\ensuremath\unskip\,\text{fb}}\xspace}
+% % new commands for cross referencing
+\def\refeq#1{\mbox{(\ref{#1})}}
+\def\reffi#1{\mbox{Figure~\ref{#1}}}
+\def\reffis#1{\mbox{Figures~\ref{#1}}}
+\def\refta#1{\mbox{Table~\ref{#1}}}
+\def\reftas#1{\mbox{Tables~\ref{#1}}}
+\def\refse#1{\mbox{Section~\ref{#1}}}
+\def\refapp#1{\mbox{App.~\ref{#1}}}
+\def\citere#1{\mbox{Ref.~\cite{#1}}}
+\def\citeres#1{\mbox{Refs.~\cite{#1}}}
+
+\newcommand{\ri}{\mathrm i}
+
+\newcommand{\ie}{\emph{i.e.}\ }
+\newcommand{\eg}{\emph{e.g.}\ }
+
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+
+\newcommand{\qqb}{\ensuremath{q\bar{q}}\xspace}
+\newcommand{\PH}{\ensuremath{\text{H}}\xspace}
+\newcommand{\Pj}{\ensuremath{\text{j}}\xspace}
+\newcommand{\Pp}{\ensuremath{\text{p}}\xspace}
+\newcommand{\Pe}{\ensuremath{\text{e}}\xspace}
+\newcommand{\Pb}{\ensuremath{\text{b}}\xspace}
+\newcommand{\Pq}{\ensuremath{\text{q}}\xspace}
+\newcommand{\Pt}{\ensuremath{\text{t}}\xspace}
+\newcommand{\Pu}{\ensuremath{\text{u}}\xspace}
+\newcommand{\Pd}{\ensuremath{\text{d}}\xspace}
+\newcommand{\Ps}{\ensuremath{\text{s}}\xspace}
+\newcommand{\Pc}{\ensuremath{\text{c}}\xspace}
+\newcommand{\Pg}{\ensuremath{\text{g}}\xspace}
+\newcommand{\Pw}{\ensuremath{\text{w}}\xspace}
+\newcommand{\PW}{\ensuremath{\text{W}}\xspace}
+\newcommand{\PZ}{\ensuremath{\text{Z}}\xspace}
+\newcommand{\Pbj}{\ensuremath{\text{j_b}}\xspace}
+
+\newcommand{\Mt}{\ensuremath{m_\Pt}\xspace}
+\newcommand{\MH}{\ensuremath{M_\PH}\xspace}
+\newcommand{\MWOS}{\ensuremath{M_\PW^\text{OS}}\xspace}
+\newcommand{\MW}{\ensuremath{M_\PW}\xspace}
+\newcommand{\MZOS}{\ensuremath{M_\PZ^\text{OS}}\xspace}
+\newcommand{\MZ}{\ensuremath{M_\PZ}\xspace}
+\newcommand{\Mb}{\ensuremath{m_\Pb}\xspace}
+\newcommand{\Gt}{\ensuremath{\Gamma_\Pt}\xspace}
+\newcommand{\GH}{\ensuremath{\Gamma_\PH}\xspace}
+\newcommand{\GZ}{\ensuremath{\Gamma_\PZ}\xspace}
+\newcommand{\GZOS}{\ensuremath{\Gamma_\PZ^\text{OS}}\xspace}
+\newcommand{\GW}{\ensuremath{\Gamma_\PW}\xspace}
+\newcommand{\GWOS}{\ensuremath{\Gamma_\PW^\text{OS}}\xspace}
+
+\newcommand{\MeV}{\ensuremath{\,\text{MeV}}\xspace}
+\newcommand{\GeV}{\ensuremath{\,\text{GeV}}\xspace}
+\newcommand{\TeV}{\ensuremath{\,\text{TeV}}\xspace}
+
+\newcommand{\alphas}{\ensuremath{\alpha_\text{s}}\xspace}
+\newcommand{\order}[1]{\ensuremath{\mathcal{O}{\left(#1\right)}}\xspace}
+
+\newcommand{\abs}[1]{\left|#1\right|}
+\newcommand{\deltar}{\ensuremath{\Delta R}\xspace}
+
+\newcommand{\GF}{\ensuremath{G_\mu}}
+
+\newcommand{\pt}{\ensuremath{p_\text{T}}\xspace}
+\newcommand{\ptsub}[1]{\ensuremath{p_{\text{T},#1}}\xspace}
+\newcommand{\etsub}[1]{\ensuremath{E_{\text{T},#1}}\xspace}
+
+\renewcommand{\Re}{\mathop{\mathrm{Re}}\nolimits}
+\renewcommand{\Im}{\mathop{\mathrm{Im}}\nolimits}
+
+\newcommand{\MVOS}{\ensuremath{M_{V}^\text{OS}}\xspace}%
+\newcommand{\GVOS}{\ensuremath{\Gamma_{V}^\text{OS}}\xspace}%
+
+\newcommand{\sq}{\tilde{q}}
+\newcommand{\su}{\tilde{u}}
+\newcommand{\sd}{\tilde{d}}
+\newcommand{\gl}{\tilde{g}}
+\def\bom#1{{\mbox{\boldmath $#1$}}}
+\newcommand\nn         {\nonumber}
+\newcommand{\sul}{\tilde{u}_L}
+\newcommand{\scl}{\tilde{c}_L}
+\newcommand{\sdl}{\tilde{d}_L}
+\newcommand{\ssl}{\tilde{s}_L}
+\newcommand{\sur}{\tilde{u}_R}
+%\newcommand{\scr}{\tilde{c}_R}
+\newcommand{\sdr}{\tilde{d}_R}
+\newcommand{\ssr}{\tilde{s}_R}
+\newcommand{\stone}{\tilde{t}_1}
+\newcommand{\sbone}{\tilde{b}_1}
+\newcommand{\sttwo}{\tilde{t}_2}
+\newcommand{\sbtwo}{\tilde{b}_2}
+\newcommand{\neutone}{\tilde{\chi}^0_1}
+\newcommand\sss{\mathchoice%
+{\displaystyle}%
+{\scriptstyle}%
+{\scriptscriptstyle}%
+{\scriptscriptstyle}%
+}
+\newcommand{\newc}{\newcommand}
+% \newc{\be}{\begin{equation}}
+% \newc{\ee}{\end{equation}}
+\newc{\bi}{\begin{itemize}}
+\newc{\ei}{\end{itemize}}
+\newc{\benu}{\begin{enumerate}}
+\newc{\eenu}{\end{enumerate}}
+\newc{\bc}{\begin{center}}
+\newc{\ec}{\end{center}}
+\newc{\bfig}{\begin{figure}}
+\newc{\efig}{\end{figure}}
+\newc{\qbar}{\bar{q}}
+\newc{\go}{\tilde{g}}
+\newc{\PB}{\textsc{Powheg-Box}}
+\newcommand\matB{{\cal B}}
+\newcommand\matR{{\cal R}}
+\newcommand\matV{{\cal V}}
+\newcommand\matO{{\cal O}}
+\newcommand\matF{{\cal F}}
+
+\newcommand{\Recola}{{\sc Recola}\xspace}
+\newcommand{\Sherpa}{{\sc Sherpa}\xspace}
+\newcommand{\Rivet}{{\sc Rivet}\xspace}
+\newcommand{\Amegic}{A\protect\scalebox{0.8}{MEGIC}\xspace}
+\newcommand{\Comix}{C\protect\scalebox{0.8}{OMIX}\xspace}
+\newcommand{\OpenLoops}{O\protect\scalebox{0.8}{PEN}L\protect\scalebox{0.8}{OOPS}\xspace}
+\newcommand{\Njet}{N\protect\scalebox{0.8}{JET}\xspace}
+\newcommand{\BlackHat}{B\protect\scalebox{0.8}{LACK}H\protect\scalebox{0.8}{AT}\xspace}
+\newcommand{\Gosam}{G\protect\scalebox{0.8}{O}S\protect\scalebox{0.8}{AM}\xspace}
+\newcommand{\mocanlo}{{\sc MoCaNLO}\xspace}
+\newcommand{\collier}{{\sc Collier}\xspace}
+\newcommand{\CutTools}{{\sc CutTools}\xspace}
+\newcommand{\OneLOop}{{\sc OneLOop}\xspace}
+%\newcommand{\madgraph}{{\sc\small MadGraph5\_aMC@NLO}\xspace}
+%\newcommand{\madgraphbis}{{\sc\small MG5\_aMC@NLO}\xspace}
+\newcommand{\rT}{{\mathrm{T}}}
+\newcolumntype{.}{D{.}{.}{-1}}
+\newcolumntype{d}[1]{D{.}{.}{#1}}
+
+\renewcommand{\vec}[1]{\mathbf{#1}}
+\colorlet{tableoverheadcolor}{gray!37.5}
+\colorlet{tableheadcolor}{gray!25}
+\colorlet{tablerowcolor}{gray!12.5}
+
+\newcommand{\lsim}
+{\;\raisebox{-.3em}{$\stackrel{\displaystyle <}{\sim}$}\;}
+\newcommand{\gsim}
+{\;\raisebox{-.3em}{$\stackrel{\displaystyle >}{\sim}$}\;}
+\def\asymp#1{\;\raisebox{-.4em}{$\widetilde{\scriptstyle #1}$}\;}
+
+\newlength{\width}
+\newlength{\height}
+\newcommand{\brabar}[1]{%
+    \settoheight{\height}{\ensuremath{#1}}%
+    \settowidth{\width}{\ensuremath{#1}}%
+    \makebox[0pt][l]{\ensuremath{#1}}%
+    \raisebox{1.26ex}{\scalebox{.3}{\textbf{(}}}%
+    \rule[1.41\height]{0.7\width}{0.35pt}%
+    \raisebox{1.26ex}{\scalebox{.3}{\textbf{)}}}%
+}
+
+% modifications for drafts for drafts
+\newcommand{\mpar}[1]{{\marginpar{\hbadness10000%
+                      \sloppy\hfuzz10pt\boldmath\bf\textcolor{red}{#1}}}%
+                      \typeout{marginpar: #1}\ignorespaces}
+\marginparwidth 1.2cm
+\marginparsep 0.2cm
+\def\draftdate{\relax}
+\def\mda{\relax}
+\def\mua{\relax}
+\def\mla{\relax}
+\def\draft{
+\def\thtystars{******************************}
+\def\sixtystars{\thtystars\thtystars}
+\typeout{}
+\typeout{\sixtystars**}
+\typeout{* Draft mode!
+         For final version remove \protect\draft\space in source file *}
+\typeout{\sixtystars**}
+\typeout{}
+\def\draftdate{\today}
+\def\mua{\marginpar[\boldmath\hfil$\uparrow$]%
+                   {\boldmath$\uparrow$\hfil}\color{black}%
+                    \typeout{marginpar: $\uparrow$}\ignorespaces}
+\def\mda{\color{red}\marginpar[\boldmath\hfil$\downarrow$]%
+                   {\boldmath$\downarrow$\hfil}%
+                    \typeout{marginpar: $\downarrow$}\ignorespaces}
+\def\mla{\marginpar[\boldmath\hfil$\rightarrow$]%
+                   {\boldmath$\leftarrow $\hfil}%
+                    \typeout{marginpar: $\leftrightarrow$}\ignorespaces}
+\def\Mua{\marginpar[\boldmath\hfil$\Uparrow$]%
+                   {\boldmath$\Uparrow$\hfil}\color{black}%
+                    \typeout{marginpar: $\uparrow$}\ignorespaces}
+\def\Mda{\color{red}\marginpar[\boldmath\hfil$\Downarrow$]%
+                   {\boldmath$\Downarrow$\hfil}%
+                    \typeout{marginpar: $\downarrow$}\ignorespaces}
+\def\Mla{\marginpar[\boldmath\hfil\textcolor{red}{$\Rightarrow$}]%
+                   {\boldmath\textcolor{red}{$\Leftarrow $}\hfil}%
+                    \typeout{marginpar: $\leftrightarrow$}\ignorespaces}
+\overfullrule 5pt
+\oddsidemargin 15mm
+\marginparwidth 29mm
+}
+
+% switch on draft mode
+%\draft
+
+%%%%END MACROS
 %
-\journalname{DESY 18-025, FR-PHENO-2018-003, KA-TP-05-2018, ZU-TH-08/18} % Preprint numbers here
+\journalname{} % Preprint numbers here
 %
@@
 
-% \thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
-% \thankstext{e2}{e-mail: m.zaro@nikhef.nl}
-
-\institute{
-INFN, Sezione di Torino, %
+\institute{INFN, Sezione di Torino, %
 Via P. Giuria 1, %
@@
 \maketitle
-% \AK{Some general comments: We don't write the names of programs consistently everywhere. I think the nicest is to use}
-% \begin{verbatim} 
-% {\sc Generator}
-% \end{verbatim}
-% \AK{Ie captial first letter and lower-case everywhere else for generator names instead of all capital. But this is a matter of taste of course...}
-% \AK{We may want to make it more clear in the abstract/introduction why this study is worth publishing.
-So focus on the large contributions from non-VBS approxiamtion at NLO which until now has been reproted as small, and the large discrepancies in the NLO+PS predictions.
-That plus the recommendations we give should be the main selling point, I think.}
-\input{abstract}
+
+\begin{abstract}
+  \noindent
+
+  Vector-boson scattering processes are of great importance for the
+  current run-II and future runs of the Large Hadron
+  Collider. The presence of triple and quartic gauge couplings in the
+  process gives access to the gauge sector of the Standard Model and
+  possible new-physics contributions there.  To test this hypothesis,
+  sound knowledge of the Standard Model contributions is necessary,
+  with a precision which at least matches the experimental
+  uncertainties of existing and forthcoming measurements.  In this
+  article we present a detailed study of the vector-boson scattering
+  process with two positively-charged leptons and missing transverse
+  momentum in the final state, mediated predominantly by same-sign
+  production of two $\PW$ bosons with positive charge.  In particular,
+  we first carry out a systematic comparison of the various
+  approximations that are usually performed for this kind of process
+  against the complete calculation, at LO and NLO QCD accuracy. Such a
+  study is performed both in the usual fiducial region used by
+  experimental collaborations and in a more inclusive phase space,
+  where the differences among the various approximations lead to more
+  sizeable effects.  Afterwards, we turn to predictions
+  matched to parton showers, at LO and NLO: we show that on the one
+  hand, the inclusion of NLO QCD corrections lead to more stable
+  predictions, but on the other the details of the matching and of the
+  parton-shower programs lead to differences which are considerably
+  larger than those observed at fixed-order, even in the experimental
+  fiducial region.  We conclude with some recommendations for
+  experimental studies of vector-boson scattering processes.\\[5mm]
+
+  % preprint numbers here
+  \noindent
+  {\small \underline {Preprint numbers:}
+
+  DESY 18-025, FR-PHENO-2018-003, KA-TP-05-2018,
+
+  Nikhef/2018-012, UWTHPH-2018-12, VBSCan-PUB-01-18,
+
+  ZU-TH-08/18}
+\end{abstract}
+\thispagestyle{empty}
+\vfill
+\newpage
+\setcounter{page}{1}
+
+%\tableofcontents
+\newpage
 
 \section{Introduction}
-\input{introduction}
+Vector-boson scattering (VBS) at a hadron collider 
+usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
+radiated by partons (quarks) of the incoming protons, 
+which in turn are deflected from the beam direction 
+and enter the volume of the particle detectors.
+As a consequence, the typical signature of VBS events
+is characterised by two energetic jets 
+and four fermions,
+originating from the decay of the two vector bosons.
+Among the possible diagrams,
+the scattering process can be mediated by a Higgs boson
+and involves in particular its longitudinal component.
+The interaction of longitudinally polarised bosons is of particular interest, 
+because the corresponding matrix elements feature unitarity cancellations 
+that strongly depend on the actual structure of the Higgs sector of the Standard Model (SM).
+A detailed study of this class of processes will therefore further constrain the Higgs couplings 
+at a very different energy scale with respect to the Higgs boson mass,
+and hint at, or exclude, non-Standard Model behaviours.
+
+The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio of all the VBS processes at the Large Hadron Collider (LHC):
+evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
+and it has been recently observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} 
+at $13\TeV$ as well.
+Presently, the measurements of VBS processes are limited by statistics, but the situation will change in the near future.
+On the theoretical side, 
+it is thus of prime importance to provide predictions with systematic uncertainties
+at least comparable to the current and envisaged experimental precision~\cite{CMS:2016rcn}.
+
+$\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
+because the double-charge structure of the leptonic final state 
+limits the number of partonic processes and total number of Feynman diagrams for each process.
+Nonetheless, it possesses all features of VBS at the LHC and is thus representative of other VBS signatures.
+Therefore, it is the ideal candidate for a comparative study of the different simulation tools.
+
+In the last few years, several next-to-leading order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
+All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Denner:2012dz,Oleari:2003tc}.
+Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, 
+making it possible for the first time to study in detail the quality of the VBS approximations at NLO QCD.\footnote{Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
+A similar study has also been made public very recently for the EW production of a Higgs boson in association with 3 jets \cite{Campanario:2018ppz}.}
+
+This article starts with the definition of the VBS process in Sec.~\ref{sec:definition}.
+After having described the approximations of the various computer 
+codes in Sec.~\ref{sec:details}, in Sec.~\ref{sec:LO} a leading-order (LO) study 
+of the different contributions which lead to the production of two same-sign $\PW$ bosons and 
+two jets is performed, as a function of typical VBS cuts. In the same section predictions for VBS from different tools are compared at 
+the level of the cross section and differential distributions. The article continues in Sec.~\ref{sec:NLO} where the comparison is extended to the
+NLO corrections to VBS. The effect of the inclusion of matching LO and NLO computations to parton shower (PS) is 
+discussed in Sec.~\ref{sec:matching}. Finally,
+Sec.~\ref{sec:conclusion} contains a summary of the article and concluding remarks.
 
@@
 \label{sec:definition}
-    \input{definition}
+\begin{figure*}[t]
+\begin{center}
+          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
+          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
+          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
+\end{center}
+        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
+        In addition to typical VBS contributions (left), this order also possesses $s$-channel contributions such as decay chain (middle) and tri-boson contributions (right).}
+\label{diag:LO}
+\end{figure*}
+
+The scattering of two positively-charged $\PW$ bosons with their subsequent decay into different-flavour leptons 
+can proceed at the LHC through the partonic process:
+%
+\begin{equation}
+\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}.
+\end{equation}
+
+This process possesses three LO contributions of different orders.
+At LO, this process can proceed via three different coupling-order combinations:
+$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
+The first, commonly referred to as EW contribution or VBS,\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
+of vector bosons.} receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
+in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
+(center diagram) or from
+triple-boson production (right diagram).
+Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines.
+$s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
+$u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical quarks or anti-quarks in the final state
+The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
+
+When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results.
+We will discuss the commonly-used possible choices in detail in the next section.
+
+The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
+radiated off the quark lines. Because of the different colour structure, this contribution features a 
+different kinematic behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.
+
+Finally, the third contribution is the interference of the two types of amplitudes described above.
+It is non-zero only for those partonic subprocesses which involve identical quarks or antiquarks.
+Such a contribution is typically small (3\%) within typical experimental cuts~\cite{Biedermann:2017bss}.
+
+In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
+These cuts are based on the different kinematical behaviour of the contributions.
+The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
+The two $\PW$ bosons are mostly produced centrally.
+This is in contrast to the QCD contribution which favours jets in the central region.
+Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
+Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes, the separation between EW and QCD production becomes ill
+defined.
+Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.
 
@@
     \label{sec:details}
+    %
     \subsection{Several descriptions for one process}
-        \input{process}
+    We now discuss the various approximations which are implemented in computer programs for the EW contribution at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
+    Since we are mostly interested in 
+    the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, it may appear justified to approximate the 
+    full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
+    However, this set of contributions is not gauge invariant.
+    In order to ensure gauge invariance, an on-shell projection of
+    the incoming and outgoing W bosons should be performed.
+    While this can be done in the usual way for the time-like
+    outgoing W bosons, the treatment of the space-like W bosons
+    emitted from the incoming quarks requires some care.
+    Following Refs.~\cite{Kuss:1995yv,Accomando:2006hq} these W-boson lines can be split,
+    the W bosons entering the scattering process can be projected
+    on-shell, and the emission of the W bosons from the quarks can be
+    described by vector-boson luminosities.
+    Such an approximation is usually called effective vector-boson
+    approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.
+
+    An improvement of such an approximation consists 
+    in considering all $t$- and $u$-channel diagrams and squaring them separately, neglecting interference contributions between the two classes.
+    These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc,Denner:2012dz}.
+    The $s$-channel squared diagrams and any interferences between them and the  $t/u$-channels are also discarded.
+    This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
+    We will adopt the latter denomination in the following of the article.
+    This approximation is gauge-invariant, a fact that can be appreciated by considering the two incoming quarks as belonging to two different copies of the $\rm{SU}(3)$ gauge group.
+
+    A further refinement is to add the squared matrix element of the $s$-channel contributions to the VBS approximation.
+
+    The approximations performed at LO can be extended when NLO QCD corrections to the order $\mathcal{O}{\left(\alpha^{6}\right)}$ are computed.
+    The VBS approximation can be extended at NLO in a straightforward manner for what concerns the virtual contributions.
+    For the real-emission contributions special care must be taken for the gluon-initiated processes.
+    The initial-state gluon and quark 
+        must not couple together, otherwise infrared divergences proportional to $s$-channels will appear, 
+         which do not match with the ones found in the virtual contributions.
+         The subset of diagrams where all couplings of the initial state gluon to initial state quark are neglected forms a gauge-invariant subset, with the same argument presented above.
+
+    A further refinement is to consider the full real contributions, which include all interferences, and part of the virtual.
+    In particular one can consider only one-loop amplitudes where there is no gluon exchange between the two quark lines and 
+    assuming a cancellation of the infrared (IR) poles.
+
+    When considering the NLO corrections of order
+    $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$
+    to the full process, besides real and virtual QCD corrections
+    to the EW tree-level contribution of order
+    $\mathcal{O}{\left(\alpha^{6}\right)}$
+    also real and virtual EW corrections to the LO interference
+    of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$
+    have to be taken into account. Since some loop diagrams contribute
+    to both types of corrections, QCD and EW corrections cannot be
+    separated any more on the basis of Feynman diagrams, and the
+    cancellation of IR singularities requires the inclusion of all of them \cite{Biedermann:2017bss}.
+    %
     \subsection{Description of the predictions}
         \label{subsec:codedescr}
-        \input{description}
+    In the following, the codes employed throughout this paper and the approximations implemented in each of them will be discussed:
+
+    \begin{itemize}
+
+    \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator written by Christopher Schwan and matrix elements taken from different sources:
+    Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
+    One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
+    For the fiducial cross sections it uses the VBS approximation at LO and NLO.
+    The virtual corrections are additionally approximated using a double-pole approximation.
+    For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) can also be used.
+
+      \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\_aMC}) is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
+          including NLO QCD corrections both at fixed order and including matching to parton showers, using the {\sc MC@NLO}\ method~\cite{Frixione:2002ik}.
+It makes use of the subtraction method by Frixione, Kunszt and Signer (FKS)~\cite{Frixione:1995ms,
+            Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
+            Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
+            two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
+            and tensor-integral reduction~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
+            in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
+            Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
+            implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweighting
+            at negligible additional CPU cost~\cite{Frederix:2011ss}.\\
+            The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
+    \begin{verbatim}
+    > set complex_mass_scheme
+    > import model loop_qcd_qed_sm_Gmu
+    > generate p p > e+ ve mu+ vm j j QCD=0 [QCD]
+    > output
+    \end{verbatim}
+      With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded\footnote{Despite
+                the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing EW corrections, it is not yet possible to compute such corrections
+            with the current public version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-EW process)
+            and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
+            Only QCD-interacting particles circulating in the loops are generated for the virtual matrix element.
+            The version capable of computing both QCD and EW corrections will be released in the future.
+            Such an approximation is equivalent to the assumption that the finite part of
+            those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
+            pole-cancellation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
+            {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards\-/FKS\_\-params.dat} file to -1.
+
+    \item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
+    It can compute arbitrary processes at the LHC with both NLO QCD and EW accuracy in the SM.
+    This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the SM.
+    To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
+    In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
+    The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
+    In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained thanks to this tool.
+    One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
+    In {\sc MoCaNLO+Recola} no approximation is performed neither at LO nor at NLO.
+    It implies that, also contributions stemming from EW corrections to the interference are computed.
+
+      \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states 
+      at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
+    It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
+    The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
+    {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of beyond the Standard Model (BSM) theories.
+
+      \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
+    It relies on the user providing the matrix elements and Born phase-space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
+    For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.
+
+      \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
+        parton-level Monte Carlo for processes with EW bosons. It
+        allows the calculation of VBS processes at NLO QCD in the VBS
+        approximation, with process IDs between 200 and 290. The corresponding
+        $s$-channel contributions are available separately as tri-boson processes with
+        semi-leptonic decays, with process IDs in the 400 range\ZM{which range is it?}. These can simply
+        be added on top of the VBS contribution. Interferences between the two are therefore neglected.
+        The usage of leptonic tensors in the calculation, pioneered in
+        Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
+        automatically generated code.  Besides the SM, also a variety of
+        new-physics models including anomalous couplings of the Higgs and gauge
+        bosons can be simulated.
+
+      \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
+          event generator with the LO matrix element generator {\sc O'Mega}.
+\ZM{ if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
+    provides FKS subtraction terms for any NLO process, while virtual matrix
+    elements are provided externally by {\sc
+    OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
+    (\emph{cf.}\ above) can be used as well). {\sc Whizard} allows to simulate a
+    huge number of BSM models as well, in particular in
+    the VBS channel in terms of both higher-dimensional operators as well as explicit
+    resonances.
+
+    \end{itemize}
+
+    We conclude this section by summarising the characteristics of the various codes in Tab.~\ref{tab:wg1_codes}.
+    In particular, it is specified whether
+    \begin{itemize}
+        \item all $s$- and $t/u$-channel diagrams are included;
+        \item interferences between diagrams of different types ($s/t/u$-channel) are included at LO;
+        \item diagrams which do not feature two resonant vector-bosons are included;
+        \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
+            are included;
+        \item EW corrections to the interference of order $\mathcal O (\alpha^5\alphas)$ are included.
+        These corrections are of the same order as the NLO QCD corrections to the contribution of order $\mathcal O (\alpha^6$) term.
+    \end{itemize}
+
+    \begin{table*}[ht!]
+        \footnotesize
+        \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
+            Code  &  $\mathcal O(\alpha^6)$ $s, t, u$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to order $\mathcal O(\alphas \alpha^5)$  \\
+            \hline
+            \hline
+            {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
+            {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+            {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & virt. No &  No \\
+            {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
+            {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
+            {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
+            {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
+        \end{tabularx}
+        \caption{\label{tab:wg1_codes} Summary of the different properties of the computer programs employed in the comparison.}
+    \end{table*}
+    %
     \subsection{Input parameters}
         \label{subsec:inputpar}
-        \input{input}
+    The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
+    The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO, as they will lead to top quarks, and not light jets, in the final state.}
+    NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
+    Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
+
+    For the massive particles, the following masses and decay widths are used:
+    %
+    \begin{alignat}{2}
+                      \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
+                    \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
+                    \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
+                    M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
+    \end{alignat}
+    %
+    The measured on-shell (OS) values for the masses and widths of the W and Z bosons are converted into pole values for the gauge bosons ($V=\PW,\PZ$) according to Ref.~\cite{Bardin:1988xt},
+    %
+    \begin{equation}
+    \begin{split}
+            M_V &= \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,, \\
+       \Gamma_V &= \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
+    \end{split}
+    \end{equation}
+    %
+    The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj}, where
+    %
+    \begin{equation}
+        G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
+    \end{equation}
+    %
+    The numerical value of $\alpha$, corresponding to the choice of input parameters is
+    %
+    \begin{equation}
+     1/\alpha = 132.3572\ldots\,.
+    \end{equation}
+    The Cabibbo-Kobayashi-Maskawa matrix is assumed to be diagonal, meaning that the mixing between different quark generations is neglected.
+    The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.
+
+    The central value of the renormalisation and factorisation scales is set to 
+    %
+    \begin{equation}
+    \label{eq:defscale}
+     \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}, 
+    \end{equation}
+    %
+    defined via the transverse momenta of the two hardest jets (identified with the procedure outlined in the following), 
+    event by event.\footnote{By default, the renormalisation and factorisation scales employed in the {\sc Powheg-Box} slightly differ from the 
+        one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are
+        employed instead of those of the two hardest jets.\label{foot:powheg}} 
+    This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.
+
+    Following experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}, the event selection used in the present study is:
+
+    \begin{itemize}
+        \item The two same-sign charged leptons are required to fulfill cuts on transverse momentum, rapidity, and separation in the rapidity-azimuthal angle separation, 
+            \begin{align}
+            \label{cut:1}
+             \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
+            \end{align}
+            %
+        \item The total missing transverse momentum, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
+            \begin{align}
+            \label{cut:2}
+              %\etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
+              p_{\rm T, miss} >  40\GeV\,.
+            \end{align}
+            %
+        \item QCD partons (light quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp}, possibly using the {\sc FastJet} implementation~\cite{Cacciari:2011ma}, with distance parameter $R=0.4$.
+%Jets are required to have
+        We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons,  
+            \begin{align}
+            \label{cut:3}
+             \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
+            \end{align}
+            VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated. In particular, we impose a cut on the 
+             in\-vari\-ant mass of the di-jet system,  as well as on the rapidity-separation of the two jets,          \begin{align}
+            \label{cut:4}
+             m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5, 
+            \end{align}
+            if not explicitly stated otherwise. 
+            %
+        \item When EW corrections are computed, real photons and charged fermions are clustered together using the anti-$k_T$ algorithm with
+            radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
+    \end{itemize}
 
@@
     \label{sec:LO}
-    \subsection{Three contributions}
+    %
+    \subsection{Contributions}
         \label{subsec:contributions}
-        \input{contributions}
+    In the present section, the cross sections and distributions are obtained without applying the VBS cuts on the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$, 
+    Eq.~(\ref{cut:4}).
+    In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three LO contributions are reported.
+    The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
+    The QCD contribution does not possess external gluons due to charge conservation.
+    Thus the diagrams of order $\mathcal{O}(g_{\rm s}^2g^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
+    This results in a small contribution even if the VBS cuts have not been imposed.
+    The interference between EW and QCD contributions is small, due to color suppression, but not negligible.
+
+    \begin{table}[h!]
+        \centering
+        \begin{tabular}{c|c|c|c}
+            Order & $\mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
+            \hline
+            \hline
+            $\sigma[\rm{fb}]$ & $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
+    %         {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
+        \end{tabular}
+        \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$, obtained with exact matrix elements.
+        These results are for the set-up described in Sec.~\protect\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
+        The uncertainties shown refer to the estimated statistical error of the Monte Carlo integrations.}
+    \end{table}
+
+    In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
+    For the di-jet invariant-mass distribution (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
+    This is due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
+    Note that these contributions are not present in calculations relying on the VBS approximation.
+    The EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
+    The same holds true for jet-rapidity difference larger than $2.5$ (right).
+    This justifies why cuts on these two observables are used in order to enhance the EW contribution over the QCD one.
+    In particular, in order to have a large EW contribution, rather exclusive cuts are required.
+
+    \begin{figure*}[hbt]
+    \centering
+    \includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
+    \includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
+    \caption{Differential distribution in the di-jet invariant mass $m_{\Pj\Pj}$ (left) and the difference of the jet rapidities $|\Delta y_{\Pj\Pj}|$ (right) for the three LO contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
+    The EW contribution is in red, the QCD one in orange, and the interference one in grey.
+    The sum of all the contributions is in blue.
+    The cuts applied are the ones of Sec.~\protect\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.}
+    \label{fig:mjjdyjj_1d}
+    \end{figure*}
+
+    This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as double-differential distributions in the di-jet invariant mass and jet rapidity difference.
+    Again, it is clear that the region with low di-jet invariant mass should be avoided in VBS studies as it is dominated by tri-boson contributions.
+    This motivates in particular the choice of employing the cut $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study in Sec.~\ref{subsec:LOinclusive}.
+
+    \begin{figure*}[hbt]
+    \centering
+    \includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
+    \includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
+    \includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
+    \caption{Double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alphas\alpha^5)$ (top right), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
+    The cuts applied are the ones of Sec.~\protect\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
+    }
+    \label{fig:mjjdyjj_2d_LO}
+    \end{figure*}
+    %
     \subsection{Inclusive comparison}
         \label{subsec:LOinclusive}
-        \input{scanLO}
+    In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the variables  $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
+    Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
+    In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
+    The low rapidity-difference region possesses remnants of the tri-bosons contributions that have a di-jet invariant mass around the $\PW$-boson mass.
+    It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
+    The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
+    The full calculation is approximated at the level of $\pm5\%$ apart in the region where $|\Delta y_{\Pj\Pj}| < 2$.
+
+    \begin{figure*}[hbt]
+    \centering
+    \includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
+    \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
+    \caption{Ratios of double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
+    Ratio of approximated squared amplitudes over the full matrix element.
+    The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
+    The cuts applied are the ones of Sec.~\protect\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
+    \label{fig:ratio2d_LO}
+    \end{figure*}
+    %
     \subsection{Comparison in the fiducial region}
         \label{subsec:LOfiducial}
-        \input{crosssectionLO}
-        \input{distributionsLO}
+    In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy at order $\mathcal{O}(\alpha^6)$ obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
+    We note that several full predictions are not in statistical agreement. These are possibly due to Monte-Carlo 
+    integrators performing too aggressive estimations of statistical uncertainties. Nonetheless, all these predictions agree within less than $0.5\%$.
+    At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
+    This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
+    the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
+    This is in agreement with the findings of Ref.~\cite{Denner:2012dz,Oleari:2003tc}.
+
+    \begin{table}[h!]
+        \centering
+        \begin{tabular}{c|r@{ $\pm$ }l}
+          Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+            \hline
+            \hline
+            {\sc Bonsay}  &  $1.43636$ & $0.00002$ \\
+            {\sc MG5\_aMC}&  $1.4304\phantom{0}$ & $0.0007$ \\
+            {\sc MoCaNLO+Recola}  &  $1.43476$ & $0.00009$ \\
+            {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
+            {\sc Powheg-Box}  &  $1.44092$ & $0.00009$ \\
+            {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
+            {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $
+        \end{tabular}
+        \caption{\label{tab:wg1_LOrates} Cross sections at LO accuracy and order $\mathcal{O}(\alpha^6)$.
+        The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
+        The uncertainties shown refer to the estimated statistical error of the Monte Carlo integrations.}
+    \end{table}
+
+    In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
+    In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
+    for which we also display the scale-uncertainty band (seven-points variation as done in Eq.~(3.11) of Ref.~\cite{Biedermann:2017bss}).
+    For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as interferences are suppressed in the fiducial region.
+    In general, the agreement is at the level of $1\%$ or below in each bin.
+    We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
+    This means that at LO, in the fiducial volume and for energies relevant to the LHC, the VBS approximation is good to a per cent.
+    This is in agreement with the findings of Sec.~\ref{subsec:LOinclusive} as the present comparison completely excludes the phase-space region where tri-boson contributions could have a noticeable impact.
+
+     \begin{figure*}[htb!]
+       \centering
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/mjj_LO.pdf}
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
+    \caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right) at LO accuracy and order $\mathcal{O}(\alpha^6)$.
+    The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
+    The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+    The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
+    \end{figure*}
 
@@
     \label{sec:NLO}
+    %
     \subsection{Inclusive comparision}
         \label{subsec:NLOinclusive}
-        \input{scanNLO}
+    According to the results of Secs.~\ref{subsec:contributions} and \ref{subsec:LOinclusive}, the VBS approximation at LO fails drastically in the region $m_{\Pj\Pj} < 200$ GeV, $|\Delta y_{\Pj\Pj}| < 2$.
+    Therefore, we present an inclusive study at NLO QCD for the EW component, namely the order $\mathcal{O}(\alphas\alpha^6)$ for the set-up described in Sec.~\ref{subsec:inputpar} but imposing the requirements $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
+
+    We compare three different predictions at NLO QCD: 
+    the VBS approximation implemented in {\sc Bonsay} (dubbed $|t|^2+|u|^2$), the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
+    The full computation employs exact matrix elements meaning that $t/u/s$ interferences, factorisable and non-factorisable QCD corrections, as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
+
+    The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
+    The $|t|^2+|u|^2$ approximation for NLO QCD predictions is lower by about $6\%$ than the full calculation.
+    The inclusion of $s$-channel diagrams improves the approximate prediction, leading to an excess at the $3\%$-level.
+
+    \begin{table}[h!]
+    \centering
+    \begin{tabular}{c|c|c}
+    Prediction & $\sigma_{\textrm{tot}}\,[\textrm{fb}]$ & $\delta [\%]$ \\
+    \hline
+    \hline
+    full &  $1.733\phantom{0} \pm 0.002\phantom{0}$ & - \\
+    \hline
+    $|t|^2 + |u|^2$ & $1.6292 \pm 0.0001$  &  $-6.0$ \\
+    \hline
+    $|s|^2 + |t|^2 + |u|^2$ & $1.7780 \pm 0.0001$  & $+2.6$
+    \end{tabular}
+    \caption{Cross sections at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+    In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
+    The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.}
+    \label{tab:crosssecINCLUSIVE}
+    \end{table}
+
+    These differences are more evident in differential distributions.
+    In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
+    For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$.
+    This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
+    the difference between the $|t|^2+|u|^2$ approximation and the full computation can be above $30\%$.
+    The inclusion of $s$-channels cures partly this behaviour by rendering the approximation good by about $10\%$.
+    This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
+
+    \begin{figure*}[hbt]
+    \centering
+    {\includegraphics[scale=0.35]{figures/scanfigures/mjj_nlo.pdf}}
+    {\includegraphics[scale=0.35]{figures/scanfigures/dyjj_nlo.pdf}}
+    \caption{
+    Differential distributions in the di-jet invariant mass (left) and the rapidity-separation of the two tagging jets (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+    In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+    \label{fig:mjjdyjj_1d_1}
+    \end{figure*}
+
+    In order to investigate further the jet-pair kinematics, we study the double-differential distribution in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
+    In particular, in Fig.~\ref{fig:ratio2d_NLO}, we compute in each bin the ratios of the approximated cross sections over the full one [$\sigma(|t|^2+|u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2+|u|^2)/\sigma(\textrm{full})$].
+    As expected, in the low invariant-mass and low rapidity-separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly (by more than $40\%$).
+    Including the $s$-channel contributions leads to a difference of less than $10\%$ in this very region.
+    However, in the region of large di-jet invariant mass and low rapidity separation of the jets, the $|s|^2+|t|^2+|u|^2$ approximation overestimate the full computation by more than $40\%$.\footnote{The bin
+    in the top-left corner of the right-hand side plot of Fig.~\ref{fig:ratio2d_NLO} suffers from large uncertainty ($30\%$) while the other errors are at the per-cent level.}
+    Again, this seems to support the fact that interferences and non-factorisable corrections can be non-negligible in this region.
+    On the other hand, in the typical VBS region, the VBS approximation shows a good agreement with the full computation as documented in details in Sec.~\ref{sec:fidNLO}.
+
+    \begin{figure*}[hbt]
+    \centering
+    {\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}}
+    {\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
+    \caption{Ratios of double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
+    Ratio of the approximated squared amplitudes over the full matrix element.
+    The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2+|u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2+|t|^2+|u|^2$ (right).
+    In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.}
+    \label{fig:ratio2d_NLO}
+    \end{figure*}
+
+    In Fig.~\ref{fig:mjjdyjj_1d_2}, the distributions in the transverse momentum of the hardest jet and its rapidity are shown.
+    At low transverse momentum, $|t|^2+|u|^2$ and $|s|^2+|t|^2+|u|^2$ approximations are lower and higher than the full computation by about $20\%$, respectively.
+    At high transverse momentum, they have a similar behaviour.
+    They both diverge from the full computation towards larger transverse momentum to reach about $10\%$ at $1000\GeV$.
+    Regarding the rapidity of the hardest jet, the two approximations have opposite behaviours.
+    In the central region, the $|t|^2+|u|^2$ approximation differs by $12\%$ with respect to the full computation while the $|s|^2+|t|^2+|u|^2$ one is good within $5\%$.
+    In the peripheral region, the $|t|^2+|u|^2$ approximation is rather close to the full computation ($5\%$) while the $|s|^2+|t|^2+|u|^2$ one differs by $10\%$.
+
+    \begin{figure*}[hbt]
+    \centering
+    {\includegraphics[scale=0.35]{figures/scanfigures/ptj1_nlo.pdf}}
+    {\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
+    \caption{Differential distributions in the transverse momentum (left) and rapidity of the hardest tagging jet (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+    In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+    \label{fig:mjjdyjj_1d_2}
+    \end{figure*}
+
+    Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions in the di-lepton invariant mass and in the Zeppenfeld variable of the electron, defined as
+    %
+    \begin{equation}
+      z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
+      \label{eq:Zeppenfeld}
+    \end{equation}
+    %
+    Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
+    %
+    \begin{figure*}[hbt]
+    \centering
+    {\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
+    {\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
+    \caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+    The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+    In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
+    \label{fig:mjjdyjj_1d_3}
+    \end{figure*}
+    %
+    The $|s|^2+|t|^2+|u|^2$ predictions for $m_{\rm e^+\mu^+}$ agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
+    The prediction from {\sc Bonsay} is about $10\%$ lower around $1000 \GeV$.
+    The Zeppenfeld variable of the positron $z_e$ is more strongly affected by the exclusion of $s$-channel contributions.
+    For increasing $z_{\rm e}$, the $|t|^2+|u|^2$ approximation diverges from the full computation to reach a difference of about $25\%$ at $1.5$.
+    On the other hand, including $s$-channel contributions leads to a better approximation, staying within $10\%$ difference over the whole range.
+
+    In conclusion, both the loose minimum di-jet invariant mass cut and the inclusion of QCD radiative correction make the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
+    In the inclusive region studied here, neglecting $s$-channel, non-factorisable corrections, and electroweak corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.
+    Nevertheless, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($m_{\Pj\Pj} \gtrsim 500 \GeV$, $|\Delta y_{\Pj\Pj}| \gtrsim 2.5$), for both total cross section and differential distributions.
+    This more exclusive region is studied in more details in the next section.
+    %
     \subsection{Comparison in the fiducial region}
-        \input{crosssectionNLO}
-        \input{distributionsNLO}
+    \label{sec:fidNLO}
+    In Tab.~\ref{tab:wg1_NLOrates}, the cross sections of the various tools at NLO-QCD accuracy are presented.
+    The order considered is again the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$ and the fiducial volume is the one described in Sec.~\ref{subsec:inputpar}.
+    In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions differ visibly according to the approximations used.
+
+    \begin{table}[h!]
+        \centering
+        \begin{tabular}{c|r@{ $\pm$ }l}
+          Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+            \hline
+            \hline
+            {\sc Bonsay}  &  $1.35039$ & $0.00006$  \\
+            {\sc Powheg-Box}  &  $1.3605\phantom{0}$  & $0.0007$   \\
+            {\sc MG5\_aMC}&  $1.363\phantom{0}\phantom{0}$ & $0.004$  \\
+            {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ \\
+            {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\
+        \end{tabular}
+        \caption{\label{tab:wg1_NLOrates} Cross sections at NLO accuracy and order $\mathcal{O}(\alphas\alpha^6)$.
+        The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
+        The uncertainties shown refes to estimated statistical errors of the Monte Carlo integrations.}
+    \end{table}
+
+    The first observation is that the predictions featuring two versions
+    of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are
+    relatively close.\footnote{The {\sc VBFNLO}-predictions omitting
+    $s$-channel contributions amounts to $1.3703(1)$ fb. This differs from
+    the {\sc Powheg-Box} prediction mainly due to the different choice of
+    scales used in the {\sc Powheg-Box} (\emph{cf.}
+    footnote \ref{foot:powheg}).} {\sc Bonsay} uses a double-pole
+    approximation for the virtual matrix element, and it is worth noticing
+    that this approximation seems to be accurate at $1\%$ level as
+    compared to the {\sc Powheg-Box}. This means that the double-pole
+    approximation on the two W bosons used in {\sc Bonsay} constitutes a
+    good approximation of the VBS-approxi\-mated virtual corrections
+    implemented in the {\sc Powheg-Box}.  Both predictions differ by about
+    $2\%$ with respect to the full computation ({\sc MoCaNLO+Recola}).
+    The second observation is that the inclusion of $s$-channel
+    contributions seems to have a significant impact.  Indeed, their
+    inclusion (as done in {\sc VBFNLO}) approximates the full computation
+    by less than a per cent ($0.7\%$). The main contribution due to 
+    the $s$-channel diagrams thereby consists of real-emission
+    contributions, where one of the two leading jets is formed by one
+    quark, or possibly also both quarks, originating from the W-boson decay,
+    and the second one by the extra radiation emitted from the initial
+    state. In such configurations, the hadronically-decaying W boson can
+    become on-shell and hence yield larger contributions than at LO, where
+    the invariant mass cut on the two jets forces the boson into the far
+    off-shell region.
+    However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effect and some non-factorisable corrections (in the real corrections) in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
+    Not unexpectedly none of the approximations used here agree perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.
+    Nevertheless, the disagreement seems to never exceed $2\%$ at the fiducial cross section level.
+
+    In Figs.~\ref{fig:distNLO1}--\ref{fig:distNLO3}, several differential distributions are shown.
+    All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alphas\alpha^6)$.
+    In the upper panel, the absolute predictions are shown while in the lower panel, the ratio with respect to the full predictions are displayed.
+    The band corresponds to a seven-points variation of the factorisation and renormalisation scales.
+
+    We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (left) and the rapidity separation (right) of the two tagging jets.
+    For high invariant mass, all predictions agree rather well.
+    On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
+    The VBS-approximated predictions ({\sc Bonsay} and {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
+    The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MG5\_aMC}.
+    Finally, {\sc VBFNLO} which includes also $s$-channel contributions provides larger predictions at low invariant mass.
+    For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.
+    Therefore, depending on the approximation used, it can vary by $\pm7\%$ and $\pm4\%$ with respect to the full computation at low invariant mass and low rapidity difference for the tagging jets, respectively
+
+     \begin{figure*}[hbt!]
+       \centering
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mjj_NLO.pdf}
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
+    \caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
+    The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+    The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
+    The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
+    }
+    \end{figure*}
+
+    Concerning the transverse momentum (left) and rapidity (right) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
+    While {\sc MG5\_aMC} is very close to the full prediction for low transverse momentum, it departs from it 
+    at larger transverse momentum by about $10\%$.
+    This is in contrast with the VBS-approximated predictions such as {\sc Bonsay}, {\sc Powheg}, and {\sc VBFNLO} which are lower than the full computation at low transverse momentum and higher for larger transverse momentum.
+    The difference at high transverse momentum between the latter predictions and the full computation can be attributed to EW Sudakov logarithms that become large in this phase-space region.
+    While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different at low transverse momentum where it is even higher than the full computation.
+    We note that for the transverse momentum of the second hardest jet, the predictions from {\sc MG5\_aMC} are in good agreement with the other VBS-approximated predictions.
+    Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
+    For larger rapidity, the other codes constitute a better description of the full process at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+
+     \begin{figure*}[hbt!]
+       \centering
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/ptj1_NLO.pdf}
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
+    \caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
+    The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+    The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
+    The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
+    }
+    \end{figure*}
+
+    The last set of differential distributions is the invariant mass of the two charged lepton (left) and the Zeppenfeld variable for the anti-muon (right).
+    Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
+    Indeed, the hierarchy mentioned previously is here respected and enhanced towards high invariant mass or high Zeppenfeld variable.
+    The predictions of {\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
+    The other three VBS approximations are close to each other within few per cent.
+
+     \begin{figure*}[hbt!]
+       \centering
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mll_NLO.pdf}
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
+    \caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
+    The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+    The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
+    The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
+    }
+    \end{figure*}
+
+    In the end, the quality of the VBS approximations is good up to $10\%$ in the fiducial region.
+    These differences are larger than those at LO.
+
+    The contributions from the $s$-channel amplitude can be sizeable especially at low invariant mass for the two tagging jets (comparing the predictions of {\sc VBFNLO} against the ones of {\sc Bonsay} and {\sc Powheg}).
+    This can be explained by the fact that $s$-channel contributions are less suppressed at NLO.
+    In the real, an extra gluon-jet can be radiated from any of the charged particles while the two quarks originating from the W-boson decay can be recombined in a single jet.
+    Therefore, the jet requirements ($ m_{\Pj \Pj} >  500\GeV$ and $|\Delta y_{\Pj \Pj}| > 2.5$) that were suppressing $s$-channel contributions at LO are partially lifted with the inclusion of a third jet at NLO.
+    Such an effect has also been observed for top--antitop production in the lepton+jet channel at NLO QCD \cite{Denner:2017kzu}.
+
+    In phase-space regions where the $s$-channel contributions are sizeable their interference with the $t/u$-channel can be of similar size.
+    This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MG5\_aMC}.
+
+    Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
+    But they can be relatively large (about $10\%$) for large transverse momentum of the hardest jet.
+    These high-energy region of the phase space are where EW Sudakov logarithms become large.
+    Nonetheless these regions are rather suppressed and thus these effects are hardly visible at the level of the cross section.
 
@@
     \label{sec:matching}
-    \input{shower}
+We now discuss how different predictions compare when the matching to parton shower is included. For such
+a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
+matching schemes, parton shower employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
+the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
+can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
+restrict ourselves to show results only in the VBS approximation,
+{\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
+also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
+{\sc MG5\_aMC}, which
+employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
+The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}.
+For the {\sc Powheg-Box}, the namesake
+matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
+for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
+Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houches Accord
+interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
+possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
+matching. As parton shower, both the default angular-ordered shower as
+well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton shower algorithms.
+Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
 
-\section{Conclusion}
+Results will be presented within the cuts described in Sec.~\ref{subsec:inputpar}, applied after shower and hadronisation (this implies that jets
+are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
+must be employed in order not to bias the results. This also implies that the tagging jets, whose momenta enter in the 
+renormalisation and factorisation scales, Eq.~(\ref{eq:defscale}), are now defined without imposing
+the $\Delta R_{\Pj\Pl}$ cut. The effect of this change is below one per cent at the level of the fiducial cross sections.
+
+Compared to the fixed order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
+${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is dominated by doubly-resonant contribution, the
+events are produced for the process with two stable ${\rm W}^+$-bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and the decay of these ${\rm W}^+$-bosons
+is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the PS. Since {\sc MadSpin}\ computes
+the partial and total decay widths of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
+an effect ($6\%$) on the normalisation is induced.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|l@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+        \hline\hline
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.352 $ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.343 $ & $ 0.003$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.275$ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.267$ & $ 0.003$  \\
+        {\sc PHANTOM}+{\sc Pythia8} &  $1.235 $ & $0.001$  \\
+        {\sc PHANTOM}+{\sc Herwig++} &  $1.260 $ & $0.001$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3001$ & $0.0002$  \\
+        {\sc WHIZARD}+{\sc Pythia8} &  $1.229$ & $0.001$  \\
+    \end{tabular}
+    \caption{\label{tab:PSratesLO} Cross sections at LO+PS accuracy.
+    The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).
+    The uncertainties shown refers to estimated statistical error of the Monte Carlo integrations.}
+\end{table}
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|l@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+        \hline\hline
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+2\%}_{-1\%} {}^{+2\%}_{-2\%} $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.368$ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
+        {\sc Powheg-Box}+{\sc Pythia8}  & $1.3642$ & $0.0004$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0\%}_{-1\%}$ & $0.0006$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
+    \end{tabular}
+    \caption{\label{tab:PSratesNLO} Cross sections at NLO+PS accuracy.
+    The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
+are respectively the nine-point scale uncertainty and the PDF one.
+The uncertainties shown refers to estimated statistical error of the Monte Carlo integrations.}
+\end{table}
+
+We now present the results of predictions matched to parton showers.
+The total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
+\ref{tab:PSratesNLO}, at LO and NLO
+accuracy respectively. For {\sc MG5\_aMC},
+the numbers with $\Gamma_{\rm resc}$ are rescaled to
+take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
+theoretical uncertainties.
+For the former, we show both PDF and scale uncertainties,\footnote{A preliminary study on PDF uncertainties in VBS has appeared
+in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorisation
+scales by a factor of two around the central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
+For the latter, we show the
+three-point scale uncertainties, obtained by considering correlated variations of the renormalisation and factorisation scales.
+Theory uncertainties should have very little dependence on the tool employed.
+We observe that, once the width effect is taken into
+account, total rates from different tools agree within some or few per cents, respectively at LO and NLO.
+Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
+independent or correlated variations of the renormalisation and factorisation scales.
+Concerning differential distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
+with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
+{\sc VBFNLO}, \emph{i.e.}\ the VBS approximation with $s$-channel).
+For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
+As for the table, we show theoretical uncertainties for the NLO+PS samples
+obtained with {\sc VBFNLO} and {\sc MG5\_aMC}:
+again, for the first the band corresponds to three-point variations, while for the second the darker (lighter) band corresponds to nine-point
+scale variations (plus PDF uncertainties, linearly added).
+
+The first observable we investigate is the exclusive jet multiplicity, shown in Fig.~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
+main effects are driven by the parton shower that is employed ({\sc Herwig++/7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
+leading to higher jet multiplicities. Differences among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
+initial scale of the parton shower (the {\tt scalup} entry of the Les Houches Event (LHE) file \cite{Alwall:2006yp,Butterworth:2010ym}). This event-by-event number corresponds
+to the maximum hardness (translated into the shower evolution variable) of the radiation that
+can be generated by the shower. \footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense,
+as it is the case for the factorisation and renormalisation scales.
+    At NLO, one has the freedom to change the shower scale without losing formal NLO accuracy within the {\sc MC@NLO} matching,
+    provided the Monte Carlo counterterms are also consistently
+updated. In the {\sc Powheg} matching, the shower scale of the so-called $\tilde B$ events is fixed to the transverse momentum of the radiation
+generated according the {\sc Powheg} Sudakov factor, while it can be changed in the remnants events.}
+The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
+among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
+{\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
+is different among the two tools. In particular, for the {\sc Powheg-Box}, the first emission is generated with an internal Sudakov form factor (the
+prediction dubbed {\sc Powheg-LHE} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
+interplay between the real-emission matrix element and the shower emission.
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/jetsexclusive.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
+\caption{Differential distribution in the
+exclusive jet multiplicity
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
+\label{fig:PSnjet}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/m_jj.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/m_jj.pdf}
+\caption{Differential distribution in the
+invariant mass of the two tagging jets
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
+\label{fig:PSmjj}
+\end{figure*}
+
+The next observable that we study is the invariant mass of the two tagging jets, shown in Fig.~\ref{fig:PSmjj}. For this observable, both at LO+PS and NLO+PS,
+the spread of predictions matched with parton shower is rather small
+($\lesssim 10\%$, if one compensates for the $6\%$ width effect for {\sc MG5\_aMC}).
+The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
+about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
+
+The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities to the invariant-mass distribution.
+At LO+PS all predictions show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
+quantitatively similar way,
+except for {\sc VBFNLO+Herwig7} where the effect is mitigated. At 
+NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
+exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations.
+Since such a suppression is already there for the {\sc Powheg-LHE} sample,
+it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
+{\sc MG5\_aMC+Herwig++} prediction (although with rather large statistical uncertainties).
+
+The transverse momentum of the hardest and second-hardest jets are shown in Figs.~\ref{fig:PSpt1} and~\ref{fig:PSpt2}, respectively. In general, for both observables,
+predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transverse-momentum spectra are softer than
+the fixed-NLO ones, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
+effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of the {\sc Powheg-Box} to suppress the
+hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).
+
+If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
+stabilisation at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions
+obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; the {\sc Powheg-Box}\ displays an enhancement of the central region, and a consequent suppression in the
+peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
+at most $10\%$.\footnote{If the setting {\tt SpaceShower:dipole\-Recoil = on} (discussed in the following)
+is used when {\sc Pythia8}\ is employed together with the {\sc Powheg-Box}, the enhancement at central rapidities and the depletion
+at small value of transverse momentum are partially compensated.}
+
+Finally, focusing on the third jet, we conclude the list of differential observables by showing the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Fig.~\ref{fig:PSz3}. This
+variable is closely related to the third jet rapidity, and small (large) values of $z$ correspond to central (peripheral) rapidities. In general, for observables which involve the third jet, one
+can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The Zeppenfeld variable is
+a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation, corresponding to low values of $z$,
+is clearly visible. Such an effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF(VBS)-type processes,
+can be mitigated by setting {\tt SpaceShower:dipole\-Recoil = on} in the {\sc Pythia8} input file.\footnote{This requires version $\ge8.230$.
+Note that such a setting is not compatible with the NLO matching
+in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching). Also, this setting has other
+effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
+the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}. A similar
+behaviour of {\sc Pythia8}
+has also been observed in the study of EW production of a $\PZ$ boson in association with two jets (see the recent CMS measurement,
+Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}.
+The central enhancement
+is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
+($z_{j_3}<0.5$) is cursed by huge differences between tools.
+Large differences, reaching a factor 2, persist also away from the central region.
+These findings are consistent with behaviour displayed in Refs.~\cite{Jager:2011ms,Jager:2012xk,Jager:2013mu,Jager:2013iza,Schissler:2013nga} where the behaviour of NLO mathcing in VBS processes have been reported.\\
+
+In conclusion, the comparison of tools including matching to parton shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
+effectively at NLO accuracy differences between tools are at (or below) the $10\%$ level.
+Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
+on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
+generated, \emph{e.g.}\ when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
+It is a remarkable fact that, even for those observables that display small discrepancies,
+the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. We note 
+that in the only VBF process where NNLO corrections are known, i.e. VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 
+the NLO scale-uncertainty band does not include the NNLO prediction. This suggest that the NLO scale variation 
+underestimates the size of the perturbative uncertainty. Again, this stresses the need
+ to employ at least two different tools in order to obtain a conservative estimate of theoretical uncertainties.
+Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
+experimental analyses should rely as little as possible on those observables and, in any case, use conservative estimate of the theory
+uncertainties. On the one hand, in order to improve the
+description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern
+automated tools, is certainly desirable.
+On the other hand, measurements of processes with similar
+color flow (EW production of a single vector boson plus jets,
+VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data~\cite{Aaboud:2017emo,Sirunyan:2017jej}.
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/Deltay_jj.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/Deltay_jj.pdf}
+\caption{Differential distribution in the
+rapidity separation of the two tagging jets
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
+\label{fig:PSdyjj}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j1.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
+\caption{Differential distribution in the
+transverse momentum of the hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
+\label{fig:PSpt1}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j2.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
+\caption{Differential distribution in the
+transverse momentum of the second-hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
+\label{fig:PSpt2}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j2.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j2.pdf}
+\caption{Differential distribution in the
+rapidity of the second-hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSy2}
+\end{figure*}
+
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/z_j3.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/z_j3.pdf}
+\caption{Differential distribution in the
+Zeppenfeld variable of the third-hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
+\label{fig:PSz3}
+\end{figure*}
+
+\section{Conclusions and recommendations}
 \label{sec:conclusion}
 
-\input{conclusion}
+In the present article, a detailed study of the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC has been presented, 
+mainly focused on the electroweak production mechanism which involves the scattering of massive vector-bosons.
+Until very recently, when the complete calculation became available for the NLO QCD corrections (order $\mathcal O (\alphas\alpha^6)$),
+the so-called VBS approximation was the standard for this kind of simulations. For this reason, various theoretical predictions 
+have been compared to the full computation, both in a typical VBS fiducial region and also in more inclusive phase-space.
+We have precisely quantified the differences that arise for several physical observables, 
+in particular for the di-jet invariant mass and the rapidity-separation of the leading two jets.
+This is the first time that such an in-depth study is performed.
+Besides the study of fixed-order predictions, we have also investigated the impact of parton showering.
+To that end, several LO and NLO event generators 
+which are able to perform matching to parton showers have been employed, and various observables have been thoroughly compared.
+While in general observables which are described at NLO accuracy show reasonable agreement among the tools, larger differences can 
+appear for those observables described at a lower accuracy, such as those that involve the third jet.
+In particular such differences are quite prominent in the central-rapidity region, and are the largest for those simulations which employ {\sc Pythia8}.
+The effect
+has been understood, and it can be partially mitigated by changing the recoil scheme of {\sc Pythia8} to distribute momenta within initial-final colour connections. These findings make it worth 
+to further investigate these issues not only in the theoretical community, but also by experimental collaborations, for example by 
+measuring related observables for similar processes.
+
+The last part of our work is devoted to 
+ remarks and recommendations concerning the usage of theoretical predictions by experimental collaborators.
+\begin{itemize}
+    \item As found in Ref.~\cite{Biedermann:2017bss}, the NLO EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ are 
+        the dominant NLO contribution to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
+        It is thus highly desirable to combine them with NLO-QCD predictions matched with parton shower, or at least that they are accounted for
+        by experimental analyses. Since, as shown in Ref.~\cite{Biedermann:2016yds}, 
+        these large EW corrections originate from the Sudakov logarithms which factorise, we recommend to combine them with QCD 
+        corrections in a multiplicative way. The estimate of missing higher-order EW corrections can be done, 
+        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$,\footnote{The quantity $\delta_{\rm NLO EW}$ through the relation $\sigma_{\rm NLO EW} = \sigma_{\rm LO} \left(1+ \delta_{\rm NLO EW}\right).$} while the missing higher-order mixed QCD-EW corrections
+        can be estimated by taking the difference between the multiplicative and additive prescriptions.
+        For more detailed studies of the combination of QCD and EW higher-order corrections, see
+        \emph{e.g.}\, Ref.~\cite{Czakon:2017wor} in the context of top-pair production, or Ref.~\cite{Lindert:2017olm} for SM 
+        backgrounds for dark matter searches at the LHC.
+    \item For the typical fiducial region used by experimental collaborations for their measurements, 
+        the agreement between the approximations and the full calculation is certainly satisfactory given 
+        the current experimental precision, as well as the one foreseen for the near future \cite{CMSCollaboration:2015zni,CMS:2016rcn}.
+        Nonetheless, care has to be taken when using such approximations, in particular if more inclusive phase-space cuts are used.
+
+    \item In addition to the standard interpretation of EW signal versus QCD background, 
+        combined measurements should also be presented as they are better defined theoretically. In fact, while at LO 
+        the interference term can be included in the background component, at NLO the separation of EW and QCD components become more blurred, as, \emph{e.g.}\,
+        at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes contribute.
+        Therefore, a combined measurement including the EW, QCD, and interference contributions is desirable.
+        Note that with such a measurement a comparison to the SM would
+        be straigtforward and still be sensitive to the EW component.
+        In addition the QCD component could be subtracted based on a
+        well-defined Monte-Carlo prediction.
+
+    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguities related to the 
+        matching details and/or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses. In doing
+        so, special care should be employed in order to estimate the theoretical uncertainties, as the standard prescription based on 
+        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different generators and/or parton showers should be employed.
+
+    \item The present study has focused on the orders $\mathcal{O}{\left(\alpha^{6}\right)}$ at 
+    LO and $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ at NLO.
+NLO computations and publicly-available tools also exist for the QCD-induced process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss,Alwall:2014hca}.
+
+    \item For practical reasons, we have focused on the ${\rm W}^+{\rm W}^+$ signature. Nonetheless, 
+    the observed features 
+    (\emph{e.g.}\ validity of the VBS approximation or comparison of theoretical predictions matched to parton shower) should 
+    be qualitatively similar for other VBS signatures with massive gauge bosons. For these other signatures, similar quantitative studies should be performed.
+\end{itemize}
 
@@
 
-\input{acknowledgements}
+The authors are grateful to the members of the VBSCan collaboration for several discussions and comments to this work. The author also thank
+the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
+discussions and clarifications about the third-jet rapidity spectrum. RF, HSS and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
+they are particularly grateful to Valentin Hirschi for comments to this manuscript.
 
-% \appendix
-% 
-% \section{Appendix one}
+The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
+Moreover, this work was supported by several STSM Grants from the COST Action CA16108.
+Many authors acknowledge hospitality from Nikhef, where part of this work has been performed.
+
+BB, AD, and MP acknowledge financial support by the
+German Federal Ministry for Education and Research (BMBF) under
+contract no.~05H15WWCA1 and the German Science Foundation (DFG) under
+reference number DE 623/6-1.
+SD and CS acknowledge support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.
+AK acknowledges financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
+MR acknowledges funding from the European Union's Horizon 2020 research and innovation programme as part of the Marie Sklodowska-Curie Innovative Training Network MCnetITN3 (grant agreement no.
+722104).
+HSS is supported by the ILP Labex (ANR-11-IDEX-0004-02, ANR-10-LABX-63).
+GZ is supported by ERC Consolidator Grant HICCUP (No. 614577).
+MZ is supported by the Netherlands National Organisation for Scientific Research (NWO).
+The work of BJ was supported in part by the Institutional Strategy of the University of T\"ubingen (DFG, ZUK 63) and in part by
+the BMBF under contract number 05H2015.
 

### 2018-03-12 Draft/old_tex/abstract.tex
Please enter the commit message for your changes. Lines starting

--- 2018-02-22 Draft/article.tex
@@
-%% Main-Version Draft
-\documentclass[twocolumn,epjc3]{svjour3} % use the EPJC template, two columns
-%%\documentclass[epjc3]{svjour3} % use the EPJC template, one column
-\smartqed  % flush right qed marks, e.g. at end of proof
-%% -------------------------------
-%% |          Packages           |
-%% -------------------------------
- \usepackage{amsmath}
- \usepackage{amssymb}
- \usepackage{graphicx}
-  \usepackage[merge,numbers,compress]{natbib}
- \usepackage[T1]{fontenc}
- \usepackage{booktabs}
- \usepackage{xcolor}
- \usepackage{xspace}
- \usepackage{dcolumn}
-%  \usepackage{hyperref}
-  \usepackage[draft]{hyperref}
- \usepackage{caption}
- \usepackage{tabularx}
- \usepackage{lmodern}
- \usepackage{url}
- \usepackage{morefloats}
- \usepackage[utf8]{inputenc}
-%  \usepackage{siunitx}
-% \usepackage
-% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
-% {subcaption}
-\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons}
+\begin{abstract}
+  \noindent
 
-%\setlength{\evensidemargin}{0cm}
-%\setlength{\oddsidemargin}{0cm}
-%\setlength{\topmargin}{0.00cm}
-%\setlength{\textwidth}{16.0cm}
-%\setlength{\textheight}{22.55cm}
-%\setlength{\headheight}{0cm}
-%\setlength{\headsep}{0cm}
-%\setlength{\voffset}{0cm}
-%\setlength{\paperheight}{27cm}
+  Vector-boson scattering processes are of great importance for the
+  current run-II and future runs of the Large Hadron
+  Collider. The presence of triple and quartic gauge couplings in the
+  process gives access to the gauge sector of the Standard Model and
+  possible new-physics contributions there.  To test this hypothesis,
+  sound knowledge of the Standard Model contributions is necessary,
+  with a precision which at least matches the experimental
+  uncertainties of existing and forthcoming measurements.  In this
+  article we present a detailed study of the vector-boson scattering
+  process with two positively-charged leptons and missing transverse
+  momentum in the final state, mediated predominantly by same-sign
+  production of two $\PW$ bosons with positive charge.  In particular,
+  we first carry out a systematic comparison of the various
+  approximations that are usually performed for this kind of process
+  against the complete calculation, at LO and NLO QCD accuracy. Such a
+  study is performed both in the usual fiducial region used by
+  experimental collaborations and in a more inclusive phase space,
+  where the differences among the various approximations lead to more
+  sizeable effects.  Afterwards, we turn to predictions
+  matched to parton showers, at LO and NLO: we show that on the one
+  hand, the inclusion of NLO QCD corrections lead to more stable
+  predictions, but on the other the details of the matching and of the
+  parton-shower programs lead to differences which are considerably
+  larger than those observed at fixed-order, even in the experimental
+  fiducial region.  We conclude with some recommendations for
+  experimental studies of vector-boson scattering processes.
 
-%\renewcommand{\topfraction}{0.8}
-%\renewcommand{\bottomfraction}{0.5}
-%\renewcommand{\textfraction}{0.2}
-%\renewcommand{\floatpagefraction}{0.7}
+\end{abstract}
+\thispagestyle{empty}
+\vfill
+\newpage
+\setcounter{page}{1}
 
-\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
-\newcommand{\MR}[1]{{ {\color{red}{ [MR: #1]}} }}
-\newcommand{\AK}[1]{{ {\color{magenta}{ [AK: #1]}} }}
-\newcommand{\ZM}[1]{{ {\color{green}{ [MZ: #1]}} }}
-
-\newcommand{\BJ}[1]{{ {\color{cyan}{ [BJ: #1]}} }}
-
-%% ---------------------------------
-%% | ToDo Marker - only for draft! |
-%% ---------------------------------
-% Remove this section for final version!
-%\setlength{\marginparwidth}{20mm}
-
-\newcommand{\margtodo}
-{\marginpar{\textbf{\textcolor{red}{ToDo}}}{}}
-
-\newcommand{\todo}[1]
-{{\textbf{\textcolor{red}{(\margtodo{}#1)}}}{}}
-
-\input{macros}
-%
-\journalname{DESY 18-025, FR-PHENO-2018-003, KA-TP-05-2018, ZU-TH-08/18} % Preprint numbers here
-%
-\begin{document}
-
-\title{Precise predictions for same-sign W-boson scattering at the LHC}
-
-\author{Alessandro Ballestrero\thanksref{infnto}
-\and
-Benedikt Biedermann\thanksref{wurz}
-\and
-Simon Brass\thanksref{sieg}
-\and
-Ansgar Denner\thanksref{wurz}
-\and
-Stefan Dittmaier\thanksref{frei}
-\and
-Pietro Govoni\thanksref{mila}
-\and
-Michele Grossi\thanksref{pavia,ibm}
-\and
-Barbara J\"ager\thanksref{tub}
-\and
-Alexander Karlberg\thanksref{uzh}
-\and
-Ezio Maina\thanksref{infnto,unito}
-\and
-Mathieu Pellen\thanksref{wurz}
-\and
-Giovanni Pelliccioli\thanksref{infnto,unito}
-\and
-Simon Pl\"atzer\thanksref{wien}
-\and
-Michael Rauch\thanksref{kit}
-\and
-Daniela Rebuzzi\thanksref{pavia}
-\and
-J\"urgen Reuter\thanksref{desy}
-\and
-Vincent Rothe\thanksref{desy}
-\and
-Christopher Schwan\thanksref{frei}
-\and
-Pascal Stienemeier\thanksref{desy}
-\and
-Giulia Zanderighi\thanksref{cern}
-\and
-Marco Zaro\thanksref{nikh}
-\and
-Dieter Zeppenfeld\thanksref{kit}
-}
-
-% \thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
-% \thankstext{e2}{e-mail: m.zaro@nikhef.nl}
-
-\institute{
-INFN, Sezione di Torino, %
-Via P. Giuria 1, %
-10125 Turin, %
-Italy\label{infnto}
-\and
-Universit\"at W\"urzburg, %
-Institut f\"ur Theoretische Physik und Astrophysik,  %
-Emil-Hilb-Weg 22, %
-97074 W\"urzburg, %
-Germany\label{wurz}
-\and
-Universit\"at Siegen, Department Physik, %
- Walter-Flex-Str.3, %
-57068 Siegen, Germany\label{sieg}
-\and
-Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut, %
- Hermann-Herder-Str.\ 3, %
-79104 Freiburg, Germany\label{frei}
-\and
-University and INFN, Milano-Bicocca, %
-piazza della Scienza, 3, 2016 Milan, %
-Italy\label{mila}
-\and
-Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia, %
-Via A. Bassi 6, %
-27100 Pavia, %
-Italy\label{pavia}
-\and
-IBM Italia s.p.a. %
-Circonvallazione Idroscalo, %
-20090 Segrate (MI), %
-Italy\label{ibm}
-\and
-University of T\"ubingen,
-Institute for Theoretical Physics,
-Auf der Morgenstelle 14,
-72076 T\"ubingen,
-Germany\label{tub}
-\and
-Universit\"at Z\"urich,
-Physik-Institut,
-Winterthurerstrasse 190,
-8057 Z\"urich,
-Switzerland\label{uzh}
-\and
-Universit\`a di Torino, %
-Dipartimento di Fisica, %
-Via P. Giuria 1, %
-10125 Turin, %
-Italy\label{unito}
-\and
-University of Vienna,
-Particle Physics, Faculty of Physics, %
-Vienna, %
-Austria\label{wien}
-\and
-Karlsruhe Institute of Technology (KIT), %
-Institute for Theoretical Physics, %
-76131 Karlsruhe,
-Germany\label{kit}
-\and
-DESY Theory Group, %
-Notkestr. 85, %
-22607 Hamburg,
-Germany\label{desy}
-\and
-CERN,
-Theoretical Physics Department,
-1211, Geneva 23,
-Switzerland\label{cern}
-\and
-Nikhef,
-Science Park 105,
-1098XG Amsterdam,
-The Netherlands\label{nikh}
-}
-
-\maketitle
-% \AK{Some general comments: We don't write the names of programs consistently everywhere. I think the nicest is to use}
-% \begin{verbatim} 
-% {\sc Generator}
-% \end{verbatim}
-% \AK{Ie captial first letter and lower-case everywhere else for generator names instead of all capital. But this is a matter of taste of course...}
-% \AK{We may want to make it more clear in the abstract/introduction why this study is worth publishing.
-So focus on the large contributions from non-VBS approxiamtion at NLO which until now has been reproted as small, and the large discrepancies in the NLO+PS predictions.
-That plus the recommendations we give should be the main selling point, I think.}
-\input{abstract}
-
-\section{Introduction}
-\input{introduction}
-
-\section{Definition of the process}
-    \label{sec:definition}
-    \input{definition}
-
-\section{Details of the calculations}
-    \label{sec:details}
-    \subsection{Several descriptions for one process}
-        \input{process}
-    \subsection{Description of the predictions}
-        \label{subsec:codedescr}
-        \input{description}
-    \subsection{Input parameters}
-        \label{subsec:inputpar}
-        \input{input}
-
-\section{Leading-order study}
-    \label{sec:LO}
-    \subsection{Three contributions}
-        \label{subsec:contributions}
-        \input{contributions}
-    \subsection{Inclusive comparison}
-        \label{subsec:LOinclusive}
-        \input{scanLO}
-    \subsection{Comparison in the fiducial region}
-        \label{subsec:LOfiducial}
-        \input{crosssectionLO}
-        \input{distributionsLO}
-
-\section{Next-to-leading order QCD}
-    \label{sec:NLO}
-    \subsection{Inclusive comparision}
-        \label{subsec:NLOinclusive}
-        \input{scanNLO}
-    \subsection{Comparison in the fiducial region}
-        \input{crosssectionNLO}
-        \input{distributionsNLO}
-
-\section{Matching to parton shower}
-    \label{sec:matching}
-    \input{shower}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\input{conclusion}
-
-\section*{Acknowledgements}
-
-\input{acknowledgements}
-
-% \appendix
-% 
-% \section{Appendix one}
-
-\bibliographystyle{utphys}
-\bibliography{article}
-
-\end{document}
+%\tableofcontents
+\newpage

### 2018-03-12 Draft/old_tex/distributionsLO.tex
Please enter the commit message for your changes. Lines starting

--- 2018-02-22 Draft/article.tex
@@
-%% Main-Version Draft
-\documentclass[twocolumn,epjc3]{svjour3} % use the EPJC template, two columns
-%%\documentclass[epjc3]{svjour3} % use the EPJC template, one column
-\smartqed  % flush right qed marks, e.g. at end of proof
-%% -------------------------------
-%% |          Packages           |
-%% -------------------------------
- \usepackage{amsmath}
- \usepackage{amssymb}
- \usepackage{graphicx}
-  \usepackage[merge,numbers,compress]{natbib}
- \usepackage[T1]{fontenc}
- \usepackage{booktabs}
- \usepackage{xcolor}
- \usepackage{xspace}
- \usepackage{dcolumn}
-%  \usepackage{hyperref}
-  \usepackage[draft]{hyperref}
- \usepackage{caption}
- \usepackage{tabularx}
- \usepackage{lmodern}
- \usepackage{url}
- \usepackage{morefloats}
- \usepackage[utf8]{inputenc}
-%  \usepackage{siunitx}
-% \usepackage
-% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
-% {subcaption}
-\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons}
+In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
+In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
+for which we also display the scale-uncertainty band (seven-points variation as done in Eq.~(3.11) of Ref.~\cite{Biedermann:2017bss}).
+For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as interferences are suppressed in the fiducial region.
+In general, the agreement is at the level of $1\%$ or below in each bin.
+We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
+This means that at LO, in the fiducial volume and for energies relevant to the LHC, the VBS approximation is good to a per cent.
+This is in agreement with the findings of Sec.~\ref{subsec:LOinclusive} as the present comparison completely excludes the phase-space region where tri-boson contributions could have a noticeable impact.
 
-%\setlength{\evensidemargin}{0cm}
-%\setlength{\oddsidemargin}{0cm}
-%\setlength{\topmargin}{0.00cm}
-%\setlength{\textwidth}{16.0cm}
-%\setlength{\textheight}{22.55cm}
-%\setlength{\headheight}{0cm}
-%\setlength{\headsep}{0cm}
-%\setlength{\voffset}{0cm}
-%\setlength{\paperheight}{27cm}
-
-%\renewcommand{\topfraction}{0.8}
-%\renewcommand{\bottomfraction}{0.5}
-%\renewcommand{\textfraction}{0.2}
-%\renewcommand{\floatpagefraction}{0.7}
-
-\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
-\newcommand{\MR}[1]{{ {\color{red}{ [MR: #1]}} }}
-\newcommand{\AK}[1]{{ {\color{magenta}{ [AK: #1]}} }}
-\newcommand{\ZM}[1]{{ {\color{green}{ [MZ: #1]}} }}
-
-\newcommand{\BJ}[1]{{ {\color{cyan}{ [BJ: #1]}} }}
-
-%% ---------------------------------
-%% | ToDo Marker - only for draft! |
-%% ---------------------------------
-% Remove this section for final version!
-%\setlength{\marginparwidth}{20mm}
-
-\newcommand{\margtodo}
-{\marginpar{\textbf{\textcolor{red}{ToDo}}}{}}
-
-\newcommand{\todo}[1]
-{{\textbf{\textcolor{red}{(\margtodo{}#1)}}}{}}
-
-\input{macros}
-%
-\journalname{DESY 18-025, FR-PHENO-2018-003, KA-TP-05-2018, ZU-TH-08/18} % Preprint numbers here
-%
-\begin{document}
-
-\title{Precise predictions for same-sign W-boson scattering at the LHC}
-
-\author{Alessandro Ballestrero\thanksref{infnto}
-\and
-Benedikt Biedermann\thanksref{wurz}
-\and
-Simon Brass\thanksref{sieg}
-\and
-Ansgar Denner\thanksref{wurz}
-\and
-Stefan Dittmaier\thanksref{frei}
-\and
-Pietro Govoni\thanksref{mila}
-\and
-Michele Grossi\thanksref{pavia,ibm}
-\and
-Barbara J\"ager\thanksref{tub}
-\and
-Alexander Karlberg\thanksref{uzh}
-\and
-Ezio Maina\thanksref{infnto,unito}
-\and
-Mathieu Pellen\thanksref{wurz}
-\and
-Giovanni Pelliccioli\thanksref{infnto,unito}
-\and
-Simon Pl\"atzer\thanksref{wien}
-\and
-Michael Rauch\thanksref{kit}
-\and
-Daniela Rebuzzi\thanksref{pavia}
-\and
-J\"urgen Reuter\thanksref{desy}
-\and
-Vincent Rothe\thanksref{desy}
-\and
-Christopher Schwan\thanksref{frei}
-\and
-Pascal Stienemeier\thanksref{desy}
-\and
-Giulia Zanderighi\thanksref{cern}
-\and
-Marco Zaro\thanksref{nikh}
-\and
-Dieter Zeppenfeld\thanksref{kit}
-}
-
-% \thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
-% \thankstext{e2}{e-mail: m.zaro@nikhef.nl}
-
-\institute{
-INFN, Sezione di Torino, %
-Via P. Giuria 1, %
-10125 Turin, %
-Italy\label{infnto}
-\and
-Universit\"at W\"urzburg, %
-Institut f\"ur Theoretische Physik und Astrophysik,  %
-Emil-Hilb-Weg 22, %
-97074 W\"urzburg, %
-Germany\label{wurz}
-\and
-Universit\"at Siegen, Department Physik, %
- Walter-Flex-Str.3, %
-57068 Siegen, Germany\label{sieg}
-\and
-Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut, %
- Hermann-Herder-Str.\ 3, %
-79104 Freiburg, Germany\label{frei}
-\and
-University and INFN, Milano-Bicocca, %
-piazza della Scienza, 3, 2016 Milan, %
-Italy\label{mila}
-\and
-Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia, %
-Via A. Bassi 6, %
-27100 Pavia, %
-Italy\label{pavia}
-\and
-IBM Italia s.p.a. %
-Circonvallazione Idroscalo, %
-20090 Segrate (MI), %
-Italy\label{ibm}
-\and
-University of T\"ubingen,
-Institute for Theoretical Physics,
-Auf der Morgenstelle 14,
-72076 T\"ubingen,
-Germany\label{tub}
-\and
-Universit\"at Z\"urich,
-Physik-Institut,
-Winterthurerstrasse 190,
-8057 Z\"urich,
-Switzerland\label{uzh}
-\and
-Universit\`a di Torino, %
-Dipartimento di Fisica, %
-Via P. Giuria 1, %
-10125 Turin, %
-Italy\label{unito}
-\and
-University of Vienna,
-Particle Physics, Faculty of Physics, %
-Vienna, %
-Austria\label{wien}
-\and
-Karlsruhe Institute of Technology (KIT), %
-Institute for Theoretical Physics, %
-76131 Karlsruhe,
-Germany\label{kit}
-\and
-DESY Theory Group, %
-Notkestr. 85, %
-22607 Hamburg,
-Germany\label{desy}
-\and
-CERN,
-Theoretical Physics Department,
-1211, Geneva 23,
-Switzerland\label{cern}
-\and
-Nikhef,
-Science Park 105,
-1098XG Amsterdam,
-The Netherlands\label{nikh}
-}
-
-\maketitle
-% \AK{Some general comments: We don't write the names of programs consistently everywhere. I think the nicest is to use}
-% \begin{verbatim} 
-% {\sc Generator}
-% \end{verbatim}
-% \AK{Ie captial first letter and lower-case everywhere else for generator names instead of all capital. But this is a matter of taste of course...}
-% \AK{We may want to make it more clear in the abstract/introduction why this study is worth publishing.
-So focus on the large contributions from non-VBS approxiamtion at NLO which until now has been reproted as small, and the large discrepancies in the NLO+PS predictions.
-That plus the recommendations we give should be the main selling point, I think.}
-\input{abstract}
-
-\section{Introduction}
-\input{introduction}
-
-\section{Definition of the process}
-    \label{sec:definition}
-    \input{definition}
-
-\section{Details of the calculations}
-    \label{sec:details}
-    \subsection{Several descriptions for one process}
-        \input{process}
-    \subsection{Description of the predictions}
-        \label{subsec:codedescr}
-        \input{description}
-    \subsection{Input parameters}
-        \label{subsec:inputpar}
-        \input{input}
-
-\section{Leading-order study}
-    \label{sec:LO}
-    \subsection{Three contributions}
-        \label{subsec:contributions}
-        \input{contributions}
-    \subsection{Inclusive comparison}
-        \label{subsec:LOinclusive}
-        \input{scanLO}
-    \subsection{Comparison in the fiducial region}
-        \label{subsec:LOfiducial}
-        \input{crosssectionLO}
-        \input{distributionsLO}
-
-\section{Next-to-leading order QCD}
-    \label{sec:NLO}
-    \subsection{Inclusive comparision}
-        \label{subsec:NLOinclusive}
-        \input{scanNLO}
-    \subsection{Comparison in the fiducial region}
-        \input{crosssectionNLO}
-        \input{distributionsNLO}
-
-\section{Matching to parton shower}
-    \label{sec:matching}
-    \input{shower}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\input{conclusion}
-
-\section*{Acknowledgements}
-
-\input{acknowledgements}
-
-% \appendix
-% 
-% \section{Appendix one}
-
-\bibliographystyle{utphys}
-\bibliography{article}
-
-\end{document}
+ \begin{figure*}[htb!]
+   \centering
+   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/mjj_LO.pdf}
+   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
+\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right) at LO accuracy and order $\mathcal{O}(\alpha^6)$.
+The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
+The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\end{figure*}

### 2018-03-12 Draft/old_tex/introduction.tex
Please enter the commit message for your changes. Lines starting

--- 2018-03-04 Draft/introduction.tex
@@
 
-% {\bf MZ: we can remove the following sentence, up to the citation of Oleari}
-% Apart from Ref.~\cite{Biedermann:2017bss}, no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}.
-
-\iffalse
-The full gauge-invariant process including the $\PW^+\PW^+$ scattering 
- is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
-This final state receives three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
-They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
-\footnote{The EW contribution is sometimes referred to as the VBS contribution, even it involves also non-VBS contributions.}
-\fi
 This article starts with the definition of the VBS process in Sec.~\ref{sec:definition}.
@@
 the level of the cross section and differential distributions. The article continues in Sec.~\ref{sec:NLO} where the comparison is extended to the
-NLO corrections to VBS. The effect of the inclusion of matching LO and NLO computations to parton-shower (PS) is 
+NLO corrections to VBS. The effect of the inclusion of matching LO and NLO computations to parton shower (PS) is 
 discussed in Sec.~\ref{sec:matching}. Finally,
 Sec.~\ref{sec:conclusion} contains a summary of the article and concluding remarks.
-
-\iffalse
-At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
-The largest ones are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
-The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
-The main focus of the paper is the comparison of these corrections, and we will henceforth refer to this order simply as \emph{NLO}.
-As for the LO study, the various predictions are compared at the level of the cross section and differential distributions now at NLO accuracy.
-In particular, this makes it possible to infer the accuracy of the so-called VBS approximation, which we will define in more details later.
-To our knowledge, such a detailed study was still missing. \AK{Vague statement. It is either missing or not. I suggest simply removing the sentence.}
-
-Finally, several parton shower matched predictions are compared, giving the possibility to infer systematic differences between the various parton showers and matching prescriptions.
-A similar study for the $\PW^+ \PW^- \Pj \Pj$ VBS process has been presented in
-Ref.~\cite{Rauch:2016upa}. Here a comparison of the default angular-ordered shower and the dipole
-shower  in {\sc Herwig 7}~\cite{Bellm:2015jjp} was carried out.
-Both {\sc MC@NLO}-like~\cite{Frixione:2002ik} and {\sc Powheg}-like~\cite{Nason:2004rx,Frixione:2007vw} matching was studied.
-In this work we extend such a comparison by presenting
-results obtained by {\sc MadGraph5\_aMC@NLO}, {\sc Powheg} and {\sc Phantom} {\bf CITES} for the $\PW^+ \PW^+ \Pj \Pj$ VBS process, possibly\AK{Why possibly?} matched with different parton-showers.
-This is the first time in the literature that NLO QCD calculations for VBS processes matched to parton shower are compared between different generators.
-
-The article is organised as follows:
-In Sec.~\ref{sec:definition}, we define the VBS process.
-The various approximation which are provided by the different computer codes at LO and NLO are described in Sec.~\ref{sec:details}.
-This is followed by a presentation of the programs used for the computations.
-Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study at fixed order, respectively.
-Section~\ref{sec:matching} complements our study by comparing predictions at LO and NLO which include the effect of parton showers and hadronisation.
-The last section consists of concluding remarks and recommendations for experimental collaborations.
-\fi

### 2018-03-12 Draft/old_tex/scanNLO.tex
Please enter the commit message for your changes. Lines starting

--- 2018-03-08 Draft/scanNLO.tex
@@
 In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
-For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$ per cent.
+For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$.
 This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where

### 2018-03-12 Draft/old_tex/shower.tex
Please enter the commit message for your changes. Lines starting

--- 2018-02-22 Draft/article.tex
@@
-%% Main-Version Draft
-\documentclass[twocolumn,epjc3]{svjour3} % use the EPJC template, two columns
-%%\documentclass[epjc3]{svjour3} % use the EPJC template, one column
-\smartqed  % flush right qed marks, e.g. at end of proof
-%% -------------------------------
-%% |          Packages           |
-%% -------------------------------
- \usepackage{amsmath}
- \usepackage{amssymb}
- \usepackage{graphicx}
-  \usepackage[merge,numbers,compress]{natbib}
- \usepackage[T1]{fontenc}
- \usepackage{booktabs}
- \usepackage{xcolor}
- \usepackage{xspace}
- \usepackage{dcolumn}
-%  \usepackage{hyperref}
-  \usepackage[draft]{hyperref}
- \usepackage{caption}
- \usepackage{tabularx}
- \usepackage{lmodern}
- \usepackage{url}
- \usepackage{morefloats}
- \usepackage[utf8]{inputenc}
-%  \usepackage{siunitx}
-% \usepackage
-% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
-% {subcaption}
-\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons}
+We now discuss how different predictions compare when the matching to parton shower is included. For such
+a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
+matching schemes, parton shower employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
+the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
+can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
+restrict ourselves to show results only in the VBS approximation,
+{\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
+also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
+{\sc MG5\_aMC}, which
+employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
+and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
+The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}.
+For the {\sc Powheg-Box}, the namesake
+matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
+for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
+Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houches Accord
+interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
+possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
+matching. As parton shower, both the default angular-ordered shower as
+well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton shower algorithms.
+Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
 
-%\setlength{\evensidemargin}{0cm}
-%\setlength{\oddsidemargin}{0cm}
-%\setlength{\topmargin}{0.00cm}
-%\setlength{\textwidth}{16.0cm}
-%\setlength{\textheight}{22.55cm}
-%\setlength{\headheight}{0cm}
-%\setlength{\headsep}{0cm}
-%\setlength{\voffset}{0cm}
-%\setlength{\paperheight}{27cm}
+Results will be presented within the cuts described in Sec.~\ref{subsec:inputpar}, applied after shower and hadronisation (this implies that jets
+are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
+must be employed in order not to bias the results. This also implies that the tagging jets, whose momenta enter in the 
+renormalisation and factorisation scales, Eq.~(\ref{eq:defscale}), are now defined without imposing
+the $\Delta R_{\Pj\Pl}$ cut. The effect of this change is below one per cent at the level of the fiducial cross sections.
 
-%\renewcommand{\topfraction}{0.8}
-%\renewcommand{\bottomfraction}{0.5}
-%\renewcommand{\textfraction}{0.2}
-%\renewcommand{\floatpagefraction}{0.7}
+Compared to the fixed order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
+${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is dominated by doubly-resonant contribution, the
+events are produced for the process with two stable ${\rm W}^+$-bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and the decay of these ${\rm W}^+$-bosons
+is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the PS. Since {\sc MadSpin}\ computes
+the partial and total decay widths of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
+an effect ($6\%$) on the normalisation is induced.
 
-\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
-\newcommand{\MR}[1]{{ {\color{red}{ [MR: #1]}} }}
-\newcommand{\AK}[1]{{ {\color{magenta}{ [AK: #1]}} }}
-\newcommand{\ZM}[1]{{ {\color{green}{ [MZ: #1]}} }}
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|l@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+        \hline\hline
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.352 $ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.343 $ & $ 0.003$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.275$ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.267$ & $ 0.003$  \\
+        {\sc PHANTOM}+{\sc Pythia8} &  $1.235 $ & $0.001$  \\
+        {\sc PHANTOM}+{\sc Herwig++} &  $1.260 $ & $0.001$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3001$ & $0.0002$  \\
+        {\sc WHIZARD}+{\sc Pythia8} &  $1.229$ & $0.001$  \\
+    \end{tabular}
+    \caption{\label{tab:PSratesLO} Cross sections at LO+PS accuracy.
+    The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).
+    The uncertainties shown refers to estimated statistical error of the Monte Carlo integrations.}
+\end{table}
 
-\newcommand{\BJ}[1]{{ {\color{cyan}{ [BJ: #1]}} }}
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|l@{ $\pm$ }l}
+      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
+        \hline\hline
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+2\%}_{-1\%} {}^{+2\%}_{-2\%} $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.368$ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
+        {\sc Powheg-Box}+{\sc Pythia8}  & $1.3642$ & $0.0004$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0\%}_{-1\%}$ & $0.0006$  \\
+        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
+    \end{tabular}
+    \caption{\label{tab:PSratesNLO} Cross sections at NLO+PS accuracy.
+    The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$
+    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
+are respectively the nine-point scale uncertainty and the PDF one.
+The uncertainties shown refers to estimated statistical error of the Monte Carlo integrations.}
+\end{table}
 
-%% ---------------------------------
-%% | ToDo Marker - only for draft! |
-%% ---------------------------------
-% Remove this section for final version!
-%\setlength{\marginparwidth}{20mm}
+We now present the results of predictions matched to parton showers.
+The total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
+\ref{tab:PSratesNLO}, at LO and NLO
+accuracy respectively. For {\sc MG5\_aMC},
+the numbers with $\Gamma_{\rm resc}$ are rescaled to
+take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
+theoretical uncertainties.
+For the former, we show both PDF and scale uncertainties,\footnote{A preliminary study on PDF uncertainties in VBS has appeared
+in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorisation
+scales by a factor of two around the central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
+For the latter, we show the
+three-point scale uncertainties, obtained by considering correlated variations of the renormalisation and factorisation scales.
+Theory uncertainties should have very little dependence on the tool employed.
+We observe that, once the width effect is taken into
+account, total rates from different tools agree within some or few per cents, respectively at LO and NLO.
+Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
+independent or correlated variations of the renormalisation and factorisation scales.
+Concerning differential distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
+with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
+{\sc VBFNLO}, \emph{i.e.}\ the VBS approximation with $s$-channel).
+For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above.
+As for the table, we show theoretical uncertainties for the NLO+PS samples
+obtained with {\sc VBFNLO} and {\sc MG5\_aMC}:
+again, for the first the band corresponds to three-point variations, while for the second the darker (lighter) band corresponds to nine-point
+scale variations (plus PDF uncertainties, linearly added).
 
-\newcommand{\margtodo}
-{\marginpar{\textbf{\textcolor{red}{ToDo}}}{}}
+The first observable we investigate is the exclusive jet multiplicity, shown in Fig.~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
+main effects are driven by the parton shower that is employed ({\sc Herwig++/7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
+leading to higher jet multiplicities. Differences among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
+initial scale of the parton shower (the {\tt scalup} entry of the Les Houches Event (LHE) file \cite{Alwall:2006yp,Butterworth:2010ym}). This event-by-event number corresponds
+to the maximum hardness (translated into the shower evolution variable) of the radiation that
+can be generated by the shower. \footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense,
+as it is the case for the factorisation and renormalisation scales.
+    At NLO, one has the freedom to change the shower scale without losing formal NLO accuracy within the {\sc MC@NLO} matching,
+    provided the Monte Carlo counterterms are also consistently
+updated. In the {\sc Powheg} matching, the shower scale of the so-called $\tilde B$ events is fixed to the transverse momentum of the radiation
+generated according the {\sc Powheg} Sudakov factor, while it can be changed in the remnants events.}
+The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
+among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
+{\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
+is different among the two tools. In particular, for the {\sc Powheg-Box}, the first emission is generated with an internal Sudakov form factor (the
+prediction dubbed {\sc Powheg-LHE} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
+interplay between the real-emission matrix element and the shower emission.
 
-\newcommand{\todo}[1]
-{{\textbf{\textcolor{red}{(\margtodo{}#1)}}}{}}
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/jetsexclusive.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
+\caption{Differential distribution in the
+exclusive jet multiplicity
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSnjet}
+\end{figure*}
 
-\input{macros}
-%
-\journalname{DESY 18-025, FR-PHENO-2018-003, KA-TP-05-2018, ZU-TH-08/18} % Preprint numbers here
-%
-\begin{document}
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/m_jj.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/m_jj.pdf}
+\caption{Differential distribution in the
+invariant mass of the two tagging jets
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSmjj}
+\end{figure*}
 
-\title{Precise predictions for same-sign W-boson scattering at the LHC}
+The next observable that we study is the invariant mass of the two tagging jets, shown in Fig.~\ref{fig:PSmjj}. For this observable, both at LO+PS and NLO+PS,
+the spread of predictions matched with parton shower is rather small
+($\lesssim 10\%$, if one compensates for the $6\%$ width effect for {\sc MG5\_aMC}).
+The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
+about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
 
-\author{Alessandro Ballestrero\thanksref{infnto}
-\and
-Benedikt Biedermann\thanksref{wurz}
-\and
-Simon Brass\thanksref{sieg}
-\and
-Ansgar Denner\thanksref{wurz}
-\and
-Stefan Dittmaier\thanksref{frei}
-\and
-Pietro Govoni\thanksref{mila}
-\and
-Michele Grossi\thanksref{pavia,ibm}
-\and
-Barbara J\"ager\thanksref{tub}
-\and
-Alexander Karlberg\thanksref{uzh}
-\and
-Ezio Maina\thanksref{infnto,unito}
-\and
-Mathieu Pellen\thanksref{wurz}
-\and
-Giovanni Pelliccioli\thanksref{infnto,unito}
-\and
-Simon Pl\"atzer\thanksref{wien}
-\and
-Michael Rauch\thanksref{kit}
-\and
-Daniela Rebuzzi\thanksref{pavia}
-\and
-J\"urgen Reuter\thanksref{desy}
-\and
-Vincent Rothe\thanksref{desy}
-\and
-Christopher Schwan\thanksref{frei}
-\and
-Pascal Stienemeier\thanksref{desy}
-\and
-Giulia Zanderighi\thanksref{cern}
-\and
-Marco Zaro\thanksref{nikh}
-\and
-Dieter Zeppenfeld\thanksref{kit}
-}
+The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities to the invariant-mass distribution.
+At LO+PS all predictions show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
+quantitatively similar way,
+except for {\sc VBFNLO+Herwig7} where the effect is mitigated. At 
+NLO+PS, when the extra radiation is described by the real matrix element, such an effect is greatly reduced. A notable
+exception is the {\sc Powheg-Box} prediction, which still shows a suppression at large separations.
+Since such a suppression is already there for the {\sc Powheg-LHE} sample,
+it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
+{\sc MG5\_aMC+Herwig++} prediction (although with rather large statistical uncertainties).
 
-% \thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
-% \thankstext{e2}{e-mail: m.zaro@nikhef.nl}
+The transverse momentum of the hardest and second-hardest jets are shown in Figs.~\ref{fig:PSpt1} and~\ref{fig:PSpt2}, respectively. In general, for both observables,
+predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transverse-momentum spectra are softer than
+the fixed-NLO ones, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
+effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of the {\sc Powheg-Box} to suppress the
+hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).
 
-\institute{
-INFN, Sezione di Torino, %
-Via P. Giuria 1, %
-10125 Turin, %
-Italy\label{infnto}
-\and
-Universit\"at W\"urzburg, %
-Institut f\"ur Theoretische Physik und Astrophysik,  %
-Emil-Hilb-Weg 22, %
-97074 W\"urzburg, %
-Germany\label{wurz}
-\and
-Universit\"at Siegen, Department Physik, %
- Walter-Flex-Str.3, %
-57068 Siegen, Germany\label{sieg}
-\and
-Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut, %
- Hermann-Herder-Str.\ 3, %
-79104 Freiburg, Germany\label{frei}
-\and
-University and INFN, Milano-Bicocca, %
-piazza della Scienza, 3, 2016 Milan, %
-Italy\label{mila}
-\and
-Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia, %
-Via A. Bassi 6, %
-27100 Pavia, %
-Italy\label{pavia}
-\and
-IBM Italia s.p.a. %
-Circonvallazione Idroscalo, %
-20090 Segrate (MI), %
-Italy\label{ibm}
-\and
-University of T\"ubingen,
-Institute for Theoretical Physics,
-Auf der Morgenstelle 14,
-72076 T\"ubingen,
-Germany\label{tub}
-\and
-Universit\"at Z\"urich,
-Physik-Institut,
-Winterthurerstrasse 190,
-8057 Z\"urich,
-Switzerland\label{uzh}
-\and
-Universit\`a di Torino, %
-Dipartimento di Fisica, %
-Via P. Giuria 1, %
-10125 Turin, %
-Italy\label{unito}
-\and
-University of Vienna,
-Particle Physics, Faculty of Physics, %
-Vienna, %
-Austria\label{wien}
-\and
-Karlsruhe Institute of Technology (KIT), %
-Institute for Theoretical Physics, %
-76131 Karlsruhe,
-Germany\label{kit}
-\and
-DESY Theory Group, %
-Notkestr. 85, %
-22607 Hamburg,
-Germany\label{desy}
-\and
-CERN,
-Theoretical Physics Department,
-1211, Geneva 23,
-Switzerland\label{cern}
-\and
-Nikhef,
-Science Park 105,
-1098XG Amsterdam,
-The Netherlands\label{nikh}
-}
+If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
+stabilisation at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions
+obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; the {\sc Powheg-Box}\ displays an enhancement of the central region, and a consequent suppression in the
+peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
+at most $10\%$.\footnote{If the setting {\tt SpaceShower:dipole\-Recoil = on} (discussed in the following)
+is used when {\sc Pythia8}\ is employed together with the {\sc Powheg-Box}, the enhancement at central rapidities and the depletion
+at small value of transverse momentum are partially compensated.}
 
-\maketitle
-% \AK{Some general comments: We don't write the names of programs consistently everywhere. I think the nicest is to use}
-% \begin{verbatim} 
-% {\sc Generator}
-% \end{verbatim}
-% \AK{Ie captial first letter and lower-case everywhere else for generator names instead of all capital. But this is a matter of taste of course...}
-% \AK{We may want to make it more clear in the abstract/introduction why this study is worth publishing.
-So focus on the large contributions from non-VBS approxiamtion at NLO which until now has been reproted as small, and the large discrepancies in the NLO+PS predictions.
-That plus the recommendations we give should be the main selling point, I think.}
-\input{abstract}
+Finally, focusing on the third jet, we conclude the list of differential observables by showing the Zeppenfeld variable defined in Eq.~\eqref{eq:Zeppenfeld}, Fig.~\ref{fig:PSz3}. This
+variable is closely related to the third jet rapidity, and small (large) values of $z$ correspond to central (peripheral) rapidities. In general, for observables which involve the third jet, one
+can clearly see a degradation of the agreement among the various tools, because of the poorer perturbative description of these observables. The Zeppenfeld variable is
+a striking example: both at LO and NLO, the tendency of {\sc Pythia8} to generate more hard and central radiation, corresponding to low values of $z$,
+is clearly visible. Such an effect, which is related to the way {\sc Pythia8} deals with the recoil of the radiation in VBF(VBS)-type processes,
+can be mitigated by setting {\tt SpaceShower:dipole\-Recoil = on} in the {\sc Pythia8} input file.\footnote{This requires version $\ge8.230$.
+Note that such a setting is not compatible with the NLO matching
+in {\sc MG5\_aMC} (but it is compatible with the {\sc Powheg} matching). Also, this setting has other
+effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
+the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}. A similar
+behaviour of {\sc Pythia8}
+has also been observed in the study of EW production of a $\PZ$ boson in association with two jets (see the recent CMS measurement,
+Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}.
+The central enhancement
+is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediction), however even at NLO+PS the central region
+($z_{j_3}<0.5$) is cursed by huge differences between tools.
+Large differences, reaching a factor 2, persist also away from the central region.
+These findings are consistent with behaviour displayed in Refs.~\cite{Jager:2011ms,Jager:2012xk,Jager:2013mu,Jager:2013iza,Schissler:2013nga} where the behaviour of NLO mathcing in VBS processes have been reported.\\
 
-\section{Introduction}
-\input{introduction}
+In conclusion, the comparison of tools including matching to parton shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
+effectively at NLO accuracy differences between tools are at (or below) the $10\%$ level.
+Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
+on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
+generated, \emph{e.g.}\ when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
+It is a remarkable fact that, even for those observables that display small discrepancies,
+the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. We note 
+that in the only VBF process where NNLO corrections are known, i.e. VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 
+the NLO scale-uncertainty band does not include the NNLO prediction. This suggest that the NLO scale variation 
+underestimates the size of the perturbative uncertainty. Again, this stresses the need
+ to employ at least two different tools in order to obtain a conservative estimate of theoretical uncertainties.
+Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
+experimental analyses should rely as little as possible on those observables and, in any case, use conservative estimate of the theory
+uncertainties. On the one hand, in order to improve the
+description of these observables, a simulation of VBS+j at NLO accuracy, currently unavailable but within the reach of modern
+automated tools, is certainly desirable.
+On the other hand, measurements of processes with similar
+color flow (EW production of a single vector boson plus jets,
+VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data~\cite{Aaboud:2017emo,Sirunyan:2017jej}.
 
-\section{Definition of the process}
-    \label{sec:definition}
-    \input{definition}
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/Deltay_jj.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/Deltay_jj.pdf}
+\caption{Differential distribution in the
+rapidity separation of the two tagging jets
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSdyjj}
+\end{figure*}
 
-\section{Details of the calculations}
-    \label{sec:details}
-    \subsection{Several descriptions for one process}
-        \input{process}
-    \subsection{Description of the predictions}
-        \label{subsec:codedescr}
-        \input{description}
-    \subsection{Input parameters}
-        \label{subsec:inputpar}
-        \input{input}
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j1.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
+\caption{Differential distribution in the
+transverse momentum of the hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSpt1}
+\end{figure*}
 
-\section{Leading-order study}
-    \label{sec:LO}
-    \subsection{Three contributions}
-        \label{subsec:contributions}
-        \input{contributions}
-    \subsection{Inclusive comparison}
-        \label{subsec:LOinclusive}
-        \input{scanLO}
-    \subsection{Comparison in the fiducial region}
-        \label{subsec:LOfiducial}
-        \input{crosssectionLO}
-        \input{distributionsLO}
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j2.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
+\caption{Differential distribution in the
+transverse momentum of the second-hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSpt2}
+\end{figure*}
 
-\section{Next-to-leading order QCD}
-    \label{sec:NLO}
-    \subsection{Inclusive comparision}
-        \label{subsec:NLOinclusive}
-        \input{scanNLO}
-    \subsection{Comparison in the fiducial region}
-        \input{crosssectionNLO}
-        \input{distributionsNLO}
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j2.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j2.pdf}
+\caption{Differential distribution in the
+rapidity of the second-hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSy2}
+\end{figure*}
 
-\section{Matching to parton shower}
-    \label{sec:matching}
-    \input{shower}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\input{conclusion}
-
-\section*{Acknowledgements}
-
-\input{acknowledgements}
-
-% \appendix
-% 
-% \section{Appendix one}
-
-\bibliographystyle{utphys}
-\bibliography{article}
-
-\end{document}
+\begin{figure*}[hbt]
+\centering
+\includegraphics[width=0.47\textwidth]{figures/LOPS/z_j3.pdf}
+\includegraphics[width=0.47\textwidth]{figures/NLOPS/z_j3.pdf}
+\caption{Differential distribution in the
+Zeppenfeld variable of the third-hardest jet
+from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
+    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
+    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
+    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
+\label{fig:PSz3}
+\end{figure*}

### 2018-03-12 Draft/article.tex
restored article.tex

@@
  \usepackage[utf8]{inputenc}
-%  \usepackage{siunitx}
-% \usepackage
-% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
-% {subcaption}
 \hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons}
@@
     %
-    \subsection{Comparison in the fiducial region}
-        \label{subsec:LOfiducial}
-    In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy at order $\mathcal{O}(\alpha^6)$ obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
-    We note that several full predictions are not in statistical agreement. These are possibly due to Monte-Carlo 
     integrators performing too aggressive estimations of statistical uncertainties. Nonetheless, all these predictions agree within less than $0.5\%$.

### 2018-03-12 Draft/article.tex
fixed

@@
     %
+    \subsection{Comparison in the fiducial region}
+    In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy at order $\mathcal O (\alpha^6)$ obtained in the fiducial region 
+    described in Sec.~\ref{subsec:inputpar}. We note that several full predictions are not in statistical agreement. These are possibly due to Monte-Carlo 
     integrators performing too aggressive estimations of statistical uncertainties. Nonetheless, all these predictions agree within less than $0.5\%$.

### 2018-03-12 parton-shower/rivetplot.sh
Update parton-shower plot file as well

@@ -12,7 +12,7 @@ rivet-mkhtml -o rivet-NLOPS \
 :"ErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_HWPP_5M_NLOPS.yoda\
+  MG5_aMC/new_results/run_FIX_NLOPS_HWPP_UNC_MUFACT1/run_HWPP_10M_mush1.yoda\
 :"Title=MG5_aMC+H++ 2.7.1"\
 :"LineColor={[rgb]{0.46,0.44,0.70}}"\
 :"LineStyle=solid"\
@@ -20,7 +20,7 @@ rivet-mkhtml -o rivet-NLOPS \
 :"ErrorBandColor={[rgb]{0.46,0.44,0.70}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.46,0.44,0.70}}"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_PY8_5M_NLOPS_error_all.yoda\
+  MG5_aMC/new_results/run_FIX_NLOPS_PY8_UNC_MUFACT1/run_PY8_10M_mush1_error_all.yoda\
 :"Title=MG5_aMC+Pythia 8"\
 :"LineColor={[rgb]{0.91,0.16,0.54}}"\
 :"LineStyle=solid"\
@@ -28,7 +28,7 @@ rivet-mkhtml -o rivet-NLOPS \
 :"ErrorBandColor={[rgb]{0.91,0.16,0.54}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.91,0.16,0.54}}"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_PY8_5M_NLOPS_error_scale.yoda\
+  MG5_aMC/new_results/run_FIX_NLOPS_PY8_UNC_MUFACT1/run_PY8_10M_mush1_error_scale.yoda\
 :"Title="\
 :"LineColor={[rgb]{0.91,0.16,0.54}}"\
 :"ErrorBands=1"\

### 2018-03-12 Draft/article.tex
Update MG5_aMC numbers in table

@@
         \hline\hline
-        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+2\%}_{-1\%} {}^{+2\%}_{-2\%} $ & $0.004$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
-        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.368$ & $0.004$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.491 ^{+1\%}_{-2\%} {}^{+2\%}_{-2\%} $ & $0.004$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.465 $ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.407$ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.382$ & $0.002$  \\
         {\sc Powheg-Box}+{\sc Pythia8}  & $1.3642$ & $0.0004$  \\

### 2018-03-12 Draft/article.tex
Fix typos

@@
     of the VBS approximation ({\sc Bonsay} and the {\sc Powheg-Box}) are
-    relatively close.\footnote{The {\sc VBFNLO}-predictions omitting
-    $s$-channel contributions amounts to $1.3703(1)$ fb. This differs from
+    relatively close.\footnote{The {\sc VBFNLO} prediction omitting
+    $s$-channel contributions amounts to $1.3703 \pm 0.0001$ fb. This differs from
     the {\sc Powheg-Box} prediction mainly due to the different choice of
@@
 Large differences, reaching a factor 2, persist also away from the central region.
-These findings are consistent with behaviour displayed in Refs.~\cite{Jager:2011ms,Jager:2012xk,Jager:2013mu,Jager:2013iza,Schissler:2013nga} where the behaviour of NLO mathcing in VBS processes have been reported.\\
+These findings are consistent with behaviour displayed in Refs.~\cite{Jager:2011ms,Jager:2012xk,Jager:2013mu,Jager:2013iza,Schissler:2013nga} where the behaviour of NLO matching in VBS processes has been reported.\\
 

### 2018-03-12 parton-shower/cpfigures.sh
Add MG5_aMC+Py8 results with different shower scale

@@ -8,3 +8,8 @@ for ORD in LOPS NLOPS; do
          cp rivet-$ORD/MC_VBSCAN_MCComparison/$F.pdf ../Draft/figures/$ORD/
     done
 done
+
+cp rivet-NLOPS2/MC_VBSCAN_MCComparison/jetsexclusive.pdf ../Draft/figures/NLOPS/
+cp rivet-NLOPS2/MC_VBSCAN_MCComparison/y_j3.pdf ../Draft/figures/NLOPS/
+cp rivet-NLOPS2/MC_VBSCAN_MCComparison/z_j3.pdf ../Draft/figures/NLOPS/
+

### 2018-03-12 parton-shower/rivetplot.sh

@@ -31,10 +31,82 @@ rivet-mkhtml -o rivet-NLOPS \
   MG5_aMC/new_results/run_FIX_NLOPS_PY8_UNC_MUFACT1/run_PY8_10M_mush1_error_scale.yoda\
 :"Title="\
 :"LineColor={[rgb]{0.91,0.16,0.54}}"\
+:"LineStyle=solid"\
 :"ErrorBands=1"\
 :"ErrorBandColor={[rgb]{0.91,0.16,0.54}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.91,0.16,0.54}}"\
 :"ErrorBandOpacity=0.5"\
+  Powheg/Powheg.yoda\
+:"Title=Powheg+Pythia 8"\
+:"LineColor={[rgb]{0.85,0.37,0.01}}"\
+:"LineStyle=solid"\
+:"ErrorBands=0"\
+:"ErrorBandColor={[rgb]{0.85,0.37,0.01}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.85,0.37,0.01}}"\
+:"ErrorBandOpacity=0.3"\
+  Powheg/lhef.yoda\
+:"Title=Powheg-no shower"\
+:"LineColor={[rgb]{0.85,0.37,0.01}}"\
+:"LineStyle=dashed"\
+:"ErrorBands=0"\
+  VBFNLO/Herwig-MCatNLO-DefaultShower.yoda\
+:"Title=VBFNLO 3+H7-Default"\
+:"LineColor={[rgb]{0.40,0.65,0.12}}"\
+:"LineStyle=solid"\
+:"ErrorBands=0"\
+:"ErrorBandColor={[rgb]{0.40,0.65,0.12}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.40,0.65,0.12}}"\
+:"ErrorBandOpacity=0.3"\
+  VBFNLO/Herwig-MCatNLO-DipoleShower_scale.yoda\
+:"Title=VBFNLO 3+H7-Dipole"\
+:"LineColor={[rgb]{0.11,0.62,0.47}}"\
+:"LineStyle=solid"\
+:"ErrorBands=1"\
+:"ErrorBandColor={[rgb]{0.11,0.62,0.47}}"\
+:"RatioPlotErrorBandColor={[rgb]{0.11,0.62,0.47}}"\
+:"ErrorBandOpacity=0.3"\
+
[…]

### 2018-03-13 Draft/article.tex
added discussion on shower scale

@@
  \usepackage[utf8]{inputenc}
-\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons}
+ \usepackage{hyphenat}
+\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons non-fac-toris-able fac-toris-able}
 
@@
         \item diagrams which do not feature two resonant vector-bosons are included;
-        \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
+        \item the so-called non-factoris\-able (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
             are included;
@@
 
-    Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
+    Finally, the effect of EW corrections and non-\-factoris\hyp{}able contributions in the virtual corrections are usually small.
     But they can be relatively large (about $10\%$) for large transverse momentum of the hardest jet.
@@
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within some or few per cents, respectively at LO and NLO.
-Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within some per cents, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
 the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
@@
 prediction dubbed {\sc Powheg-LHE} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
-interplay between the real-emission matrix element and the shower emission.
+interplay between the real-emission matrix element and the shower emission. For this observable we also show the prediction obtained
+with {\sc MG5\_aMC+Pythia8} by reducing the shower-starting scale by a factor 2 with respect to the default value, dubbed 
+{\sc MG5\_aMC+Py8, $Q_{sh}/2$}.\footnote{The reduction of the shower scale for {\sc MG5\_aMC+Herwig++} gives no visible effect on any of the observables 
+discussed in this work.} The main effect of reducing the shower scale is that events migrate from the three-jet bin into the two-jet bin, i.e. less radiation is generated. The
+amount of this effect on the jet rate is +4\% (-8\%) on the two (three) jet bin, while the total rate within cuts is left unchanged.
 
@@
 The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
-about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
+about -30\% at the end of the displayed range.
+At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
+For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is
+negligible, hence the corresponding histogram will not be shown.
 
@@
 effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
-the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}. A similar
+the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}, and that
+it is only marginally attenuated when the shower scale is reduced. A similar
 behaviour of {\sc Pythia8}

### 2018-03-13 Draft/article.tex
further add

@@
 It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. We note 
+the theoretical uncertainty obtained via scale variations (renormalization, factorization and shower scale) 
+systematically underestimates the spread of predictions. We note 
 that in the only VBF process where NNLO corrections are known, i.e. VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 

### 2018-03-13 parton-shower/rivetplot.sh
Adjust labels for parton-shower plots

@@ -13,7 +13,7 @@ rivet-mkhtml -o rivet-NLOPS \
 :"RatioPlotErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"ErrorBandOpacity=0.3"\
   MG5_aMC/new_results/run_FIX_NLOPS_HWPP_UNC_MUFACT1/run_HWPP_10M_mush1.yoda\
-:"Title=MG5_aMC+H++ 2.7.1"\
+:"Title=MG5_aMC+H++2.7.1"\
 :"LineColor={[rgb]{0.46,0.44,0.70}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\
@@ -21,7 +21,7 @@ rivet-mkhtml -o rivet-NLOPS \
 :"RatioPlotErrorBandColor={[rgb]{0.46,0.44,0.70}}"\
 :"ErrorBandOpacity=0.3"\
   MG5_aMC/new_results/run_FIX_NLOPS_PY8_UNC_MUFACT1/run_PY8_10M_mush1_error_all.yoda\
-:"Title=MG5_aMC+Pythia 8"\
+:"Title=MG5_aMC+Py8"\
 :"LineColor={[rgb]{0.91,0.16,0.54}}"\
 :"LineStyle=solid"\
 :"ErrorBands=1"\
@@ -37,7 +37,7 @@ rivet-mkhtml -o rivet-NLOPS \
 :"RatioPlotErrorBandColor={[rgb]{0.91,0.16,0.54}}"\
 :"ErrorBandOpacity=0.5"\
   Powheg/Powheg.yoda\
-:"Title=Powheg+Pythia 8"\
+:"Title=Powheg+Py8"\
 :"LineColor={[rgb]{0.85,0.37,0.01}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\
@@ -76,7 +76,7 @@ rivet-mkhtml -o rivet-NLOPS2 \
 :"RatioPlotErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"ErrorBandOpacity=0.3"\
   MG5_aMC/new_results/run_FIX_NLOPS_HWPP_UNC_MUFACT1/run_HWPP_10M_mush1.yoda\
-:"Title=MG5_aMC+H++ 2.7.1"\
+:"Title=MG5_aMC+H++2.7.1"\
 :"LineColor={[rgb]{0.46,0.44,0.70}}"\
[…]

### 2018-03-13 Draft/article.tex
Address comment on ID range

@@
         $s$-channel contributions are available separately as tri-boson processes with
-        semi-leptonic decays, with process IDs in the 400 range\ZM{which range is it?}. These can simply
+        semi-leptonic decays, with process IDs between 401 and 492. These can simply
         be added on top of the VBS contribution. Interferences between the two are therefore neglected.

### 2018-03-13 Draft/article.tex
Add MCnet preprint number
Add specific process IDs in VBFNLO description
Rewrite BONSAY section a bit

@@
 
-  Nikhef/2018-012, UWTHPH-2018-12, VBSCan-PUB-01-18,
-
-  ZU-TH-08/18}
+  MCnet-18-06, Nikhef/2018-012, UWTHPH-2018-12,
+
+  VBSCan-PUB-01-18, ZU-TH-08/18}
 \end{abstract}
@@
 
-    \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator written by Christopher Schwan and matrix elements taken from different sources:
-    Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
+    \item The program {\sc Bonsay}~\cite{Dittmaier:2018zzz} consists of a general-purpose Monte Carlo integrator and matrix elements taken from different sources:
+    Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, which have been generalized to calculate also real matrix elements.
+    Virtual matrix elements have been calculated using an in-house matrix element generator.
     One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
@@
         allows the calculation of VBS processes at NLO QCD in the VBS
-        approximation, with process IDs between 200 and 290. The corresponding
+        approximation, with process IDs between 200 and 290. Same-sign
+        $\PW^+\PW^+jj$ production is provided via the process ID 250. The corresponding
         $s$-channel contributions are available separately as tri-boson processes with
-        semi-leptonic decays, with process IDs between 401 and 492. These can simply
-        be added on top of the VBS contribution. Interferences between the two are therefore neglected.
+        semi-leptonic decays, with process IDs between 401 and 492. For the
+        final state studied in this article, only $\PW^+\PW^+\PW^-$
+        production with a hadronically decaying $\PW^-$ boson, process ID 432,
+        can contribute. These can simply be added on top of the VBS
+        contribution. Interferences between the two are therefore neglected.
         The usage of leptonic tensors in the calculation, pioneered in

### 2018-03-14 Draft/article_before_qsh.tex
ncluded

--- 2018-03-13 Draft/article.tex
@@
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within some per cents, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within some or few per cents, respectively at LO and NLO.
+Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
 the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
@@
 prediction dubbed {\sc Powheg-LHE} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
-interplay between the real-emission matrix element and the shower emission. For this observable we also show the prediction obtained
-with {\sc MG5\_aMC+Pythia8} by reducing the shower-starting scale by a factor 2 with respect to the default value, dubbed 
-{\sc MG5\_aMC+Py8, $Q_{sh}/2$}.\footnote{The reduction of the shower scale for {\sc MG5\_aMC+Herwig++} gives no visible effect on any of the observables 
-discussed in this work.} The main effect of reducing the shower scale is that events migrate from the three-jet bin into the two-jet bin, i.e. less radiation is generated. The
-amount of this effect on the jet rate is +4\% (-8\%) on the two (three) jet bin, while the total rate within cuts is left unchanged.
+interplay between the real-emission matrix element and the shower emission.
 
@@
 The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
-about -30\% at the end of the displayed range.
-At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
-For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is
-negligible, hence the corresponding histogram will not be shown.
+about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
 
@@
 effects, though smaller, on the rapidity spectra of the two hardest jets.} It is interesting to notice that
-the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}, and that
-it is only marginally attenuated when the shower scale is reduced. A similar
+the effect survives beyond the first emission, as it can be observed by comparing {\sc Powheg-LHE} with {\sc Powheg+ Pythia8}. A similar
 behaviour of {\sc Pythia8}
@@
 It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty obtained via scale variations (renormalization, factorization and shower scale) 
-systematically underestimates the spread of predictions. We note 
+the theoretical uncertainty obtained via scale variations systematically underestimates the spread of predictions. We note 
 that in the only VBF process where NNLO corrections are known, i.e. VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 

### 2018-03-14 Draft/article.tex
addeed acknowledgements to the H7 people

@@
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1).
-The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}.
-For the {\sc Powheg-Box}, the namesake
+and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the angular-ordered shower will be employed. 
+The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
         {\sc MG5\_aMC}+{\sc Pythia8}&  $1.352 $ & $0.003$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.343 $ & $ 0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig7}&  $1.342 $ & $ 0.003$  \\
         {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.275$ & $0.003$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.267$ & $ 0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig7}, $\Gamma_{\rm resc}$&  $1.266$ & $ 0.003$  \\
         {\sc PHANTOM}+{\sc Pythia8} &  $1.235 $ & $0.001$  \\
-        {\sc PHANTOM}+{\sc Herwig++} &  $1.260 $ & $0.001$  \\
+        {\sc PHANTOM}+{\sc Herwig7} &  $1.258 $ & $0.001$  \\
         {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3001$ & $0.0002$  \\
@@
         {\sc MG5\_aMC}+{\sc Pythia8}&  $1.491 ^{+1\%}_{-2\%} {}^{+2\%}_{-2\%} $ & $0.004$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.465 $ & $0.003$  \\
+        {\sc MG5\_aMC}+{\sc Herwig7}&  $1.427 $ & $0.003$  \\
         {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.407$ & $0.003$  \\
-        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.382$ & $0.002$  \\
+        {\sc MG5\_aMC}+{\sc Herwig7}, $\Gamma_{\rm resc}$&  $1.346$ & $0.002$  \\
         {\sc Powheg-Box}+{\sc Pythia8}  & $1.3642$ & $0.0004$  \\
         {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0\%}_{-1\%}$ & $0.0006$  \\
-        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
+        {\sc VBFNLO}+{\sc Herwig7} &  $1.3067$ & $0.0006$  \\
     \end{tabular}
@@
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within some per cents, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within some per cents ($\le7\%$), both at LO and NLO.
+Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
 the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
@@
 The first observable we investigate is the exclusive jet multiplicity, shown in Fig.~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
-main effects are driven by the parton shower that is employed ({\sc Herwig++/7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
+main effects are driven by the parton shower that is employed ({\sc Herwig7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
 leading to higher jet multiplicities. Differences among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
@@
 with {\sc MG5\_aMC+Pythia8} by reducing the shower-starting scale by a factor 2 with respect to the default value, dubbed 
-{\sc MG5\_aMC+Py8, $Q_{sh}/2$}.\footnote{The reduction of the shower scale for {\sc MG5\_aMC+Herwig++} gives no visible effect on any of the observables 
+{\sc MG5\_aMC+Py8, $Q_{sh}/2$}.\footnote{The reduction of the shower scale for {\sc MG5\_aMC+Herwig7} gives no visible effect on any of the observables 
 discussed in this work.} The main effect of reducing the shower scale is that events migrate from the three-jet bin into the two-jet bin, i.e. less radiation is generated. The
@@
 it is very likely that it is driven by the way the first emission is generated. A minor effect in the same direction is visible in the last two bins of the
-{\sc MG5\_aMC+Herwig++} prediction (although with rather large statistical uncertainties).
+{\sc MG5\_aMC+Herwig7} prediction (although with rather large statistical uncertainties).
 
@@
 has also been observed in the study of EW production of a $\PZ$ boson in association with two jets (see the recent CMS measurement,
-Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}.
+Ref.~\cite{Sirunyan:2017jej} Figure 12), where the experimental data seem to prefer the description by {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb}.
 The central enhancement
@@
 the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
-discussions and clarifications about the third-jet rapidity spectrum. RF, HSS and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
+discussions and clarifications about the third-jet rapidity spectrum. MZ would like to talk Andreas Papaefstathiou, Christian Reuschle and David Grellscheid 
+for their help with {\sc Herwig7}. RF, HSS and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
 they are particularly grateful to Valentin Hirschi for comments to this manuscript.

### 2018-03-14 Draft/article.tex
Minor typos in acknowledgment fixed

@@
 The authors are grateful to the members of the VBSCan collaboration for several discussions and comments to this work. The author also thank
-the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
-discussions and clarifications about the third-jet rapidity spectrum. MZ would like to talk Andreas Papaefstathiou, Christian Reuschle and David Grellscheid 
-for their help with {\sc Herwig7}. RF, HSS and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
-they are particularly grateful to Valentin Hirschi for comments to this manuscript.
+the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand, and Peter Skands for 
+discussions and clarifications about the third-jet rapidity spectrum. RF, HSS, and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
+they are particularly grateful to Valentin Hirschi for comments on the manuscript.
 

### 2018-03-14 Draft/article.tex

@@
 the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand, and Peter Skands for 
-discussions and clarifications about the third-jet rapidity spectrum. RF, HSS, and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
-they are particularly grateful to Valentin Hirschi for comments on the manuscript.
+discussions and clarifications about the third-jet rapidity spectrum. MZ would like to talk Andreas Papaefstathiou, Christian Reuschle and David Grellscheid 
+for their help with {\sc Herwig7}. RF, HSS, and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
+they are particularly grateful to Valentin Hirschi for comments to this manuscript.
 

### 2018-03-14 parton-shower/cpfigures.sh
Update parton-shower plots to new H7 files

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-FIGS="jetsexclusive m_jj pT_j1 pT_j2 y_j2 Deltay_jj y_j3 z_j3"
+FIGS="jetsexclusive m_jj pT_j1 pT_j2 y_j2 Deltay_jj z_j3"
 
 for ORD in LOPS NLOPS; do
     for F in $FIGS; do
@@ -10,6 +10,5 @@ for ORD in LOPS NLOPS; do
 done
 
 cp rivet-NLOPS2/MC_VBSCAN_MCComparison/jetsexclusive.pdf ../Draft/figures/NLOPS/
-cp rivet-NLOPS2/MC_VBSCAN_MCComparison/y_j3.pdf ../Draft/figures/NLOPS/
 cp rivet-NLOPS2/MC_VBSCAN_MCComparison/z_j3.pdf ../Draft/figures/NLOPS/
 

### 2018-03-14 parton-shower/rivetplot.sh

@@ -12,8 +12,8 @@ rivet-mkhtml -o rivet-NLOPS \
 :"ErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/new_results/run_FIX_NLOPS_HWPP_UNC_MUFACT1/run_HWPP_10M_mush1.yoda\
-:"Title=MG5_aMC+H++2.7.1"\
+  MG5_aMC/new_results/H7/run_H7_10M_mush1.yoda\
+:"Title=MG5_aMC+H7-Default"\
 :"LineColor={[rgb]{0.46,0.44,0.70}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\
@@ -75,8 +75,8 @@ rivet-mkhtml -o rivet-NLOPS2 \
 :"ErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/new_results/run_FIX_NLOPS_HWPP_UNC_MUFACT1/run_HWPP_10M_mush1.yoda\
-:"Title=MG5_aMC+H++2.7.1"\
+  MG5_aMC/new_results/H7/run_H7_10M_mush1.yoda\
+:"Title=MG5_aMC+H7-Default"\
 :"LineColor={[rgb]{0.46,0.44,0.70}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\
@@ -148,8 +148,8 @@ rivet-mkhtml -o rivet-LOPS \
 :"ErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"RatioPlotErrorBandColor={[rgb]{0.40,0.40,0.40}}"\
 :"ErrorBandOpacity=0.3"\
-  MG5_aMC/run_HWPP_1M_LOPS.yoda\
-:"Title=MG5_aMC+H++2.7.1"\
+  MG5_aMC/new_results/H7/run_1M_LOPS-H7.yoda\
+:"Title=MG5_aMC+H7-Default"\
 :"LineColor={[rgb]{0.46,0.44,0.70}}"\
 :"LineStyle=solid"\
 :"ErrorBands=0"\
[…]

### 2018-03-14 Draft_arXiv/article.tex
added folder Draft_arXiv with the final version of the draft
fixed some linebreaks

--- 2018-03-14 Draft/article.tex
@@
  \usepackage{hyphenat}
-\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons non-fac-toris-able fac-toris-able}
+\hyphenation{quan-ti-ta-tive-ly fer-mi-on fer-mi-ons non-fac-toris-able fac-toris-able in-ter-act-ing fac-torise VBF-NLO show-er Mad-Graph}
 
@@
     \begin{verbatim}
-    > set complex_mass_scheme
-    > import model loop_qcd_qed_sm_Gmu
-    > generate p p > e+ ve mu+ vm j j QCD=0 [QCD]
-    > output
+set complex_mass_scheme
+import model loop_qcd_qed_sm_Gmu
+generate p p > e+ ve mu+ vm j j QCD=0 [QCD]
+output
     \end{verbatim}
@@
             and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
-            Only QCD-interacting particles circulating in the loops are generated for the virtual matrix element.
+            Only QCD-in\-ter\-act\-ing particles circulating in the loops are generated for the virtual matrix element.
             The version capable of computing both QCD and EW corrections will be released in the future.
@@
         \item all $s$- and $t/u$-channel diagrams are included;
-        \item interferences between diagrams of different types ($s/t/u$-channel) are included at LO;
+        \item interferences between diagrams of different types ($s$/ $t$/$u$-channel) are included at LO;
         \item diagrams which do not feature two resonant vector-bosons are included;
@@
 employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the angular-ordered shower will be employed. 
+and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the default angular-ordered shower will be employed. 
 The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
@@
 possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
-matching. As parton shower, both the default angular-ordered shower as
-well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton shower algorithms.
+matching. As parton show\-er, both the default angular-ordered shower as
+well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton show\-er algorithms.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
@@
 It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty obtained via scale variations (renormalization, factorization and shower scale) 
+the theoretical uncertainty obtained via scale variations (renormalization, factorization and show\-er scale) 
 systematically underestimates the spread of predictions. We note 
@@
     \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguities related to the 
-        matching details and/or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses. In doing
+        matching details and/ or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses. In doing
         so, special care should be employed in order to estimate the theoretical uncertainties, as the standard prescription based on 
-        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different generators and/or parton showers should be employed.
+        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different generators and/ or parton showers should be employed.
 
@@
 discussions and clarifications about the third-jet rapidity spectrum. MZ would like to talk Andreas Papaefstathiou, Christian Reuschle and David Grellscheid 
-for their help with {\sc Herwig7}. RF, HSS, and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
+for their help with {\sc Herwig7}. RF, HSS, and MZ thank the {\sc MadGraph5\_\-aMC@NLO} authors for discussions, and
 they are particularly grateful to Valentin Hirschi for comments to this manuscript.
@@
 SD and CS acknowledge support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.
+The work of BJ was supported in part by the Institutional Strategy of the University of T\"ubingen (DFG, ZUK 63) and in part by
+the BMBF under contract number 05H2015.
 AK acknowledges financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
@@
 MZ is supported by the Netherlands National Organisation for Scientific Research (NWO).
-The work of BJ was supported in part by the Institutional Strategy of the University of T\"ubingen (DFG, ZUK 63) and in part by
-the BMBF under contract number 05H2015.
 

### 2018-03-15 Draft/article.tex
Corrections of Ansgar (some are of mine)

@@
   matched to parton showers, at LO and NLO: we show that on the one
-  hand, the inclusion of NLO QCD corrections lead to more stable
+  hand, the inclusion of NLO QCD corrections leads to more stable
   predictions, but on the other the details of the matching and of the
-  parton-shower programs lead to differences which are considerably
-  larger than those observed at fixed-order, even in the experimental
+  parton-shower programs cause differences which are considerably
+  larger than those observed at fixed order, even in the experimental
   fiducial region.  We conclude with some recommendations for
@@
   {\small \underline {Preprint numbers:}
+
+  \vspace{0.1cm}
 
@@
 Vector-boson scattering (VBS) at a hadron collider 
-usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
+usually refers to the interaction of massive vector bosons ($\PW^\pm,\PZ$),
 radiated by partons (quarks) of the incoming protons, 
@@
 Among the possible diagrams,
-the scattering process can be mediated by a Higgs boson
-and involves in particular its longitudinal component.
+the scattering process can be mediated by a Higgs boson.
 The interaction of longitudinally polarised bosons is of particular interest, 
@@
 A detailed study of this class of processes will therefore further constrain the Higgs couplings 
-at a very different energy scale with respect to the Higgs boson mass,
+at a very different energy scale with respect to the Higgs-boson mass,
 and hint at, or exclude, non-Standard Model behaviours.
@@
 
-$\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
+$\PW^+\PW^+$ scattering is the simplest VBS process to calculate, 
 because the double-charge structure of the leptonic final state 
@@
 
-In the last few years, several next-to-leading order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
-All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Denner:2012dz,Oleari:2003tc}.
+In the last few years, several next-to-leading-order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
+All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small in realistic experimental setups~\cite{Denner:2012dz,Oleari:2003tc}.
 Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, 
 making it possible for the first time to study in detail the quality of the VBS approximations at NLO QCD.\footnote{Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.
-A similar study has also been made public very recently for the EW production of a Higgs boson in association with 3 jets \cite{Campanario:2018ppz}.}
+A similar study has also appeared very recently for the electroweak (EW) production of a Higgs boson in association with 3 jets \cite{Campanario:2018ppz}.}
 
@@
 \label{sec:definition}
-\begin{figure*}[t]
+\begin{figure*}
 \begin{center}
@@
 
-This process possesses three LO contributions of different orders.
 At LO, this process can proceed via three different coupling-order combinations:
@@
 $u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical quarks or anti-quarks in the final state
-The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
+The $s$-channel contributions plays a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
 
 When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results.
-We will discuss the commonly-used possible choices in detail in the next section.
+We discuss the commonly-used possible choices in detail in the next section.
 
@@
 These cuts are based on the different kinematical behaviour of the contributions.
-The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
+The EW contribution is characterised by two jets with large rapidities as well as a large di-jet invariant mass.
 The two $\PW$ bosons are mostly produced centrally.
@@
     %
-    \subsection{Several descriptions for one process}
+    \subsection{Theoretical predictions for VBS}
     We now discuss the various approximations which are implemented in computer programs for the EW contribution at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
     Since we are mostly interested in 
-    the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, it may appear justified to approximate the 
+    the scattering of two $\PW$ bosons, which includes the quartic gauge-boson vertex, it may appear justified to approximate the 
     full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
@@
     This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
-    We will adopt the latter denomination in the following of the article.
+    We adopt the latter denomination in the following.
     This approximation is gauge-invariant, a fact that can be appreciated by considering the two incoming quarks as belonging to two different copies of the $\rm{SU}(3)$ gauge group.
@@
     The initial-state gluon and quark 
-        must not couple together, otherwise infrared divergences proportional to $s$-channels will appear, 
+        must not couple together, otherwise infrared divergences proportional to $s$-channels appear, 
          which do not match with the ones found in the virtual contributions.
@@
     %
-    \subsection{Description of the predictions}
+    \subsection{Description of the programs used}
         \label{subsec:codedescr}
-    In the following, the codes employed throughout this paper and the approximations implemented in each of them will be discussed:
+    In the following, the codes employed throughout this paper and the approximations implemented in each of them are discussed:
 
@@
     \item The program {\sc Bonsay}~\cite{Dittmaier:2018zzz} consists of a general-purpose Monte Carlo integrator and matrix elements taken from different sources:
-    Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, which have been generalized to calculate also real matrix elements.
-    Virtual matrix elements have been calculated using an in-house matrix element generator.
-    One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
+    Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, which have been generalised to calculate also real matrix elements.
+    Virtual matrix elements have been calculated using an in-house matrix-element generator.
+    One-loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
     For the fiducial cross sections it uses the VBS approximation at LO and NLO.
@@
 
-      \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\_aMC}) is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
+      \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\_aMC}) is a meta-code (a code that generates codes) which makes it possible to simulate any scattering process
           including NLO QCD corrections both at fixed order and including matching to parton showers, using the {\sc MC@NLO}\ method~\cite{Frixione:2002ik}.
@@
             and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
-            Only QCD-interacting particles circulating in the loops are generated for the virtual matrix element.
+            Only strongly-interacting particles circulating in the loops are generated for the virtual matrix element.
             The version capable of computing both QCD and EW corrections will be released in the future.
@@
 
-    \item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
+    \item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix-element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
     It can compute arbitrary processes at the LHC with both NLO QCD and EW accuracy in the SM.
@@
     In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
-    The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
+    The code has demonstrated its ability to compute at NLO high-multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
     In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained thanks to this tool.
-    One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
+    One key aspect for these high-multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
     In {\sc MoCaNLO+Recola} no approximation is performed neither at LO nor at NLO.
@@
 
-      \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states 
+      \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six-parton final states 
       at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
     It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
-    The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
+    The integration uses a multi-channel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
     {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of beyond the Standard Model (BSM) theories.
@@
       \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
-    It relies on the user providing the matrix elements and Born phase-space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
+    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
     For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.
@@
 \ZM{ if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
-    provides FKS subtraction terms for any NLO process, while virtual matrix
+    It provides FKS subtraction terms for any NLO process, while virtual matrix
     elements are provided externally by {\sc
@@
         \item interferences between diagrams of different types ($s/t/u$-channel) are included at LO;
-        \item diagrams which do not feature two resonant vector-bosons are included;
+        \item diagrams which do not feature two resonant vector bosons are included;
         \item the so-called non-factoris\-able (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
@@
 
-    \begin{table*}[ht!]
+    \begin{table*}
         \footnotesize
@@
             \hline
-            {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
-            {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
-            {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & virt. No &  No \\
-            {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
-            {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
-            {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
-            {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
+            {\sc Bonsay}        &  $t,u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
+            {\sc Powheg}        &  $t,u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+            {\sc MG5\_aMC}      &  $s,t,u$  &  Yes      &  Yes              &  Yes   & virt. No &  No \\
+            {\sc MoCaNLO+Recola}&  $s,t,u$  &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
+            {\sc PHANTOM}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
+            {\sc VBFNLO}        &  $s,t,u$  &  No       &  Yes              &  Yes   & No       &  No  \\
+            {\sc Whizard}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
         \end{tabularx}
@@
         \label{subsec:inputpar}
-    The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
-    The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO, as they will lead to top quarks, and not light jets, in the final state.}
-    NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
+    The hadronic scattering processes are simulated at the LHC with a centre-of-mass energy $\sqrt s = 13 \TeV$.
+    The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massless flavours,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO, as they would lead to top quarks, and not light jets, in the final state.}
+    NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.} are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}
     Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
@@
     \end{equation}
-    The Cabibbo-Kobayashi-Maskawa matrix is assumed to be diagonal, meaning that the mixing between different quark generations is neglected.
+    The Cabibbo--Kobayashi--Maskawa matrix is assumed to be diagonal, meaning that the mixing between different quark generations is neglected.
     The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.
@@
     event by event.\footnote{By default, the renormalisation and factorisation scales employed in the {\sc Powheg-Box} slightly differ from the 
-        one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are
+        ones defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying Born event are
         employed instead of those of the two hardest jets.\label{foot:powheg}} 
@@
     \begin{itemize}
-        \item The two same-sign charged leptons are required to fulfill cuts on transverse momentum, rapidity, and separation in the rapidity-azimuthal angle separation, 
+        \item The two same-sign charged leptons are required to fulfil cuts on transverse momentum, rapidity, and separation in the rapidity--azimuthal-angle separation, 
             \begin{align}
@@
             \label{cut:2}
-              %\etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
               p_{\rm T, miss} >  40\GeV\,.
@@
         \item QCD partons (light quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp}, possibly using the {\sc FastJet} implementation~\cite{Cacciari:2011ma}, with distance parameter $R=0.4$.
-%Jets are required to have
         We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons,  
@@
             \end{align}
-            VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated. In particular, we impose a cut on the 
-             in\-vari\-ant mass of the di-jet system,  as well as on the rapidity-separation of the two jets,          \begin{align}
+            VBS cuts are applied on the two jets with largest transverse momentum, unless otherwise stated. In particular, we impose a cut on the 
+             in\-vari\-ant mass of the di-jet system, as well as on the rapidity separation of the two jets,          
+            \begin{align}
             \label{cut:4}
@@
     This results in a small contribution even if the VBS cuts have not been imposed.
-    The interference between EW and QCD contributions is small, due to color suppression, but not negligible.
-
-    \begin{table}[h!]
+    The interference between EW and QCD contributions is small, due to colour suppression, but not negligible.
+
+    \begin{table}
         \centering
@@
         These results are for the set-up described in Sec.~\protect\ref{subsec:inputpar} but no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.
-        The uncertainties shown refer to the estimated statistical error of the Monte Carlo integrations.}
+        The uncertainties shown refer to the estimated statistical errors of the Monte Carlo integrations.}
     \end{table}
@@
 
-    \begin{figure*}[hbt]
+    \begin{figure*}
     \centering
@@
     Again, it is clear that the region with low di-jet invariant mass should be avoided in VBS studies as it is dominated by tri-boson contributions.
-    This motivates in particular the choice of employing the cut $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study in Sec.~\ref{subsec:LOinclusive}.
-
-    \begin{figure*}[hbt]
+    This motivates in particular the choice of the cut $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study in Sec.~\ref{subsec:LOinclusive}.
+
+    \begin{figure*}
     \centering
@@
         \label{subsec:LOinclusive}
-    In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the variables  $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
+    In Fig.~\ref{fig:ratio2d_LO}, ratios for double-differential cross sections in the variables  $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
     Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
     In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
-    The low rapidity-difference region possesses remnants of the tri-bosons contributions that have a di-jet invariant mass around the $\PW$-boson mass.
+    The low rapidity-difference region possesses remnants of the tri-bosons contribution that have a di-jet invariant mass around the $\PW$-boson mass.
     It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
     The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
-    The full calculation is approximated at the level of $\pm5\%$ apart in the region where $|\Delta y_{\Pj\Pj}| < 2$.
-
-    \begin{figure*}[hbt]
+    The full calculation is approximated at the level of $\pm5\%$ apart from the region where $|\Delta y_{\Pj\Pj}| < 2$.
+
+    \begin{figure*}
     \centering
@@
     \includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
-    \caption{Ratios of double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
-    Ratio of approximated squared amplitudes over the full matrix element.
+    \caption{Ratios for double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$ of approximated squared amplitudes over the full matrix element.
     The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
@@
     \end{figure*}
-    %
+
     \subsection{Comparison in the fiducial region}
     In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy at order $\mathcal O (\alpha^6)$ obtained in the fiducial region 
-    described in Sec.~\ref{subsec:inputpar}. We note that several full predictions are not in statistical agreement. These are possibly due to Monte-Carlo 
+    described in Sec.~\ref{subsec:inputpar}. We note that several full predictions are not in statistical agreement. These are possibly due to Monte Carlo 
     integrators performing too aggressive estimations of statistical uncertainties. Nonetheless, all these predictions agree within less than $0.5\%$.
-    At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
+    At the level of the cross section, it seems difficult to infer the quality of the various approximations.
     This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
     the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
-    This is in agreement with the findings of Ref.~\cite{Denner:2012dz,Oleari:2003tc}.
-
-    \begin{table}[h!]
+    This is in agreement with the findings of Refs.~\cite{Denner:2012dz,Oleari:2003tc}.
+
+    \begin{table}
         \centering
@@
         The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
-        The uncertainties shown refer to the estimated statistical error of the Monte Carlo integrations.}
+        The uncertainties shown refer to the estimated statistical errors of the Monte Carlo integrations.}
     \end{table}
 
-    In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
+    In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference (right) of the two tagging jets which are key observables for VBS measurements.
     In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
@@
 
-     \begin{figure*}[htb!]
+     \begin{figure*}
        \centering
@@
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
-    The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
-    The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+    The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
+    The band corresponds to a seven-point variation of the renormalisation and factorisation scales.
     The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.}
@@
     %
-    \subsection{Inclusive comparision}
+    \subsection{Inclusive comparison}
         \label{subsec:NLOinclusive}
@@
 
-    The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
+    The total cross sections within the above-mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.
     The $|t|^2+|u|^2$ approximation for NLO QCD predictions is lower by about $6\%$ than the full calculation.
-    The inclusion of $s$-channel diagrams improves the approximate prediction, leading to an excess at the $3\%$-level.
-
-    \begin{table}[h!]
+    The inclusion of $s$-channel diagrams improves the approximate prediction, leading to an excess at the $3\%$ level.
+
+    \begin{table}
     \centering
@@
     In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.
-    The uncertainties shown refer to the estimated statistical error of the Monte Carlo programs.}
+    The uncertainties shown refer to the estimated statistical errors of the Monte Carlo programs.}
     \label{tab:crosssecINCLUSIVE}
@@
     For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$.
-    This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
+    This is in contrast with the regions  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
     the difference between the $|t|^2+|u|^2$ approximation and the full computation can be above $30\%$.
-    The inclusion of $s$-channels cures partly this behaviour by rendering the approximation good by about $10\%$.
+    The inclusion of $s$-channels cures partly this behaviour by improving the approximation to about $10\%$.
     This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
 
-    \begin{figure*}[hbt]
+    \begin{figure*}
     \centering
@@
     \caption{
-    Differential distributions in the di-jet invariant mass (left) and the rapidity-separation of the two tagging jets (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+    Differential distributions in the di-jet invariant mass (left) and the rapidity separation of the two tagging jets (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
     In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
@@
     In order to investigate further the jet-pair kinematics, we study the double-differential distribution in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
-    In particular, in Fig.~\ref{fig:ratio2d_NLO}, we compute in each bin the ratios of the approximated cross sections over the full one [$\sigma(|t|^2+|u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2+|u|^2)/\sigma(\textrm{full})$].
+    In particular, in Fig.~\ref{fig:ratio2d_NLO}, we compute in each bin the ratios of the approximated cross sections over the full ones [$\sigma(|t|^2+|u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2+|u|^2)/\sigma(\textrm{full})$].
     As expected, in the low invariant-mass and low rapidity-separation region of the jet pair ($200 \GeV < m_{\Pj\Pj} < 500 \GeV$, $2<|\Delta y_{\Pj\Pj}|<2.5$) the VBS approximation fails significantly (by more than $40\%$).
     Including the $s$-channel contributions leads to a difference of less than $10\%$ in this very region.
-    However, in the region of large di-jet invariant mass and low rapidity separation of the jets, the $|s|^2+|t|^2+|u|^2$ approximation overestimate the full computation by more than $40\%$.\footnote{The bin
-    in the top-left corner of the right-hand side plot of Fig.~\ref{fig:ratio2d_NLO} suffers from large uncertainty ($30\%$) while the other errors are at the per-cent level.}
+    However, in the region of large di-jet invariant mass and low rapidity separation of the jets, the $|s|^2+|t|^2+|u|^2$ approximation overestimates the full computation by more than $40\%$.\footnote{The bin
+    in the top-left corner of the right-hand-side plot of Fig.~\ref{fig:ratio2d_NLO} suffers from large uncertainty ($30\%$) while the other errors are at the per-cent level.}
     Again, this seems to support the fact that interferences and non-factorisable corrections can be non-negligible in this region.
-    On the other hand, in the typical VBS region, the VBS approximation shows a good agreement with the full computation as documented in details in Sec.~\ref{sec:fidNLO}.
-
-    \begin{figure*}[hbt]
+    On the other hand, in the typical VBS region, the VBS approximation shows a good agreement with the full computation as documented in detail in Sec.~\ref{sec:fidNLO}.
+
+    \begin{figure*}
     \centering
@@
     {\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-    \caption{Ratios of double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation.
-    Ratio of the approximated squared amplitudes over the full matrix element.
+    \caption{Ratios for double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation of the approximated squared amplitudes over the full matrix element.
     The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2+|u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2+|t|^2+|u|^2$ (right).
@@
     At high transverse momentum, they have a similar behaviour.
-    They both diverge from the full computation towards larger transverse momentum to reach about $10\%$ at $1000\GeV$.
+    They both diverge from the full computation towards larger transverse momentum (about $10\%$ at $1000\GeV$).
     Regarding the rapidity of the hardest jet, the two approximations have opposite behaviours.
-    In the central region, the $|t|^2+|u|^2$ approximation differs by $12\%$ with respect to the full computation while the $|s|^2+|t|^2+|u|^2$ one is good within $5\%$.
-    In the peripheral region, the $|t|^2+|u|^2$ approximation is rather close to the full computation ($5\%$) while the $|s|^2+|t|^2+|u|^2$ one differs by $10\%$.
-
-    \begin{figure*}[hbt]
+    In the central region, the $|t|^2+|u|^2$ approximation differs by $12\%$ with respect to the full computation, while the $|s|^2+|t|^2+|u|^2$ one is good within $5\%$.
+    In the peripheral region, the $|t|^2+|u|^2$ approximation is rather close to the full computation ($5\%$), while the $|s|^2+|t|^2+|u|^2$ one differs by $10\%$.
+
+    \begin{figure*}
     \centering
@@
     \caption{Differential distributions in the transverse momentum (left) and rapidity of the hardest tagging jet (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
     In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
@@
     %
-    Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
-    %
-    \begin{figure*}[hbt]
+    Analogous definitions are later also be used for the Zeppenfeld variable of the muon and of the third jet.
+    %
+    \begin{figure*}
     \centering
@@
     \caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-    The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
+    The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
     In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
@@
     %
-    The $|s|^2+|t|^2+|u|^2$ predictions for $m_{\rm e^+\mu^+}$ agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
+    The $|s|^2+|t|^2+|u|^2$ predictions for $m_{\rm e^+\mu^+}$ agree rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
     The prediction from {\sc Bonsay} is about $10\%$ lower around $1000 \GeV$.
@@
 
-    In conclusion, both the loose minimum di-jet invariant mass cut and the inclusion of QCD radiative correction make the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
-    In the inclusive region studied here, neglecting $s$-channel, non-factorisable corrections, and electroweak corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.
+    In conclusion, both the loose minimum di-jet invariant-mass cut and the inclusion of QCD radiative corrections render the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
+    In the inclusive region studied here, neglecting $s$-channel, non-factorisable corrections, and EW corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.
     Nevertheless, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($m_{\Pj\Pj} \gtrsim 500 \GeV$, $|\Delta y_{\Pj\Pj}| \gtrsim 2.5$), for both total cross section and differential distributions.
-    This more exclusive region is studied in more details in the next section.
+    This more exclusive region is studied in more detail in the next section.
     %
@@
     In Tab.~\ref{tab:wg1_NLOrates}, the cross sections of the various tools at NLO-QCD accuracy are presented.
-    The order considered is again the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$ and the fiducial volume is the one described in Sec.~\ref{subsec:inputpar}.
+    The order considered is again the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$, and the fiducial volume is the one described in Sec.~\ref{subsec:inputpar}.
     In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions differ visibly according to the approximations used.
 
-    \begin{table}[h!]
+    \begin{table}
         \centering
@@
         The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
-        The uncertainties shown refes to estimated statistical errors of the Monte Carlo integrations.}
+        The uncertainties shown refer to estimated statistical errors of the Monte Carlo integrations.}
     \end{table}
@@
     inclusion (as done in {\sc VBFNLO}) approximates the full computation
-    by less than a per cent ($0.7\%$). The main contribution due to 
+    by a per cent. The main contribution due to 
     the $s$-channel diagrams thereby consists of real-emission
@@
     off-shell region.
-    However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effect and some non-factorisable corrections (in the real corrections) in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
-    Not unexpectedly none of the approximations used here agree perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.
-    Nevertheless, the disagreement seems to never exceed $2\%$ at the fiducial cross section level.
+    However, the agreement between {\sc MoCaNLO+Recola} and {\sc VBFNLO} is mostly accidental, as the inclusion of interference effects and some non-factorisable corrections (in the real corrections) in {\sc MG5\_aMC} brings the prediction down and closer to the VBS approximation.
+    Not unexpectedly none of the approximations used here agrees perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.
+    Nevertheless, the disagreement seems to never exceed $2\%$ at the fiducial cross-section level.
 
@@
     For high invariant mass, all predictions agree rather well.
-    On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
+    On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is reproduced.
     The VBS-approximated predictions ({\sc Bonsay} and {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
@@
 
-     \begin{figure*}[hbt!]
+     \begin{figure*}
        \centering
@@
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
-    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
-    The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full prediction.
+    The band corresponds to a seven-point variation of the renormalisation and factorisation scales.
     The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
@@
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
-    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
-    The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full prediction.
+    The band corresponds to a seven-point variation of the renormalisation and factorisation scales.
     The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
@@
     This can be explained by the fact that $s$-channel contributions are less suppressed at NLO.
-    In the real, an extra gluon-jet can be radiated from any of the charged particles while the two quarks originating from the W-boson decay can be recombined in a single jet.
+    As real radiation, an extra gluon-jet can be radiated from any of the charged particles while the two quarks originating from the W-boson decay can be recombined in a single jet.
     Therefore, the jet requirements ($ m_{\Pj \Pj} >  500\GeV$ and $|\Delta y_{\Pj \Pj}| > 2.5$) that were suppressing $s$-channel contributions at LO are partially lifted with the inclusion of a third jet at NLO.
@@
 We now discuss how different predictions compare when the matching to parton shower is included. For such
-a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
-matching schemes, parton shower employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
+a comparison we expect larger discrepancies than what we found at fixed order, as a consequence of the different
+matching schemes, parton showers employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
 the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
@@
 also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
-{\sc MG5\_aMC}, which
-employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the angular-ordered shower will be employed. 
-The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
+{\sc MG5\_aMC}, which employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, is used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
+and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the default angular-ordered shower is employed. 
+The same parton showers are employed for the LO results of {\sc PHANTOM}.
+{\sc Pythia8} is also employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
 matching. As parton shower, both the default angular-ordered shower as
-well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton shower algorithms.
+well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton-shower algorithms.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
 
-Results will be presented within the cuts described in Sec.~\ref{subsec:inputpar}, applied after shower and hadronisation (this implies that jets
+Results are presented within the cuts described in Sec.~\ref{subsec:inputpar}, applied after shower and hadronisation (this implies that jets
 are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
@@
 
-Compared to the fixed order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
+Compared to the fixed-order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
 ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is dominated by doubly-resonant contribution, the
@@
 
-\begin{table}[h!]
+\begin{table}
     \centering
@@
     The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$
-    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).
-    The uncertainties shown refers to estimated statistical error of the Monte Carlo integrations.}
+    are rescaled to account for the effect related to the W-boson width computed by {\sc MadSpin} (see the text for details).
+    The uncertainties shown refer to estimated statistical errors of the Monte Carlo integrations.}
 \end{table}
 
-\begin{table}[h!]
+\begin{table}
     \centering
@@
     The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$
-    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
+    are rescaled to account for the effect related to the W-boson width computed by {\sc MadSpin} (see the text for details). For
     {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
 are respectively the nine-point scale uncertainty and the PDF one.
-The uncertainties shown refers to estimated statistical error of the Monte Carlo integrations.}
+The uncertainties shown refer to estimated statistical errors of the Monte Carlo integrations.}
 \end{table}
@@
 We observe that, once the width effect is taken into
-account, total rates from different tools agree within some per cents ($\le7\%$), both at LO and NLO.
-Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
+account, total rates from different tools agree within some per cents ($\le7\%$), both at LO and NLO. Larger discrepancies, however, appear for differential observables, which we discuss in
 the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
 independent or correlated variations of the renormalisation and factorisation scales.
-Concerning differential distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
+Concerning differential distributions, for each observable we display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
 with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
@@
 initial scale of the parton shower (the {\tt scalup} entry of the Les Houches Event (LHE) file \cite{Alwall:2006yp,Butterworth:2010ym}). This event-by-event number corresponds
-to the maximum hardness (translated into the shower evolution variable) of the radiation that
-can be generated by the shower. \footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense,
+to the maximum hardness (translated into the shower-evolution variable) of the radiation that
+can be generated by the shower.\footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense,
 as it is the case for the factorisation and renormalisation scales.
@@
 {\sc MG5\_aMC+Py8, $Q_{sh}/2$}.\footnote{The reduction of the shower scale for {\sc MG5\_aMC+Herwig7} gives no visible effect on any of the observables 
-discussed in this work.} The main effect of reducing the shower scale is that events migrate from the three-jet bin into the two-jet bin, i.e. less radiation is generated. The
+discussed in this work.} The main effect of reducing the shower scale is that events migrate from the three-jet bin into the two-jet bin, \emph{i.e.}\ less radiation is generated. The
 amount of this effect on the jet rate is +4\% (-8\%) on the two (three) jet bin, while the total rate within cuts is left unchanged.
 
-\begin{figure*}[hbt]
+\begin{figure*}
 \centering
@@
 
-\begin{figure*}[hbt]
+\begin{figure*}
 \centering
@@
 The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
-about -30\% at the end of the displayed range.
-At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
-For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is
-negligible, hence the corresponding histogram will not be shown.
+about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
+For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is negligible, hence the corresponding histogram is not be shown.
 
@@
 Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
-on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
+clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
 generated, \emph{e.g.}\ when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
 It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty obtained via scale variations (renormalization, factorization and shower scale) 
+the theoretical uncertainty obtained via scale variations (renormalisation, factorisation and shower scale) 
 systematically underestimates the spread of predictions. We note 
-that in the only VBF process where NNLO corrections are known, i.e. VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 
-the NLO scale-uncertainty band does not include the NNLO prediction. This suggest that the NLO scale variation 
+that in the only VBF process where NNLO corrections are known, \emph{i.e.}\ VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 
+the NLO scale-uncertainty band does not include the NNLO prediction. This suggests that the NLO scale variation 
 underestimates the size of the perturbative uncertainty. Again, this stresses the need
@@
 On the other hand, measurements of processes with similar
-color flow (EW production of a single vector boson plus jets,
+colour flow (EW production of a single vector boson plus jets,
 VBF, \ldots) can certainly help in order to discriminate which tools perform better in the comparison with data~\cite{Aaboud:2017emo,Sirunyan:2017jej}.
 
-\begin{figure*}[hbt]
+\begin{figure*}
 \centering
@@
 In the present article, a detailed study of the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC has been presented, 
-mainly focused on the electroweak production mechanism which involves the scattering of massive vector-bosons.
+mainly focused on the EW production mechanism which involves the scattering of massive vector bosons.
 Until very recently, when the complete calculation became available for the NLO QCD corrections (order $\mathcal O (\alphas\alpha^6)$),
 the so-called VBS approximation was the standard for this kind of simulations. For this reason, various theoretical predictions 
-have been compared to the full computation, both in a typical VBS fiducial region and also in more inclusive phase-space.
+have been compared to the full computation, both in a typical VBS fiducial region and also in more inclusive phase space.
 We have precisely quantified the differences that arise for several physical observables, 
-in particular for the di-jet invariant mass and the rapidity-separation of the leading two jets.
+in particular for the di-jet invariant mass and the rapidity separation of the leading two jets.
 This is the first time that such an in-depth study is performed.
@@
 The effect
-has been understood, and it can be partially mitigated by changing the recoil scheme of {\sc Pythia8} to distribute momenta within initial-final colour connections. These findings make it worth 
+has been understood, and it can be partially mitigated by changing the recoil scheme of {\sc Pythia8} to distribute momenta within initial--final colour connections. These findings make it worth 
 to further investigate these issues not only in the theoretical community, but also by experimental collaborations, for example by 
@@
         the dominant NLO contribution to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
-        It is thus highly desirable to combine them with NLO-QCD predictions matched with parton shower, or at least that they are accounted for
-        by experimental analyses. Since, as shown in Ref.~\cite{Biedermann:2016yds}, 
+        It is thus highly desirable to combine them with NLO-QCD predictions matched with parton shower, or at least to include them into experimental analyses. 
+        Since, as shown in Ref.~\cite{Biedermann:2016yds}, 
         these large EW corrections originate from the Sudakov logarithms which factorise, we recommend to combine them with QCD 
         corrections in a multiplicative way. The estimate of missing higher-order EW corrections can be done, 
-        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$,\footnote{The quantity $\delta_{\rm NLO EW}$ through the relation $\sigma_{\rm NLO EW} = \sigma_{\rm LO} \left(1+ \delta_{\rm NLO EW}\right).$} while the missing higher-order mixed QCD-EW corrections
+        in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$,\footnote{The quantity $\delta_{\rm NLO EW}$ is defined through the relation $\sigma_{\rm NLO EW} = \sigma_{\rm LO} \left(1+ \delta_{\rm NLO EW}\right).$} while the missing higher-order mixed QCD-EW corrections
         can be estimated by taking the difference between the multiplicative and additive prescriptions.
@@
         backgrounds for dark matter searches at the LHC.
+
     \item For the typical fiducial region used by experimental collaborations for their measurements, 
-        the agreement between the approximations and the full calculation is certainly satisfactory given 
+        the agreement between the approximations and the full calculation is satisfactory given 
         the current experimental precision, as well as the one foreseen for the near future \cite{CMSCollaboration:2015zni,CMS:2016rcn}.
@@
         combined measurements should also be presented as they are better defined theoretically. In fact, while at LO 
-        the interference term can be included in the background component, at NLO the separation of EW and QCD components become more blurred, as, \emph{e.g.}\,
+        the interference term can be included in the background component, at NLO the separation of EW and QCD components becomes more blurred, as, \emph{e.g.}\,
         at the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ both types of amplitudes contribute.
@@
         Note that with such a measurement a comparison to the SM would
-        be straigtforward and still be sensitive to the EW component.
+        be straightforward and still be sensitive to the EW component.
         In addition the QCD component could be subtracted based on a
-        well-defined Monte-Carlo prediction.
-
-    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguities related to the 
+        well-defined Monte Carlo prediction.
+
+    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiation and reduces the ambiguities related to the 
         matching details and/or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses. In doing

### 2018-03-15 Draft/article.tex
automatic put back

@@
 
-      \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\_aMC}) is a meta-code (a code that generates codes) which makes it possible to simulate any scattering process
+      \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\_aMC}) is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
           including NLO QCD corrections both at fixed order and including matching to parton showers, using the {\sc MC@NLO}\ method~\cite{Frixione:2002ik}.

### 2018-03-15 Draft_arXiv/article.tex
Comment of Ansgar also in Arxiv presenvering the adjustement of Barbara

@@
 
-    When considering the NLO corrections of order 
-    $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$
-    to the full process, besides real and virtual QCD corrections
+    When considering the NLO corrections of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$ to the full process, besides real and virtual QCD corrections
     to the EW tree-level contribution of order
@@
             and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
-            Only QCD-in\-ter\-act\-ing particles circulating in the loops are generated for the virtual matrix element.
+            Only strongly-in\-ter\-act\-ing particles circulating in the loops are generated for the virtual matrix element.
             The version capable of computing both QCD and EW corrections will be released in the future.
@@
         \item all $s$- and $t/u$-channel diagrams are included;
-        \item interferences between diagrams of different types ($s$/ $t$/$u$-channel) are included at LO;
-        \item diagrams which do not feature two resonant vector-bosons are included;
+        \item interferences between diagrams of different types ($s$/$t$/$u$-channel) are included at LO;
+        \item diagrams which do not feature two resonant vector bosons are included;
         \item the so-called non-factoris\-able (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
@@
 also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
-{\sc MG5\_aMC}, which
-employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
-and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the default angular-ordered shower will be employed. 
-The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
+{\sc MG5\_aMC}, which employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, is used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
+and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the default angular-ordered shower is employed. 
+The same parton showers are employed for the LO results of {\sc PHANTOM}.
+{\sc Pythia8} is also employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
 matching. As parton show\-er, both the default angular-ordered shower as
-well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton show\-er algorithms.
+well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton-show\-er algorithms.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
 
-Results will be presented within the cuts described in Sec.~\ref{subsec:inputpar}, applied after shower and hadronisation (this implies that jets
+Results are presented within the cuts described in Sec.~\ref{subsec:inputpar}, applied after shower and hadronisation (this implies that jets
 are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or even no cuts at all)
@@
 Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
-on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
+clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
 generated, \emph{e.g.}\ when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
 It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty obtained via scale variations (renormalization, factorization and show\-er scale) 
+the theoretical uncertainty obtained via scale variations (renormalisation, factorisation and show\-er scale) 
 systematically underestimates the spread of predictions. We note 
-that in the only VBF process where NNLO corrections are known, i.e. VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 
-the NLO scale-uncertainty band does not include the NNLO prediction. This suggest that the NLO scale variation 
+that in the only VBF process where NNLO corrections are known, \emph{i.e.}\ VBF Higgs production~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}, 
+the NLO scale-uncertainty band does not include the NNLO prediction. This suggests that the NLO scale variation 
 underestimates the size of the perturbative uncertainty. Again, this stresses the need
@@
         Note that with such a measurement a comparison to the SM would
-        be straigtforward and still be sensitive to the EW component.
+        be straightforward and still be sensitive to the EW component.
         In addition the QCD component could be subtracted based on a
-        well-defined Monte-Carlo prediction.
-
-    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiations and reduces the ambiguities related to the 
-        matching details and/ or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses. In doing
+        well-defined Monte Carlo prediction.
+
+    \item Since the inclusion of NLO QCD corrections gives a better control of extra QCD radiation and reduces the ambiguities related to the 
+        matching details and/or the parton shower employed, we encourage the use of NLO-accurate event generators in experimental analyses. In doing
         so, special care should be employed in order to estimate the theoretical uncertainties, as the standard prescription based on 
-        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different generators and/ or parton showers should be employed.
+        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different generators and/or parton showers should be employed.
 

### 2018-03-18 Draft_arXiv/article.tex
Some comments of Frederix implemented

@@
 Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines.
-$s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
-$u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical quarks or anti-quarks in the final state
+The $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, while for the $t$- and $u$-channel the fermion lines connect initial state quarks to final state quarks.
+The $u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical (anti-)quarks in the final state
 The $s$-channel contributions plays a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
-
 When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results.
@@
 Finally, the third contribution is the interference of the two types of amplitudes described above.
-It is non-zero only for those partonic subprocesses which involve identical quarks or antiquarks.
+It is non-zero only for those partonic subprocesses which involve identical quarks or anti-quarks.
 Such a contribution is typically small (3\%) within typical experimental cuts~\cite{Biedermann:2017bss}.
@@
 
-    When considering the NLO corrections of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$ to the full process, besides real and virtual QCD corrections
+    When considering the full NLO corrections of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, besides real and virtual QCD corrections
     to the EW tree-level contribution of order
@@
     For the fiducial cross sections it uses the VBS approximation at LO and NLO.
-    The virtual corrections are additionally approximated using a double-pole approximation.
+    The virtual corrections are additionally approximated using a double-pole approximation where the final state leptons are assumed to originate from the decay of two resonant W-bosons.\MP{Specifiy what type of DPA by citation}
     For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) can also be used.
@@
 
-    The last set of differential distributions is the invariant mass of the two charged lepton (left) and the Zeppenfeld variable for the anti-muon (right).
+    The last set of differential distributions is the invariant mass of the two charged leptons (left) and the Zeppenfeld variable for the anti-muon (right).
     Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
@@
 for their help with {\sc Herwig7}. RF, HSS, and MZ thank the {\sc MadGraph5\_\-aMC@NLO} authors for discussions, and
-they are particularly grateful to Valentin Hirschi for comments to this manuscript.
+they are particularly grateful to Valentin Hirschi for comments on this manuscript.
 

### 2018-03-18 Draft_arXiv/article.tex
Some corrections of Mathieu

@@
   Collider. The presence of triple and quartic gauge couplings in the
-  process gives access to the gauge sector of the Standard Model and
+  process gives access to the gauge sector of the Standard Model (SM) and
   possible new-physics contributions there.  To test this hypothesis,
-  sound knowledge of the Standard Model contributions is necessary,
+  sound knowledge of the SM contributions is necessary,
   with a precision which at least matches the experimental
@@
   process with two positively-charged leptons and missing transverse
-  momentum in the final state, mediated predominantly by same-sign
-  production of two $\PW$ bosons with positive charge.  In particular,
+  momentum in the final state. In particular,
   we first carry out a systematic comparison of the various
@@
 
-This article starts with the definition of the VBS process in Sec.~\ref{sec:definition}.
-After having described the approximations of the various computer 
-codes in Sec.~\ref{sec:details}, in Sec.~\ref{sec:LO} a leading-order (LO) study 
+This article starts with the definition of the VBS process in Sec.~\ref{sec:definition}, before describing the approximations of the various computer 
+codes in Sec.~\ref{sec:details}. In Sec.~\ref{sec:LO} a leading-order (LO) study 
 of the different contributions which lead to the production of two same-sign $\PW$ bosons and 
-two jets is performed, as a function of typical VBS cuts. In the same section predictions for VBS from different tools are compared at 
-the level of the cross section and differential distributions. The article continues in Sec.~\ref{sec:NLO} where the comparison is extended to the
-NLO corrections to VBS. The effect of the inclusion of matching LO and NLO computations to parton shower (PS) is 
+two jets is performed. In the same section predictions for VBS from different tools are compared at 
+the level of the cross section and differential distributions.
+The comparison is extended to the
+NLO corrections to VBS in Sec.~\ref{sec:NLO}. The effect of the inclusion of matching LO and NLO computations to parton shower (PS) is 
 discussed in Sec.~\ref{sec:matching}. Finally,
@@
 The first, commonly referred to as EW contribution or VBS,\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
-of vector bosons.} receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
+of vector bosons.} receives contributions from Feynman diagrams such as those depicted in Fig.~\ref{diag:LO}:
 in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
@@
 radiated off the quark lines. Because of the different colour structure, this contribution features a 
-different kinematic behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.
+different kinematic behaviour than VBS.
+Nonetheless they share the same final state, and therefore constitutes an irreducible background to EW process.
 
 Finally, the third contribution is the interference of the two types of amplitudes described above.
-It is non-zero only for those partonic subprocesses which involve identical quarks or anti-quarks.
-Such a contribution is typically small (3\%) within typical experimental cuts~\cite{Biedermann:2017bss}.
+It is non-zero only for those partonic sub-processes which involve identical quarks or anti-quarks.
+Such a contribution is typically small ($3\%$) within typical experimental cuts~\cite{Biedermann:2017bss}.
 
@@
     The initial-state gluon and quark 
-        must not couple together, otherwise infrared divergences proportional to $s$-channels appear, 
+        must not couple together, otherwise infrared (IR) divergences proportional to $s$-channels appear, 
          which do not match with the ones found in the virtual contributions.
@@
     In particular one can consider only one-loop amplitudes where there is no gluon exchange between the two quark lines and 
-    assuming a cancellation of the infrared (IR) poles.
+    assuming a cancellation of the IR poles.
 
@@
         \label{subsec:codedescr}
-    In the following, the codes employed throughout this paper and the approximations implemented in each of them are discussed:
+    In the following, the codes employed throughout this article and the approximations implemented in each of them are discussed:
 
@@
     One-loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
-    For the fiducial cross sections it uses the VBS approximation at LO and NLO.
-    The virtual corrections are additionally approximated using a double-pole approximation where the final state leptons are assumed to originate from the decay of two resonant W-bosons.\MP{Specifiy what type of DPA by citation}
-    For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) can also be used.
+    For the results presented here, it uses the VBS approximation at LO and NLO.
+    The virtual corrections are additionally approximated using a double-pole approximation where the final state leptons are assumed to originate from the decay of two resonant W-bosons.\MP{Specify what type of DPA by citation}
+    At LO the exact matrix elements can also be used.
 
@@
     \end{verbatim}
-      With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded\footnote{Despite
+      With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded,\footnote{Despite
                 the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing EW corrections, it is not yet possible to compute such corrections
-            with the current public version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-EW process)
+            with the current public version of the code.} finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-EW process)
             and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
@@
     In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
-    The code has demonstrated its ability to compute at NLO high-multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
+    The code has demonstrated its ability to compute NLO corrections for high-multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
     In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained thanks to this tool.
@@
       \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six-parton final states 
-      at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
+      at $\Pp \Pp,\, \Pp\bar{\Pp}$, and $\Pe^+\Pe^-$ colliders at orders $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
     It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
@@
       \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
-    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
+    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space phase corresponding to the real emission.
     For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.
@@
     huge number of BSM models as well, in particular in
-    the VBS channel in terms of both higher-dimensional operators as well as explicit
+    the VBS channels in terms of both higher-dimensional operators as well as explicit
     resonances.
@@
     \begin{itemize}
-        \item all $s$- and $t/u$-channel diagrams are included;
-        \item interferences between diagrams of different types ($s$/$t$/$u$-channel) are included at LO;
-        \item diagrams which do not feature two resonant vector bosons are included;
+        \item all $s$-,$t$-,$u$-channel diagrams are included;
+        \item interferences between diagrams of different types are included at LO;
+        \item diagrams which do not feature two resonant W bosons are included;
         \item the so-called non-factoris\-able (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
@@
             \hline
-            {\sc Bonsay}        &  $t,u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
-            {\sc Powheg}        &  $t,u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+            {\sc Bonsay}        &  $t,u$    &  No       &  No		    &  Yes   & No       &  No  \\
+            {\sc Powheg}        &  $t,u$    &  No       &  No               &  Yes   & No       &  No  \\
             {\sc MG5\_aMC}      &  $s,t,u$  &  Yes      &  Yes              &  Yes   & virt. No &  No \\
@@
     %
-    The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj}, where
-    %
+    The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} according to 
     \begin{equation}
-        G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
+    \alpha =  \frac{\sqrt{2}}{\pi} G_{\mu} M_{\rm W}^2 \left(1-\frac{M_{\rm W}^2}{M_{\rm Z}^2} \right),
     \end{equation}
-    %
+    with
+    %
+    \begin{equation}
+        G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2},
+    \end{equation}
+    %
+    and where $M_V$ corresponds to the real part of the squared pole mass.
     The numerical value of $\alpha$, corresponding to the choice of input parameters is
@@
     The QCD contribution does not possess external gluons due to charge conservation.
-    Thus the diagrams of order $\mathcal{O}(g_{\rm s}^2g^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
+    Thus the diagrams of order $\mathcal{O}(g_{\rm s}^2g^4)$ only involve gluon exchange between the quark lines.
     This results in a small contribution even if the VBS cuts have not been imposed.
@@
 
-    In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
+    In Fig.~\ref{fig:mjjdyjj_1d}, these three contributions are shown separately and summed in the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
     For the di-jet invariant-mass distribution (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
     This is due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
-    Note that these contributions are not present in calculations relying on the VBS approximation.
+    Note that these contributions are not present in calculations relying on the VBS approximation as these are only $s$-channel contributions.
     The EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
@@
     described in Sec.~\ref{subsec:inputpar}. We note that several full predictions are not in statistical agreement. These are possibly due to Monte Carlo 
-    integrators performing too aggressive estimations of statistical uncertainties. Nonetheless, all these predictions agree within less than $0.5\%$.
+    integrators performing too aggressive estimations of statistical uncertainties or different implementation of the complex-mss scheme.
+    Nonetheless, all these predictions agree within less than $0.5\%$.
     At the level of the cross section, it seems difficult to infer the quality of the various approximations.
@@
     In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
-    for which we also display the scale-uncertainty band (seven-points variation as done in Eq.~(3.11) of Ref.~\cite{Biedermann:2017bss}).
+    for which we also display the scale-uncertainty band (seven-points variation defined as in Eq.~(3.11) of Ref.~\cite{Biedermann:2017bss}).
     For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as interferences are suppressed in the fiducial region.
@@
        \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/mjj_LO.pdf}
-       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
-    \caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right) at LO accuracy and order $\mathcal{O}(\alpha^6)$.
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.3cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
+    \caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right) at LO accuracy \emph{i.e.}\ at order $\mathcal{O}(\alpha^6)$.
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
@@
     the difference between the $|t|^2+|u|^2$ approximation and the full computation can be above $30\%$.
-    The inclusion of $s$-channels cures partly this behaviour by improving the approximation to about $10\%$.
+    The inclusion of $s$-channel contributions cures partly this behaviour by improving the approximation to about $10\%$.
     This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
@@
     \caption{
-    Differential distributions in the di-jet invariant mass (left) and the rapidity separation of the two tagging jets (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+    Differential distributions in the di-jet invariant mass (left) and the rapidity separation (right) of the two tagging jets at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
     The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
@@
     {\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
-    \caption{Ratios for double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the VBS approximation over the full computation of the approximated squared amplitudes over the full matrix element.
+    \caption{Ratios for double-differential distributions in the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ of the approximated squared amplitudes over the full matrix element.
     The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2+|u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2+|t|^2+|u|^2$ (right).
@@
     {\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
-    \caption{Differential distributions in the transverse momentum (left) and rapidity of the hardest tagging jet (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
+    \caption{Differential distributions in the transverse momentum (left) and rapidity (right) of the hardest tagging jet at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
     The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
@@
     %
-    Analogous definitions are later also be used for the Zeppenfeld variable of the muon and of the third jet.
+    Analogous definitions are later also used for the Zeppenfeld variable of the muon and of the third jet.
     %
@@
     In conclusion, both the loose minimum di-jet invariant-mass cut and the inclusion of QCD radiative corrections render the $s$-channel contributions less suppressed than at LO, making their inclusion mandatory, in order to provide trustworthy predictions at NLO accuracy.
-    In the inclusive region studied here, neglecting $s$-channel, non-factorisable corrections, and EW corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.
+    In the inclusive region studied here, neglecting $s$-channel contributions, non-factorisable corrections, and EW corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.
     Nevertheless, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($m_{\Pj\Pj} \gtrsim 500 \GeV$, $|\Delta y_{\Pj\Pj}| \gtrsim 2.5$), for both total cross section and differential distributions.
@@
     Not unexpectedly none of the approximations used here agrees perfectly with the full calculation of {\sc MoCaNLO\-+Recola} at NLO.
-    Nevertheless, the disagreement seems to never exceed $2\%$ at the fiducial cross-section level.
+    Nevertheless, the disagreement seems never to exceed $2\%$ at the fiducial cross-section level.
 
@@
     In the upper panel, the absolute predictions are shown while in the lower panel, the ratio with respect to the full predictions are displayed.
-    The band corresponds to a seven-points variation of the factorisation and renormalisation scales.
+    The band corresponds to a seven-points variation of the factorisation and renormalisation scales (as defined in Eq.~(3.11) of Ref.~\cite{Biedermann:2017bss}).
 
@@
        \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
-    \caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
-    The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+    \caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference (right) of the two tagging jets at NLO accuracy \emph{i.e.}\ at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
@@
        \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/ptj1_NLO.pdf}
-       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
-    \caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
-    The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+       \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.3cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
+    \caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity (right) of the hardest jet at NLO accuracy \emph{i.e.}\ at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
@@
        \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
-    \caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
-    The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+    \caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right) \emph{i.e.}\ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
@@
     This can be explained by the fact that $s$-channel contributions are less suppressed at NLO.
-    As real radiation, an extra gluon-jet can be radiated from any of the charged particles while the two quarks originating from the W-boson decay can be recombined in a single jet.
+    As real radiation, an extra gluon-jet can be radiated from any of the strongly-interacting particles while the two quarks originating from the W-boson decay can be recombined in a single jet.
     Therefore, the jet requirements ($ m_{\Pj \Pj} >  500\GeV$ and $|\Delta y_{\Pj \Pj}| > 2.5$) that were suppressing $s$-channel contributions at LO are partially lifted with the inclusion of a third jet at NLO.
@@
 matching. As parton show\-er, both the default angular-ordered shower as
-well as the dipole shower can be employed. We here use the subtractive (MC@NLO-type) matching to these parton-show\-er algorithms.
+well as the dipole shower can be employed. We use here the subtractive (MC@NLO-type) matching to these parton-show\-er algorithms.
 Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.
@@
 renormalisation and factorisation scales, Eq.~(\ref{eq:defscale}), are now defined without imposing
-the $\Delta R_{\Pj\Pl}$ cut. The effect of this change is below one per cent at the level of the fiducial cross sections.
+the $\Delta R_{\Pj\Pl}$ cut. The effect of this change is below one per cent at the level of the fiducial cross sections at NLO.
 
@@
 events are produced for the process with two stable ${\rm W}^+$-bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and the decay of these ${\rm W}^+$-bosons
-is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the PS. Since {\sc MadSpin}\ computes
+is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the parton shower. Since {\sc MadSpin}\ computes
 the partial and total decay widths of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
@@
 discussed in this work.} The main effect of reducing the shower scale is that events migrate from the three-jet bin into the two-jet bin, \emph{i.e.}\ less radiation is generated. The
-amount of this effect on the jet rate is +4\% (-8\%) on the two (three) jet bin, while the total rate within cuts is left unchanged.
+size of this effect on the jet rate is +4\% (-8\%) on the two (three) jet bin, while the total rate within cuts is left unchanged.
 
@@
 about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
-For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is negligible, hence the corresponding histogram is not be shown.
-
-The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities to the invariant-mass distribution.
+For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is negligible, hence the corresponding histogram is not shown.
+
+The rapidity difference between the two tagging jets, shown in Fig.~\ref{fig:PSdyjj}, has some similarities with the invariant-mass distribution.
 At LO+PS all predictions show the tendency to deplete the large-separation region with respect to the fixed-order prediction, in a
@@
 Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
-clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in detail the way QCD radiation is
+clearly suggest not to rely on a single tool/parton shower, and on the other make it worth investigating more in detail the way QCD radiation is
 generated, \emph{e.g.}\ when fully-differential computations at NNLO will become available (for VBF Higgs production, see Refs.~\cite{Cacciari:2015jma, Cruz-Martinez:2018rod}).
 It is a remarkable fact that, even for those observables that display small discrepancies,
-the theoretical uncertainty obtained via scale variations (renormalisation, factorisation and show\-er scale) 
+the theoretical uncertainty obtained via scale variations (renormalisation, factorisation, and show\-er scale) 
 systematically underestimates the spread of predictions. We note 
@@
 The last part of our work is devoted to 
- remarks and recommendations concerning the usage of theoretical predictions by experimental collaborators.
+ remarks and recommendations concerning the usage of theoretical predictions by experimental collaborations.
 \begin{itemize}
@@
         these large EW corrections originate from the Sudakov logarithms which factorise, we recommend to combine them with QCD 
-        corrections in a multiplicative way. The estimate of missing higher-order EW corrections can be done, 
+        corrections in a multiplicative way. The estimate of missing higher-order EW corrections can be obtained, 
         in a first approximation, by considering $\pm \delta^2_{\rm NLO EW}$,\footnote{The quantity $\delta_{\rm NLO EW}$ is defined through the relation $\sigma_{\rm NLO EW} = \sigma_{\rm LO} \left(1+ \delta_{\rm NLO EW}\right).$} while the missing higher-order mixed QCD-EW corrections
@@
         be straightforward and still be sensitive to the EW component.
-        In addition the QCD component could be subtracted based on a
+        In addition, the QCD component could be subtracted based on a
         well-defined Monte Carlo prediction.
@@
 
-The authors are grateful to the members of the VBSCan collaboration for several discussions and comments to this work. The author also thank
-the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand, and Peter Skands for 
-discussions and clarifications about the third-jet rapidity spectrum. MZ would like to talk Andreas Papaefstathiou, Christian Reuschle and David Grellscheid 
+The authors are grateful to the members of the VBSCan collaboration for several discussions and comments on this work. The author also thank
+the {\sc Pythia8} developers, in particular Stefan Prestel, Torbj{\"o}rn Sj{\"o}strand, and Peter Skands for 
+discussions and clarifications about the third-jet rapidity spectrum. MZ would like to thank Andreas Papaefstathiou, Christian Reuschle and David Grellscheid 
 for their help with {\sc Herwig7}. RF, HSS, and MZ thank the {\sc MadGraph5\_\-aMC@NLO} authors for discussions, and
@@
 German Federal Ministry for Education and Research (BMBF) under
-contract no.~05H15WWCA1 and the German Science Foundation (DFG) under
+contract no.~05H15WWCA1 and the German Research Foundation (DFG) under
 reference number DE 623/6-1.
-SD and CS acknowledge support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.
+SD and CS acknowledge support by the state of Baden-W\"urttemberg through bwHPC and the DFG through grant no. INST 39/963-1 FUGG and grant DI 784/3.
 The work of BJ was supported in part by the Institutional Strategy of the University of T\"ubingen (DFG, ZUK 63) and in part by
@@
 AK acknowledges financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
-MR acknowledges funding from the European Union's Horizon 2020 research and innovation programme as part of the Marie Sklodowska-Curie Innovative Training Network MCnetITN3 (grant agreement no.
+MR acknowledges funding from the European Union's Horizon 2020 research and innovation programme as part of the Marie Sk\l{}odowska-Curie Innovative Training Network MCnetITN3 (grant agreement no.
 722104).
 HSS is supported by the ILP Labex (ANR-11-IDEX-0004-02, ANR-10-LABX-63).
-GZ is supported by ERC Consolidator Grant HICCUP (No. 614577).
+GZ is supported by ERC Consolidator Grant HICCUP (no. 614577).
 MZ is supported by the Netherlands National Organisation for Scientific Research (NWO).

### 2018-03-18 Draft_arXiv/article.tex
Comment Mathieu

@@
 The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
-among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
+among tools are reduced to about $10\%$.
+For the three-jet bin, which is described only at LO accuracy\MP{Here only MG has the full ME and we have argued that the s-channel contribution can be large in the real.
+A comment might be in order.}, differences among tools remain large: the largest rate is predicted by
 {\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated

### 2018-03-18 Draft_arXiv/article.tex
fixed some margin problems

@@
 
-      \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\_aMC}) is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
+      \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} (henceforth {\sc MG5\-\_aMC}) is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
           including NLO QCD corrections both at fixed order and including matching to parton showers, using the {\sc MC@NLO}\ method~\cite{Frixione:2002ik}.
@@
     In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
-    for which we also display the scale-uncertainty band (seven-points variation defined as in Eq.~(3.11) of Ref.~\cite{Biedermann:2017bss}).
+    for which we also display the scale-uncertainty band (seven-points variation as in Eq.~(3.11) of Ref.~\cite{Biedermann:2017bss}).
     For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as interferences are suppressed in the fiducial region.
@@
     In the inclusive region studied here, neglecting $s$-channel contributions, non-factorisable corrections, and EW corrections can lead to discrepancies of up to $30\%$ with respect to the full computation.
-    Nevertheless, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where VBS contributions are dominant ($m_{\Pj\Pj} \gtrsim 500 \GeV$, $|\Delta y_{\Pj\Pj}| \gtrsim 2.5$), for both total cross section and differential distributions.
+    Nevertheless, the VBS approximation at NLO provides a good approximation of full calculations in the kinematic region where $m_{\Pj\Pj} \gtrsim 500 \GeV$ and $|\Delta y_{\Pj\Pj}| \gtrsim 2.5$), for both total cross section and differential distributions.
     This more exclusive region is studied in more detail in the next section.

### 2018-03-18 Draft_arXiv/article.tex
implemented last comment by rikkert, plus fixed some typos

@@
     For the real-emission contributions special care must be taken for the gluon-initiated processes.
-    The initial-state gluon and quark 
+    The initial-state gluon and initial-state quark 
         must not couple together, otherwise infrared (IR) divergences proportional to $s$-channels appear, 
@@
     described in Sec.~\ref{subsec:inputpar}. We note that several full predictions are not in statistical agreement. These are possibly due to Monte Carlo 
-    integrators performing too aggressive estimations of statistical uncertainties or different implementation of the complex-mss scheme.
+    integrators performing too aggressive estimations of statistical uncertainties or different implementation of the complex-mass scheme.
     Nonetheless, all these predictions agree within less than $0.5\%$.
@@
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
-    The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
+    The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provide the full prediction.
     The band corresponds to a seven-point variation of the renormalisation and factorisation scales.
@@
     Differential distributions in the di-jet invariant mass (left) and the rapidity separation (right) of the two tagging jets at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provide the full prediction.
     In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
@@
     \caption{Differential distributions in the transverse momentum (left) and rapidity (right) of the hardest tagging jet at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
+    The upper plots provide the absolute value for each prediction while the lower plots present all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provide the full prediction.
     In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
@@
     \caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
-    The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provides the full prediction.
+    The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the programs that provide the full prediction.
     In addition to the cuts of Sec.~\protect\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
@@
 The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
-among tools are reduced to about $10\%$.
-For the three-jet bin, which is described only at LO accuracy\MP{Here only MG has the full ME and we have argued that the s-channel contribution can be large in the real.
-A comment might be in order.}, differences among tools remain large: the largest rate is predicted by
+among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large, and are
+possibly related to the underlying approximation performed, in particular the inclusion of the $s$-channel contributions: the largest rate is predicted by
 {\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated

### 2018-03-19 Draft_arXiv/article.tex
small fixes in the draft

@@
   process gives access to the gauge sector of the Standard Model (SM) and
-  possible new-physics contributions there.  To test this hypothesis,
+  possible new-physics contributions there.  To test any new-physics hypothesis,
   sound knowledge of the SM contributions is necessary,
@@
 It is non-zero only for those partonic sub-processes which involve identical quarks or anti-quarks.
-Such a contribution is typically small ($3\%$) within typical experimental cuts~\cite{Biedermann:2017bss}.
+Such a contribution is normally small ($3\%$) within typical experimental cuts~\cite{Biedermann:2017bss}.
 
@@
       \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
-    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space phase corresponding to the real emission.
+    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space corresponding to the real emission.
     For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.

### 2018-03-19 Draft_arXiv/article.tex
Small corrections

@@
 among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large, and are
-possibly related to the underlying approximation performed, in particular the inclusion of the $s$-channel contributions: the largest rate is predicted by
+possibly related to the underlying approximation performed ({\sc MG5\_aMC} is the only tool to use the full matrix elment for the real radiation), in particular the inclusion of the $s$-channel contributions: the largest rate is predicted by
 {\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
@@
 discussed in this work.} The main effect of reducing the shower scale is that events migrate from the three-jet bin into the two-jet bin, \emph{i.e.}\ less radiation is generated. The
-size of this effect on the jet rate is +4\% (-8\%) on the two (three) jet bin, while the total rate within cuts is left unchanged.
+size of this effect on the jet rate is $+4\%$ ($-8\%$) on the two (three) jet bin, while the total rate within cuts is left unchanged.
 

### 2018-03-19 Draft_arXiv/article.tex
M_V^2
usually+biblio fixed

@@
 It is non-zero only for those partonic sub-processes which involve identical quarks or anti-quarks.
-Such a contribution is normally small ($3\%$) within typical experimental cuts~\cite{Biedermann:2017bss}.
+Such a contribution is usually small ($3\%$) within typical experimental cuts~\cite{Biedermann:2017bss}.
 
@@
     %
-    and where $M_V$ corresponds to the real part of the squared pole mass.
+    and where $M_V^2$ corresponds to the real part of the squared pole mass.
     The numerical value of $\alpha$, corresponding to the choice of input parameters is

### 2018-03-19 Draft_arXiv/article.tex
Bonsay DPA

@@
     For the results presented here, it uses the VBS approximation at LO and NLO.
-    The virtual corrections are additionally approximated using a double-pole approximation where the final state leptons are assumed to originate from the decay of two resonant W-bosons.\MP{Specify what type of DPA by citation}
+    The virtual corrections are additionally approximated using a double-pole approximation where the final state leptons are assumed to originate from the decay of two resonant W-bosons; see Ref.~\cite{Denner:2000bj} for a
+detailed description and Ref.~\cite{Dittmaier:2015bfe} for the on-shell projection used.
     At LO the exact matrix elements can also be used.

### 2018-03-20 Draft_arXiv/article.tex
put back resonant diag for Bonsay/Powheg
Comment Juergen

@@
 different kinematic behaviour than VBS.
-Nonetheless they share the same final state, and therefore constitutes an irreducible background to EW process.
+Nonetheless it shares the same final state, and therefore constitutes an irreducible background to EW process.
 
@@
             \hline
-            {\sc Bonsay}        &  $t,u$    &  No       &  No		    &  Yes   & No       &  No  \\
-            {\sc Powheg}        &  $t,u$    &  No       &  No               &  Yes   & No       &  No  \\
+            {\sc Bonsay}        &  $t,u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
+            {\sc Powheg}        &  $t,u$    &  No       &  Yes              &  Yes   & No       &  No  \\
             {\sc MG5\_aMC}      &  $s,t,u$  &  Yes      &  Yes              &  Yes   & virt. No &  No \\

### 2018-03-20 Draft_arXiv/article.tex
Typo fixed
Final description of Whizard

@@
 different kinematic behaviour than VBS.
-Nonetheless it shares the same final state, and therefore constitutes an irreducible background to EW process.
+Nonetheless it shares the same final state, and therefore constitutes an irreducible background to the EW process.
 
@@
 
-      \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
-          event generator with the LO matrix element generator {\sc O'Mega}.
-\ZM{ if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
-    It provides FKS subtraction terms for any NLO process, while virtual matrix
-    elements are provided externally by {\sc
-    OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
-    (\emph{cf.}\ above) can be used as well). {\sc Whizard} allows to simulate a
-    huge number of BSM models as well, in particular in
-    the VBS channels in terms of both higher-dimensional operators as well as explicit
-    resonances.
+      \item WHIZARD~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
+      For QCD amplitudes it uses the colour flow formalism~\cite{Kilian:2012pz}.
+      For NLO QCD calculations~\cite{Nejad:2016bci}, where WHIZARD is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
+      Furthermore, WHIZARD can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
+      WHIZARD allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
 

### 2018-03-21 Draft_arXiv/article.tex
Comemnts of Juergen

@@
     \begin{equation}
-      z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
+      z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj_2}}2}{|\Delta y_{jj}|} \,.
       \label{eq:Zeppenfeld}
@@
     The difference at high transverse momentum between the latter predictions and the full computation can be attributed to EW Sudakov logarithms that become large in this phase-space region.
-    While, the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different at low transverse momentum where it is even higher than the full computation.
+    While the predictions of {\sc Bonsay} and {\sc Powheg} are rather close over the whole range, the one of {\sc VBFNLO} is very different at low transverse momentum where it is even higher than the full computation.
     We note that for the transverse momentum of the second hardest jet, the predictions from {\sc MG5\_aMC} are in good agreement with the other VBS-approximated predictions.
@@
 For the former, we show both PDF and scale uncertainties,\footnote{A preliminary study on PDF uncertainties in VBS has appeared
-in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorisation
+in Ref.~\cite{Dittmaier:2018zzz}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorisation
 scales by a factor of two around the central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
@@
 Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
-experimental analyses should rely as little as possible on those observables and, in any case, use conservative estimate of the theory
+experimental analyses should rely as little as possible on those observables and, in any case, use conservative estimates of the theory
 uncertainties. On the one hand, in order to improve the
@@
         so, special care should be employed in order to estimate the theoretical uncertainties, as the standard prescription based on 
-        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different generators and/or parton showers should be employed.
+        renormalisation and factorisation-scale variation is clearly inadequate. Rather, different combinations of generators and parton showers should be employed.
 

### 2018-03-21 Draft_arXiv/article.tex
Corrections of Michael

@@
   hand, the inclusion of NLO QCD corrections leads to more stable
-  predictions, but on the other the details of the matching and of the
+  predictions, but on the other hand the details of the matching and of the
   parton-shower programs cause differences which are considerably
   larger than those observed at fixed order, even in the experimental
-  fiducial region.  We conclude with some recommendations for
+  fiducial region.  We conclude with recommendations for
   experimental studies of vector-boson scattering processes.\\[5mm]
@@
 The $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, while for the $t$- and $u$-channel the fermion lines connect initial state quarks to final state quarks.
-The $u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical (anti-)quarks in the final state
+The $u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical (anti-)quarks in the final state.
 The $s$-channel contributions plays a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
@@
 
-The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
+The second coupling combination of order $\mathcal{O}{\left(\alpha_{\rm s}^2\alpha^{4}\right)}$ corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
 radiated off the quark lines. Because of the different colour structure, this contribution features a 
@@
 
-Finally, the third contribution is the interference of the two types of amplitudes described above.
+Finally, the third contribution of order $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$ is the interference of the two types of amplitudes described above.
 It is non-zero only for those partonic sub-processes which involve identical quarks or anti-quarks.
@@
     The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
-    The full calculation is approximated at the level of $\pm5\%$ apart from the region where $|\Delta y_{\Pj\Pj}| < 2$.
+    The full calculation is approximated at the level of $\pm5\%$ everywhere apart in the region where $|\Delta y_{\Pj\Pj}| < 2$.
 
@@
 the numbers with $\Gamma_{\rm resc}$ are rescaled to
-take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
+take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}+{\sc Herwig7-Dipole}, we also quote
 theoretical uncertainties.
@@
 For the latter, we show the
-three-point scale uncertainties, obtained by considering correlated variations of the renormalisation and factorisation scales.
+three-point scale uncertainties, obtained by considering correlated variations of the renormalisation, factorisation, and shower starting scale.
 Theory uncertainties should have very little dependence on the tool employed.
@@
 The LO+PS predictions tend to be significantly softer than the fixed NLO one, with an effect of
-about -30\% at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
-For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is negligible, hence the corresponding histogram is not shown.
+about $-30\%$ at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
+For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is negligible, hence it is not shown.
 
@@
  to employ at least two different tools in order to obtain a conservative estimate of theoretical uncertainties.
-Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that
+Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggests that
 experimental analyses should rely as little as possible on those observables and, in any case, use conservative estimates of the theory

### 2018-04-04 Draft_arXiv/article.tex
References updated/added

@@
 it is thus of prime importance to provide predictions with systematic uncertainties
-at least comparable to the current and envisaged experimental precision~\cite{CMS:2016rcn}.
+at least comparable to the current and envisaged experimental precision~\cite{CMS:2016rcn,ATL-PHYS-PUB-2017-023}.
 
@@
         the agreement between the approximations and the full calculation is satisfactory given 
-        the current experimental precision, as well as the one foreseen for the near future \cite{CMSCollaboration:2015zni,CMS:2016rcn}.
+        the current experimental precision, as well as the one foreseen for the near future \cite{CMSCollaboration:2015zni,CMS:2016rcn,ATL-PHYS-PUB-2017-023}.
         Nonetheless, care has to be taken when using such approximations, in particular if more inclusive phase-space cuts are used.

### 2018-06-11 Draft_EPJC/Referee/answer_referee.tex
added new folder with revised draft and answer to the referee

\documentclass{report}
\usepackage[margin=2.5cm]{geometry}
\usepackage{amssymb}
\usepackage{color}

\newcommand{\smallz}{{\scriptscriptstyle Z}}
\newcommand{\smallw}{{\scriptscriptstyle W}}
\newcommand{\mz}{m_\smallz}
\newcommand{\mw}{m_\smallw}
\newcommand{\qsh}{Q_{sh}}
\newcommand{\ptw}{p_\perp^{\ell\nu}}
\newcommand{\ptz}{p_\perp^{\ell^+\ell^-}}
\newcommand{\ptv}{p_\perp^{\smallv}}
\newcommand{\amcnlo}{{\sc MG5\_aMC}\,\,}
\newcommand{\amcnlonospace}{{\sc MG5\_aMC}}
\newcommand{\powheg}{{\sc POWHEG}\,\,}
\newcommand{\powhegnospace}{{\sc POWHEG}}
\newcommand{\pythia}{{\sc Pythia8}\,\,}

\begin{document}

\noindent

\begin{center}
  \LARGE \textbf{Author answer to the referee report of JHEP\_187P\_0318}
\end{center}
\vspace{0.5cm}
We thank the referee for the positive report and for his insightful comments and detailed comments. Below, we address all the questions and suggestions contained in the report in order. To ease the reading, the points raised by the referee (quoted in italic) are followed by an  explanation of the actions undertaken to address them.

\vspace{0.5cm}
\begin{enumerate}

    \item \emph{ At the beginning of Sec. 2 "LO" is defined as the three possible coupling
combinationas $\alpha^6$, $\alpha_s \alpha^5$, $\alpha_s^2 \alpha^4$. However for most of the paper "LO" is more 
and more taken equivalent to only mean the EW $\alpha^6$ contribution. (At first it still says "LO at $\alpha^6$", 
then it becomes
LO i.e. $\alpha^6$, and eventually in the LO+PS section the coupling order is dropped completely. 
This is of course just semantics, but it was quite confusing on the first reading and it would be good to make this a bit clearer from the start.}

    \item \emph{The ordering of the various programs in tables 1, 3, and 5 is very helpful.
I can perhaps understand the reasoning behind choosing this alphabetical
ordering, but I think it is misplaced here and makes it quite hard to get
anything out of this. It would be much more useful to have programs with similar levels of approximations next to each other. So keep Phantom and Whizard together (both having the same approxmations), then Bonsay, Powheg, VBFNLO (all without interference with VBFNLO adding the s-channel), then MG5\_AMC (also adding interference), and last MoCaNLO+Recola having the full result.}

\item \emph{In table 3: Please indicate which ones are exact at LO, and which ones are not. Also, regarding the discussion in Sec. 4.3 and the fact that several full LO
predictions differ far outside their statistical MC uncertainties. This I find
extremely puzzling and the offered explanations are quite unsatisfactory. After
all, at LO, MC statistics is just statistics, I don't understand how statistical
uncertainties can be aggressive or not, they are what they are.
Also, the complex-mass scheme is a well-defined procedure, so how can different implementations of it lead to numerical differences? (If there are somewhat different approximations being employed, it would be good to spell this out clearly.) The fact that the differences are at the 0.5\% level
cannot hide the fact that they are much much bigger than the MC statistics.
Taken at face value, that means that there are clear systematic differences where from what I understand there shouldn't be any, so the reader is left to wonder what is going on? To play the devil's advocate, if there are systematic differences at LO that cannot be understood, how can I trust the NLO comparison?}

\item \emph{ page 16, 2nd column, line 13, typo: "elment" $\to$ "element"}\\
    It has been corrected

\item \emph{ page 18, 2nd column, line 48: "on the other ..." the part of the sentence is
    nonsensical.}
\item \emph{page 19, 1st column, line 14:
I think it is important to not mistake "more realistic" for "conservative". The
scale variations are clearly underestimating the actual theoretical uncertainties. This does not mean that another method, which implies larger uncertainties, is "conservative", it is simply (hopefully) "more realistic". Conservative is easily (mis)interpreted as possibly overestimated, which I don't think is the case here. (In fact, there is no guarantee that even the comparison of different tools will provide an estimate that covers the next order, so calling this a conservative estimate is really misplaced.}
\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-06-11 Draft_EPJC/Referee/answer_referee.tex
Modifications according to the discussion

@@
 \vspace{0.5cm}
-We thank the referee for the positive report and for his insightful comments and detailed comments.
+We thank the referee for the positive report and for her/his insightful comments and detailed comments.
 Below, we address all the questions and suggestions contained in the report in order.
@@
 
+Answer: Before section 3, ``if not specified explicitly LO refers to the order alpha6.
+In the same way, NLO refers if not specified to the order alphas alpha6''.
+
     \item \emph{The ordering of the various programs in tables 1, 3, and 5 is very helpful.
@@
 So keep Phantom and Whizard together (both having the same approxmations), then Bonsay, Powheg, VBFNLO (all without interference with VBFNLO adding the s-channel), then MG5\_AMC (also adding interference), and last MoCaNLO+Recola having the full result.}
+
+Answer: We have changed the order as suggested.
+For consistency, we have also changed the order of the description of the various codes in section...
 
@@
 
+Answer: PSP and maybe then just argue about the physical message.
+
 \item \emph{ page 16, 2nd column, line 13, typo: "elment" $\to$ "element"}\\
-    It has been corrected
+
+Answer: It has been corrected
 
@@
     nonsensical.}
+
+Answer: ``which clearly suggest not to rely on a single tool/parton shower, and on the other make'' ->
+    ``which on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make''
+
 \item \emph{page 19, 1st column, line 14:
@@
 (In fact, there is no guarantee that even the comparison of different tools will provide an estimate that covers the next order, so calling this a conservative estimate is really misplaced.}
+
+Answer: "conservative" -> "more realistic"
+
 \end{enumerate}

### 2018-06-11 Draft_EPJC/Referee/answer_referee.tex
work on answer
more on the referee answer

--- 2018-06-11 Draft_EPJC/Referee/answer_referee.tex
@@
 \begin{center}
-  \LARGE \textbf{Author answer to the referee report of JHEP\_187P\_0318}
+  \LARGE \textbf{Author answer to the referee report of EPJC-18-04-021}
 \end{center}
 \vspace{0.5cm}
-We thank the referee for the positive report and for his insightful comments and detailed comments.
+We thank the referee for the positive report and for her/his insightful comments and detailed comments.
 Below, we address all the questions and suggestions contained in the report in order.
@@
 
-    \item \emph{ At the beginning of Sec. 2 "LO" is defined as the three possible coupling
+    \item \emph{At the beginning of Sec. 2 "LO" is defined as the three possible coupling
 combinationas $\alpha^6$, $\alpha_s \alpha^5$, $\alpha_s^2 \alpha^4$. However for most of the paper "LO" is more 
@@
 This is of course just semantics, but it was quite confusing on the first reading and it would be good to make this a bit clearer from the start.}
+
+In section 2, before the last paragraph, we have added the following sentence
+\begin{quote}
+In the rest of this paper, the notation ``LO'' or ``NLO(-QCD)'' without any specification of coupling powers will refer to the contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$ respectively.
+\end{quote}
+For better clarity, we have also re-stated the coupling orders at the beginning of section 6 (Matching to parton shower).
 
@@
 So keep Phantom and Whizard together (both having the same approxmations), then Bonsay, Powheg, VBFNLO (all without interference with VBFNLO adding the s-channel), then MG5\_AMC (also adding interference), and last MoCaNLO+Recola having the full result.}
+
+We have changed the order as suggested.
+For consistency, we have also changed the order of the description of the various codes in section 3.2, and of the
+results in tables 3 and 5.
 
@@
 
-\item \emph{ page 16, 2nd column, line 13, typo: "elment" $\to$ "element"}\\
+Answer: PSP and maybe then just argue about the physical message.
+
+\item \emph{ page 16, 2nd column, line 13, typo: "elment" $\to$ "element"}
+
 It has been corrected
@@
     nonsensical.}
+
+We have corrected the sentence 
+\begin{quote}
+which clearly suggest not to rely on a single tool/parton shower, and on the other make\ldots
+\end{quote}
+to
+\begin{quote}
+which on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make\ldots
+\end{quote}
+
 \item \emph{page 19, 1st column, line 14:
@@
 (In fact, there is no guarantee that even the comparison of different tools will provide an estimate that covers the next order, so calling this a conservative estimate is really misplaced.}
+
+We have replaced "conservative" with "more realistic", as suggested.
+
 \end{enumerate}

### 2018-06-11 Draft_EPJC/article.tex
more on the referee answer

--- 2018-04-04 Draft_arXiv/article.tex
@@
 
+In the rest of this paper, the notation ``LO'' or ``NLO(-QCD)'' without any specification of coupling powers will refer to the contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$ respectively.
+
 In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
@@
 defined.
-Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.
+Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.\\
 
@@
     \begin{itemize}
+      \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six-parton final states 
+      at $\Pp \Pp,\, \Pp\bar{\Pp}$, and $\Pe^+\Pe^-$ colliders at orders $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
+    It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
+    The integration uses a multi-channel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
+    {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of beyond the Standard Model (BSM) theories.
+
+      \item WHIZARD~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
+      For QCD amplitudes it uses the colour flow formalism~\cite{Kilian:2012pz}.
+      For NLO QCD calculations~\cite{Nejad:2016bci}, where WHIZARD is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
+      Furthermore, WHIZARD can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
+      WHIZARD allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
 
@@
     At LO the exact matrix elements can also be used.
+
+      \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
+    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space corresponding to the real emission.
+    For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.
+
+      \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
+        parton-level Monte Carlo for processes with EW bosons. It
+        allows the calculation of VBS processes at NLO QCD in the VBS
+        approximation, with process IDs between 200 and 290. Same-sign
+        $\PW^+\PW^+jj$ production is provided via the process ID 250. The corresponding
+        $s$-channel contributions are available separately as tri-boson processes with
+        semi-leptonic decays, with process IDs between 401 and 492. For the
+        final state studied in this article, only $\PW^+\PW^+\PW^-$
+        production with a hadronically decaying $\PW^-$ boson, process ID 432,
+        can contribute. These can simply be added on top of the VBS
+        contribution. Interferences between the two are therefore neglected.
+        The usage of leptonic tensors in the calculation, pioneered in
+        Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
+        automatically generated code.  Besides the SM, also a variety of
+        new-physics models including anomalous couplings of the Higgs and gauge
+        bosons can be simulated.
 
@@
 
-      \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six-parton final states 
-      at $\Pp \Pp,\, \Pp\bar{\Pp}$, and $\Pe^+\Pe^-$ colliders at orders $\mathcal O(\alpha^6)$ and $\mathcal O(\alphas^2\alpha^4)$ including interferences between the two sets of diagrams.
-    It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
-    The integration uses a multi-channel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
-    {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of beyond the Standard Model (BSM) theories.
-
-      \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
-    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space corresponding to the real emission.
-    For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.
-
-      \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
-        parton-level Monte Carlo for processes with EW bosons. It
-        allows the calculation of VBS processes at NLO QCD in the VBS
-        approximation, with process IDs between 200 and 290. Same-sign
-        $\PW^+\PW^+jj$ production is provided via the process ID 250. The corresponding
-        $s$-channel contributions are available separately as tri-boson processes with
-        semi-leptonic decays, with process IDs between 401 and 492. For the
-        final state studied in this article, only $\PW^+\PW^+\PW^-$
-        production with a hadronically decaying $\PW^-$ boson, process ID 432,
-        can contribute. These can simply be added on top of the VBS
-        contribution. Interferences between the two are therefore neglected.
-        The usage of leptonic tensors in the calculation, pioneered in
-        Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
-        automatically generated code.  Besides the SM, also a variety of
-        new-physics models including anomalous couplings of the Higgs and gauge
-        bosons can be simulated.
-
-      \item WHIZARD~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
-      For QCD amplitudes it uses the colour flow formalism~\cite{Kilian:2012pz}.
-      For NLO QCD calculations~\cite{Nejad:2016bci}, where WHIZARD is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
-      Furthermore, WHIZARD can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
-      WHIZARD allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
-
     \end{itemize}
@@
             \hline
+            {\sc PHANTOM}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
+            {\sc Whizard}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
             {\sc Bonsay}        &  $t,u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
             {\sc Powheg}        &  $t,u$    &  No       &  Yes              &  Yes   & No       &  No  \\
+            {\sc VBFNLO}        &  $s,t,u$  &  No       &  Yes              &  Yes   & No       &  No  \\
             {\sc MG5\_aMC}      &  $s,t,u$  &  Yes      &  Yes              &  Yes   & virt. No &  No \\
             {\sc MoCaNLO+Recola}&  $s,t,u$  &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
-            {\sc PHANTOM}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
-            {\sc VBFNLO}        &  $s,t,u$  &  No       &  Yes              &  Yes   & No       &  No  \\
-            {\sc Whizard}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
         \end{tabularx}
@@
             \hline
+            {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
+            {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $ \\
             {\sc Bonsay}  &  $1.43636$ & $0.00002$ \\
-            {\sc MG5\_aMC}&  $1.4304\phantom{0}$ & $0.0007$ \\
-            {\sc MoCaNLO+Recola}  &  $1.43476$ & $0.00009$ \\
-            {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
             {\sc Powheg-Box}  &  $1.44092$ & $0.00009$ \\
             {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
-            {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $
+            {\sc MG5\_aMC}&  $1.4304\phantom{0}$ & $0.0007$ \\
+            {\sc MoCaNLO+Recola}  &  $1.43476$ & $0.00009$ 
         \end{tabular}
@@
             {\sc Powheg-Box}  &  $1.3605\phantom{0}$  & $0.0007$   \\
+            {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\
             {\sc MG5\_aMC}&  $1.363\phantom{0}\phantom{0}$ & $0.004$  \\
-            {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ \\
-            {\sc VBFNLO}  &  $1.3916\phantom{0}$ & $0.0001$  \\
+            {\sc MoCaNLO+Recola}  &  $ 1.378\phantom{0}\phantom{0}$ & $0.001$ 
         \end{tabular}
@@
     \label{sec:matching}
-We now discuss how different predictions compare when the matching to parton shower is included. For such
+We now discuss how different predictions compare when the matching to parton shower is included, both at LO 
+($\mathcal O (\alpha^6)$) and at NLO-QCD ($\mathcal O (\alpha^6\alphas)$) accuracy. For such
 a comparison we expect larger discrepancies than what we found at fixed order, as a consequence of the different
@@
 among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large, and are
-possibly related to the underlying approximation performed ({\sc MG5\_aMC} is the only tool to use the full matrix elment for the real radiation), in particular the inclusion of the $s$-channel contributions: the largest rate is predicted by
+possibly related to the underlying approximation performed ({\sc MG5\_aMC} is the only tool to use the full matrix element for the real radiation), in particular the inclusion of the $s$-channel contributions: the largest rate is predicted by
 {\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
@@
 effectively at NLO accuracy differences between tools are at (or below) the $10\%$ level.
-Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which
+Some exceptions exist, \emph{e.g.}\ the rapidity separation of the two tagging jets, which on the one hand
 clearly suggest not to rely on a single tool/parton shower, and on the other make it worth investigating more in detail the way QCD radiation is
@@
 underestimates the size of the perturbative uncertainty. Again, this stresses the need
- to employ at least two different tools in order to obtain a conservative estimate of theoretical uncertainties.
+ to employ at least two different tools in order to obtain a more realistic estimate of theoretical uncertainties.
 Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggests that

### 2018-06-12 Draft_EPJC/Referee/answer_referee.tex
Modification of the article and referee answer

@@
 
-In section 2, before the last paragraph, we have added the following sentence
+In section 2, before the last paragraph, we have added the following sentence:
 \begin{quote}
-In the rest of this paper, the notation ``LO'' or ``NLO(-QCD)'' without any specification of coupling powers will refer to the contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$ respectively.
+In the rest of this article, the notations \emph{LO} or \emph{NLO(-QCD)} without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.
 \end{quote}
-For better clarity, we have also re-stated the coupling orders at the beginning of section 6 (Matching to parton shower).
+For clarity, we have also re-stated the coupling orders at the beginning of section 6 (Matching to parton shower).
 
@@
 
-We have corrected the sentence 
+We have corrected the sentence.
 \begin{quote}
@@
 
-We have replaced "conservative" with "more realistic", as suggested.
+We have replaced ``conservative'' with ``more realistic'', as suggested.
+
+\item We have modified the sentence:
+``combined measurements which are better theoretically defined'' to ``combined measurements which are theoretically better defined''.
+
+\item We have updated the LO+PS plots.
+It has been found that the predictions for WHIZARD+P8 suffered from a bug which has now been fixed.
+The agreement with other Pythia parton-shower predictions is now even better.
+In addition, the plot at LO+PS for the Zeppenfeld variable of the third jet suffered from a miss-match of the PHANTOM+H7-default due to bug in the plotting routine.
+Again, the predictions of Phantom+H7-default are now in better agreement with Herwig parton-shower predictions is improved.
+No modifications to the text have been made.
 

### 2018-06-12 Draft_EPJC/article.tex
Modification of the article and referee answer

@@
 
-In the rest of this paper, the notation ``LO'' or ``NLO(-QCD)'' without any specification of coupling powers will refer to the contribution at $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$ respectively.
+In the rest of this article, the notations \emph{LO} or \emph{NLO(-QCD)} without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.
 
@@
 defined.
-Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.\\
+Hence, combined measurements which are theoretically better defined should be preferably performed by the experimental collaborations at the LHC.
 
@@
 We now discuss how different predictions compare when the matching to parton shower is included, both at LO 
-($\mathcal O (\alpha^6)$) and at NLO-QCD ($\mathcal O (\alpha^6\alphas)$) accuracy. For such
+(\emph{i.e.}\ at order $\mathcal O (\alpha^6)$) and at NLO-QCD (\emph{i.e.}\ at order $\mathcal O (\alpha^6\alphas)$) accuracy. For such
 a comparison we expect larger discrepancies than what we found at fixed order, as a consequence of the different

### 2018-06-14 Draft_EPJC/Referee/answer_referee.tex
further changes in the new article and in the referee's answer

@@
 \vspace{0.5cm}
-We thank the referee for the positive report and for her/his insightful comments and detailed comments.
+We thank the referee for the positive report and for her/his insightful comments.
 Below, we address all the questions and suggestions contained in the report in order.
@@
 
-Answer: PSP and maybe then just argue about the physical message.
+In the caption of table 3, we have added the sentence
+\begin{quote}
+     The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc PHANTOM},
+        {\sc Whizard}, {\sc MG5\_aMC} and {\sc MoCaNLO+Recola}. 
+\end{quote}
+In order to have a better understanding of the origin of the differences among the four codes, we have compared
+the matrix-elements in a phase-space point, finding very good agreement. Other possible sources of the differences 
+may originate from the factorization scale setting or the cuts, or, more likely, from the non-perfect or non-ideal
+coverage of the VBS phase space, which is rather complex (in particular when also non-resonant contributions have to
+be included). Another issue of concern, as we alredy have written in the submitted version, is whether one should
+trust or not the uncertainties quoted by the Monte-Carlo integrator.
+We have modified the text in which we discuss the results at LO accuracy:
+\begin{quote}
+    Two things should be highlighted here: first, despite the different underlying approximations,
+    the two most-distant predictions ({\sc Powheg-box}\ and {\sc MG5\_aMC}) are only 0.7\% apart. This simply means that the details
+    of the various VBS approximations have an impact well below 1\% at the level of the fiducial cross section at LO for a
+    typical phase-space volume used by experimental collaborations. This is in agreement with the findings of
+Refs.~[Denner:2012dz,Oleari:2003tc]. Second, the four complete predictions ({\sc Whizard}, {\sc PHANTOM}, {\sc MG5\_aMC}
+    and {\sc MoCaNLO+Recola}) are not in statistical agreement. While we have checked the point-wise agreement of the matrix-element,
+    we cannot exclude other reasons for the disagreement, for example a non representative (i.e. too-aggressive)
+    estimate of the MonteCarlo uncertainty or
+    a non-perfect mapping of the six-body phase-space. However, the level of ambiguity is at the 0.5\% level, which
+    we deem satisfactory if compared to the larger differences we will observe at NLO or including matching to parton shower.
+\end{quote}
 
@@
 
+\end{enumerate}
+\vspace{1cm}
+Two further modifications have been performed, not related to the referee's comments:
+\begin{enumerate}
 \item We have modified the sentence:

### 2018-06-14 Draft_EPJC/Referee/answer_referee.tex
Small changes here and there

--- 2018-06-12 Draft_EPJC/Referee/answer_referee.tex
@@
 
-Answer: PSP and maybe then just argue about the physical message.
+In the caption of table 3, we have added the sentence
+\begin{quote}
+     The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc PHANTOM},
+        {\sc Whizard}, {\sc MG5\_aMC} and {\sc MoCaNLO+Recola}. 
+\end{quote}
+In order to have a better understanding of the origin of the differences among the four codes, we have compared
+the matrix-elements, finding very good agreement. Other possible sources of the differences 
+may originate from the factorisation scale setting or the cuts, or, more likely, from the non-perfect or non-ideal
+coverage of the VBS phase space, which is rather complex (in particular when also non-resonant contributions have to
+be included). Another issue of concern, as we already have written in the submitted version, is whether one should
+trust or not the uncertainties quoted by the Monte Carlo integrator.
+We have modified the text in which we discuss the results at LO accuracy:
+\begin{quote}
+    Two things should be highlighted here: first, despite the different underlying approximations, 
+    the two most-distant predictions ({\sc Powheg-box}\ and {\sc MG5\_aMC}) are only $0.7\%$ apart. This simply means that the details 
+    of the various VBS approximations have an impact below $1\%$ at the level of the fiducial cross section at LO for a 
+    typical phase-space volume used by experimental collaborations. This is in agreement with the findings of 
+    Refs.~\cite{Denner:2012dz,Oleari:2003tc}. Second, the four complete predictions ({\sc Whizard}, {\sc PHANTOM}, {\sc MG5\_aMC}, 
+    and {\sc MoCaNLO+Recola}) are not in statistical agreement. While we have checked the point-wise agreement of the matrix-element, 
+    we cannot exclude other reasons for the disagreement, for example a non representative (\emph{i.e.}\ too-aggressive) 
+    estimate of the Monte Carlo uncertainty or a non-perfect mapping of the six-body phase-space. However, the level of ambiguity is at the $0.5\%$ level, which 
+    we deem satisfactory compared to the larger differences observed at NLO or when including matching to parton shower.
+\end{quote}
 
@@
 In addition, the plot at LO+PS for the Zeppenfeld variable of the third jet suffered from a miss-match of the PHANTOM+H7-default due to bug in the plotting routine.
-Again, the predictions of Phantom+H7-default are now in better agreement with Herwig parton-shower predictions is improved.
+Again, the predictions of Phantom+H7-default are now in better agreement with Herwig parton-shower predictions.
 No modifications to the text have been made.

### 2018-06-14 Draft_EPJC/article.tex
Small changes here and there

@@
     In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy at order $\mathcal O (\alpha^6)$ obtained in the fiducial region 
-    described in Sec.~\ref{subsec:inputpar}. We note that several full predictions are not in statistical agreement. These are possibly due to Monte Carlo 
-    integrators performing too aggressive estimations of statistical uncertainties or different implementation of the complex-mass scheme.
-    Nonetheless, all these predictions agree within less than $0.5\%$.
-    At the level of the cross section, it seems difficult to infer the quality of the various approximations.
-    This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
-    the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.
-    This is in agreement with the findings of Refs.~\cite{Denner:2012dz,Oleari:2003tc}.
-
+    described in Sec.~\ref{subsec:inputpar}. Two things should be highlighted here: first, despite the different underlying approximations, 
+    the two most-distant predictions ({\sc Powheg-box}\ and {\sc MG5\_aMC}) are only $0.7\%$ apart. This simply means that the details 
+    of the various VBS approximations have an impact below $1\%$ at the level of the fiducial cross section at LO for a 
+    typical phase-space volume used by experimental collaborations. This is in agreement with the findings of 
+    Refs.~\cite{Denner:2012dz,Oleari:2003tc}. Second, the four complete predictions ({\sc Whizard}, {\sc PHANTOM}, {\sc MG5\_aMC}, 
+    and {\sc MoCaNLO+Recola}) are not in statistical agreement. While we have checked the point-wise agreement of the matrix-element, 
+    we cannot exclude other reasons for the disagreement, for example a non representative (\emph{i.e.}\ too-aggressive) 
+    estimate of the Monte Carlo uncertainty or a non-perfect mapping of the six-body phase-space. However, the level of ambiguity is at the $0.5\%$ level, which 
+    we deem satisfactory compared to the larger differences observed at NLO or when including matching to parton shower. 
     \begin{table}
@@
             \hline
-            {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
-            {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $ \\
             {\sc Bonsay}  &  $1.43636$ & $0.00002$ \\
@@
             {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
+            {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
+            {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $ \\
             {\sc MG5\_aMC}&  $1.4304\phantom{0}$ & $0.0007$ \\
@@
         \caption{\label{tab:wg1_LOrates} Cross sections at LO accuracy and order $\mathcal{O}(\alpha^6)$.
-        The predictions are obtained in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
+        The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc PHANTOM},
+        {\sc Whizard}, {\sc MG5\_aMC} and {\sc MoCaNLO+Recola}. The predictions are obtained 
+        in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
         The uncertainties shown refer to the estimated statistical errors of the Monte Carlo integrations.}

### 2018-06-15 Draft_EPJC/article.tex
fixces related to Pascal's comment

@@
 evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
-and it has been recently observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} 
+and it has been recently measured~\cite{Aaboud:2016ffv} and (re-)observed~\cite{Sirunyan:2017ret}
 at $13\TeV$ as well.
@@
 
-      \item WHIZARD~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
+      \item Whizard~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
       For QCD amplitudes it uses the colour flow formalism~\cite{Kilian:2012pz}.
-      For NLO QCD calculations~\cite{Nejad:2016bci}, where WHIZARD is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
-      Furthermore, WHIZARD can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
-      WHIZARD allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
+      For NLO QCD calculations~\cite{Nejad:2016bci}, where Whizard is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
+      Furthermore, Whizard can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
+      Whizard allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
 
@@
             \hline
-            {\sc PHANTOM}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
+            {\sc Phantom}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
             {\sc Whizard}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
@@
     typical phase-space volume used by experimental collaborations. This is in agreement with the findings of 
-    Refs.~\cite{Denner:2012dz,Oleari:2003tc}. Second, the four complete predictions ({\sc Whizard}, {\sc PHANTOM}, {\sc MG5\_aMC}, 
+    Refs.~\cite{Denner:2012dz,Oleari:2003tc}. Second, the four complete predictions ({\sc Whizard}, {\sc Phantom}, {\sc MG5\_aMC}, 
     and {\sc MoCaNLO+Recola}) are not in statistical agreement. While we have checked the point-wise agreement of the matrix-element, 
@@
             {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
-            {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
+            {\sc Phantom} &  $1.4374\phantom{0}$ & $0.0006 $  \\
             {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $ \\
@@
         \caption{\label{tab:wg1_LOrates} Cross sections at LO accuracy and order $\mathcal{O}(\alpha^6)$.
-        The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc PHANTOM},
+        The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc Phantom},
         {\sc Whizard}, {\sc MG5\_aMC} and {\sc MoCaNLO+Recola}. The predictions are obtained 
@@
 {\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
-also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
+also {\sc Phantom} and {\sc Whizard} are used for LO+PS results.\\
 {\sc MG5\_aMC}, which employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, is used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
 and {\sc Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx} (version 7.1.2). For the latter, the default angular-ordered shower is employed. 
-The same parton showers are employed for the LO results of {\sc PHANTOM}.
-{\sc Pythia8} is also employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
+The same parton showers are employed for the LO results of {\sc Phantom}.
+{\sc Pythia8} is also employed for the LO results of {\sc Whizard}. For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
         {\sc MG5\_aMC}+{\sc Herwig7}, $\Gamma_{\rm resc}$&  $1.266$ & $ 0.003$  \\
-        {\sc PHANTOM}+{\sc Pythia8} &  $1.235 $ & $0.001$  \\
-        {\sc PHANTOM}+{\sc Herwig7} &  $1.258 $ & $0.001$  \\
+        {\sc Phantom}+{\sc Pythia8} &  $1.235 $ & $0.001$  \\
+        {\sc Phantom}+{\sc Herwig7} &  $1.258 $ & $0.001$  \\
         {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3001$ & $0.0002$  \\
-        {\sc WHIZARD}+{\sc Pythia8} &  $1.229$ & $0.001$  \\
+        {\sc Whizard}+{\sc Pythia8} &  $1.229$ & $0.001$  \\
     \end{tabular}

### 2018-06-15 Draft_EPJC/Referee/answer_referee.tex
further changes in the article and referee's answer

@@
 \begin{quote}
-     The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc PHANTOM},
+     The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc Phantom},
         {\sc Whizard}, {\sc MG5\_aMC} and {\sc MoCaNLO+Recola}. 
@@
     typical phase-space volume used by experimental collaborations. This is in agreement with the findings of 
-    Refs.~\cite{Denner:2012dz,Oleari:2003tc}. Second, the four complete predictions ({\sc Whizard}, {\sc PHANTOM}, {\sc MG5\_aMC}, 
+    Refs.[Denner:2012dz,Oleari:2003tc]. Second, the four complete predictions ({\sc Whizard}, {\sc PHANTOM}, {\sc MG5\_aMC}, 
     and {\sc MoCaNLO+Recola}) are not in statistical agreement. While we have checked the point-wise agreement of the matrix-element, 
@@
 \vspace{1cm}
-Two further modifications have been performed, not related to the referee's comments:
+Further minor changes have been performed, not related to the referee's comments:
 \begin{enumerate}
+\item The references to experimental measurements in the second paragraph of the Introduction were not consistent
+    with the text. The sentence has been corrected.
+\item The program {\sc Phantom} was sometimes referred to as {\sc PHANTOM}, with all capital letters. All occurrences
+    have been changed to {\sc Phantom}. The same applies for {\sc Whizard}.
+\item The left plot of Figure 5 (dijet invariant mass at LO) 
+    has been updated, as the {\sc Whizard} histogram was not present
+    in the inset because of an error in the plotting script.
 \item We have modified the sentence:
 ``combined measurements which are better theoretically defined'' to ``combined measurements which are theoretically better defined''.
-
 \item We have updated the LO+PS plots.
@@
 No modifications to the text have been made.
-
+\item In Ref. [81] (Yu, Bardin, Leike, Riemann, 1988), the hyperlink was pointing to a wrong DOI. It has been fixed.
 \end{enumerate}

### 2018-06-15 Draft_EPJC/article.tex
further changes in the article and referee's answer

@@
 The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio of all the VBS processes at the Large Hadron Collider (LHC):
-evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
-and it has been recently measured~\cite{Aaboud:2016ffv} and (re-)observed~\cite{Sirunyan:2017ret}
-at $13\TeV$ as well.
+evidence for it was found at the centre-of-mass energy of $8~\TeV$~\cite{Aad:2014zda,Khachatryan:2014sta,Aaboud:2016ffv},
+and it has been recently measured
+at $13\TeV$ as well~\cite{Sirunyan:2017ret}.
 Presently, the measurements of VBS processes are limited by statistics, but the situation will change in the near future.

### 2018-06-15 Draft_EPJC/Referee/answer_referee.tex
One comma added

@@
      The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc Phantom},
-        {\sc Whizard}, {\sc MG5\_aMC} and {\sc MoCaNLO+Recola}. 
+        {\sc Whizard}, {\sc MG5\_aMC}, and {\sc MoCaNLO+Recola}. 
 \end{quote}

### 2018-06-15 Draft_EPJC/article.tex
One comma added

@@
         The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc Phantom},
-        {\sc Whizard}, {\sc MG5\_aMC} and {\sc MoCaNLO+Recola}. The predictions are obtained 
+        {\sc Whizard}, {\sc MG5\_aMC}, and {\sc MoCaNLO+Recola}. The predictions are obtained 
         in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.

### 2018-06-25 Draft_EPJC/Referee/answer_referee.tex
Small differences fixed

@@
 \begin{quote}
-In the rest of this article, the notations \emph{LO} or \emph{NLO(-QCD)} without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.
+In the rest of this article, the notations LO or NLO(-QCD) without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.
 \end{quote}
@@
     and {\sc MoCaNLO+Recola}) are not in statistical agreement. While we have checked the point-wise agreement of the matrix-element, 
-    we cannot exclude other reasons for the disagreement, for example a non representative (\emph{i.e.}\ too-aggressive) 
+    we cannot exclude other reasons for the disagreement, for example a non-representative (\emph{i.e.}\ too-aggressive) 
     estimate of the Monte Carlo uncertainty or a non-perfect mapping of the six-body phase-space. However, the level of ambiguity is at the $0.5\%$ level, which 

### 2018-06-25 Draft_EPJC/article.tex
Small differences fixed

@@
 
-In the rest of this article, the notations \emph{LO} or \emph{NLO(-QCD)} without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.
+In the rest of this article, the notations LO or NLO(-QCD) without any specification of coupling powers refer to the contributions at order $\mathcal{O}{\left(\alpha^{6}\right)}$ and $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{6}\right)}$, respectively.
 

### 2018-08-20 Draft_EPJC/article.tex
Comments of Juerge, version matches the EPJC version after proofs

@@
 in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
-(center diagram) or from
+(centre diagram) or from
 triple-boson production (right diagram).
@@
 The $u$-channel refers to contributions with crossed fermion lines with respect to $t$-channel, which appears for identical (anti-)quarks in the final state.
-The $s$-channel contributions plays a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
+The $s$-channel contributions play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
 When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results.
@@
 
-      \item Whizard~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
+      \item WHIZARD~\cite{Kilian:2007gr,Moretti:2001zz} is a multi-purpose event generator with LO matrix-element generator O'Mega. 
       For QCD amplitudes it uses the colour flow formalism~\cite{Kilian:2012pz}.
-      For NLO QCD calculations~\cite{Nejad:2016bci}, where Whizard is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
-      Furthermore, Whizard can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
-      Whizard allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
+      For NLO QCD calculations~\cite{Nejad:2016bci}, where WHIZARD is in the final validation phase, it provides FKS subtraction terms~\cite{Frixione:1995ms,Frixione:1997np}, while virtual matrix elements are provided externally by OpenLoops~\cite{Cascioli:2011va} or Recola~\cite{Actis:2012qn,Actis:2016mpe}.
+      Furthermore, WHIZARD can automatically provide POWHEG matching to parton shower~\cite{Reuter:2016qbi}.
+      WHIZARD allows to simulate a huge number of BSM models as well, in particular in terms of higher-dimensional operators for VBS processes including means to provide unitarity limits~\cite{Alboteanu:2008my,Kilian:2014zja}.
 
@@
             {\sc Phantom}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
-            {\sc Whizard}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
+            {\sc WHIZARD}       &  $s,t,u$  &  Yes      &  Yes              &  No    & -        & - \\
             {\sc Bonsay}        &  $t,u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
@@
     Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
-    In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
+    In the first case, the approximation is good within $\pm10\%$ over the whole range apart from the low invariant-mass region at both low and large rapidity difference.
     The low rapidity-difference region possesses remnants of the tri-bosons contribution that have a di-jet invariant mass around the $\PW$-boson mass.
@@
     The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
-    The full calculation is approximated at the level of $\pm5\%$ everywhere apart in the region where $|\Delta y_{\Pj\Pj}| < 2$.
+    The full calculation is approximated at the level of $\pm5\%$ everywhere apart from the region where $|\Delta y_{\Pj\Pj}| < 2$.
 
@@
     typical phase-space volume used by experimental collaborations. This is in agreement with the findings of 
-    Refs.~\cite{Denner:2012dz,Oleari:2003tc}. Second, the four complete predictions ({\sc Whizard}, {\sc Phantom}, {\sc MG5\_aMC}, 
+    Refs.~\cite{Denner:2012dz,Oleari:2003tc}. Second, the four complete predictions ({\sc WHIZARD}, {\sc Phantom}, {\sc MG5\_aMC}, 
     and {\sc MoCaNLO+Recola}) are not in statistical agreement. While we have checked the point-wise agreement of the matrix-element, 
@@
             {\sc Phantom} &  $1.4374\phantom{0}$ & $0.0006 $  \\
-            {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $ \\
+            {\sc WHIZARD} &  $1.4381\phantom{0}$ & $0.0002 $ \\
             {\sc MG5\_aMC}&  $1.4304\phantom{0}$ & $0.0007$ \\
@@
         The complete $2\to 6$ matrix-element, without any approximation, is employed by {\sc Phantom},
-        {\sc Whizard}, {\sc MG5\_aMC}, and {\sc MoCaNLO+Recola}. The predictions are obtained 
+        {\sc WHIZARD}, {\sc MG5\_aMC}, and {\sc MoCaNLO+Recola}. The predictions are obtained 
         in the fiducial region described in Sec.~\protect\ref{subsec:inputpar}.
@@
        \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
-    \caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right) \emph{i.e.}\ at NLO accuracy at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
+    \caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right) at NLO accuracy \emph{i.e.}\ at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
     The description of the different programs used can be found in Sec.~\protect\ref{subsec:codedescr}.
@@
 {\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
-also {\sc Phantom} and {\sc Whizard} are used for LO+PS results.\\
+also {\sc Phantom} and {\sc WHIZARD} are used for LO+PS results.\\
 {\sc MG5\_aMC}, which employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, is used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
@@
 The same parton showers are employed for the LO results of {\sc Phantom}.
-{\sc Pythia8} is also employed for the LO results of {\sc Whizard}. For the {\sc Powheg-Box}, the namesake
+{\sc Pythia8} is also employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
 matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
@@
         {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3001$ & $0.0002$  \\
-        {\sc Whizard}+{\sc Pythia8} &  $1.229$ & $0.001$  \\
+        {\sc WHIZARD}+{\sc Pythia8} &  $1.229$ & $0.001$  \\
     \end{tabular}
@@
 updated. In the {\sc Powheg} matching, the shower scale of the so-called $\tilde B$ events is fixed to the transverse momentum of the radiation
-generated according the {\sc Powheg} Sudakov factor, while it can be changed in the remnants events.}
+generated according the {\sc Powheg} Sudakov factor, while it can be changed in the remnant events.}
 The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
@@
 about $-30\%$ at the end of the displayed range. At NLO+PS, this effect is mitigated, owing to the better description of the first QCD emission which is now driven by the real-emission matrix element.
-For this observable (and all the others which are NLO accurate) the effect of reducing the shower-scale is negligible, hence it is not shown.
+For this observable (and all the others which are NLO accurate) the effect of reducing the shower scale is negligible, hence it is not shown.
 
